### 2019-10-02 manuscript.tex
Initial Overleaf Import

\documentclass[10pt,journal,compsoc]{IEEEtran}
\usepackage{alltt}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{color}
\usepackage[labelfont=bf,textfont={bf}]{caption}
\usepackage{subcaption}
\usepackage{pifont}% http://ctan.org/pkg/pifont
\usepackage{boxedminipage}
\usepackage{notoccite}
\usepackage{array}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\usepackage{enumerate}
\usepackage{booktabs}
\usepackage{minted}
\usepackage[framemethod=tikz]{mdframed}
\usepackage{lipsum}
\usetikzlibrary{shadows}
\usepackage{mathtools}
 \usepackage{paralist}
 \definecolor{light-gray}{gray}{0.80}
\usepackage{graphics}
\usepackage[shortlabels]{enumitem}
%\usepackage{balance}
\usepackage{dblfloatfix}

%\usepackage{hyperref}
%\usepackage{cleveref}
\usepackage{colortbl}
\newmdenv[
  tikzsetting= {fill=light-gray},
  linewidth=1pt,
  roundcorner=0pt, 
  shadow=false
]{myshadowbox}
\usepackage{colortbl} 
\usepackage{subcaption}
\usepackage{blindtext, graphicx}
\usepackage{textcomp}
\usepackage{mathtools}
\usepackage[hidelinks]{hyperref}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{caption}
\usepackage{color}
\usepackage[final]{listings}
\usepackage{graphicx} 
\usepackage{multirow}
\usepackage{balance}
\usepackage{picture}
\usepackage{relsize}
\usepackage{multicol}
\usepackage{soul}
\usepackage{enumitem}
\setitemize{noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=*}
\setenumerate{noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=*}
\DeclarePairedDelimiter\abs{\lvert}{\rvert}%
\usepackage{array}
\usepackage{makecell}
\usepackage{bigstrut}
\newcommand{\tion}[1]{\S\ref{sect:#1}}
\newcommand{\fig}[1]{Figure~\ref{fig:#1}}
\newcommand{\tab}[1]{Table~\ref{tab:#1}}
\definecolor{comment_color}{rgb}{0.5, 0, 1}
\definecolor{steel}{rgb}{0.1, 0.3, 0.5} 
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\newcommand{\todoc}[2]{{\textcolor{#1}{\textbf{[[#2]]}}}}
\newcommand{\todobrown}[1]{\todoc{green}{\textbf{[[#1]]}}}
\newcommand{\todoblue}[1]{\todoc{blue}{\textbf{[[#1]]}}}
\newcommand{\todoorange}[1]{\todoc{cyan}{\textbf{[[#1]]}}}
\newcommand{\todored}[1]{\todoc{red}{\textbf{[[#1]]}}}
\newcommand{\rahul}[1]{{\textcolor{steel}{#1}}}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\usepackage[
 pass,% keep layout unchanged
 % showframe,% show the layout
]{geometry}
\usepackage[skins]{tcolorbox}
\usepackage{verbatim}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage[export]{adjustbox}
\usepackage{mathtools}
\setlength{\belowcaptionskip}{-10pt}
\renewcommand{\footnotesize}{\scriptsize}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\definecolor{lightgray}{gray}{0.8}
\definecolor{LightCyan}{rgb}{0.88,1,1}
\definecolor{darkgray}{gray}{0.6}
\definecolor{Gray}{rgb}{0.88,1,1}
\definecolor{Gray}{gray}{0.85}
\definecolor{Blue}{RGB}{0,29,193}
\definecolor{MyDarkBlue}{rgb}{0,0.08,0.45} 
\definecolor{pink}{RGB}{231,95,110}
\definecolor{lightergray}{rgb}{0.85, 0.85, 0.85}
\definecolor{lightestgray}{rgb}{0.95, 0.95, 0.95}
\definecolor{ao(english)}{rgb}{0.0, 0.5, 0.0}
% \frenchspacing
\lstset{
  language=Python,
  basicstyle=\sffamily\fontsize{2.5mm}{0.8em}\selectfont,
  breaklines=true,
  prebreak=\raisebox{0ex}[0ex][0ex]{\ensuremath{\hookleftarrow}},
  frame=l,
  showtabs=true,
  columns=fullflexible,
  showspaces=false,
  showstringspaces=false,
  keywordstyle=\color{pink}\bfseries\sffamily\fontsize{2.8mm}{0.6em},
  emph={train, predict, add_samples, FindBellwether, BEETLE, get_cost, sample, get_perf, remove_non_bellwethers, LinearTransform, GPTransform}, 
  emphstyle=\bfseries\color{black!80} ,
  stringstyle=\itshape\color{black!50},
  commentstyle=\color{red!50!black}\it,
  numbers=left,
  captionpos=t,
  escapeinside={\%*}{*)}
}
\usepackage[tikz]{bclogo}
\newenvironment{RQ}[1]%
{\noindent\begin{minipage}[c]{\linewidth}%
\begin{bclogo}[couleur=gray!20,%
                arrondi=0.1,logo=\bctrombone,% 
                ombre=true]{{\small ~#1}}}%
{\end{bclogo}\vspace{2mm}\end{minipage}}

\usepackage{fancyvrb}
\fvset{%
fontsize=\small,
numbers=left
}
\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}
\newcommand{\eq}[1]{Equation~\ref{eq:#1}}

%%% graph
\newcommand{\crule}[3][darkgray]{\textcolor{#1}{\rule{#2}{#3}}}
\newcommand{\quartex}[3]{
\begin{picture}(13,6)%1
  {
   \color{black}
    \put(#3,3)
    {\circle*{4}}
    \put(#1,3)
    {\line(1,0){#2}}
  }
\end{picture}
}
\definecolor{lightgray}{gray}{0.7}
\tikzstyle{highlighter} = [lightgray, line width = \baselineskip]
\usepackage{wrapfig}
\newcounter{highlight}[page]
\newcommand{\tikzhighlightanchor}[1]{\ensuremath{\vcenter{\hbox{\tikz[remember picture, overlay]{\coordinate (#1 highlight \arabic{highlight});}}}}}
\newcommand{\bh}[0]{\stepcounter{highlight}\tikzhighlightanchor{begin}}
\newcommand{\eh}[0]{\tikzhighlightanchor{end}}
\AtBeginShipout{\AtBeginShipoutUpperLeft{\ifthenelse{\value{highlight} > 0}{\tikz[remember picture, overlay]{\foreach \stroke in {1,...,\arabic{highlight}} \draw[highlighter] (begin highlight \stroke) -- (end highlight \stroke);}}{}}}

\newcommand{\squishlist}{
 \begin{list}{$\bullet$}
 { \setlength{\itemsep}{0pt}
   \setlength{\parsep}{3pt}
   \setlength{\topsep}{3pt}
   \setlength{\partopsep}{0pt}
   \setlength{\leftmargin}{1.5em}
   \setlength{\labelwidth}{1em}
   \setlength{\labelsep}{0.5em} } }

\newcommand{\squishlisttwo}{
 \begin{list}{$\bullet$}
 { \setlength{\itemsep}{0pt}
  \setlength{\parsep}{0pt}
  \setlength{\topsep}{0pt}
  \setlength{\partopsep}{0pt}
  \setlength{\leftmargin}{1em}
  \setlength{\labelwidth}{1.5em}
  \setlength{\labelsep}{0.5em} } }

\newcommand{\squishend}{
 \end{list} }

\newcommand{\specialcell}[2][c]{%
 \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}

\newcommand{\flash}{{\sc Flash}\xspace}
\usepackage{soul}
\usepackage{color}

\definecolor{awesome}{rgb}{1.0, 0.13, 0.32}

\usepackage{amsmath}
\definecolor{Gray}{gray}{0.95}
\definecolor{LightGray}{gray}{0.975}

\DeclareRobustCommand{\hlgreen}[1]{{\sethlcolor{green}\hl{#1}}}
\DeclareRobustCommand{\hlyellow}[1]{{\sethlcolor{yellow}\hl{#1}}}
\DeclareRobustCommand{\hlred}[1]{{\sethlcolor{awesome}\textbf{\hl{#1}}}}

%% reviewing
\newcommand{\blue}[1]{{\color{blue}{#1}}}
\newcommand{\review}[1]{\vspace{3mm}{\noindent\textit{#1}}\vspace{3mm}}
\newcommand{\reponse}[1]{\noindent{#1\\}}
\newcommand{\todo}[1]{\textbf{\color{red}{#1}}}
\newcommand{\subsect}[1]{\SS\ref{subsect:#1}}

%% Response text prefix
\newcommand{\respto}[1]{
\fcolorbox{black}{black!15}{%
\label{resp:#1}%
\bf\scriptsize R{#1}}}

%% Response text prefix
\newcommand{\bareresp}[1]{
\fcolorbox{black}{black!15}{%
\bf\scriptsize R{#1}}}

%% Cite responses
\newcommand{\citeresp}[1]{%
{(see }\fcolorbox{black}{black!15}{%
\bf\scriptsize R{#1}}~{{on page \pageref{resp:#1})}}}%
\usepackage{cite}
% \usepackage[switch, pagewise]{lineno}
% \linenumbers

\newenvironment{steelblue}
{\color{steel}}
{\color{black}}

\newenvironment{result}
{\vspace{0.15cm}
\noindent\begin{minipage}{\linewidth}
\begin{center}
\arrayrulecolor{lightergray}
\begin{tabular}{|p{0.95\linewidth}|}
\hline%
\rowcolor{lightergray}%
\textbf{Result:}~%
}
{\\\hline
\end{tabular}
\end{center}
\end{minipage}
\vspace{0.15cm}
}

\newenvironment{goal}
{\vspace{0.15cm}
\noindent\begin{minipage}{\linewidth}
\begin{center}
\arrayrulecolor{black}
\begin{tabular}{|p{0.95\linewidth}|}
\hline\rowcolor{lightestgray}}
{\\\hline
\end{tabular}
\end{center}
\end{minipage}
\vspace{0.15cm}
}

\newcommand{\quart}[4]{\begin{picture}(100,6)%1
{\color{black}\put(#2,3){\color{black}\circle*{4}}\put(#1,3){\line(1,0){#3}}}\end{picture}}
\newcommand{\quartr}[4]{\begin{picture}(100,6)%1
{\color{black}\put(#2,3){\color{red}\circle*{4}}\put(#1,3){\line(1,0){#3}}}\end{picture}}
\newcommand{\quartx}[4]{\begin{picture}(100,1)%1
{\color{black}\put(\numexpr #2 * 6  \relax,3){\color{red}\circle*{4}}\put(\numexpr #1*6 \relax ,3){\line(1,0){\numexpr #3*6 \relax}}}\end{picture}}

\begin{document}
\title{BUBBLE: Scaling Transfer Learning to 100s of Projects}

\author{Suvodeep Majumder, Rahul Krishna and Tim Menzies,~\IEEEmembership{IEEE Fellow}
%\affiliation{Computer Science, NCSU, USA, North Carolina}  
%\email{[smajumd3,rkrish11]@ncsu.edu, tim@ieee.org}

\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem S, Majumder, R. Krishna and  T. Menzies are with the Department
of Computer Science, North Carolina State University, Raleigh, USA.\protect\\
E-mail:[smajumd3,rkrish11]@ncsu.edu, tim@ieee.org}}

% The paper headers
\markboth{IEEE Transactions on Software Engineering, submitted Oct `19}{Majumder \MakeLowercase{\textit{et al.}}: BUBBLE: Scaling Transfer Learning to 100s of Projects}

\IEEEtitleabstractindextext{%
\begin{abstract}
When one   exemplar project (the ``bellwether'') offers best advice, then it can be used to offer    advice for all other projects. These bellwethers can be used to make quality predictions about new projects (even before there is much experience with those new projects).  Also, such general conclusions   simplifies     software quality policies (since the list of quality problems, and their mitigations, is static);   the cost of  training (since ``best practices'' are now constant); and tool development (since it is clear where it is most cost-effective to buy/build tools to mitigate
for software quality issues).

But finding that bellwether is a slow process since that needs an  analysis of all pairs of projects. 
Hence,  we  BUBBLE, a bellwether based on
  hierarchical clustering. At each level, one bellwether is computed from sibling projects, then promoted up the tree.

   In studies of a corpus of   nearly 700 projects, we find that   the bellwether promoted to the top of the cluster tree is just as good as those found via a traditional bellwether analysis.    Further, this bellwether was 
found in    1.5 hours (versus 3 days needed for  prior work). 
  More importantly, BUBBLE   scales to larger problems since it uses a $O(m*(N/m)^2)$ analysis and not the $O(N^2)$ all pairs analysis used by standard bellwether methods.

 Accordingly, to   extract software quality rules from a   large corpus of SE, we recommend BUBBLE.

\end{abstract}

\begin{IEEEkeywords}
Transfer Learning, Bellwether, Defect Prediction,Scalable Method. 
\end{IEEEkeywords}}

% make the title area
\maketitle

\IEEEdisplaynontitleabstractindextext
\IEEEdisplaynontitleabstractindextext

\ifCLASSOPTIONcaptionsoff
 \newpage
\fi

\section{Introduction}
How should we reason about SE quality?  Should we use  general models that hold over many projects? Or must we use an ever changing set of ideas that are   continually adapted to the task at hand? 
Or does the truth lie somewhere in-between?

This is an open and important question. After a decade of intensive research into automated software analytics, what general principles have we learned? While that work has generated specific results about specific projects~\cite{Bird:2015,menzies2013software}, it has failed (so far) to deliver general principles that are demonstrably useful across many projects~\cite{menzies2013guest} (for an example of how {\em more} data can lead to {\em less} general conclusions, see below in {\S}2a).

Is that the best we can do? Are there general principles we can use to guide project management, software standards, education,   tool development, and legislation about software? 
Or is  software engineering some ``patchwork quilt'' of ideas and methods where it only makes sense to reason about specific, specialized, and small sets of  projects? Not to mention, if software was ``patchwork'' of ideas,then that would  there would be no stable conclusions about what constitutes best practice for software engineering (since those best practices would keep changing as we move from project to project). As discussed in section~\ref{sec:Motivation}, such conclusion instability would have detrimental implications for {\em generality, trust, insight, training}, and {\em tool development}.

One  explanation for the limited conclusions (so far) from automated analytics is  {\em how much} data we are using for analysis. A typical software analytics research paper uses less than a few dozen projects  (exceptions: see~\cite{krishna18a, zhao17, agrawal18}). Such small samples can never represent something as diverse as software engineering.

Reasoning across multiple projects is a complex task.
Krishna and Keung et al. reports some success in transferring conclusions from one project to another using ``bellwethers''\footnote{Traditionally,
the bellwether is the  leading sheep of a flock, with a bell on its neck.
In modern parlance, the bellwether is an 
  indicator or predictor of something.}
\bi
\item Find a  ``bellwether'' project that is exemplar for rest;
\item Draw conclusions from  that project.
\ei
This approach has successfully been successfully applied to defect prediction, software effort estimation, bad smell detection, issue lifetime estimation, and configuration optimization. As a 
method of transferring lessons learned from one project to another, bellwethers have worked better than the Burak filter~\cite{turhan09}, Ma et al.~\cite{Ma2012}'s transfer naive Bayes (TNB); and Nam et al.  TCA  and TCA+, algorithms~\cite{Nam13,Nam2015}.

But Krishna and Keung et al.'s bellwether methods are very slow. When applied to the 679 projects studied here, it took 60 days to find and certify. There are many reasons for that including what how the models were certified (20 repeats  with different train/test sets)
and the complexity of the the analysis procedure (which including fixing class imbalance and feature selection). But the major cause of this slow down was that Krishna and Keung's   methods  required an $O(N^2)$ comparison between   $N=697$ projects.

\begin{figure}[!bh]
    \centering
    \includegraphics[width=\linewidth]{figs/predictive_power.png}
    \caption{Two hypothetical results about how training set size might effect the efficacy of quality prediction for software projects.}
    \label{fig:predictive_power}
\end{figure}

This paper dramatically improves standard bellwether methods to find general conclusions from 697 projects.
 Our BUBBLE  methods applies divide and conquer  by utilizing a hierarchical clustering model to recursively divide the large number of projects in to smaller clusters. Starting at the leaves of that tree of clusters, BUBBLE finds the    bellwethers within sibling projects. That bellwether is then promoted up the tree. The output of BUBBLE is the project promoted to the top of the tree of clusters.

 This paper evaluates the models generated from the bellwether project found by BUBBLE. In terms of the traditional measures such as recall, precision, Popt(20) or IFA, there is no significant performance different between BUBBLE's models and those found  via ``within'' learning (where quality models are learned just from data within a particular project) and ``all-pairs'' learning (where the bellwether is selected in the traditional way via a laborious $O(N^2)$ analysis).

In terms of {\em transfer} and {\em lessons learned},  this result has tremendous practical significance.  When new projects arrive, then even before there is much experience with those tasks,  lessons learned from other projects can be applied to the new project (just by querying the bellwether),

While {\em many models} are generated via ``within'' learning, bellwethers only produce one model. And since the bellwether is equivalent to the other models,
 then when new projects appear, their quality cn be evalauted even before there is an extensive experience base with that particular project (just be applying the bellwether learend from r
 that means that general lessons about (a)~major quality issues;
 or (b)~best practices to avoid quality problems;
 or (c)~cost-benefit justifications for buying or building tools can be made stable across these 697 projects. Another advantage of the bellwethers

 Also, BUBBLE finds and certifies those general lessons much faster than traditional bellwether methods (30 hours vs 60 days).

 That is, lessons learned from BUBBLE's bellwether can be said to be general across multiple projects.

 The BUBBLE approach peformed better than ``within'' and similarly to ``all-pairs''. That is
 \bi
 \item
Learning from many other projects is bettter than learning just from your own project data;
\item
Taking the extra time required to learn via ``all-pairs'' is not necessary. This is important since BUBBLE runs mich faster than all-pairs (30 hours vs 60 days). 
\ei
More importantly, since it bases its conclusions from one exemplar bellwether project, BUBBLE can offer conclusions general to a very large set of projects. 
By reasoning over a tree of clusters with a branching factor of $b$, BUBBLE only requires $O(\log_bN)$  comparisons. This means BUBBLE will scale up better than traditional bellwether methods that need $O(N^2)$ comparisons. Here, we show results that are general to hundres of projects. In the future, our research goal is to find general conclusions across 10,000 projects, or perhaps even more.

The contributions of this paper are
\bi

\item \textbf{Showing inherent generality in SE} Since we show  offer a proof of generality in SE data sets via transfer learning. In this study we discover a source data set for transfer learner from a large number of potential projects, hence proving generality in the SE datasets where some dataset can act as examples for rest of them for defect prediction.

\item \textbf{An very fast algorithm to test generality in datasets:} A vary fast algorithm to test generality in other datasets with only minor changes.

\item \textbf{Hierarchical bellwethers as a transfer learner:} A hierarchical clustering based \textit{bellwether method} algorithm ``BUBBLE'' to find \textit{bellwether effect} in datasets by finding a source project for the transfer learner. The algorithm uses bellwether selection and bellwether promotion (described in section~\ref{BUBBLE}) to find bellwether in hierarchical cluster and promote the bellwethers to upper levels in a divide and conquer approach.

\item \textbf{Rich Replication Package:} We have made available a rich replication package\footnote{\href{http://tiny.cc/bellwether}{http://tiny.cc/bellwether}} . The  replication package consists of all the datasets used in this paper, in addition to mechanisms for computation of other statistical measures.

\item \textbf{A new algorithm for transferring data from other projects, unlike prior works it can scale to large datasets:} Unlike previous studies for transfer learning, this method is order of magnitude faster for selecting a source project for transfer learning. Figure~\ref{fig:cost} shows a hypothetical cost comparison in AWS between default bellwether and BUBBLE when running for 100 to 1,000,000 projects based on number of comparison required.

\item \textbf{Demo a fast bellwether method which run hours is comparable to a robust method which runs in months:}

\ei

to the best of out knowledge bell/bubble is new high-water mark in qualitative empirical SE. XXX

This new transfer learning approach lets us ask and answer the following questions:

\begin{itemize}
        \item 
            \textbf{RQ1}:  Can we confirm bellwether on large datasets??

            \begin{RQ}{
                Default \textit{bellwether method} can find \textit{bellwether effect} in large datasets to discover source datasets for transfer learning. But this \textit{bellwether method} is very expensive making it infeasible for large datasets.}
            \end{RQ}

        \item 
            \textbf{RQ2}: How to tame complexity of bellwether?

             \begin{RQ}{
                The proposed new \textit{transfer learner} ``BUBBLE'', using hierarchical data clustering is order of magnitude faster for discovering a source project both in term of number of comparison and run-time.}
            \end{RQ}
        \\   
        \\
        \\
        \\
        \\
        \\
        \item 
            \textbf{RQ3}:  Is faster bellwether effective?

            \begin{RQ}{
                The new transfer learner ``BUBBLE'' is statistically as effective as or sometime even better then the default bellwether which is an exhaustive search and local learning. }
            \end{RQ}

        \item 
            \textbf{RQ4}: Does learning from too many projects has detrimental effect?

            \begin{RQ}{
                Based on the results seen in this study we can see learning from too many projects do have detrimental effect in-term of predictive power and shows conclusion instability.}
            \end{RQ}

        \item 
            \textbf{RQ5}: What did we learn?

            \begin{RQ}{
                Based on the results seen in this study using Feature Subset Selector and Logistic Regression, the ``Bellwether Project'' learned only a 12\% of the features(mostly interface related metrics) are important for predicting defects.}
            \end{RQ}

    \end{itemize}

\section{Background and Related Work}
\label{sec:literature}

\subsection{Motivation}
\label{sec:Motivation}
There are many reasons to seek stable general conclusions in software engineering. If our conclusions about best practices for SE projects keep changing, that will be detrimental to generality, trust, insight, training, and tool development.

\textbf{Generality:} Data science for software engineering cannot be called a ``science'' unless it makes general conclusions that hold across  multiple  projects. If we cannot offer general rules across a large number of software projects, then it is   difficult to demonstrate such generality.

\textbf{Trust:} Hassan~\cite{Hassan17} cautions that managers lose faith in software analytics if its models keep changing since  the assumptions used to make prior policy decisions may no longer hold.

\textbf{Insight:} Kim et al.~\cite{Kim2016}, say  that the aim of software analytics is to obtain actionable insights that help practitioners accomplish software development goals. For Tan et al.~\cite{tan2016defining}, such   insights  are a core deliverable. Sawyer et al. agrees, saying that  insights are the key driver for businesses to invest in data analytics initiatives~\cite{sawyer2013bi}. Bird, Zimmermann, et al.~\cite{Bird:2015} say that such  insights occur when users reflect, and react, to the output of a model generated via software analytics. But if  new models keep being generated in new projects, then that exhausts the ability of  users to draw insight from  new data.

\textbf{Training:} Another concern is what do we train novice software engineers or newcomers to a project? If our models are not stable, then it hard to teach what factors  most influence software quality.

\textbf{Tool development:} Further to the last point--- if we are unsure what factors most influence quality, it is difficult to design and implement and deploy tools that can successfully improve that quality.

\begin{figure}[!ht]
    \centering
    \includegraphics[width=\linewidth]{figs/cost.png}
    \caption{Hypothetical cost comparison between BUBBLE and default Bellwether.}
    \label{fig:cost}
\end{figure}

Petersen and Wohlin~\cite{Petersen2009} argue that for empirical SE, context matters.That is, they would predict that one model  will NOT  cover all  projects and that tools that report  generality  over many software projects need to also know the {\em communities} within which those conclusions   apply. Hence, this work divides into (a)~automated methods for finding sets of projects in the same {\em community}; and (b)~within each {\em community}, find the model what works best.

The {\em size} of the communities found in this way would have a profound impact on how we should reason about software engineering. Consider the hypothetical results of Figure~\ref{fig:predictive_power}. The \textcolor{ao(english)}{{\bf GREEN}} curve shows some quality predictor that (hypothetically) gets better, the more projects it learns from (i.e. higher levels in the hierarchical cluster). After about 2 levels, the \textcolor{ao(english)}{{\bf GREEN}} curve's growth stops and we would say that community size here was around cluster size in level 1. In this case, while we could not offer a single model that cover {\em all} of SE, we could offer a handful of models, each of which would be relevant to project clusters in that level. Accordingly, we would say that there are many cases where  wisdom from prior projects can be readily applied to guide future projects and (b)~the generality issues raised are not be so pressing.

Now consider the hypothetical \textcolor{red}{{\bf RED}} curve of Figure~\ref{fig:predictive_power}. Here, we see that (hypothetically)  learning from more projects makes quality predictions worse which means the our 10,000 projects break up into ``communities'' of size one. In this case,  (a)~principles about what is ``best practice'' for different software projects would be constantly change (whenever we jump from small community to small community); and (b)~the generality issues would be become open and urgent concerns for the SE analytics community.

\subsection{Related Work}
\label{sec:related}

In this section, we ask ``Why even bother to transfer lessons learned between projects?''. In several recent studies ~\cite{bettenburg2012think, menzies2012local, posnett2011ecological} with readily-available data from SE repositories, numerous authors report the locality effect in SE; i.e. general models outperformed by specialized models localized to particular parts of the data. Menzies et al. showed in their paper about local vs global learning in defect prediction and effort estimation domain that using a rule based learner locality based learning was much effective then rules learned from the global dataset. While Herbold et al.~\cite{herbold2017global} in their study regarding global vs local model for cross-project defect prediction showed evident proof that local models make only a minor difference in comparison to global models. While local can cause conclusion instabilities, global models can miss details which is specific to certain dataset. So in this study, we review the evidence that if it is useful to explore more than just the local data. This evidence falls into four groups:

\textbf{(a) The lesson on big data is that that the {\em more} training data, the {\em better} the learned model.} Vapnik~\cite{vapnik14} discusses examples where models accuracy improves to nearly 100\%, just by training on $10^2$ times as much data. This effect has yet to be seen in SE data~\cite{menzies2013guest} but that might just mean we have yet to use enough training data (hence, this study).

\textbf{(b) We need to learn from more data since there is very little agreement on what has been learned to far:} Another reason to try generalizing across more SE data is that, among developers, there is little agreement on what many issues relating to software:
\bi
    \item
    According to Passos et al.~\cite{passos11},  developers often  assume that the lessons they learn from a few past projects are general to all their future projects. They comment, ``past experiences were taken into account without much consideration for their context'' ~\cite{passos11}. 
	\item
	J{\o}rgensen \& Gruschke~\cite{Jo09} offer a similar warning. They report that the suppose software engineering ``gurus'' rarely use lessons from past projects to improve their future reasoning and that such poor past advice can be detrimental to new projects.~\cite{Jo09}.
    \item 
    Other studies have shown some widely-held views are   now questionable given new evidence. Devanbu et al. examined responses from 564 Microsoft software developers from around
	the world. They comment programmer beliefs can vary with each project, but do not necessarily
	correspond with actual evidence in that project~\cite{De16}. 
\ei

The good news is that, using software analytics, we can correct the above misconceptions. If data mining shows that doing  XYZ is bug prone, then we could  guide developers to avoid XYZ. But will developers listen to us? If they ask ``are we sure  XYZ causes problems?'', can we say that we have mined enough projects to ensure that XYZ is problematic?

It turns out that developers are not the only ones confused about how various factors influence software projects. Much recent research calls into question  the``established widoms'' of SE field. For example, here is a list of recent conclusions that contradict prior conclusions:

\bi

    \item In stark contrast to  much prior research, pre- and post- release failures are not connected~\cite{fenton2000quantitative};

    \item Static code analyzers perform no better than simple statistical predictors~\cite{Fa13};

    \item The language construct GOTO, as used in contemporary practice, is rarely considered harmful~\cite{nagappan2015empirical};

    \item Strongly typed languages are not associated with successful projects~\cite{ray2014large};

    \item Test-driven development is not any better than "test last"~\cite{fucci2017dissection};

    \item Delayed issues are not exponentially more expensive to fix~\cite{menzies2017delayed};

\ei

Note that if the reader disputes any of the above, then we ask how would you challenge the items on this list? Where would you get the data, from enough projects, to   successfully refute the above? And where would you get that data? And how would you draw conclusions from that large set?

\textbf{(c) Imported data can be more useful than local data:} Another benefit of  importing data from other projects is that, sometimes, that imported data can be better than the local information. For example, Rees-Jones reports in one study that while building predictors
for Github close time  for open source projects~\cite{rees2017better} using data from other projects performs much better then building models using {\em local learning} (because there is better  information {\em there} than {\em here}).

\textbf{(d) When there is insufficient local data, learning from other projects is very useful:} When developing new software in  novel areas, it is useful to draw on the relevant  experience  from related areas with a larger experience base.This is particularly true when developers are doing something that is novel to them, but has been widely applied elsewhere
For example, Clark and Madachy~\cite{clark15} discuss 65 types of software they see        under-development by the US Defense Department in 2015.   Some of these types are very common (e.g. 22 ground-based communication systems) but other types are very rare (e.g. only  one avionics communication system). (e.g. workers on   flight avionics   might check for lessons learned from ground-based communications). Developers  working in an uncommon area (e.g. avionics communications) might want to transfer in lessons from more common areas (e.g. ground-based communication).

This fuels the art of moving data and/or lessons learned from one project or another is Transfer Learning. This is when there is insufficient data to apply data miners to learn defect predictors, transfer learning can be used to transfer lessons learned from other source projects S to the target project T .

Initial experiments with transfer learning offered very pessimistic results. Zimmermann et al.~\cite{zimmermann2009cross} tried to port models between two web browsers (Internet Explorer and Firefox) and found that cross-project prediction was still not consistent: a model built on Firefox was useful for Explorer, but not vice versa, even though both of them are similar applications. Turhan's initial experimental results were also very negative: given data from 10 projects, training on S = 9 source projects and testing on T = 1 target projects resulted in alarmingly high false positive rates (60\% or more). Subsequent research realized that data had to be carefully sub-sampled and possibly transformed before quality predictors from one source are applied to a target project. Transfer learning can be have two variants -

(a) \textbf{Homogeneous Transfer Learning:} This kind of transfer learning operates on source and target data that contain the same attributes.

(b) \textbf{Heterogeneous Transfer Learning:} This type of transfer learning operates on source and target data that contain the different attributes.

Another way of to divide transfer learning is the approach that is followed. There are  2 approaches that is frequently used in many research  -

(a) \textbf{Similarity Based Approach:} In this approach we can transfer some/all subset of the rows or columns of data from source to target. For example, the Burak filter~\cite{turhan09} builds its training sets by finding the k = 10 nearest code modules in S for every $ t \in T $. However, the Burak filter suffered from the all too common instability problem (here, whenever the source or target is updated, data miners will learn a new model since different code modules will satisfy the k = 10 nearest neighbor criteria). Other researchers ~\cite{kocaguneli2012, kocaguneli2011find} doubted that a fixed value of k was appropriate for all data. That work recursively bi-clustered the source data, then pruned the cluster sub-trees with greatest ``varianc'' (where the ``variance'' of a sub-tree is the variance of the conclusions in its leaves). This method combined row selection with row pruning (of nearby rows with large variance). Other similarity methods~\cite{Zhang16aa} combine domain knowledge with automatic processing: e.g. data is partitioned using engineering judgment before automatic tools cluster the data. To address variations of software metrics between different projects, the original metric values were discretized by rank transformation according to similar degree of context factors.

(b) \textbf{Dimensionality Transformation Based Approach:} In this approach we manipulate the raw source data until it matches the target. An initial attempt on performing transfer learning with Dimensionality transform was undertaken by Ma et al.~\cite{Ma2012} with an algorithm called transfer naive Bayes (TNB). This algorithm used information from all of the suitable attributes in the training data. Based on the estimated distribution of the target data, this method transferred the source information to weight instances the training data. The defect prediction model was constructed using these weighted training data. Nam et al.~\cite{Nam13} originally proposed a transform-based method that used TCA based dimensionality rotation, expansion, and contraction to align the source dimensions to the target. They also proposed a new approach called TCA+, which selected suitable normalization options for TCA, When there are no overlapping attributes (in heterogeneous transfer learning) Nam et al.~\cite{Nam2015} found they could dispense with the optimizer in TCA+ by combining feature selection on the source/target following by a Kolmogorov-Smirnov test to find associated subsets of columns. Other researchers take a similar approach, they prefer instead a canonical-correlation analysis (CCA) to find the relationships between variables in the source and target data~\cite{jing2015heterogeneous}.

Considering all the attempts at transfer learning sampled above, suggested a surprising lack of consistency in the choice of datasets, learning methods, and statistical measures while reporting results of transfer learning. This issue was addressed by ``Bellwether'' suggested by Krishna et al. ~\cite{krishna2017simpler,krishna16}. which is a simple transfer learning technique is defined in 2- folds namely the Bellwether effect and the Bellwether method:

\bi

    \item \textbf{The Bellwether effect} states that, when a community works on multiple software projects,  then there exists one exemplary project, called the bellwether, which can define predictors for the others.

    \item \textbf{The Bellwether method} is where we search for the exemplar bellwether project and construct a transfer learner with it. This transfer learner is then used to predict for effects in future data for that community.

\ei

In their paper Krishna et al. performs experiment with communities of 3, 5 and 10 projects in each, and shows that bellwethers are not rare, their prediction performance is better than local learning, they do fairly well when compared with State of the Art transfer learning methods discussed above and with selection of bellwether shows a consistency for choice of source dataset for transfer learning. This motivated us to use ``Bellwether'' as our choice of method for transfer learning to search for generality in SE datasets. But as per Krishna et al. in order to find bellwether we need to do a $ N*(N-1) $ comparison which is order of $ N^2 $ (N being the number of projects in community). This indeed a very expensive computation. This motivated our study to find generality in SE datasets using a faster Bellwether method.

Include details about BIRCH and effect of clustering and talk about divide and conquer.

\section{BUBBLE}
\label{BUBBLE}

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{figs/BUBBLE.png}
    \caption{BUBBLE algoroithm.}
    \label{fig:BUBBLE}
\end{figure}

{\small 
{\small 
\begin{figure}[]
    \small
     %\begin{lstlisting}[mathescape,linewidth=7.5cm,frame=none,numbers=right]
    \inputminted[numbersep=1pt, linenos=true, fontsize=\small]{python}{pseudocode/bubble.py}
    \vspace{-0.2cm}
    \caption{Pseudo-code of BUBBLE Experiment}
    \label{fig:GAP_pseudocode} 
    \vspace{-0.3cm}
\end{figure}
}
}
{\small 
{\small 
\begin{figure}[]
     %\begin{lstlisting}[mathescape,linewidth=7.5cm,frame=none,numbers=right]
        \begin{minipage}{\linewidth}
            \inputminted[numbersep=2pt, linenos=true, fontsize=\small]{python}{pseudocode/heirarchical_bellw.py}
        \end{minipage}
    \vspace{-0.2cm}
    \caption{Pseudo-code of Hierarchical Bellwether}
    \label{fig:GAP_pseudocode} 
    \vspace{-0.3cm}
\end{figure}
}
}
In this study we introduce BUBBLE, which is a transfer learning method utilizing \textit{bellwether method} algorithm by combining the components described in section~\ref{sec:Experimental}.  This creates a fast way to find \textit{bellwether effect} in large datasets. BUBBLE works in 6 stages -

    (1) \textbf{Feature Extraction:} In this stage the whole dataset is used to extract feature from each projects. This is done using the FSS algorithm as shown in~\ref{subsec:FSS}. Here each project is sent to the FSS and the FSS returns most suitable features for building models, we do this for every project and that information as a vector (i.e. a vector or length equal to total number of features, where 1 represents a feature being selected ,0 is the other way around) that represents each project. By performing this we have a vector representation of each project in the dataset. BUBBLE uses this information to create the hierarchical clusters to find the communities. We perceive this is a good representation of community, as in this work we try to find community which has similar information distribution according to the attributes. Thus 2 projects with similar features selected have much higher chance of building similar models.

    (2) \textbf{Cluster Creation:} After the feature extraction has been done, the data is sent to a modified BIRCH algorithm. The algorithm requires a branching factor (i.e. Maximum number of CF sub-clusters in each node) and threshold value (i.e. when to form a new cluster based on radius). For this experiment we have set the branching factor as 20 and threshold value as 0.5. Using this version of BIRCH algorithm we build the hierarchical cluster, while storing all necessary details about the cluster like parent-child node, data points, level information etc. This stage returns a Clustering Feature Tree (CF Tree) with all those information, which is passed to the next phase of experiment.

    (3) \textbf{Bellwether selection phase 1:} The CF Tree from the last phase is passed to the hierarchical bellwether. In this phase we use \textit{bellwether method} to identify bellwether at the leaf level. Using the CF Tree, we identify the clusters at the leaf level where each cluster represents the smallest community produced by the BIRCH algorithm in the last phase. Here we use the default ``Bellwether'' to perform a $ N*(N-1) $ comparison at each cluster.Here we select each project in the cluster one by one as a source dataset for transfer learning apply SMOTE as mentioned in sec~\ref{subsec:SMOTE} to handle any data imbalance and then use the FSS algorithm to get rid of any unnecessary attributes as mentioned in sec~\ref{subsec:FSS}. This informative and balanced dataset is used to build a LR model as mentioned in sec~\ref{subsec:LR} and we measure the performance of all other projects in the community(cluster). The performance measures that are used are mentioned in sec~\ref{sec:Measures}. To find the bellwether in each community we use cdom function to find the best source dataset among each cluster considering all performance measures. This phase returns a bellwether for each cluster at the leaf level of the CF Tree.

    (4) \textbf{Bellwether promotion:} In this phase of the algorithm is an iterative process, here we receive the selected bellwethers from the child clusters of each cluster in the level. This is called the bellwether promotion. Here each parent cluster instead of being represented by all projects within them, they are represented by only the bellwethers in them.

    (5) \textbf{Bellwether selection phase 2:} In this phase instead of finding a bellwether for each cluster at the level by performing a $ N*(N-1) $ comparison, we select the projects which represented as bellwether at the child nodes and then try to find a bellwether among them. So at each cluster at the level we perform a a $ M*(M-1) $ comparison at each cluster where M is the selected bellwether from child clusters. This creates a order of magnitude faster \textbf{bellwether method}. This is again an iterative process, and the end of all the iterations, we will have a bellwether at each cluster at every level.

    (6) \textbf{Bellwether Prediction:} This is the transfer learning phase, when a new project is to evaluated we will use the FSS algorithm to get its features, then use the feature vectors to identify which cluster it belongs and use that cluster's bellwether as the transfer learning model.

To report the finding and results of this study without any bias, we repeat the experiment 20 times by dividing the dataset randomly into train\_1 and test\_1 as a 90-10 split, the projects in train\_1 was used to find the bellwether in each cluster in the CF Tree, and then each project in test\_1 was divide into train\_2 and test\_2 split. We trained a LR model using train\_2 for each project and tested on test\_2, this is represented as self test in this study. We also used the predict stage of the BUBBLE to identify bellwether for each project in test\_1 and tested the performance on test\_2.

\section{Data and Experimental Setup}
\label{sec:Data Collection}

\subsection{Data Collection}
\label{sec:data}

To perform our experiments we choose to work with defect prediction datasets. We use data collected by zhang et al.~\cite{zhang15}. The original data was initially collected by Mockus et al.~\cite{mockus2009amassing} from SourceForge and GoogleCode. The dataset contains the full history of about 154K projects that are hosted on SourceForge and 81K projects that are hosted on GoogleCode to the date they were collected. In the original dataset each file contained the revision history and commit logs linked using a unique identified. Although there were 235K projects in the original database, we know from previous literature surveys and experience there were many trivial and non-software development projects. zhang et al. cleaned the dataset using 5 different criteria which resulted in 1385 projects being selected in the final datasets \footnote{\href{http://tiny.cc/bellwether_data}{http://tiny.cc/bellwether\_data}}. As part of this experiment we also included few filters to select a subset of 1385 projects, which are useful for our experiment. This eventually gave us a dataset of 697 projects. The filters applied to filter out trivial projects are -

\bi

    \item \textbf{Programming Languages:} Filtering Out Projects by Programming Languages(only object-oriented i.e *.c, *.cpp, *.cxx, *.cc, *.cs, *.java, and *.pas). This was done as the dataset was collected using a commercial tool, called Understand~\cite{visualize}(which supports the object oriented programming languages) , to compute code metrics.

    \item \textbf{Projects with a Small Number of Commits:} zhang et al. removed any projects with less than 32 commits(25 \% quantile of the number of commits as the threshold).

    \item \textbf{Projects with Lifespan Less Than One Year:} zhang et al. filtered out any  projects with a lifespan less than one year.

    \item \textbf{Projects with Limited Defect Data:} zhang et al. in their study counted the number of fix-inducing and non-fixing commits from a one-year period and removed any projects with 75 \% quantile of the number of fix-inducing and non-fixing commits.

    \item \textbf{Projects Without Fix-Inducing Commits:} zhang et al. filtered out projects that have no fix-inducing commits during six months as abnormal projects, as projects in defect prediction studies need to contain both defective and non-defective commits.

    \item \textbf{Projects with less than 50 rows:} We removed any project with less than 50 rows as they are too small to build a meaningful predictor.

\ei

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{figs/meta.png}
    \caption{Two hypothetical results about how training set size might effect the efficacy of quality prediction for software projects.}
    \label{fig:meta}
\end{figure}

Along with above filtering criteria, there were few projects which didn't have enough fix-inducing vs non-fixing data points to to create a stratified k=5 fold cross-validation and we removed those projects from the final datasets. These criteria culled 99\% of projects by zhang et al. and culled 54\% of the remaining by our criteria, thus resulted in 697 projects in the final dataset.

From these selected projects, the data was labeled using issue tracking system and commit messages. If a project used issue tracking system for maintaining issue/defect history the data was labeled using that. But as per zhang et al. 42\% of the projects didn't not used issue tracking systems. For these projects labels were created analyzing commit messages by tagging them as fix-inducing commit if commit message matches the following regular expression

\begin{center}
\textit{(bug $\mid$ fix $\mid$ error $\mid$ issue $\mid$ crash $\mid$ problem $\mid$ fail $\mid$ defect $\mid$ patch)}
\end{center}

\subsection{Metric Extraction}
\label{sec:Metric Extraction}

For building any defect predictor we rely on software metrics. Software metrics can be categorized into 3 types according to Xenos \cite{Xenos} distinguishes software metrics as  follows (a) {\em Product metrics} are metrics that are directly related to the product itself, such as code statements, delivered executable, manuals, and strive to measure product quality, or attributes of the product that can be related to product quality. (b) {\em Process metrics} focus on the process of software development and measure process characteristics, aiming to detect problems or to push forward successful practices. Lastly, (c) {\em personnel metrics} (a.k.a. {\em resource metrics}) are those related to the resources required for software development and their performance. The capability, experience of each programmer and communication among all the programmers are related to product quality \cite{wolf2009predicting,de2004sometimes,cataldo2013coordination,cataldo2007coordination}. zhang et al. selected and calculated 21 product and 5 process metrics to build their universal defect prediction model, we will be using the same set of metrics for our study. The product metrics are computed by the Understand tool~\cite{visualize} using the files from the snapshot on the split date of 6 months. The process metrics are computed using the change history in the six-months period before the split date my manual collection of data using scripts. The metrics used in this study are described in table~\ref{tbl:metric}.

{\small 
\begin{table}[]
\centering
\caption{List of software metrics used in this study}
\label{tbl:metric}
\scriptsize
\begin{tabular}{|p{1cm}|c|l|p{3cm}|}
\hline
\multicolumn{1}{|l|}{Metric}        & \multicolumn{1}{l|}{Metric level} & Metric Name & Metric Description             \\ \hline
\multirow{21}{*}{Product   } & \multirow{6}{*}{File}             & LOC         & Lines of Code                  \\ \cline{3-4} 
                                  &                                   & CL          & Comment Lines                  \\ \cline{3-4} 
                                  &                                   & NSTMT       & Number of Statements           \\ \cline{3-4} 
                                  &                                   & NFUNC       & Number of Functions            \\ \cline{3-4} 
                                  &                                   & RCC         & Ratio Comments to Code         \\ \cline{3-4} 
                                  &                                   & MNL         & Max Nesting Level              \\ \cline{2-4} 
                                  & \multirow{12}{*}{Class}           & WMC         & Weighted Methods per Class     \\ \cline{3-4} 
                                  &                                   & DIT         & Depth of Inheritance Tree      \\ \cline{3-4} 
                                  &                                   & RFC         & Response For a Class           \\ \cline{3-4} 
                                  &                                   & NOC         & Number of Immediate Subclasses \\ \cline{3-4} 
                                  &                                   & CBO         & Coupling Between Objects       \\ \cline{3-4} 
                                  &                                   & LCOM        & Lack of Cohesion in Methods    \\ \cline{3-4} 
                                  &                                   & NIV         & Number of instance variables   \\ \cline{3-4} 
                                  &                                   & NIM         & Number of instance methods     \\ \cline{3-4} 
                                  &                                   & NOM         & Number of Methods              \\ \cline{3-4} 
                                  &                                   & NPBM        & Number of Public Methods       \\ \cline{3-4} 
                                  &                                   & NPM         & Number of Protected Methods    \\ \cline{3-4} 
                                  &                                   & NPRM        & Number of Private Methods      \\ \cline{2-4} 
                                  & \multirow{3}{*}{Methods}          & CC          & McCabe Cyclomatic Complexity   \\ \cline{3-4} 
                                  &                                   & FANIN       & Number of Input Data           \\ \cline{3-4} 
                                  &                                   & FANOUT      & Number of Output Data          \\ \hline
\multirow{5}{*}{Process }  & \multirow{5}{*}{File}             & NREV        & Number of revisions            \\ \cline{3-4} 
                                  &                                   & NFIX        & Number of revisions a file     \\ \cline{3-4} 
                                  &                                   & ADDED LOC    & Lines added                    \\ \cline{3-4} 
                                  &                                   & DELETED LOC  & Lines deleted                  \\ \cline{3-4} 
                                  &                                   & MODIFIED LOC & Lines modified                 \\ \hline
\end{tabular}
\end{table}
}

\subsection{Experimental Setup}
\label{sec:Experimental}

In this study we try to establish the presence of generality in SE datasets. We do this by analyzing the presence of bellwether incrementally by adding more and more projects and how the bellwether's predictive power changes. In this case to show the presence of generality in SE datasets the predictive power of the bellwether should look like the \textcolor{ao(english)}{GREEN} in figure~\ref{fig:predictive_power}, that is the predictive power of bellwether should increase or remains same, if our results look like the \textcolor{red}{RED} curve, that will show absence of generality in SE datasets.

In order to achieve this we try to explore the \textit{bellwether effect} as mentioned in ~\ref{sec:related}. We know the default \textit{bellwether method} is very expensive ($ O(N^2) $). Thus in this paper we proposes an alternative transfer learning method (BUBBLE), that explores \textit{bellwether effect} by exploring an order of magnitude faster \textit{bellwether method}. Our approach has three key components:

\bi

    \item A feature extractor to find a representation of each project, which will be used for clustering the projects.

    \item A hierarchical clustering model to use the features extracted from previous step to build the hierarchical cluster.

    \item A transfer learning model to identify bellwether in the hierarchical cluster.

\ei

BUBBLE employs few different algorithms to complete and compose it's 4 different components -

\subsubsection{\textbf{Feature Subset Selection (FSS):}}
\label{subsec:FSS}
To extract features from each dataset, we use a feature selector algorithm called Feature Subset Selection(FSS)~\cite{hall1999correlation,hall1997feature}. Which is a process of identifying and removing as much irrelevant and redundant information as possible. This is achieved using a correlation based feature evolution strategy to evaluate importance of an attribute and a best first search strategy with back tracking that moves through the search space by making local changes to the current feature subset.Here if the path being explored begins to look less promising, the best first search can back-track to a more promising previous subset and continue the search from there. Given enough time, a best first search will explore the entire search space, so it uses a stopping criterion (i.e. no improvement for five consecutive attributes).

{\small 
\begin{figure}[]
    \small 
    \inputminted[numbersep=2pt, linenos=true, fontsize=\small]{python}{pseudocode/cfs.py}
    \vspace{-0.2cm}
    \caption{Pseudo-code of Feature Subset Selection}
    \label{fig:GAP_pseudocode} 
    \vspace{-0.3cm}
\end{figure}
}
\subsubsection{\textbf{Balanced Iterative Reducing and Clustering using Hierarchies (BIRCH):}}
\label{subsec:BIRCH}
To find presence or absence of generality in SE datasets, we need to incrementally check for ``Bellwether'' from smaller to larger community. A community is a set of project which is similar in nature. We use the BIRCH algorithm on our defect prediction dataset to create a hierarchical clustering tree to form these communities. BIRCH~\cite{zhang1996birch} is  a hierarchical clustering algorithm, which has a ability to incrementally and dynamically cluster incoming, multi-dimensional data in an attempt to produce the best quality clustering. BIRCH also has the ability to identify data points that are not part of the underlying pattern effectively identifying outliers. In this study we uses a modified BIRCH algorithm to store additional information regarding each cluster in the clustering feature tree, which help us in the experiment.

\subsubsection{\textbf{Synthetic Minority Over-Sampling Technique (SMOTE):}}
\label{subsec:SMOTE}

Machine learning models exploits the inherent bias in the dataset to segregate and classify different classes. Hence class imbalance can create major bias towards the majority class when building a machine learning model, thus producing biased model which provides bad classification results. Synthetic Minority Over-Sampling Technique (SMOTE)~\cite{chawla2002smote} is a technique to handle class imbalance by changing the frequency of different classes of the training data. When applied to data, SMOTE sub-samples the majority class (i.e., deletes examples) while over-sampling the minority class until all classes have the same frequency. In the case of software defect data, the minority class is usually the defective class. During super-sampling, a member of the minority class finds k nearest neighbors. It builds an artificial member of minority class at some point in-between itself and one of its random nearest neighbors. During that process, some distance function is required which is the \textit{minkowski distance} function.

\subsubsection{\textbf{Logistic Regression (LR):}}
\label{subsec:LR}

Logistic regression is a statistical machine learning model that in its basic form uses a logistic function to model a binary dependent variable. In this study we use scikit learn's default logistic regression implementation as our learner for building source models and evaluating on target models inside each community. In this study we selected logistic regression, as it is very fast to build in comparison to other more complex learners and its much more comprehensible and explainable in-terms of attributes and their importance. Logistic Regression is widely used in defect prediction domain and have shown promising results both in-term of predictive power and comprehensibility.

\subsubsection{\textbf{Bellwether\_0:}}
\label{Bellwether}

In this study to compare our novel method to the state of the art method, we uses Krishna et al. 's \textit{bellwether method}. We use all the projects available in the community to perform a $N*(N-1)$ comparison, where N is the number of projects in the community to measure the performance of each project measured on all others on the performance measures mentioned in sec~\ref{sec:Measures}. Following this we use cdom function to select a bellwether project among them.

\section{Evaluation Criteria}
\label{eval}
\subsection{Statistical Tests}
\label{stats}

When comparing the results different models in this study, we used a statistical significance test and an effect size test. Significance test are useful for detecting if two populations
differ merely by random noise. Also, effect sizes are useful for checking that two populations differ by more than just a trivial amount. For the significance test,  we use the Scott-Knott procedure  recommended at TSE'13~\cite{mittas2013ranking} and ICSE'15~\cite{ghotra2015revisiting}. This technique recursively bi-clusters a sorted set of numbers. If any two clusters are statistically indistinguishable, Scott-Knott reports them both as one group. Scott-Knott first looks for a break in the sequence that maximizes the expected values in the difference in the means before and after the break.More specifically,  it  splits $l$ values into sub-lists $m$ and $n$ in order to maximize the expected value of differences  in the observed performances before and after divisions. For e.g., lists $l,m$ and $n$ of size $ls,ms$ and $ns$ where $l=m\cup n$, Scott-Knott divides the sequence at the break that maximizes:

\begin{equation}
    E(\Delta)=ms/ls*abs(m.\mu - l.\mu)^2 \\ + ns/ls*abs(n.\mu - l.\mu)^2
\end{equation}

Scott-Knott then applies some statistical hypothesis test $H$ to check if $m$ and $n$ are significantly different. If so, Scott-Knott then recurses on each division. For this study, our hypothesis test $H$ was a conjunction of the A12 effect size test (endorsed by \cite{arcuri2011practical})  and non-parametric bootstrap sampling \cite{efron94}, i.e., our Scott-Knott divided the data if {\em both} bootstrapping and an effect size test agreed that the division was statistically significant (90\% confidence) and not a ``small'' effect ($A12 \ge 0.6$).

\subsection{Continuous Domination(cdom)}
\label{cdom}
In this study, we compare each project's performance against all other projects in each cluster at the leaf level of the BIRCH as described in section~\ref{BUBBLE} and section~\ref{Bellwether}. We calculate 5 different performance measure for each project as described in section~\ref{sec:Measures}. In order to find a \textit{bellwether effect} in the performances collected we need to combine those 5 performance measures and then rank them using certain criteria. We have used continuous domination (cdom) for this purpose. continuous domination is defined as the set of all points in the objective space that are not dominated by any other points. Unlike Boolean domination, which says a point is dominated by another if and only if the first point is better in every single objective then the second point, continuous domination combines all the objective into a continuous function to compare and then calculate if one point dominates another. Throughout literature continuous domination has proven to be very effective when multiple goals are concerned. The continuous domination function is defined as below, where P is the total population, k is fitness scaling factor, n is a scaling factor and $X\_1$ is the data points we are calculating the domination for - 
\begin{equation}
    F(X_1) = \sum_{{(X_2\in P) - X_1}} -n*e^{-I(X_2,X_1)/k}
\end{equation}
{\small 
\begin{figure*}[ht!]
    \centering
    \begin{tikzpicture}[nodes={draw, circle,fill=pink!50}, ->,sibling distance=.7cm,minimum size=.1cm,scale=.5]

    \node{627}
        child { node {57}
            child {node {9}} 
            child {node {9}} 
            child {node {7}} 
            child {node {17}}
            child {node {13}}}
        child [missing]
        child [missing]
        child [missing]
        child [missing]
        child [missing]
        child [missing]
        child [missing]
        child { node {127} 
            child {node {3}} 
            child {node {9}} 
            child {node {19}} 
            child {node {15}}
            child {node {4}}
            child {node {17}} 
            child {node {15}} 
            child {node {19}} 
            child {node {11}}
            child {node {15}}}
        child [missing]
        child [missing]
        child [missing]
        child [missing]
        child [missing]
        child [missing]
        child [missing]
        child [missing]
        child [missing]
        child [missing]
        child [missing]
        child [missing]
        child { node {183} 
            child {node {8}} 
            child {node {3}} 
            child {node {12}} 
            child {node {16}}
            child {node {20}}
            child {node {18}} 
            child {node {12}} 
            child {node {4}} 
            child {node {12}}
            child {node {16}}
            child {node {5}}
            child {node {17}} 
            child {node {9}} 
            child {node {9}} 
            child {node {10}}
            child {node {14}}}
        child [missing]
        child [missing]
        child [missing]
        child [missing]
        child [missing]
        child [missing]
        child [missing]
        child [missing]
        child [missing]
        child [missing]
        child [missing]
        child [missing]
        child [missing]
        child [missing]
        child [missing]
        child [missing]
        child [missing]
        child { node {260} 
            child {node {17}} 
            child {node {17}} 
            child {node {20}} 
            child {node {14}}
            child {node {9}}
            child {node {13}} 
            child {node {18}} 
            child {node {10}} 
            child {node {18}}
            child {node {10}}
            child {node {6}} 
            child {node {15}} 
            child {node {14}} 
            child {node {9}}
            child {node {10}}
            child {node {8}} 
            child {node {7}} 
            child {node {13}} 
            child {node {15}}}
            ;
\end{tikzpicture}
    \caption{Example of Hierarchical Clustering for 627 projects}
    \label{fig:example tree}
\end{figure*}
}

\section{Performance Measures}
\label{sec:Measures}

In this section, we introduce the following 5 evaluation measures used in this study to evaluate the performance of machine learning models. Suppose we have a dataset with M changes and N defects. After inspecting 20\% LOC, we inspected m changes and found n defects. Besides, when we find the first defective change, we have inspected k changes. Then the 5 evaluation measures are defined and computed as follows:

(1) \textbf{Recall:} Proportion of inspected defective changes among all the actual defective changes. This is the evaluation measure used by many previous studies~\cite{kamei2012large,yang2016effort,yang2017tlel,xia2016collective,yang2015deep} . They focused on achieving high Recall so that more defective changes could be detected. Recall is computed as: $n/N$.

(2) \textbf{Precision:} Proportion of inspected defective changes among all the inspected changes. A low Precision indicates that developers would encounter more false alarms, which may have negative impact on developers' confidence on the prediction model. Precision is computed as: $n/m$.

(3) \textbf{pf:} Proportion of all suggested defective changes which are not actual defective changes among all the suggested defective changes. A high pf suggests developers will encounter more false alarms which may have negative impact on developers' confidence on the prediction model.

(4) \textbf{popt20:} Proportion number of suggested defective changes among all suggested defective changes, when when 20\% LOC modified by all changes are inspected. A high popt20 indicates that, under the same number of LOC to inspect, developers developers will find more bugs, which means developers will be able to fix more defects with same amount of effort invested.

(5) \textbf{ifa\_auc:} Number of Initial False Alarms encountered before we find the first defect. Inspired by previous studies on fault localization~\cite{parnin2011automated,kochhar2016practitioners,xia2016automated}, we assume that if the top-k changes recommended by the model are all false alarms, developers would be frustrated and are not likely to continue inspecting the other changes. For example, Parnin and Orso ~\cite{parnin2011automated} found that developers would stop inspecting suspicious statements, and turn back to traditional debugging, if they could not get promising results within the first few statements they inspect. ifs is computed as: k. In this study we use a modified version of ifa called ifa\_auc, which calculates ifa based on efforts spent on inspecting the code. We use gradually increment the efforts spent by increasing the total LOC inspected and calculate ifa on each iteration to get the area under the curve (auc), here the x-axis is the percentage of effort spent on inspection and y-axis is ifa.

\section{Results}
\label{sec:results}

\subsection*{RQ1: Can we confirm bellwether on large datasets?}
\label{sec:rq1}

In the literature, we saw most of the previous studies has shown bellwether effect with very small datasets. In order to use bellwether to prove presence of generality in SE domain datasets, we first have to showcase the bellwether method suggested by Krishna et al. in their experiment works for large datasets. We use our defect prediction dataset with 697 projects for this purpose.

We divide the dataset in train\_1 and test\_1 set and then performed a $ N*(N-1) $ comparison on all the projects in train\_1 set to find a bellwether, and then dividing each project in test\_1 set into train\_2 and test\_2 using a train\_test split. We use the train\_2 to train a LR model and test on test\_2 which is represented as \textit{self\_0} in the figures. Similarly we use the bellwether project from train\_1 to train a LR model and test it on test\_2 which is represented as \textit{bellwether0}. We use statistical tests mentioned in section~\ref{stats} to compare the performance of \textit{self\_0} vs \textit{bellwether0} for all the performance measures mentioned in section~\ref{sec:Measures}, which is shown in figure~\ref{fig:Statistical}.

It is evident that using the \textit{bellwether method} proposed by Krishna et al. we were able to find bellwether effect in large dataset with 697 projects. This answers this RQ and creates the baseline results for our study. In this RQ1 although we are able to find \textit{bellwether effect}, this method is very expensive, requiring a $ N*(N-1) $ comparison, which in our experimental setup took nearly 3 days of computation. Which takes us to the next research question. In summary, we find that

\begin{result} {Bellwethers are found when studying over 697 software projects. However, conventional methods of Krishna et al~\cite{krishna2017learning} take far too long to discover these bellwethers, e.g., experimentation took 3 days to find a bellwether project from among the 697 projects.}
\end{result}

\subsection*{RQ2: How to tame complexity of bellwether?}
\label{sec:rq2}

To tame complexity of bellwether in this RQ, we propose a new bellwether method called ``BUBBLE'' to find bellwether in large datasets. This bellwether method is composed of 6 stages, (a) a feature extraction process to summarize each project into a single representative vector, (b) a hierarchical clustering algorithm, which uses the feature vectors to cluster similar projects into community of increasing size at different levels of cluster, (c) a bellwether selection phase where a $N*(N-1)$ comparison is performed at each leaf level cluster and using a cdom calculation in all the metrics mentioned in~\ref{tbl:metric} a bellwether is selected, (d) a iterative bellwether promotion stage, where bellwether from child clusters are promoted as potential bellwethers at parent cluster, (e) another bellwether selection phase at non-leaf levels, where comparisons are only made among potential bellwethers from leaf node and finally (f) a bellwether prediction phase, which suggests a bellwether based on project similarity when a new project is to be predicted. The details of each phase is mentioned in sec~\ref{BUBBLE}.

In the \textit{bellwether method} proposed by Krishna et al. if there are N projects in a community it will make $\approx N^2$ comparisons to discover the bellwether. While ``BUBBLE'' different approach to discover bellwether by dividing the data into smaller cluster and finding bellwether among each, here if we assume we have m cluster at leaf level with N projects in each, we will have 
$\approx m*(N/m)^2$ comparisons to discover the bellwether which is m times less comparison. For example if we see the example figure~\ref{fig:example tree} for hierarchically cluster a community of 627 projects, if we use the default \textit{bellwether method} it will require \textbf{393129} comparisons. While if we use the ``BUBBLE'' algorithm to find the bellwether it will require only \textbf{9080} comparisons. Using this process we are able to find bellwether in ~\textbf{1.5 hours}, which is order of magnitude faster then the bellwether method proposed by Krishna et al. In summary, we find that

\begin{result}
{``BUBBLE'' can find ``Bellwether Project'' order of magnitude faster, only requiring 1.5 hours in comparison to 3 days. Also ``BUBBLE'' requires far less comparison 9080 instead of 393129 required for ``Bellwether method'' proposed by krishna et al. }
\end{result}

\begin{equation}
\label{eq:bellwether}
    Bellwether\_complexity  \approx O(N^2)
\end{equation}

\begin{equation}
\label{eq:BUBBLE}
    BUBBLE\_complexity \approx O(m*(N/m)^2)
\end{equation}

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{figs/time.png}
    \caption{Runtime for default bellwether and BUBBLE.}
    \label{fig:time}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%Latex Table%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!t]
{\small
{\small \begin{tabular}{p{.1cm}lp{1.5cm}rrc}
\arrayrulecolor{darkgray}
\rowcolor[gray]{.9}  & rank & treatment & mean & sd & \\
 \multirow{5}{*}{\rotatebox[origin=c]{90}{Recall}} &   1 &      random2 &    40 &  49 & \quart{16}{40}{49}{25} \\
  &   1 &      BUBBLE\_level2 &    38 &  32 & \quart{22}{38}{32}{16} \\
  &   1 &      bellwether0 &    39 &  31 & \quart{23}{39}{31}{15} \\
  &   2 &      BUBBLE\_level1 &    48 &  33 & \quart{31}{48}{33}{16} \\
  &   3 &      BUBBLE\_level0 &    56 &  31 & \quart{42}{56}{31}{16} \\
  &   3 &      self\_0 &    55 &  27 & \quart{41}{55}{27}{12} \\
  &   4 &      global2 &    78 &  40 & \quart{57}{78}{40}{20} \\ \hline
\multirow{5}{*}{\rotatebox[origin=c]{90}{Pf}} &    1 &      random2 &    39 &  49 & \quart{15}{39}{49}{25} \\
  &  1 &      random2 &    39 &  49 & \quart{15}{39}{49}{25} \\
  &  1 &      BUBBLE\_level2 &    28 &  28 & \quart{14}{28}{28}{13} \\
  &  1 &      bellwether0 &    28 &  25 & \quart{15}{28}{25}{11} \\
  &  1 &      self\_0 &    30 &  20 & \quart{20}{30}{20}{10} \\
  &  1 &      BUBBLE\_level1 &    35 &  28 & \quart{21}{35}{28}{14} \\
  &  2 &      BUBBLE\_level0 &    47 &  31 & \quart{31}{47}{31}{15} \\
  &  3 &      global2 &    79 &  39 & \quart{59}{79}{39}{19} \\\hline
\multirow{5}{*}{\rotatebox[origin=c]{90}{Precision}} &   1 &      random2 &    21 &  30 & \quart{6}{21}{30}{15} \\
    &  2 &      global2 &    35 &  28 & \quart{21}{35}{28}{14} \\
    &   2 &      bellwether0 &    40 &  33 & \quart{23}{40}{33}{16} \\
    &   2 &      BUBBLE\_level2 &    39 &  34 & \quart{22}{39}{34}{17} \\
    &   2 &      BUBBLE\_level1 &    42 &  31 & \quart{26}{42}{31}{15} \\
    &   2 &      BUBBLE\_level0 &    44 &  30 & \quart{28}{44}{30}{15} \\
    &   2 &      self\_0 &    50 &  30 & \quart{35}{50}{30}{15} \\\hline
\multirow{5}{*}{\rotatebox[origin=c]{90}{Popt20}} &   1 &      random2 &    13 &  16 & \quart{5}{13}{16}{8} \\
  & 2 &      BUBBLE\_level2 &    26 &  22 & \quart{15}{26}{22}{11} \\
  &  2 &      global2 &    26 &  13 & \quart{19}{26}{13}{6} \\
  &  2 &      bellwether0 &    28 &  21 & \quart{17}{28}{21}{9} \\
  &  2 &      BUBBLE\_level0 &    28 &  15 & \quart{22}{28}{15}{8} \\
  &  2 &      BUBBLE\_level1 &    28 &  19 & \quart{19}{28}{19}{9} \\
  &  3 &      self\_0 &    35 &  19 & \quart{26}{35}{19}{10} \\\hline
\multirow{5}{*}{\rotatebox[origin=c]{90}{ifa\_auc}} &   1 &      random2 &    7 &  11 & \quart{1.12}{6.77}{11.29}{5.65} \\
  &  2 &      global2 &    19 &  16 & \quart{11.35}{19.38}{16.06}{8.03} \\
  &  3 &      BUBBLE\_level2 &    22 &  14 & \quart{14.48}{21.59}{14.21}{7.10} \\
  &  3 &      bellwether0 &    23 &  14 & \quart{15.48}{22.56}{14.15}{7.07} \\
  &  3 &      self\_0 &    23 &  12 & \quart{17.09}{22.93}{11.68}{5.84} \\
  &  3 &      BUBBLE\_level1 &    23 &  14 & \quart{16.10}{22.98}{13.74}{6.87} \\
  &  3 &      BUBBLE\_level0 &    25 &  13 & \quart{17.87}{24.51}{13.27}{6.63} \\
\end{tabular}}
}
\caption{Statistical Results comparison
}\label{fig:Statistical}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%End Latex Table%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection*{RQ3: Is faster bellwether effective?}
\label{sec:rq3}

In RQ2, we can see using ``BUBBLE'' we are able to find bellwether for a large dataset in order of magnitude faster. This raises the question is  \textit{bellwether method} ``BUBBLE'' as effective as \textit{bellwether method} proposed by krishna et al. and can it be compared against local(self test) and global models?

To answer this question in this study we have used the defect prediction dataset with 697 projects and divided the projects randomly into train\_1 and test\_1 as a 90-10 split, the projects in train\_1 was used to find the bellwether in each cluster in the CF Tree as mentioned in sec~\ref{BUBBLE}, and then each project in test\_1 was divide into train\_2 and test\_2 split. We trained a LR model using train\_2 for each project and tested on test\_2 (represented as self\_0), this is represented as self test in this study. We also used the predict stage of the ``BUBBLE'' to identify a bellwether in each level of hierarchical model, for each project in test\_1 and tested the performance on test\_2 (represented as bellwether\_level0, bellwether\_level1, bellwether\_level respectively). Similarly we used the projects in train\_1 to find the bellwether using default bellwether method as mentioned in sec~\ref{Bellwether}, and use that project to build a LR model and test the performance of each project's test\_2 (represented as bellwether0). And we combined all the data from train\_1, and used that to build a global model and tested on test\_2 (represented as global2). We compare the performance of each model described above using statistical tests as mentioned in section~\ref{stats} and if 2 models are ranked different that represents their performance is significantly different.

We can see from the figure~\ref{fig:Statistical} that bellwether\_level0 model (i.e. the bellwether discovered by ``BUBBLE'' at level 0) performs similar or  better than bellwether0 in most of performance metrics. Similarly for self\_0 in terms of precision, recall and ifa\_auc bellwether\_level0 scores same rank using statistical significance and effect size test. Although for bellwether0 and self\_0 the performance rank for pf and Popt20 is little better than bellwether\_level0, the difference is very small. We can see similar results for the global2 results, where bellwether\_level0 performs significantly better. Seeing these results we can conclude the ``BUBBLE'' is an effective and fast algorithm to find a exemplary ``Bellwether Projects'', whose predictive performance is comparable with  \textit{bellwether method} proposed by krishna et al. , local(self test) and global models. In summary, we find that

\begin{result}
{``BUBBLE'' is a fast and effective algorithm, which can find exemplary ``Bellwether Projects'' with comparable predictive performance.}
\end{result}

\subsection*{RQ4: Does learning from too many projects has detrimental effect?}
\label{sec:rq4}
In RQ4, we try to answer the question if learning from too many projects detrimental effect, this question has two parts one on predictive power, other on making general conclusion and conclusion instability. Figure~\ref{fig:Statistical} show the results of statistical significance and effect size tests to rank them in order for all the different methods(treatments) used in this experiment. In this figure for a performance measure two methods showing same rank means there performance is not statistically significantly different, while a different ranks means they are different, while a smaller rank is better if the performance goal is negative (i.e. Pf), and higher rank is better in case of positive goal (i.e. Recall).

To answer the first part of the question, if learning from too many projects have detrimental effect on predictive power of models, we compare the results of default ``bellwether method'' (a.k.a bellwether0) proposed by krishna et al. and ``BUBBLE''(a.k.a BUBBLE\_level0) method. The results of scott-knott test shows that for positive goals such as Recall the BUBBLE\_level0 is significantly doing better than Bellwether0 and it is doing as good as or better for precision ans recall. While for negative goals such as ifa\_auc BUBBLE\_level0 is doing as good as bellwether0. Although in case of Pf they score different ranks with BUBBLE showing higher Pf then bellwether0, it is not by much. Similarly while comparing BUBBLE\_level0 with global (which is learning from all the projects) shows although it achieves higher Recall, but it has very high Pf, low precision. Which answers the first part of the question that learning from too many projects do have detrimental effect on predictive power of models.

\begin{table}[!t]
\centering
\caption{Importance of coefs on \textit{log p} from logistic regression model of ``Bellwether'' shown in fig~\ref{fig:FSS_compare}. Here Odds ratio shows one increment in in respective variable increase in the log-odds of being defective.}
\begin{tabular}{|l|l|l|l|} \hline
Rank & Attr               & coef  & Odds ratio \\ \hline
1    & avg\_NPRM          & 2.23  & 9.26      \\ \hline
2    & avg\_NPBM          & -1.31 & 0.27      \\ \hline
3    & max\_NPBM          & -1.12 & 0.33      \\ \hline
4    & max\_RFC           & 0.74  & 2.09      \\ \hline 
5    & total\_NPBM        & -0.70 & 0.50      \\ \hline
6    & max\_CBO           & -0.64 & 0.53      \\ \hline
7    & total\_ModifiedLOC & 0.10  & 1.10      \\ \hline
8    & avg\_WMC           & 0.07  & 1.07     \\ \hline
\end{tabular}
\label{tbl:coefs}
\end{table}

Now to answer the second part of the question, that is if learning from too many projects creates conclusion instability, we will look at the figure~\ref{fig:FSS_compare}. Figure~\ref{fig:FSS_compare} show the distribution of attributes selected while building a ML model for defect prediction using local models(a.k.a self\_0), the \textcolor{red}{{\bf red bars}} shows the attributes selected by the ``Bellwether Project''. Conclusion instability causes vastly different and often contradicting conclusions to be derived from a data source. This sort of instability is very prevalent in several domains of software engineering. We can see from figure~\ref{fig:FSS_compare}, when learning from local data, each model selected different sets of attributes and resulted in selecting almost all different attributes. That means there is no general conclusion can be drawn for defect prediction models by saying which attributes are important, this results in conclusion instability and that effects the trusts on those models, the insights that can be drawn from them. Which farther affects training and tool development as mentioned in sec~\ref{sec:Motivation}. From these results we can see learning from too many data can cause conclusion instability and thus affecting generality in SE domain. In Summary, we can say

\begin{result}
{Learning from too many projects have detrimental effect on predictive power, which can be seen on performance difference found between bellwether0 and BUBBLE\_level0, it also introduces conclusion instability. By selecting ``Bellwether Project'' using BUBBLE can have better predictive performance as well as it can create generalized model which are explainable and actionable thus minimizing conclusion instability.}
\end{result}

\begin{figure*}[h]
    \centering
    \includegraphics[width=\linewidth]{figs/FSS_compare.png}
    \caption{Distribution of attributes selected using self\_0 model and ``Bellwether'' model.}
    \label{fig:FSS_compare}
\end{figure*}

\subsection*{RQ5: What did we learn?}
\label{sec:rq5}

In this RQ we show what did we learn by selecting a ``Bellwether Project'' to create defect prediction models. Using ``Bellwether Project''  minimizes the issue of conclusion instability and thus building trust in the model and deduce better insights about what can be a better indicator of bugs. Table~\ref{tbl:coefs} show the attributes selected by the ``Bellwether Project'' and the coefs and Odd ratios for the LR model build using that. The insights that we can draw from these results are an increase of 1 in avg\_NPRM can increase the ratio of probability of having a defect and not having a defect by almost 9 times, while an unit increase in total\_NPBM, avg\_NPBM, max\_NPBM, max\_CBO will reduce the ration of probabilities by 0.5, 0.27, 0.33 and 0.53 times respectively. an unit increase in total\_ModifiedLOC and avg\_WMC will have almost no effect in Odd ratio. From this we can conclude NPRM, NPBM, RFC and CBO are important factor while predicting for defects all of which are interface related metrics in these datasets. The learning from these information can be if there is increase in number of private methods in a certain class, developers need to be extra careful as that is a good indicator of introducing bugs in code. In Summary, we can say

\begin{result}
{Learning from ``Bellwether Project'' is very concise, can be used to extract meaningful and actionable insights. The insight from this study is interface related metrics collected from these 697 projects are good indicator of bugs in the codebase. }
\end{result}

\section{Threats to Validity}
\label{sec:validity}

As with any large scale empirical study, biases can affect the final
results. Therefore, any conclusions made from this work
must be considered with the following issues in mind:

(a) \textit{Evaluation Bias}: 
In  RQ1, RQ2 and RQ3 we have shown the performance of local model, hierarchical bellwether models, default bellwether model and compared them using statistical tests on their performance to make conclusion about presence of generality in SE datasets. While those results are true, that conclusion is scoped by the evaluation metrics we used to write this paper. It is possible that, using other measurements, there may well be a difference in these different kinds of projects. This is a matter that needs to be explored in future research.

(b) \textit{Construct Validity}: At various places in this report, we made engineering decisions about (e.g.) choice of machine learning models, hierarchical clustering algorithm, selecting feature vectors for each project. While those decisions were made using advice from the literature, we acknowledge that other constructs might lead to different conclusions.

(c) \textit{External Validity}: For this study we have relied on data collected by zhang et al.~\cite{zhang15} for their studies. The metrics collected for each project was done using an commercialized tool called ``Understand''. There is a possibility that calculation of metrics or labeling of defective vs non-defective using other tools or methods may result in different outcome. That said, the ``Understand'' is a commercialized tool which has detailed documentation about the metrics calculations and zhang et al. has shared their scripts and process to convert the metrics to usable format and has described the approach to label defects.

We have relied on issues marked as a `bug' or `enhancement' to count bugs or enhancements, and bug or enhancement resolution times. In Github, a bug or enhancement might not be marked in an issue but in commits. There is also a possibility that the team of that project might be using different tag identifiers for bugs and enhancements. To reduce the impact of this problem, we  did take precautionary step to (e.g.,) include various tag identifiers from Cabot et al.~\cite{cabot2015exploring}. We also took precaution to remove any pull merge requests from the commits to remove any extra contributions added to the hero programmer.

(d) \textit{Statistical Validity}: To increase the validity of our results, we applied two statistical tests, bootstrap and the a12. Hence, anytime in this paper we reported that ``X was different from Y'' then that report was based on both an effect size and a statistical significance test.

(e) \textit{Sampling Bias}: Our conclusions are based on the 697 projects collected by zhang et al.~\cite{zhang15} for their studies. It is possible that different initial projects would have lead to different conclusions. That said, this sample is very large so we have some confidence that this sample represents an interesting range of projects. As evidence of that, we note that our sampling bias is less pronounced than other ``Bellwether'' studies since we explored.

\section{Conclusion}
\label{sec:concl}
In this paper, we have proposed a new transfer learning ``bellwether method'' to find ``Bellwether effect'' called ``BUBBLE'' and uses this to find generality in Software Engineering by minimizing conclusion instability thus increasing trust and deducing meaningful insights from them which in turn helps in training and tool developments.

Our results show that regardless size of software engineering datasets we can still find ``Bellwether'' in those datasets. In this study bellwethers were found when studying over 697 software projects. However, conventional methods of Krishna et. al. are computationally very expensive and took long time to discover these bellwethers, e.g.,experimentation took 3 days to find a bellwether project from among the 697 projects.

We showed in this paper, the new algorithm ``BUBBLE'' can find ``Bellwether Project'' order of magnitude faster. We show ``Bellwether method'' proposed by krishna et al. has a computational complexity of $\approx O(N*2)$ while ``BUBBLE'' has a computational complexity of $\approx O((N*2/m))$ where m is the number of cluster at the leaf level of the CF tree and N is the number of projects. ``BUBBLE'' only requiring 1.5 hours to run in comparison to 3 days and requires far less comparison 9080 instead of 393129 required for ``Bellwether method'' proposed by krishna et al.

The study also showed the ``BUBBLE'' is a fast and effective algorithm, which can find exemplary ``Bellwether Projects'' with comparable predictive performance. The figure~\ref{fig:Statistical} shows ``Bellwether Projects'' discovered by ``BUBBLE'' have similar or better predictive performance while comparing with bellwether0, Self\_0 or global2.

We also try to answer the question if learning from too many projects have detrimental effect, the study showed it can have detrimental effect on predictive performance of models also it introduces conclusion instability. We can see local models(a.k.a self tests) although having almost similar predictive performance does not allow us to draw general conclusions and insights for software defect prediction models. Thus it is very unlikely users will be able to trust these models and uses them for training, tool development and other related activities. Contrast to that, using a ``Bellwether Project'' we are able to make general conclusion about software defect prediction models.

Hence, from a  engineering perspective there are two main reasons to use ``BUBBLE'': (a) This is a very fast algorithm to find ``Bellwether project'';  (b) They have comparable predictive performance than its counter parts; and (c) They slow down the pace of conclusion changes and allow users to draw generalized conclusions and meaningful actionable insights .

Finally, we remark that much of the prior work on homogeneous transfer learning have complicated the homogeneous transfer learning process and are computationally expensive. We strongly recommend that when building increasingly complex and expensive  methods, researchers should pause and compare their supposedly more sophisticated method against simpler alternatives. Going forward from this paper, we would recommend that the transfer learning community uses ``BUBBLE'' as a baseline method against which they can test more complex methods.

% \section{Future Work}
% \label{sec:furute}

\section{Acknowledgements}
\label{sec:ack}

\bibliographystyle{IEEEtran}
\bibliography{main} 
\clearpage

% \input{response.tex}

\end{document}

### 2019-10-02 pseudocode/bubble.py

@@ -1,0 +1,12 @@
+def BUBBLE(data):
+  project_features = get_features(data)
+  cluster_tree = BIRCH(project_features)
+  bellwethers = h_bellwether(cluster_tree)
+  for project in test_1:
+    train_2, test_2 = tt_split(data[project])
+    self_clf = LR(train_2)
+    b_clf = find_bellw(project_features[project])
+    self_score = self_clf.predict(test_2)
+    bellwether_score = b_clf.predict(test_2)
+    results += [self_score, bellwether_score]
+  return results

### 2019-10-02 pseudocode/cfs.py

@@ -1,0 +1,16 @@
+def CFS(data):
+  features = []
+  score = -1e-9
+  while True:
+    best_feature = None
+    for feature in range(data.features):
+      features.append(feature)
+      temp_score = calculate_corr(data[F])
+      if temp_score > score:
+        score = temp_score
+        best_feature = features
+      features.pop()
+    features.append(best_feature)
+    if not improve(score):
+      break
+  return features

### 2019-10-02 pseudocode/heirarchical_bellw.py

@@ -1,0 +1,19 @@
+def h_bellwether(cluster_tree):
+  bellwethers = {}
+  def bellwether(list1, list2):
+    for source in list1:
+    clf = LR(source)
+    _list2 = list2.pop(source)
+    for dest in _list2:
+      score[source][dest] = clf.predict(dest)
+    return best(score.key())
+
+  for level in cluster_tree.levels:
+    if level == cluster_tree.max_level:
+      for c in cluster_tree[level].clusters:
+        bellwethers[c] = bellwether(c.proj)
+    else:
+      for c in cluster_tree[level].clusters:
+        _bell = bellwethers[c.child]
+        bellwethers[c] = bellwether(_bell)
+  return bellwethers

### 2019-10-22 manuscript.tex
Updates from Overleaf

@@
                 arrondi=0.1,logo=\bctrombone,% 
-                ombre=true]{{\small ~#1}}}%
+                ombre=true%
+                ]{{\small  ~#1}}}%
 {\end{bclogo}\vspace{2mm}\end{minipage}}
@@
 \begin{document}
-\title{BUBBLE: Scaling Transfer Learning to 100s of Projects}
+\title{  Learning GENERAL Principles \\from Hundreds of     Projects}
 
@@
 % The paper headers
-\markboth{IEEE Transactions on Software Engineering, submitted Oct `19}{Majumder \MakeLowercase{\textit{et al.}}: BUBBLE: Scaling Transfer Learning to 100s of Projects}
+\markboth{IEEE Transactions on Software Engineering, submitted Oct `19}{Majumder \MakeLowercase{\textit{et al.}}: GENERAL: Scaling Transfer Learning to 100s of Projects}
 
@@
 \begin{abstract}
-When one   exemplar project (the ``bellwether'') offers best advice, then it can be used to offer    advice for all other projects.
+
+This paper seeks scalable methods for learning general lessons from hundreds of software projects.
+When one   exemplar project (the ``bellwether'') offers the best advice, it can be used to offer    advice for
+many others.
 These bellwethers can be used to make quality predictions about new projects (even before there is much experience with those new projects).
-Also, such general conclusions   simplifies     software quality policies (since the list of quality problems, and their mitigations, is static);   the cost of  training (since ``best practices'' are now constant); and tool development (since it is clear where it is most cost-effective to buy/build tools to mitigate
+Such general conclusions   simplifies     software quality policies (since the list of quality problems, and their mitigations, is static);   the cost of  training (since ``best practices'' are now constant); and tool development (since it is clear where it is most cost-effective to buy/build tools to mitigate
 for software quality issues).
@@
 But finding that bellwether is a slow process since that needs an  analysis of all pairs of projects. 
-Hence,  we  BUBBLE, a bellwether based on
-  hierarchical clustering. At each level, one bellwether is computed from sibling projects, then promoted up the tree.
-
-   In studies of a corpus of   nearly 700 projects, we find that   the bellwether promoted to the top of the cluster tree is just as good as those found via a traditional bellwether analysis.
-Further, this bellwether was
-found in    1.5 hours (versus 3 days needed for  prior work). 
-  More importantly, BUBBLE   scales to larger problems since it uses a $O(m*(N/m)^2)$ analysis and not the $O(N^2)$ all pairs analysis used by standard bellwether methods.
-
- Accordingly, to   extract software quality rules from a   large corpus of SE, we recommend BUBBLE.
+Hence,  we  propose GENERAL:  a novel bellwether based on
+  hierarchical clustering. At each level within a tree of clusters, one bellwether is computed from sibling projects, then promoted up the tree. 
+This hierarchical method is a scalable approach to learning effective models from very
+large data sets. 
+For example, the defect prediction models found by GENERAL from
+nearly 700 projects were  just as good as those found via  traditional methods.
 
@@
 \begin{IEEEkeywords}
-Transfer Learning, Bellwether, Defect Prediction,Scalable Method. 
+Transfer Learning, Bellwether, Defect Prediction, Scalable Method. 
 \end{IEEEkeywords}}
@@
 \section{Introduction}
-How should we reason about SE quality?  Should we use  general models that hold over many projects? Or must we use an ever changing set of ideas that are   continually adapted to the task at hand? 
+
+%   After a decade of intensive research into automated software analytics, what general principles have we learned?
+While that work has generated specific results about specific projects~\cite{Bird:2015,menzies2013software}, it has failed (so far) to deliver general principles that are demonstrably useful across many projects~\cite{menzies2013guest} (for an example of how {\em more} data can lead to {\em less} general conclusions, see below in {\S}2a).
+
+% Is that the best we can do?
+How should we reason about software quality?
+Should we use  general models that hold over many projects?
+Or must we use an ever-changing set of ideas that are   continually adapted to the task at hand?
 Or does the truth lie somewhere in-between?  
-
-This is an open and important question.
-After a decade of intensive research into automated software analytics, what general principles have we learned?
-While that work has generated specific results about specific projects~\cite{Bird:2015,menzies2013software}, it has failed (so far) to deliver general principles that are demonstrably useful across many projects~\cite{menzies2013guest} (for an example of how {\em more} data can lead to {\em less} general conclusions, see below in {\S}2a).
-
-Is that the best we can do? Are there general principles we can use to guide project management, software standards, education,   tool development, and legislation about software? 
+To say that another way:
+\bi
+\item
+Are there general principles we can use to guide project management, software standards, education,   tool development, and legislation about software? 
+\item
 Or is  software engineering some ``patchwork quilt'' of ideas and methods where it only makes sense to reason about specific, specialized, and small sets of  projects?
-Not to mention, if software was ``patchwork'' of ideas,then that would  there would be no stable conclusions about what constitutes best practice for software engineering (since those best practices would keep changing as we move from project to project).
-As discussed in section~\ref{sec:Motivation}, such conclusion instability would have detrimental implications for {\em generality, trust, insight, training}, and {\em tool development}.
-
-One  explanation for the limited conclusions (so far) from automated analytics is  {\em how much} data we are using for analysis.
+\ei
+If the latter were true then
+ then there would be no stable conclusions about what is best practice for SE   (since those best practices would keep changing as we move from project to project).
+As discussed in section~\ref{sec:Motivation}, such conclusion instability has   detrimental implications for {\em generality, trust, insight, training}, and {\em tool development}.
+
+%One  explanation for the limited conclusions (so far) from automated analytics is  {\em how much} data we are using for analysis.
 A typical software analytics research paper uses less than a few dozen projects  (exceptions: see~\cite{krishna18a, zhao17, agrawal18}).
@@
 
-Reasoning across multiple projects is a complex task.
-Krishna and Keung et al. reports some success in transferring conclusions from one project to another using ``bellwethers''\footnote{Traditionally,
-the bellwether is the  leading sheep of a flock, with a bell on its neck.
-In modern parlance, the bellwether is an 
-  indicator or predictor of something.}
+Finding general lessons across multiple projects is a complex task.
+A new approach, that shows much promise,
+is the ``bellwether'' method
+ for   transferring conclusions between   projects~\cite{krishna2018bellwethers,krishna16a,mensah18z,mensah2017stratification,mensah2017investigating}  (the bellwether is the  leading sheep of a flock, with a bell on its neck).
+That method:
 \bi
-\item Find a  ``bellwether'' project that is exemplar for rest;
+\item Finds a  ``bellwether'' project that is exemplar for the rest;
 \item Draw conclusions from  that project.
 \ei
-This approach has successfully been successfully applied to defect prediction, software effort estimation, bad smell detection, issue lifetime estimation, and configuration optimization. As a 
+This approach has been successfully applied to defect prediction, software effort estimation, bad smell detection, issue lifetime estimation, and configuration optimization. As a 
 method of transferring lessons learned from one project to another, bellwethers have worked better than the Burak filter~\cite{turhan09}, Ma et al.~\cite{Ma2012}'s transfer naive Bayes (TNB); and Nam et al.
@@
 
-But Krishna and Keung et al.'s bellwether methods are very slow.
-When applied to the 679 projects studied here, it took 60 days to find and certify.
-There are many reasons for that including what how the models were certified (20 repeats  with different train/test sets)
-and the complexity of the the analysis procedure (which including fixing class imbalance and feature selection).
-But the major cause of this slow down was that Krishna and Keung's   methods  required an $O(N^2)$ comparison between   $N=697$ projects.
-
-\begin{figure}[!bh]
+In terms of {\em transfer} and {\em lessons learned},  such bellwethers have
+  tremendous practical significance.
+When new projects arrive, then even before there is much experience with those new projects,  lessons learned from other projects can be applied to the new project (just by querying the bellwether),
+ Further, since the bellwether is equivalent to the other models,
+ then when new projects appear, their quality can be evaluated even before there is an extensive experience base within that particular project (just by applying the bellwether).
+ %That is, bellwethers can be queried  to find general lessons about (a)~major quality issues;
+ %or (b)~best practices to avoid quality problems;
+ %or (c)~cost-benefit justifications for buying or building tools can be made stable across a large number 
+ %of projects.
+
+But existing  methods for bellwether transfer are very slow.
+When applied to the 697 projects studied here, they took 60 days of CPU to find and certify the bellwethers.
+There are many reasons for that including how the models were certified (20 repeats  with different train/test sets)
+and the complexity of the analysis procedure (which includes fixing class imbalance and feature selection).
+But the major cause of this slow down was that those   methods  required an $O(N^2)$ comparison between   $N=697$ projects.
+
+This paper reports a novel approach  that dramatically improves on existing bellwether methods.
+ Our GENERAL  method  uses hierarchical clustering model to recursively divide a large number of projects into smaller clusters.
+Starting at the leaves of that tree of clusters, GENERAL finds the    bellwethers within sibling projects.
+That bellwether is then promoted up the tree.
+The output of GENERAL is the project promoted to the top of the tree of clusters.
+
+ This paper evaluates the model built from the project   found by GENERAL. 
+ We will find that  the predictions
+ from this model  are as good, or better,
+ than those found  via ``within'' learning (where models are trained and tested on local data)
+ or ``all-pairs'' learning (where models are found after building models from all pairs of projects).
+   That is
+\begin{quote}
+{\em 
+Learning from many other projects is better than learning just from your own project data.
+}\end{quote}
+GENERAL's clustering methods divide $N$ projects into $m$ groups. In that space,   GENERAL only needs
+to compare $O(m*(N/m)^2)$  projects to find the bellwether. Theoretically and empirically, 
+this means GENERAL will scale up much better than traditional   methods.
+For example:
+\bi
+\item
+This paper applies GENERAL and traditional $O(N^2)$ bellwether to 697 projects.
+GENERAL and the traditional approach terminated in 1.5 and 72 hours (respectively).
+
+\item 
+ Figure~\ref{fig:cost} shows a hypothetical cost comparison in AWS between standard bellwethers and   GENERAL when running for 100 to 1,000,000 projects. Note that GENERAL
+ is inherently more scalable.
+ \ei
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=\linewidth]{figs/cost.png}
+    \caption{Hypothetical cost comparison between GENERAL and default Bellwether.}
+    \label{fig:cost}
+\end{figure} 
+Using GENERAL, we can  explore five research questions:
+
+\begin{itemize}
+        \item 
+            \textbf{RQ1}:  What are the drawbacks of traditional bellwether  methods?
+
+            \begin{RQ}{
+                With hundreds of projects, traditional bellwether methods can discover  source datasets which offer general lessons for all the rest.
+But this traditional approach can require hundreds of hours of computations and will not scale to larger data sets.
+}
+            \end{RQ}
+
+        \item 
+            \textbf{RQ2}: How to tame complexity of bellwether?
+
+             \begin{RQ}{
+                The proposed new  transfer learner called GENERAL uses hierarchical data clustering is order of magnitude faster for discovering a source project both in term of number of comparison and run-time.}
+            \end{RQ}
+
+        \item 
+            \textbf{RQ3}:  Is this faster bellwether effective?
+
+            \begin{RQ}{
+                The new transfer learner GENERAL  is statistically as effective as or sometime even better then the default bellwether which is an exhaustive search and local learning. }
+            \end{RQ}
+
+        \item 
+            \textbf{RQ4}: Does learning from too many projects have detrimental effect?
+
+            \begin{RQ}{
+                Based on the results seen in this study we can see learning from too many projects does have a detrimental effect in-term of predictive power and shows conclusion instability.}
+            \end{RQ}
+
+        \item 
+            \textbf{RQ5}: What exactly did we learn from all those projects?
+
+            \begin{RQ}{
+                Based on the results seen in this study, our best models uses only a fraction of the features in the dataset.
+Looking at the selected metrics, we can conclude that in these 697 projects, code interface issues are the dominant factor on software defects.
+}
+            \end{RQ}
+
+    \end{itemize}
+Overall, the  contributions of this paper are
+\bi
+
+\item \textbf{Hierarchical bellwethers for  transfer learner:} A hierarchical clustering based \textit{bellwether method} algorithm GENERAL to find \textit{bellwether effect} in datasets by finding a source project for the transfer learner.
+The algorithm uses bellwether selection and bellwether promotion (described in section~\ref{GENERAL}) to find bellwether in hierarchical cluster and promote the bellwethers to upper levels in a divide and conquer approach.
+
+\item \textbf{Showing inherent generality in SE}  In this study we discover a source data set for transfer learner from a large number of   projects, hence proving generality in the SE datasets (where some datasets can act as exemplars for the rest of them for defect prediction).
+
+\item \textbf{ Lessons   about software quality that are general
+to hundreds of software projects:}
+  As said above,    in  this sample of  697  projects,  we find that code  interface issues are the dominant factor on software defects.
+
+\item \textbf{ Replication Package:} We have made available a  replication package\footnote{\href{http://tiny.cc/bellwether}{http://tiny.cc/bellwether}} .
+The  replication package consists of all the datasets used in this paper, in addition to mechanisms for computation of other statistical measures.
+
+\ei
+
+The rest of this paper is structured as follows.
+.
+Some background and related work are discussed in section~\ref{sec:literature}.
+Our algorithm GENERAL is described in section~\ref{GENERAL}.
+Data collection and experimental setup are in section~\ref{sec:Data Collection}.
+Followed by evaluation criteria in section~\ref{eval} and performance measures in section~\ref{sec:Measures}.
+The results and answers to the research questions are presented in section~\ref{sec:results}, which is followed by threats to validity in section~\ref{sec:validity}.
+Finally the conclusion is provided in section~\ref{sec:concl}.
+
+\section{Background and Related Work}
+\label{sec:literature}
+
+\subsection{Why Seek Generality?}
+\label{sec:Motivation}
+There are many reasons to seek stable general conclusions in software engineering.
+If our conclusions about best practices for SE projects keep changing, that will be detrimental to generality, trust, insight, training, and tool development.
+
+\textbf{Generality:} Data science for software engineering cannot be called a ``science'' unless it makes general conclusions that hold across  multiple  projects.
+If we cannot offer general rules across a large number of software projects, then it is   difficult to demonstrate such generality.
+
+\textbf{Trust:} Hassan~\cite{Hassan17} cautions that managers lose faith in software analytics if its models keep changing since  the assumptions used to make prior policy decisions may no longer hold.
+
+\textbf{Insight:} Kim et al.~\cite{Kim2016}, say  that the aim of software analytics is to obtain actionable insights that help practitioners accomplish software development goals.
+For Tan et al.~\cite{tan2016defining}, such   insights  are a core deliverable.
+Sawyer et al.
+agree, saying that  insights are the key driver for businesses to invest in data analytics initiatives~\cite{sawyer2013bi}.
+Bird, Zimmermann, et al.~\cite{Bird:2015} say that such  insights occur when users reflect, and react, to the output of a model generated via software analytics.
+But if  new models keep being generated in new projects, then that exhausts the ability of  users to draw insight from  new data.
+
+\textbf{Training:} Another concern is what do we train novice software engineers or newcomers to a project?
+If our models are not stable, then it hard to teach what factors  most influence software quality.
+
+\textbf{Tool development:} Further to the last point--- if we are unsure what factors most influence quality, it is difficult to design and implement and deploy tools that can successfully improve that quality.
+
+\begin{figure}[!b]
     \centering
@@
 
-This paper dramatically improves standard bellwether methods to find general conclusions from 697 projects.
- Our BUBBLE  methods applies divide and conquer  by utilizing a hierarchical clustering model to recursively divide the large number of projects in to smaller clusters.
-Starting at the leaves of that tree of clusters, BUBBLE finds the    bellwethers within sibling projects.
-That bellwether is then promoted up the tree.
-The output of BUBBLE is the project promoted to the top of the tree of clusters.
-
- This paper evaluates the models generated from the bellwether project found by BUBBLE.
-In terms of the traditional measures such as recall, precision, Popt(20) or IFA, there is no significant performance different between BUBBLE's models and those found  via ``within'' learning (where quality models are learned just from data within a particular project) and ``all-pairs'' learning (where the bellwether is selected in the traditional way via a laborious $O(N^2)$ analysis).
-
-In terms of {\em transfer} and {\em lessons learned},  this result has tremendous practical significance.
-When new projects arrive, then even before there is much experience with those tasks,  lessons learned from other projects can be applied to the new project (just by querying the bellwether),
-
-While {\em many models} are generated via ``within'' learning, bellwethers only produce one model. And since the bellwether is equivalent to the other models,
- then when new projects appear, their quality cn be evalauted even before there is an extensive experience base with that particular project (just be applying the bellwether learend from r
- that means that general lessons about (a)~major quality issues;
- or (b)~best practices to avoid quality problems;
- or (c)~cost-benefit justifications for buying or building tools can be made stable across these 697 projects. Another advantage of the bellwethers
-
- Also, BUBBLE finds and certifies those general lessons much faster than traditional bellwether methods (30 hours vs 60 days).
-
- That is, lessons learned from BUBBLE's bellwether can be said to be general across multiple projects.
-
- The BUBBLE approach peformed better than ``within'' and similarly to ``all-pairs''. That is
- \bi
- \item
-Learning from many other projects is bettter than learning just from your own project data;
-\item
-Taking the extra time required to learn via ``all-pairs'' is not necessary. This is important since BUBBLE runs mich faster than all-pairs (30 hours vs 60 days). 
-\ei
-More importantly, since it bases its conclusions from one exemplar bellwether project, BUBBLE can offer conclusions general to a very large set of projects. 
-By reasoning over a tree of clusters with a branching factor of $b$, BUBBLE only requires $O(\log_bN)$  comparisons.
-This means BUBBLE will scale up better than traditional bellwether methods that need $O(N^2)$ comparisons.
-Here, we show results that are general to hundres of projects.
-In the future, our research goal is to find general conclusions across 10,000 projects, or perhaps even more.
-
-The contributions of this paper are
-\bi
-
-\item \textbf{Showing inherent generality in SE} Since we show  offer a proof of generality in SE data sets via transfer learning.
-In this study we discover a source data set for transfer learner from a large number of potential projects, hence proving generality in the SE datasets where some dataset can act as examples for rest of them for defect prediction.
-
-\item \textbf{An very fast algorithm to test generality in datasets:} A vary fast algorithm to test generality in other datasets with only minor changes.
-
-\item \textbf{Hierarchical bellwethers as a transfer learner:} A hierarchical clustering based \textit{bellwether method} algorithm ``BUBBLE'' to find \textit{bellwether effect} in datasets by finding a source project for the transfer learner.
-The algorithm uses bellwether selection and bellwether promotion (described in section~\ref{BUBBLE}) to find bellwether in hierarchical cluster and promote the bellwethers to upper levels in a divide and conquer approach.
-
-\item \textbf{Rich Replication Package:} We have made available a rich replication package\footnote{\href{http://tiny.cc/bellwether}{http://tiny.cc/bellwether}} .
-The  replication package consists of all the datasets used in this paper, in addition to mechanisms for computation of other statistical measures.
-
-\item \textbf{A new algorithm for transferring data from other projects, unlike prior works it can scale to large datasets:} Unlike previous studies for transfer learning, this method is order of magnitude faster for selecting a source project for transfer learning.
-Figure~\ref{fig:cost} shows a hypothetical cost comparison in AWS between default bellwether and BUBBLE when running for 100 to 1,000,000 projects based on number of comparison required.
-
-\item \textbf{Demo a fast bellwether method which run hours is comparable to a robust method which runs in months:}
-
-\ei
-
-to the best of out knowledge bell/bubble is new high-water mark in qualitative empirical SE. XXX
-
-This new transfer learning approach lets us ask and answer the following questions:
-
-\begin{itemize}
-        \item 
-            \textbf{RQ1}:  Can we confirm bellwether on large datasets??
-
-            \begin{RQ}{
-                Default \textit{bellwether method} can find \textit{bellwether effect} in large datasets to discover source datasets for transfer learning.
-But this \textit{bellwether method} is very expensive making it infeasible for large datasets.}
-            \end{RQ}
-
-        \item 
-            \textbf{RQ2}: How to tame complexity of bellwether?
-
-             \begin{RQ}{
-                The proposed new \textit{transfer learner} ``BUBBLE'', using hierarchical data clustering is order of magnitude faster for discovering a source project both in term of number of comparison and run-time.}
-            \end{RQ}
-        \\   
-        \\
-        \\
-        \\
-        \\
-        \\
-        \item 
-            \textbf{RQ3}:  Is faster bellwether effective?
-
-            \begin{RQ}{
-                The new transfer learner ``BUBBLE'' is statistically as effective as or sometime even better then the default bellwether which is an exhaustive search and local learning. }
-            \end{RQ}
-
-        \item 
-            \textbf{RQ4}: Does learning from too many projects has detrimental effect?
-
-            \begin{RQ}{
-                Based on the results seen in this study we can see learning from too many projects do have detrimental effect in-term of predictive power and shows conclusion instability.}
-            \end{RQ}
-
-        \item 
-            \textbf{RQ5}: What did we learn?
-
-            \begin{RQ}{
-                Based on the results seen in this study using Feature Subset Selector and Logistic Regression, the ``Bellwether Project'' learned only a 12\% of the features(mostly interface related metrics) are important for predicting defects.}
-            \end{RQ}
-
-    \end{itemize}
-
-\section{Background and Related Work}
-\label{sec:literature}
-
-\subsection{Motivation}
-\label{sec:Motivation}
-There are many reasons to seek stable general conclusions in software engineering.
-If our conclusions about best practices for SE projects keep changing, that will be detrimental to generality, trust, insight, training, and tool development.
-
-\textbf{Generality:} Data science for software engineering cannot be called a ``science'' unless it makes general conclusions that hold across  multiple  projects.
-If we cannot offer general rules across a large number of software projects, then it is   difficult to demonstrate such generality.
-
-\textbf{Trust:} Hassan~\cite{Hassan17} cautions that managers lose faith in software analytics if its models keep changing since  the assumptions used to make prior policy decisions may no longer hold.
-
-\textbf{Insight:} Kim et al.~\cite{Kim2016}, say  that the aim of software analytics is to obtain actionable insights that help practitioners accomplish software development goals.
-For Tan et al.~\cite{tan2016defining}, such   insights  are a core deliverable.
-Sawyer et al.
-agrees, saying that  insights are the key driver for businesses to invest in data analytics initiatives~\cite{sawyer2013bi}.
-Bird, Zimmermann, et al.~\cite{Bird:2015} say that such  insights occur when users reflect, and react, to the output of a model generated via software analytics.
-But if  new models keep being generated in new projects, then that exhausts the ability of  users to draw insight from  new data.
-
-\textbf{Training:} Another concern is what do we train novice software engineers or newcomers to a project?
-If our models are not stable, then it hard to teach what factors  most influence software quality.
-
-\textbf{Tool development:} Further to the last point--- if we are unsure what factors most influence quality, it is difficult to design and implement and deploy tools that can successfully improve that quality.
-
-\begin{figure}[!ht]
-    \centering
-    \includegraphics[width=\linewidth]{figs/cost.png}
-    \caption{Hypothetical cost comparison between BUBBLE and default Bellwether.}
-    \label{fig:cost}
-\end{figure}
-
-Petersen and Wohlin~\cite{Petersen2009} argue that for empirical SE, context matters.That is, they would predict that one model  will NOT  cover all  projects and that tools that report  generality  over many software projects need to also know the {\em communities} within which those conclusions   apply.
-Hence, this work divides into (a)~automated methods for finding sets of projects in the same {\em community}; and (b)~within each {\em community}, find the model what works best.
+\subsection{Why Shun Generality?}
+Just to balance the above argument,
+we add that   sometimes it is possible to learn from
+{\em too much data}.
+Petersen and Wohlin~\cite{Petersen2009} argue that for empirical SE, context matters.
+That is, they would predict that one model  will \underline{not}  cover all  projects and that tools that report  generality  over many software projects need to also know the {\em communities} within which those conclusions   apply.
+Hence, this work divides into (a)~automated methods for finding sets of projects in the same {\em community}; and (b)~within each {\em community}, find the model that works best.
 
@@
 After about 2 levels, the \textcolor{ao(english)}{{\bf GREEN}} curve's growth stops and we would say that community size here was around cluster size in level 1.
-In this case, while we could not offer a single model that cover {\em all} of SE, we could offer a handful of models, each of which would be relevant to project clusters in that level.
+In this case, while we could not offer a single model that covers {\em all} of SE, we could offer a handful of models, each of which would be relevant to project clusters at that level.
 Accordingly, we would say that there are many cases where  wisdom from prior projects can be readily applied to guide future projects and (b)~the generality issues raised are not be so pressing.
@@
 Here, we see that (hypothetically)  learning from more projects makes quality predictions worse which means the our 10,000 projects break up into ``communities'' of size one.
-In this case,  (a)~principles about what is ``best practice'' for different software projects would be constantly change (whenever we jump from small community to small community); and (b)~the generality issues would be become open and urgent concerns for the SE analytics community.
-
-\subsection{Related Work}
+In this case,  (a)~principles about what is ``best practice'' for different software projects would be constantly changing (whenever we jump from small community to small community); and (b)~the generality issues would be becoming open and urgent concerns for the SE analytics community.
+
+In summary, the above two sections lead to our  research question {\bf  RQ4}:
+does learning from too many projects have detrimental effects. Later in this
+paper, we will return to this issue.
+
+\subsection{Why Transfer Knowledge?}
 \label{sec:related}
@@
 Menzies et al.
-showed in their paper about local vs global learning in defect prediction and effort estimation domain that using a rule based learner locality based learning was much effective then rules learned from the global dataset.
+showed in their paper about local vs global learning in defect prediction and effort estimation domain that using a rule based learner locality based learning was much effective than rules learned from the global dataset.
 While Herbold et al.~\cite{herbold2017global} in their study regarding global vs local model for cross-project defect prediction showed evident proof that local models make only a minor difference in comparison to global models.
-While local can cause conclusion instabilities, global models can miss details which is specific to certain dataset.
+While local can cause conclusion instabilities, global models can miss details which are specific to a certain dataset.
 So in this study, we review the evidence that if it is useful to explore more than just the local data.
@@
 
-The good news is that, using software analytics, we can correct the above misconceptions.
+The good news is that using software analytics, we can correct the above misconceptions.
 If data mining shows that doing  XYZ is bug prone, then we could  guide developers to avoid XYZ.
@@
 
-It turns out that developers are not the only ones confused about how various factors influence software projects.
-Much recent research calls into question  the``established widoms'' of SE field.
+It turns out that developers are not the only one's confused about how various factors influence software projects.
+Much recent research calls into question  the ``established wisdoms'' of SE field.
 For example, here is a list of recent conclusions that contradict prior conclusions:
@@
 \ei
-
 Note that if the reader disputes any of the above, then we ask how would you challenge the items on this list?
@@
 
-This fuels the art of moving data and/or lessons learned from one project or another is Transfer Learning.
-This is when there is insufficient data to apply data miners to learn defect predictors, transfer learning can be used to transfer lessons learned from other source projects S to the target project T .
+\subsection{ How to  Transfer Knowledge}
+This     art of moving data and/or lessons learned from one project or another is {\em Transfer Learning}.
+When there is insufficient current data to apply data miners to learn defect predictors, transfer learning can be used to transfer lessons learned from other source projects S to the target project T .
 
@@
 Turhan's initial experimental results were also very negative: given data from 10 projects, training on S = 9 source projects and testing on T = 1 target projects resulted in alarmingly high false positive rates (60\% or more).
+
 Subsequent research realized that data had to be carefully sub-sampled and possibly transformed before quality predictors from one source are applied to a target project.
-Transfer learning can be have two variants -
-
-(a) \textbf{Homogeneous Transfer Learning:} This kind of transfer learning operates on source and target data that contain the same attributes.
-
-(b) \textbf{Heterogeneous Transfer Learning:} This type of transfer learning operates on source and target data that contain the different attributes.
-
-Another way of to divide transfer learning is the approach that is followed. There are  2 approaches that is frequently used in many research  -
-
-(a) \textbf{Similarity Based Approach:} In this approach we can transfer some/all subset of the rows or columns of data from source to target.
+Successful transfer learning can have two variants -
+
+\bi
+\item
+\textbf{Homogeneous Transfer Learning:} This kind of transfer learning operates on source and target data that contain the same attributes.
+\item    
+ \textbf{Heterogeneous Transfer Learning:} This type of transfer learning operates on source and target data that contain the different attributes.
+\ei
+Another way to divide transfer learning is the approach that is followed.
+There are  2 approaches that are frequently used in many research: {\bf similarity-based approaches} and {\bf dimensional transforms}.
+
+ \textbf{Similarity-Based Approaches:} In this approach we can transfer some/all subset of the rows or columns of data from source to target.
 For example, the Burak filter~\cite{turhan09} builds its training sets by finding the k = 10 nearest code modules in S for every $ t \in T $.
@@
 
-(b) \textbf{Dimensionality Transformation Based Approach:} In this approach we manipulate the raw source data until it matches the target.
+\textbf{Dimensional Transformation:} In this approach we manipulate the raw source data until it matches the target.
 An initial attempt on performing transfer learning with Dimensionality transform was undertaken by Ma et al.~\cite{Ma2012} with an algorithm called transfer naive Bayes (TNB).
@@
 In their paper Krishna et al.
-performs experiment with communities of 3, 5 and 10 projects in each, and shows that bellwethers are not rare, their prediction performance is better than local learning, they do fairly well when compared with State of the Art transfer learning methods discussed above and with selection of bellwether shows a consistency for choice of source dataset for transfer learning.
-This motivated us to use ``Bellwether'' as our choice of method for transfer learning to search for generality in SE datasets.
-But as per Krishna et al.
-in order to find bellwether we need to do a $ N*(N-1) $ comparison which is order of $ N^2 $ (N being the number of projects in community).
-This indeed a very expensive computation.
-This motivated our study to find generality in SE datasets using a faster Bellwether method.
-
-Include details about BIRCH and effect of clustering and talk about divide and conquer.
-
-\section{BUBBLE}
-\label{BUBBLE}
+performed experiment with communities of 3, 5 and 10 projects in each, and showed that (a)~bellwethers are not rare, (b)~their prediction performance is better than local learning, and (c)~they do fairly well when compared with
+the state-of-the-art transfer learning methods discussed above.
+%and with selection of bellwether shows a consistency for choice of source dataset for transfer learning. 
+This motivated us to use  bellwethers as our choice of method for transfer learning to search for generality in SE datasets.
+
+That said,  Krishna et al. warn that in order to find bellwether we need to do a $ N*(N-1) $ comparison; i.e. standard bellwethers
+have complexity $ O(N^2) $ (N being the number of projects in community).
+
+\begin{equation}
+\label{eq:bellwether}
+    \mathit{Bellwether\; complexity } = O(N^2)
+\end{equation}
+
+The goal of this paper is to find ways to reduce the Equation~\ref{eq:bellwether} complexity.
+
+\section{About GENERAL}\label{sec:Metric Extraction}
+\label{GENERAL}
+
+% \begin{figure}[!t]
+%     \small
+%      %\begin{lstlisting}[mathescape,linewidth=7.5cm,frame=none,numbers=right]
+%     ~~~~~~\inputminted[numbersep=1pt, linenos=true, fontsize=\scriptsize]{python}{pseudocode/bubble.py}
+%     %\vspace{-0.2cm}
+%     \caption{Pseudo-code of GENERAL Experiment}
+%     \label{fig:GAP_pseudocode} 
+%     %\vspace{-0.3cm}
+% \end{figure}
+
+% \begin{figure}[!t]
+%      %\begin{lstlisting}[mathescape,linewidth=7.5cm,frame=none,numbers=right]
+%         \begin{minipage}{\linewidth}
+%             \inputminted[numbersep=2pt, linenos=true, fontsize=\scriptsize]{python}{pseudocode/heirarchical_bellw.py}
+%         \end{minipage}
+%     %\vspace{-0.2cm}
+%     \caption{Pseudo-code of Hierarchical Bellwether}
+%     \label{fig:GAP_pseudocode} 
+%     %\vspace{-0.3cm}
+% \end{figure}
+
+ Our proposed improvement to bellwethers is called GENERAL.
+The core intuition of this new approach is that if many projects are similar, then we do not need to run comparisons between all pairs of projects.
+When such similar projects exist, if may suffice to just compare a small number of   representative examples.
+
+ Accordingly, the rest of this paper performs the following experiment:
+ \be
+ \item Sumamrize the projects via {\bf feature extraction} (see \S\ref{sec:fx}).
+ \item Using some clustering algorithm, group all our data into sets of similar projects.
+ \item The groups are themselves grouped into super-groups, then super-super-groups, etc to form a tree.  This step requires a {\bf hierarchical clustering} algorithm (see \S\ref{sec:hc}).
+ \item Starting at the leaves of that tree,   the best project is discovered by training on each project, and test its model
+ on all others in that leaf cluster.
+ This step needs
+  a {\bf data mining} algorithm to generate models (see \S\ref{sec:dm})
+ and  a comparison method to {\bf select the best model} (see \S\ref{sec:best}).
+ \item  Once bellwether from each group is  pushed up the tree, then steps 4,5 are repeated,
+ recursively.
+ \item The project pushed to the root of the tree is then used as  the bellwether for all the projects.
+ \ee
+ Note that when the clustering algorithm divides the data into $m$ clusters, then the complexity of this method (which we call GENERAL) is: 
+ \begin{equation}
+\label{eq:GENERAL}
+    {GENERAL\; complexity } =  O(m*(N/m)^2)
+\end{equation}
+ \fig{cost} contrasts the computational cost of Equation~\ref{eq:GENERAL} with Equation~\ref{eq:bellwether}   
+ (and that figure assumes $m=20$, which is the devision constant we used in these experiments-- see below.).
+ As seen in that figure,  the $O(m*(N/m)^2)$ analysis is inherently far more scalable than the $O(N^2)$ analysis  required by standard bellwether.
+
+To operationalize steps 1,2,3,4,5 listed above, we need to make some lower-level engineering decisions. The rest of this section documents those decisions.
+
+\subsection{Feature Extraction}\label{sec:fx}
+
+Prior to anything else, we must summarize our projects.  Xenos \cite{Xenos} distinguishes
+between {\em product metrics} (e.g.  counts of lines
+of code );  and  {\em process metrics} 
+about the  development process (e.g.    number of file revisions).
+Using the   Understand tool~\cite{visualize},
+we   calculated 21 product and 5 process metrics to build     defect prediction models
+ (see Table~\ref{tbl:metric}).
+ These product  metrics are
+ calculated from snapshots from every 6 months of the data.
+The process metrics are computed using the change history in the six-months period before the split date via manual collection of data using scripts.
 
@@
 \centering
-    \includegraphics[width=\linewidth]{figs/BUBBLE.png}
-    \caption{BUBBLE algoroithm.}
-    \label{fig:BUBBLE}
+{\small \renewcommand{\baselinestretch}{0.7}
+\begin{tabular}{rrl}
+    \textbf{Language} & \textbf{Projects} & \\
+    Java & 290 &\rule{41.6pt}{8pt} \\
+    CPP & 241 &\rule{34.5pt}{8pt} \\
+    C & 116 &\rule{16.6pt}{8pt} \\
+    CS & 42 &\rule{6.3pt}{8pt} \\
+    Pascal & 8 &\rule{1.1pt}{8pt} \\
+     & 
+\end{tabular}}
+\caption{Distribution of projects depending on languages.
+Many  projects use combinations of languages to
+achieve their results. Here, we show majority language used in the project.}
+\label{fig:lang_projects}
 \end{figure}
 
-{\small 
-{\small 
-\begin{figure}[]
-    \small
-     %\begin{lstlisting}[mathescape,linewidth=7.5cm,frame=none,numbers=right]
-    \inputminted[numbersep=1pt, linenos=true, fontsize=\small]{python}{pseudocode/bubble.py}
-    \vspace{-0.2cm}
-    \caption{Pseudo-code of BUBBLE Experiment}
-    \label{fig:GAP_pseudocode} 
-    \vspace{-0.3cm}
-\end{figure}
-}
-}
-{\small 
-{\small 
-\begin{figure}[]
-     %\begin{lstlisting}[mathescape,linewidth=7.5cm,frame=none,numbers=right]
-        \begin{minipage}{\linewidth}
-            \inputminted[numbersep=2pt, linenos=true, fontsize=\small]{python}{pseudocode/heirarchical_bellw.py}
-        \end{minipage}
-    \vspace{-0.2cm}
-    \caption{Pseudo-code of Hierarchical Bellwether}
-    \label{fig:GAP_pseudocode} 
-    \vspace{-0.3cm}
-\end{figure}
-}
-}
-In this study we introduce BUBBLE, which is a transfer learning method utilizing \textit{bellwether method} algorithm by combining the components described in section~\ref{sec:Experimental}.
-This creates a fast way to find \textit{bellwether effect} in large datasets.
-BUBBLE works in 6 stages -
-
-    (1) \textbf{Feature Extraction:} In this stage the whole dataset is used to extract feature from each projects.
-This is done using the FSS algorithm as shown in~\ref{subsec:FSS}.
-Here each project is sent to the FSS and the FSS returns most suitable features for building models, we do this for every project and that information as a vector (i.e.
-a vector or length equal to total number of features, where 1 represents a feature being selected ,0 is the other way around) that represents each project.
-By performing this we have a vector representation of each project in the dataset.
-BUBBLE uses this information to create the hierarchical clusters to find the communities.
-We perceive this is a good representation of community, as in this work we try to find community which has similar information distribution according to the attributes.
-Thus 2 projects with similar features selected have much higher chance of building similar models.
-
-    (2) \textbf{Cluster Creation:} After the feature extraction has been done, the data is sent to a modified BIRCH algorithm.
-The algorithm requires a branching factor (i.e.
-Maximum number of CF sub-clusters in each node) and threshold value (i.e.
-when to form a new cluster based on radius).
-For this experiment we have set the branching factor as 20 and threshold value as 0.5.
-Using this version of BIRCH algorithm we build the hierarchical cluster, while storing all necessary details about the cluster like parent-child node, data points, level information etc.
-This stage returns a Clustering Feature Tree (CF Tree) with all those information, which is passed to the next phase of experiment.
-
-    (3) \textbf{Bellwether selection phase 1:} The CF Tree from the last phase is passed to the hierarchical bellwether.
-In this phase we use \textit{bellwether method} to identify bellwether at the leaf level.
-Using the CF Tree, we identify the clusters at the leaf level where each cluster represents the smallest community produced by the BIRCH algorithm in the last phase.
-Here we use the default ``Bellwether'' to perform a $ N*(N-1) $ comparison at each cluster.Here we select each project in the cluster one by one as a source dataset for transfer learning apply SMOTE as mentioned in sec~\ref{subsec:SMOTE} to handle any data imbalance and then use the FSS algorithm to get rid of any unnecessary attributes as mentioned in sec~\ref{subsec:FSS}.
-This informative and balanced dataset is used to build a LR model as mentioned in sec~\ref{subsec:LR} and we measure the performance of all other projects in the community(cluster).
-The performance measures that are used are mentioned in sec~\ref{sec:Measures}.
-To find the bellwether in each community we use cdom function to find the best source dataset among each cluster considering all performance measures.
-This phase returns a bellwether for each cluster at the leaf level of the CF Tree.
-
-    (4) \textbf{Bellwether promotion:} In this phase of the algorithm is an iterative process, here we receive the selected bellwethers from the child clusters of each cluster in the level.
-This is called the bellwether promotion.
-Here each parent cluster instead of being represented by all projects within them, they are represented by only the bellwethers in them.
-
-    (5) \textbf{Bellwether selection phase 2:} In this phase instead of finding a bellwether for each cluster at the level by performing a $ N*(N-1) $ comparison, we select the projects which represented as bellwether at the child nodes and then try to find a bellwether among them.
-So at each cluster at the level we perform a a $ M*(M-1) $ comparison at each cluster where M is the selected bellwether from child clusters.
-This creates a order of magnitude faster \textbf{bellwether method}.
-This is again an iterative process, and the end of all the iterations, we will have a bellwether at each cluster at every level.
-
-    (6) \textbf{Bellwether Prediction:} This is the transfer learning phase, when a new project is to evaluated we will use the FSS algorithm to get its features, then use the feature vectors to identify which cluster it belongs and use that cluster's bellwether as the transfer learning model.
-
-To report the finding and results of this study without any bias, we repeat the experiment 20 times by dividing the dataset randomly into train\_1 and test\_1 as a 90-10 split, the projects in train\_1 was used to find the bellwether in each cluster in the CF Tree, and then each project in test\_1 was divide into train\_2 and test\_2 split.
-We trained a LR model using train\_2 for each project and tested on test\_2, this is represented as self test in this study.
-We also used the predict stage of the BUBBLE to identify bellwether for each project in test\_1 and tested the performance on test\_2.
-
-\section{Data and Experimental Setup}
-\label{sec:Data Collection}
-
-\subsection{Data Collection}
-\label{sec:data}
-
-To perform our experiments we choose to work with defect prediction datasets.
-We use data collected by zhang et al.~\cite{zhang15}.
-The original data was initially collected by Mockus et al.~\cite{mockus2009amassing} from SourceForge and GoogleCode.
-The dataset contains the full history of about 154K projects that are hosted on SourceForge and 81K projects that are hosted on GoogleCode to the date they were collected.
-In the original dataset each file contained the revision history and commit logs linked using a unique identified.
-Although there were 235K projects in the original database, we know from previous literature surveys and experience there were many trivial and non-software development projects.
-zhang et al.
-cleaned the dataset using 5 different criteria which resulted in 1385 projects being selected in the final datasets \footnote{\href{http://tiny.cc/bellwether_data}{http://tiny.cc/bellwether\_data}}.
-As part of this experiment we also included few filters to select a subset of 1385 projects, which are useful for our experiment.
-This eventually gave us a dataset of 697 projects.
-The filters applied to filter out trivial projects are -
-
-\bi
-
-    \item \textbf{Programming Languages:} Filtering Out Projects by Programming Languages(only object-oriented i.e *.c, *.cpp, *.cxx, *.cc, *.cs, *.java, and *.pas).
-This was done as the dataset was collected using a commercial tool, called Understand~\cite{visualize}(which supports the object oriented programming languages) , to compute code metrics.
-
-    \item \textbf{Projects with a Small Number of Commits:} zhang et al. removed any projects with less than 32 commits(25 \% quantile of the number of commits as the threshold).
-
-    \item \textbf{Projects with Lifespan Less Than One Year:} zhang et al. filtered out any  projects with a lifespan less than one year.
-
-    \item \textbf{Projects with Limited Defect Data:} zhang et al.
-in their study counted the number of fix-inducing and non-fixing commits from a one-year period and removed any projects with 75 \% quantile of the number of fix-inducing and non-fixing commits.
-
-    \item \textbf{Projects Without Fix-Inducing Commits:} zhang et al.
-filtered out projects that have no fix-inducing commits during six months as abnormal projects, as projects in defect prediction studies need to contain both defective and non-defective commits.
-
-    \item \textbf{Projects with less than 50 rows:} We removed any project with less than 50 rows as they are too small to build a meaningful predictor.
-
-\ei
-
-\begin{figure}
+\begin{figure*}[!h]
     \centering
-    \includegraphics[width=\linewidth]{figs/meta.png}
-    \caption{Two hypothetical results about how training set size might effect the efficacy of quality prediction for software projects.}
+    \includegraphics[width=\linewidth]{figs/meta.pdf}
+    \caption{Distribution of projects depending on Defect Percentage, Data set Size, Lines of Code and Number of Files.}
     \label{fig:meta}
-\end{figure}
-
-Along with above filtering criteria, there were few projects which didn't have enough fix-inducing vs non-fixing data points to to create a stratified k=5 fold cross-validation and we removed those projects from the final datasets.
-These criteria culled 99\% of projects by zhang et al.
-and culled 54\% of the remaining by our criteria, thus resulted in 697 projects in the final dataset.
-
-From these selected projects, the data was labeled using issue tracking system and commit messages.
-If a project used issue tracking system for maintaining issue/defect history the data was labeled using that.
-But as per zhang et al.
-42\% of the projects didn't not used issue tracking systems.
-For these projects labels were created analyzing commit messages by tagging them as fix-inducing commit if commit message matches the following regular expression
-
-\begin{center}
-\textit{(bug $\mid$ fix $\mid$ error $\mid$ issue $\mid$ crash $\mid$ problem $\mid$ fail $\mid$ defect $\mid$ patch)}
-\end{center}
-
-\subsection{Metric Extraction}
-\label{sec:Metric Extraction}
-
-For building any defect predictor we rely on software metrics.
-Software metrics can be categorized into 3 types according to Xenos \cite{Xenos} distinguishes software metrics as  follows (a) {\em Product metrics} are metrics that are directly related to the product itself, such as code statements, delivered executable, manuals, and strive to measure product quality, or attributes of the product that can be related to product quality.
-(b) {\em Process metrics} focus on the process of software development and measure process characteristics, aiming to detect problems or to push forward successful practices.
-Lastly, (c) {\em personnel metrics} (a.k.a.
-{\em resource metrics}) are those related to the resources required for software development and their performance.
-The capability, experience of each programmer and communication among all the programmers are related to product quality \cite{wolf2009predicting,de2004sometimes,cataldo2013coordination,cataldo2007coordination}.
-zhang et al.
-selected and calculated 21 product and 5 process metrics to build their universal defect prediction model, we will be using the same set of metrics for our study.
-The product metrics are computed by the Understand tool~\cite{visualize} using the files from the snapshot on the split date of 6 months.
-The process metrics are computed using the change history in the six-months period before the split date my manual collection of data using scripts.
-The metrics used in this study are described in table~\ref{tbl:metric}.
-
-{\small 
-\begin{table}[]
-\centering
-\caption{List of software metrics used in this study}
-\label{tbl:metric}
+\end{figure*}
+
+Understand is a widely used tool in software analytics~\cite{Zhang16aa,gizas2012comparative,fontana2011experience,orru2015curated,pattison2008talk,malloy2002testing}.
+ The advantage of using this tool is that much of the tooling needed for this kind of large scale analysis is already available.
+On the other hand, it also means that we can only reason about the features that Understand can report-- which could be  a threat to the validity of the conclusions reached.
+As shown below, the Table~\ref{tbl:metric} metrics were shown to be effective for our task.
+Nevertheless, in future work, this study needs to be repeated whenever new tools allow for the widespread collection of different kinds of features.
+
+\begin{table}[!t]
+
 \scriptsize
@@
 \hline
-\multicolumn{1}{|l|}{Metric}        & \multicolumn{1}{l|}{Metric level} & Metric Name & Metric Description             \\ \hline
+\multicolumn{1}{|l|}{\textbf{Metric}}        & \multicolumn{1}{l|}{\textbf{Metric level}} & \textbf{Metric Name} &\textbf{ Metric Description}             \\ \hline
 \multirow{21}{*}{Product   } & \multirow{6}{*}{File}             & LOC         & Lines of Code                  \\ \cline{3-4} 
@@
 \end{tabular}
+\caption{List of software metrics used in this study}
+\label{tbl:metric}
 \end{table}
-}
+\subsection{Hierarchical Clustering}\label{sec:hc}
+
+ After data collection, comes  the  hierarchical clustering needed for step 2.
+For this purpose, we followed the
+advice from the scikit.learn~\cite{scikit-learn} documentation
+that recommends the  Balanced Iterative Reducing and Clustering using Hierarchies  (BIRCH) algorithm for hierarchical
+clustering for large sample datasets that might
+contain spurious outliers~\cite{zhang1996birch}. 
+BIRCH has the ability to incrementally and dynamically cluster incoming, multi-dimensional data in an attempt to maintain  best quality clustering.
+BIRCH also has the ability to identify data points that are not part of the underlying pattern (so it can effectively identifying and avoid outliers).
+ Google Scholar reports that  the original  paper proposing BIRCH has been cited over 5,400 times.
+For this experiment we have set BIRCH's branching factor as 20 and  threshold  value  as  0.5.
+
+\subsection{Data Mining}\label{sec:dm}
+The bellwether analysis of step3 requires a working data miner. Three requirements for that learner are:
+\bi
+\item Since it will be called thousands of times, it must run quickly. Hence, we did not use any methods
+that require  neural nets or ensembles. 
+\item Since some projects have relatively few defects, before learning, 
+some {\em over-sampling} is required to increase the number of defective examples in the training sets
+\item Since one of our research questions ({\bf RQ5}) asks ``what did we learn from all these projects'', we needed a learning method that generate succinct models.
+According, we used {\em feature selection}  to check which subset of Table~\ref{tbl:metric}
+mattered the most.
+\ei
+According, this study used:
+\bi
+\item
+The logistic regression learner 
+(since it is relatively fast);
+\item
+The SMOTE class imbalance correction algorithm~\cite{Chawla2002},  which we run  on the training data\footnote{  The SMOTE Synthetic Minority Over-Sampling Technique algorithms sub-samples the majority class (i.e., deletes examples) while over-sampling the minority class until all classes have the same frequency.
+To over-sample, new examples are synthesized extrapolating between known examples (of the minority class) and its $k$ nearest neighbors.
+ While it is useful
+  to artificially boost the number of target examples
+in the training data~\cite{Chawla2002,Pelayo2007,mensah2017investigating}, it is a methodological error to also change the distributions in   the test data~\cite{agrawal17}. Hence, for our work,
+we take care to {\em only} resample the training data.};
+\item
+and Hall's
+CFS feature selector~\cite{hall1999correlation}\footnote{CFS  is based on the heuristic
+that ``good feature subsets contain features highly correlated with the classification, yet uncorrelated to each other''. Using this heuristic,
+CFS performs a best-first search  to discover interesting sets of features.
+Each subset is  scored via
+$\mathit{merit}_s = k\overbar{r_{\mathit{cf}}}/\sqrt{k+k(k-1)\overbar{r_{\mathit{ff}}}}$
+where
+$\mathit{merit}_s$ is the value of some subset $s$ of the
+features containing $k$ features; 
+$r_{\mathit{cf}}$ is a score describing the connection of that feature
+set to the class;
+and $r_{\mathit{ff}}$ is the mean score of the feature to feature
+connection between the items in $s$.
+Note that for this to be maximal, $r_{\mathit{cf}}$  must be large
+and $r_{\mathit{ff}}$ must be small. That is, features have to connect
+more to the class than each other.}. 
+\ei
+We selected  use these tools
+since   in the domain of software analytics,
+the use of LR (logistic regression) and SMOTE
+is endorsed by recent ICSE papers~\cite{Rahman:2013,ghotra2015revisiting,agrawal17}.
+As to CFS, we found that without it, our recalls were very low and we could not identify which metrics mattered the most.
+Also,   extensive studies have found that CFS more useful than many other feature subset selection methods such as  PCA or InfoGain or RELIEF~\cite{hall1999correlation}.
+
+\subsection{Select the Best Model}\label{sec:best}
+As discussed below, the defect models assessed in these experiments
+
+To find the bellwether, our method must compare many models and select the best one.
+As discussed below, we score model performance according to five goals:
+\bi
+\item
+Maximize
+recall and precision and popt(20);
+\item
+While minimizing  false alarms  and
+ifa\_auc.
+\ei
+(For definitions and details for these criteria, and why we selected them, see \S\ref{sec:Measures}.)
+
+In such   {\em multi-objective} problems, one model is better than another if it
+ satisfies a ``domination predicate''.
+ We use the Zitler indicator dominance
+ predictor~\cite{zit02} to select our bellwether (since this is known to select better models
+ for 5-goal optimization~\cite{Sayyad:2013,Sayyad:2013:SPL}).
+This predicate favors model
+  $y$ over $x$  model if $x$ ``losses'' most:
+\begin{equation}\label{eq:cdom}
+\begin{array}{rcl}
+\textit{worse}(x,y)& =& \textit{loss}(x,y) > \textit{loss}(y,x)\\
+\textit{loss}(x,y)& = &\sum_j^n -e^{\Delta(j,x,y,n)}/n\\
+\Delta(j,x,y,n) & = & w_j(o_{j,x}  - o_{j,y})/n
+\end{array}
+\end{equation}
+where  ``$n$'' is the number of objectives (for us, $n=5$) and $w_j\in \{-1,1\}$ depending on whether
+we seek to maximize goal $x_j$.
+
+An alternative to the Zitler indicator is    `boolean domination ''
+ that says one thing is better than another it if it no worse on any criteria and better on at least one criteria. We prefer Equattion~\ref{eq:cdom} to boolean domination since we
+ have a   5-goal optimization problem and it it is known that boolean domination often  fails for 3 or more goals~\cite{Wagner:2007,Sayyad:2013}.
+
+% The above equation is actually Pearson's correlation  where
+% all variables have been standardized.  To be applied
+% for discrete class learning (as done by KDP and this paper),
+% Hall et al. employ the Fayyad Irani discretizer~\cite{FayIra93Multi} then apply the following
+% entropy-based measure to infer $r$ (the degree of associations
+% between  discrete sets $X$ and $Y$):
+
+% \begin{equation}\label{eq:cfs}
+% r_{\mathit{xy}}=2\times \left[ \frac{H(x) + H(y) - H(x,y)}{H(y)+H(x)} \right]
+% \end{equation}
+% where $H$ is the standard information gain measure used in 
+% decision tree learning.
+% \lstset{language=Python}
+% \lstset{frame=lines} 
+% \lstset{label={lst:code_direct}}
+% \lstset{basicstyle=\footnotesize}
+% \begin{center}\begin{minipage}{2.5in}\begin{lstlisting}
+% def CFS(data):
+%   features = []
+%   score = -1
+%   while True:
+%     best = None
+%     for feature in range(data.features):
+%       features += [feature]
+%       tmp = merit( data, features) # see above equation
+%       if tmp > score:
+%         score = tmp
+%         bests = features
+%       features.pop()
+%     features += bests
+%     if not improve(score): break
+%   return features
+% \end{lstlisting}
+% \end{minipage}\end{center}
+% \end{figure}
+
+%  This algorithm works is  works in 6 stages.
+
+%     (1) \textbf{Feature Extraction:} In this stage the whole dataset is used to extract features from each project.
+This is done using the FSS algorithm as shown in~\ref{subsec:FSS}.
+Here each project is sent to the FSS and the FSS returns most suitable features for building models, we do this for every project and that information as a vector (i.e.
+a vector or length equal to total number of features, where 0,1 represents a feature being absent,selected) that represents each project.
+By performing this we have a vector representation of each project in the dataset.
+GENERAL uses this information to create the hierarchical clusters to find the communities.
+We perceive this is a good representation of community, as in this work we try to find community which has similar information distribution according to the attributes.
+Thus 2 projects with similar features selected have much higher chance of building similar models.
+
+%     (2) \textbf{Cluster Creation:} After the feature extraction has been done, the data is sent to a modified BIRCH algorithm.
+The algorithm requires a branching factor (i.e.
+Maximum number of CF sub-clusters in each node) and threshold value (i.e.
+when to form a new cluster based on radius).
+For this experiment we have set the branching factor as 20 and threshold value as 0.5.
+Using this version of BIRCH algorithm we build the hierarchical cluster, while storing all necessary details about the cluster like parent-child node, data points, level information, etc.
+This stage returns a Clustering Feature Tree (CF Tree) with all this information, which is passed to the next phase of experiment.
+
+%     (3) \textbf{Bellwether selection phase 1:} The CF Tree from the last phase is passed to the hierarchical bellwether.
+In this phase we use \textit{bellwether method} to identify bellwether at the leaf level.
+Using the CF Tree, we identify the clusters at the leaf level where each cluster represents the smallest community produced by the BIRCH algorithm in the last phase.
+Here we use the default ``Bellwether'' to perform a $ N*(N-1) $ comparison at each cluster.
+Here we select each project in the cluster one by one as a source dataset for transfer learning apply SMOTE as mentioned in sec~\ref{subsec:SMOTE} to handle any data imbalance and then use the FSS algorithm to get rid of any unnecessary attributes as mentioned in sec~\ref{subsec:FSS}.
+This informative and balanced dataset is used to build a LR model as mentioned in sec~\ref{subsec:LR} and we measure the performance of all other projects in the community (cluster).
+The performance measures that are used are mentioned in sec~\ref{sec:Measures}.
+To find the bellwether in each community we use cdom function to find the best source dataset among each cluster considering all performance measures.
+This phase returns a bellwether for each cluster at the leaf level of the CF Tree.
+
+%     (4) \textbf{Bellwether promotion:} In this phase of the algorithm is an iterative process, here we receive the selected bellwethers from the child clusters of each cluster in the level.
+This is called the bellwether promotion.
+Here each parent cluster instead of being represented by all projects within them, they are represented by only the bellwethers in them.
+
+%     (5) \textbf{Bellwether selection phase 2:} In this phase instead of finding a bellwether for each cluster at the level by performing a $ N*(N-1) $ comparison, we select the projects which represented as bellwether at the child nodes and then try to find a bellwether among them.
+So at each cluster at the level we perform a $ M*(M-1) $ comparison at each cluster where M is the selected bellwether from child clusters.
+This creates an order of magnitude faster \textbf{bellwether method}.
+This is again an iterative process, and the end of all the iterations, we will have a bellwether at each cluster at every level.
+
+%     (6) \textbf{Bellwether Prediction:} This is the transfer learning phase, when a new project is evaluated, we will use the FSS algorithm to get its features, then use the feature vectors to identify which cluster it belongs and use that cluster's bellwether as the transfer learning model.
+
+\section{Experimental Methods}
+\label{sec:Data Collection}
+
+\begin{figure*}[!t]
+    \centering
+    \includegraphics[width=\linewidth]{figs/General.pdf}
+    \caption{GENERAL algorithm.}
+    \label{fig:GENERAL}
+\end{figure*}
+
+\subsection{Data Collection}
+\label{sec:data}
+
+To perform our experiments we choose to work with defect prediction datasets. We use 
+the data collected by Zhang et al.~\cite{zhang15}.
+This data has the features of Table~\ref{tbl:metric}.
+Originally, this data  was collected by Mockus et al.~\cite{mockus2009amassing} from SourceForge and GoogleCode.
+The dataset contains the full history of about 154,000 projects that are hosted on SourceForge and 81,000 projects that are hosted on GoogleCode to the date they were collected.
+In the original dataset each file contained the revision history and commit logs linked using a unique identifier.
+Although there were 235K,000 projects in the original database, many of there are
+trivially small or are about  non-software development projects. Zhang et al. cleaned the dataset using the following    criteria:
+
+\bi
+  \item \textbf{Avoid projects with a small number of commits:} Zhang et al. removed any projects with less than 32 commits (which is the 25 \% quantile of the number of commits as the threshold).
+
+    \item \textbf{Avoid projects with lifespan less than one year:} Zhang et al. filtered out any  projects with a lifespan less than one year.
+
+    \item \textbf{Aovid projects with limited defect data:} Zhang et al.
+in their study counted the number of fix-inducing and non-fixing commits from a one-year period and removed any projects with 75 \% quantile of the number of fix-inducing and non-fixing commits.
+
+    \item \textbf{Avoid projects without fix-inducing commits:} Zhang et al.
+filtered out projects that have no fix-inducing commits during six months as abnormal projects, as projects in defect prediction studies need to contain both defective and non-defective commits.
+\ei
+On top of that, we also applied two more filters:
+\bi
+    \item \textbf{Use mainstream programming Languages:} the tool
+    we used (Understand~\cite{visualize}) only supported     mainstream languages in widespread
+    industrial use; specifically: object-oriented languages with file extension i.e *.c, *.cpp, *.cxx, *.cc, *.cs, *.java, and *.pas.
+
+    \item \textbf{Avoid projects with less than 50 rows:} We removed any project with less than 50 rows as they are too small to build a meaningful predictor. 
+       \item \textbf{Avoid pojects with too few errors:}
+    We pruned  projects which did not  have enough fix-inducing vs non-fixing data points to create a stratified k=5 fold cross-validation an
+
+\ei
+These filters resulted in a training set of   697 projects\footnote{\href{http://tiny.cc/bellwether_data}{http://tiny.cc/bellwether\_data}}. 
+From these selected projects, the data was labeled using issue tracking system and commit messages.
+If a project used issue tracking system for maintaining issue/defect history the data was labeled using that.
+Like  Zhang et al., we found that nearly half  of the projects did not use an issue tracking system.
+For these projects, labels were created analyzing commit messages by tagging them as fix-inducing commit if commit message matches the following regular expression
+
+\begin{center}
+\textit{(bug $\mid$ fix $\mid$ error $\mid$ issue $\mid$ crash $\mid$ problem $\mid$ fail $\mid$ defect $\mid$ patch)}
+\end{center}
 
@@
 
-In this study we try to establish the presence of generality in SE datasets.
+To report the finding and results of this study without any bias, we repeat the experiment 20 times by dividing the dataset randomly into train\_1 and test\_1 as a 90-10 split, the projects in train\_1 was used to find the bellwether in each cluster in the CF Tree, and then each project in test\_1 was divide into train\_2 and test\_2 split.
+We trained a LR model using train\_2 for each project and tested on test\_2, this is represented as self test in this study.
+We also used the predict stage of the GENERAL to identify bellwether for each project in test\_1 and tested the performance on test\_2.
+
+% \begin{figure}[!t]
+%     \centering
+%     \includegraphics[width=\linewidth]{figs/BUBBLE.png}
+%     \caption{GENERAL algorithm.}
+%     \label{fig:GENERAL}
+% \end{figure}
+
+% In this study we try to establish the presence of generality in SE datasets.
 We do this by analyzing the presence of bellwether incrementally by adding more and more projects and how the bellwether's predictive power changes.
@@
 
-In order to achieve this we try to explore the \textit{bellwether effect} as mentioned in ~\ref{sec:related}.
+% In order to achieve this, we try to explore the \textit{bellwether effect} as mentioned in ~\ref{sec:related}.
 We know the default \textit{bellwether method} is very expensive ($ O(N^2) $).
-Thus in this paper we proposes an alternative transfer learning method (BUBBLE), that explores \textit{bellwether effect} by exploring an order of magnitude faster \textit{bellwether method}.
+Thus in this paper we proposes an alternative transfer learning method (GENERAL), that explores \textit{bellwether effect} by exploring an order of magnitude faster \textit{bellwether method}.
 Our approach has three key components:
 
-\bi
-
-    \item A feature extractor to find a representation of each project, which will be used for clustering the projects.
-
-    \item A hierarchical clustering model to use the features extracted from previous step to build the hierarchical cluster.
-
-    \item A transfer learning model to identify bellwether in the hierarchical cluster.
-
-\ei
-
-BUBBLE employs few different algorithms to complete and compose it's 4 different components -
-
-\subsubsection{\textbf{Feature Subset Selection (FSS):}}
-\label{subsec:FSS}
-To extract features from each dataset, we use a feature selector algorithm called Feature Subset Selection(FSS)~\cite{hall1999correlation,hall1997feature}.
+% \bi
+
+%     \item A feature extractor to find a representation of each project, which will be used for clustering the projects.
+
+%     \item A hierarchical clustering model to use the features extracted from previous step to build the hierarchical cluster.
+
+%     \item A transfer learning model to identify bellwether in the hierarchical cluster.
+
+% \ei
+
+% GENERAL employs a few different algorithms to complete and compose it's 4 different components -
+
+% \subsubsection{\textbf{Feature Subset Selection (FSS):}}
+% \label{subsec:FSS}
+% To extract features from each dataset, we use a feature selector algorithm called Feature Subset Selection(FSS)~\cite{hall1999correlation,hall1997feature}.
 Which is a process of identifying and removing as much irrelevant and redundant information as possible.
-This is achieved using a correlation based feature evolution strategy to evaluate importance of an attribute and a best first search strategy with back tracking that moves through the search space by making local changes to the current feature subset.Here if the path being explored begins to look less promising, the best first search can back-track to a more promising previous subset and continue the search from there.
+This is achieved using a correlation based feature evolution strategy to evaluate importance of an attribute and a best first search strategy with backtracking that moves through the search space by making local changes to the current feature subset.
+Here if the path being explored begins to look less promising, the best first search can back-track to a more promising previous subset and continue the search from there.
 Given enough time, a best first search will explore the entire search space, so it uses a stopping criterion (i.e.
@@
 
-{\small 
-\begin{figure}[]
-    \small 
-    \inputminted[numbersep=2pt, linenos=true, fontsize=\small]{python}{pseudocode/cfs.py}
-    \vspace{-0.2cm}
-    \caption{Pseudo-code of Feature Subset Selection}
-    \label{fig:GAP_pseudocode} 
-    \vspace{-0.3cm}
-\end{figure}
-}
-\subsubsection{\textbf{Balanced Iterative Reducing and Clustering using Hierarchies (BIRCH):}}
-\label{subsec:BIRCH}
-To find presence or absence of generality in SE datasets, we need to incrementally check for ``Bellwether'' from smaller to larger community.
-A community is a set of project which is similar in nature.
-We use the BIRCH algorithm on our defect prediction dataset to create a hierarchical clustering tree to form these communities.
-BIRCH~\cite{zhang1996birch} is  a hierarchical clustering algorithm, which has a ability to incrementally and dynamically cluster incoming, multi-dimensional data in an attempt to produce the best quality clustering.
-BIRCH also has the ability to identify data points that are not part of the underlying pattern effectively identifying outliers.
-In this study we uses a modified BIRCH algorithm to store additional information regarding each cluster in the clustering feature tree, which help us in the experiment.
-
-\subsubsection{\textbf{Synthetic Minority Over-Sampling Technique (SMOTE):}}
-\label{subsec:SMOTE}
-
-Machine learning models exploits the inherent bias in the dataset to segregate and classify different classes.
-Hence class imbalance can create major bias towards the majority class when building a machine learning model, thus producing biased model which provides bad classification results.
-Synthetic Minority Over-Sampling Technique (SMOTE)~\cite{chawla2002smote} is a technique to handle class imbalance by changing the frequency of different classes of the training data.
-When applied to data, SMOTE sub-samples the majority class (i.e., deletes examples) while over-sampling the minority class until all classes have the same frequency.
-In the case of software defect data, the minority class is usually the defective class.
-During super-sampling, a member of the minority class finds k nearest neighbors.
-It builds an artificial member of minority class at some point in-between itself and one of its random nearest neighbors.
-During that process, some distance function is required which is the \textit{minkowski distance} function.
-
-\subsubsection{\textbf{Logistic Regression (LR):}}
-\label{subsec:LR}
-
-Logistic regression is a statistical machine learning model that in its basic form uses a logistic function to model a binary dependent variable.
-In this study we use scikit learn's default logistic regression implementation as our learner for building source models and evaluating on target models inside each community.
-In this study we selected logistic regression, as it is very fast to build in comparison to other more complex learners and its much more comprehensible and explainable in-terms of attributes and their importance.
-Logistic Regression is widely used in defect prediction domain and have shown promising results both in-term of predictive power and comprehensibility.
-
-\subsubsection{\textbf{Bellwether\_0:}}
-\label{Bellwether}
-
-In this study to compare our novel method to the state of the art method, we uses Krishna et al.
-'s \textit{bellwether method}.
-We use all the projects available in the community to perform a $N*(N-1)$ comparison, where N is the number of projects in the community to measure the performance of each project measured on all others on the performance measures mentioned in sec~\ref{sec:Measures}.
-Following this we use cdom function to select a bellwether project among them.
-
-\section{Evaluation Criteria}
-\label{eval}
+% {\small 
+% \begin{figure}[]
+%     \small 
+%     \inputminted[numbersep=2pt, linenos=true, fontsize=\small]{python}{pseudocode/cfs.py}
+%     \vspace{-0.2cm}
+%     \caption{Pseudo-code of Feature Subset Selection}
+%     \label{fig:GAP_pseudocode} 
+%     \vspace{-0.3cm}
+% \end{figure}
+% }
+
 \subsection{Statistical Tests}
-\label{stats}
-
-When comparing the results different models in this study, we used a statistical significance test and an effect size test. Significance test are useful for detecting if two populations
+\label{stats}\label{eval}
+
+When comparing the results different models in this study, we used a statistical significance test and an effect size test. Significance test is useful for detecting if two populations
 differ merely by random noise.
@@
 If any two clusters are statistically indistinguishable, Scott-Knott reports them both as one group.
-Scott-Knott first looks for a break in the sequence that maximizes the expected values in the difference in the means before and after the break.More specifically,  it  splits $l$ values into sub-lists $m$ and $n$ in order to maximize the expected value of differences  in the observed performances before and after divisions.
+Scott-Knott first looks for a break in the sequence that maximizes the expected values in the difference in the means before and after the break.
+More specifically,  it  splits $l$ values into sub-lists $m$ and $n$ in order to maximize the expected value of differences  in the observed performances before and after divisions.
 For e.g., lists $l,m$ and $n$ of size $ls,ms$ and $ns$ where $l=m\cup n$, Scott-Knott divides the sequence at the break that maximizes:
@@
 
-\subsection{Continuous Domination(cdom)}
-\label{cdom}
-In this study, we compare each project's performance against all other projects in each cluster at the leaf level of the BIRCH as described in section~\ref{BUBBLE} and section~\ref{Bellwether}.
-We calculate 5 different performance measure for each project as described in section~\ref{sec:Measures}.
-In order to find a \textit{bellwether effect} in the performances collected we need to combine those 5 performance measures and then rank them using certain criteria.
-We have used continuous domination (cdom) for this purpose.
-continuous domination is defined as the set of all points in the objective space that are not dominated by any other points.
-Unlike Boolean domination, which says a point is dominated by another if and only if the first point is better in every single objective then the second point, continuous domination combines all the objective into a continuous function to compare and then calculate if one point dominates another.
-Throughout literature continuous domination has proven to be very effective when multiple goals are concerned.
-The continuous domination function is defined as below, where P is the total population, k is fitness scaling factor, n is a scaling factor and $X\_1$ is the data points we are calculating the domination for -
-\begin{equation}
-    F(X_1) = \sum_{{(X_2\in P) - X_1}} -n*e^{-I(X_2,X_1)/k}
-\end{equation}
 {\small 
@@
 
-\section{Performance Measures}
+\subsection{Performance Measures}
 \label{sec:Measures}
@@
 (1) \textbf{Recall:} Proportion of inspected defective changes among all the actual defective changes.
-This is the evaluation measure used by many previous studies~\cite{kamei2012large,yang2016effort,yang2017tlel,xia2016collective,yang2015deep} .
+This is the evaluation measure used by many previous studies~\cite{kamei2012large,yang2016effort,yang2017tlel,xia2016collective,yang2015deep}.
 They focused on achieving high Recall so that more defective changes could be detected.
@@
 (3) \textbf{pf:} Proportion of all suggested defective changes which are not actual defective changes among all the suggested defective changes.
-A high pf suggests developers will encounter more false alarms which may have negative impact on developers' confidence on the prediction model.
+A high pf suggests developers will encounter more false alarms which may have negative impact on developers' confidence in the prediction model.
 
 (4) \textbf{popt20:} Proportion number of suggested defective changes among all suggested defective changes, when when 20\% LOC modified by all changes are inspected.
-A high popt20 indicates that, under the same number of LOC to inspect, developers developers will find more bugs, which means developers will be able to fix more defects with same amount of effort invested.
+A high popt20 indicates that, under the same number of LOC to inspect, developers will find more bugs, which means developers will be able to fix more defects with the same amount of effort invested.
 
@@
 
-\subsection*{RQ1: Can we confirm bellwether on large datasets?}
+\subsection*{RQ1: What are the drawbacks of traditional bellwether  methods?}
 \label{sec:rq1}
 
-In the literature, we saw most of the previous studies has shown bellwether effect with very small datasets.
+In the literature, we saw most of the previous studies have shown bellwether effect with very small datasets.
 In order to use bellwether to prove presence of generality in SE domain datasets, we first have to showcase the bellwether method suggested by Krishna et al.
@@
 
-To tame complexity of bellwether in this RQ, we propose a new bellwether method called ``BUBBLE'' to find bellwether in large datasets.
+To tame complexity of bellwether in this RQ, we propose a new bellwether method called GENERAL to find bellwether in large datasets.
 This bellwether method is composed of 6 stages, (a) a feature extraction process to summarize each project into a single representative vector, (b) a hierarchical clustering algorithm, which uses the feature vectors to cluster similar projects into community of increasing size at different levels of cluster, (c) a bellwether selection phase where a $N*(N-1)$ comparison is performed at each leaf level cluster and using a cdom calculation in all the metrics mentioned in~\ref{tbl:metric} a bellwether is selected, (d) a iterative bellwether promotion stage, where bellwether from child clusters are promoted as potential bellwethers at parent cluster, (e) another bellwether selection phase at non-leaf levels, where comparisons are only made among potential bellwethers from leaf node and finally (f) a bellwether prediction phase, which suggests a bellwether based on project similarity when a new project is to be predicted.
-The details of each phase is mentioned in sec~\ref{BUBBLE}.
+The details of each phase is mentioned in sec~\ref{GENERAL}.
 
@@
 if there are N projects in a community it will make $\approx N^2$ comparisons to discover the bellwether.
-While ``BUBBLE'' different approach to discover bellwether by dividing the data into smaller cluster and finding bellwether among each, here if we assume we have m cluster at leaf level with N projects in each, we will have
+While GENERAL different approach to discover bellwether by dividing the data into smaller cluster and finding bellwether among each, here if we assume we have m cluster at leaf level with N projects in each, we will have
 $\approx m*(N/m)^2$ comparisons to discover the bellwether which is m times less comparison.
-For example if we see the example figure~\ref{fig:example tree} for hierarchically cluster a community of 627 projects, if we use the default \textit{bellwether method} it will require \textbf{393129} comparisons.
-While if we use the ``BUBBLE'' algorithm to find the bellwether it will require only \textbf{9080} comparisons.
-Using this process we are able to find bellwether in ~\textbf{1.5 hours}, which is order of magnitude faster then the bellwether method proposed by Krishna et al.
-In summary, we find that
+For example if we see the example figure~\ref{fig:example tree} for hierarchically cluster a community of 627 projects, if we use the default bellwether method it will require  393,129 comparisons.
+On the other hand, if we use the GENERAL algorithm to find the bellwether,  it will require only 9,080 comparisons.
+Using this process we are able to find bellwether in 1.5 hours, which is order of magnitude faster then the bellwether method proposed by Krishna et al.
+In summary, we find that:
 
 \begin{result}
-{``BUBBLE'' can find ``Bellwether Project'' order of magnitude faster, only requiring 1.5 hours in comparison to 3 days.
-Also ``BUBBLE'' requires far less comparison 9080 instead of 393129 required for ``Bellwether method'' proposed by krishna et al.
-}
+{GENERAL can find the bellwether project
+an order of magnitude faster than prior work
+(1.5 hours versus 3 days)
+since GENERAL  requires far fewer
+ comparisons between projects
+ (9,080 instead of 393,129 required for 
+ Krishna et al.'s bellwether method). }
 \end{result}
 
+XXXX
+
 \begin{equation}
-\label{eq:bellwether}
-    Bellwether\_complexity  \approx O(N^2)
-\end{equation}
-
-\begin{equation}
-\label{eq:BUBBLE}
-    BUBBLE\_complexity \approx O(m*(N/m)^2)
+\label{eq:GENERAL}
+    {GENERAL\; complexity } =  O(m*(N/m)^2)
 \end{equation}
@@
     \includegraphics[width=\linewidth]{figs/time.png}
-    \caption{Runtime for default bellwether and BUBBLE.}
+    \caption{Runtime for default bellwether and GENERAL.}
     \label{fig:time}
@@
 \begin{figure}[!t]
-{\small
-{\small \begin{tabular}{p{.1cm}lp{1.5cm}rrc}
+{\scriptsize
+{\scriptsize \begin{tabular}{p{.1cm}lp{1.5cm}rrc}
 \arrayrulecolor{darkgray}
@@
  \multirow{5}{*}{\rotatebox[origin=c]{90}{Recall}} &   1 &      random2 &    40 &  49 & \quart{16}{40}{49}{25} \\
-  &   1 &      BUBBLE\_level2 &    38 &  32 & \quart{22}{38}{32}{16} \\
+  &   1 &      GENERAL\_level2 &    38 &  32 & \quart{22}{38}{32}{16} \\
   &   1 &      bellwether0 &    39 &  31 & \quart{23}{39}{31}{15} \\
-  &   2 &      BUBBLE\_level1 &    48 &  33 & \quart{31}{48}{33}{16} \\
-  &   3 &      BUBBLE\_level0 &    56 &  31 & \quart{42}{56}{31}{16} \\
+  &   2 &      GENERAL\_level1 &    48 &  33 & \quart{31}{48}{33}{16} \\
+  &   3 &      GENERAL\_level0 &    56 &  31 & \quart{42}{56}{31}{16} \\
   &   3 &      self\_0 &    55 &  27 & \quart{41}{55}{27}{12} \\
@@
   &  1 &      random2 &    39 &  49 & \quart{15}{39}{49}{25} \\
-  &  1 &      BUBBLE\_level2 &    28 &  28 & \quart{14}{28}{28}{13} \\
+  &  1 &      GENERAL\_level2 &    28 &  28 & \quart{14}{28}{28}{13} \\
   &  1 &      bellwether0 &    28 &  25 & \quart{15}{28}{25}{11} \\
   &  1 &      self\_0 &    30 &  20 & \quart{20}{30}{20}{10} \\
-  &  1 &      BUBBLE\_level1 &    35 &  28 & \quart{21}{35}{28}{14} \\
-  &  2 &      BUBBLE\_level0 &    47 &  31 & \quart{31}{47}{31}{15} \\
+  &  1 &      GENERAL\_level1 &    35 &  28 & \quart{21}{35}{28}{14} \\
+  &  2 &      GENERAL\_level0 &    47 &  31 & \quart{31}{47}{31}{15} \\
   &  3 &      global2 &    79 &  39 & \quart{59}{79}{39}{19} \\\hline
@@
     &   2 &      bellwether0 &    40 &  33 & \quart{23}{40}{33}{16} \\
-    &   2 &      BUBBLE\_level2 &    39 &  34 & \quart{22}{39}{34}{17} \\
-    &   2 &      BUBBLE\_level1 &    42 &  31 & \quart{26}{42}{31}{15} \\
-    &   2 &      BUBBLE\_level0 &    44 &  30 & \quart{28}{44}{30}{15} \\
+    &   2 &      GENERAL\_level2 &    39 &  34 & \quart{22}{39}{34}{17} \\
+    &   2 &      GENERAL\_level1 &    42 &  31 & \quart{26}{42}{31}{15} \\
+    &   2 &      GENERAL\_level0 &    44 &  30 & \quart{28}{44}{30}{15} \\
     &   2 &      self\_0 &    50 &  30 & \quart{35}{50}{30}{15} \\\hline
 \multirow{5}{*}{\rotatebox[origin=c]{90}{Popt20}} &   1 &      random2 &    13 &  16 & \quart{5}{13}{16}{8} \\
-  & 2 &      BUBBLE\_level2 &    26 &  22 & \quart{15}{26}{22}{11} \\
+  & 2 &      GENERAL\_level2 &    26 &  22 & \quart{15}{26}{22}{11} \\
   &  2 &      global2 &    26 &  13 & \quart{19}{26}{13}{6} \\
   &  2 &      bellwether0 &    28 &  21 & \quart{17}{28}{21}{9} \\
-  &  2 &      BUBBLE\_level0 &    28 &  15 & \quart{22}{28}{15}{8} \\
-  &  2 &      BUBBLE\_level1 &    28 &  19 & \quart{19}{28}{19}{9} \\
+  &  2 &      GENERAL\_level0 &    28 &  15 & \quart{22}{28}{15}{8} \\
+  &  2 &      GENERAL\_level1 &    28 &  19 & \quart{19}{28}{19}{9} \\
   &  3 &      self\_0 &    35 &  19 & \quart{26}{35}{19}{10} \\\hline
@@
   &  2 &      global2 &    19 &  16 & \quart{11.35}{19.38}{16.06}{8.03} \\
-  &  3 &      BUBBLE\_level2 &    22 &  14 & \quart{14.48}{21.59}{14.21}{7.10} \\
+  &  3 &      GENERAL\_level2 &    22 &  14 & \quart{14.48}{21.59}{14.21}{7.10} \\
   &  3 &      bellwether0 &    23 &  14 & \quart{15.48}{22.56}{14.15}{7.07} \\
   &  3 &      self\_0 &    23 &  12 & \quart{17.09}{22.93}{11.68}{5.84} \\
-  &  3 &      BUBBLE\_level1 &    23 &  14 & \quart{16.10}{22.98}{13.74}{6.87} \\
-  &  3 &      BUBBLE\_level0 &    25 &  13 & \quart{17.87}{24.51}{13.27}{6.63} \\
+  &  3 &      GENERAL\_level1 &    23 &  14 & \quart{16.10}{22.98}{13.74}{6.87} \\
+  &  3 &      GENERAL\_level0 &    25 &  13 & \quart{17.87}{24.51}{13.27}{6.63} \\
 \end{tabular}}
@@
 
-\subsection*{RQ3: Is faster bellwether effective?}
+\subsection*{RQ3: Is this faster bellwether effective?}
 \label{sec:rq3}
 
-In RQ2, we can see using ``BUBBLE'' we are able to find bellwether for a large dataset in order of magnitude faster.
-This raises the question is  \textit{bellwether method} ``BUBBLE'' as effective as \textit{bellwether method} proposed by krishna et al.
+In RQ2, we can see using GENERAL we are able to find bellwether for a large dataset in order of magnitude faster.
+This raises the question is  \textit{bellwether method} GENERAL as effective as \textit{bellwether method} proposed by krishna et al.
 and can it be compared against local(self test) and global models?
 
-To answer this question in this study we have used the defect prediction dataset with 697 projects and divided the projects randomly into train\_1 and test\_1 as a 90-10 split, the projects in train\_1 was used to find the bellwether in each cluster in the CF Tree as mentioned in sec~\ref{BUBBLE}, and then each project in test\_1 was divide into train\_2 and test\_2 split.
+To answer this question in this study we have used the defect prediction dataset with 697 projects and divided the projects randomly into train\_1 and test\_1 as a 90-10 split, the projects in train\_1 was used to find the bellwether in each cluster in the CF Tree as mentioned in sec~\ref{GENERAL}, and then each project in test\_1 was divide into train\_2 and test\_2 split.
 We trained a LR model using train\_2 for each project and tested on test\_2 (represented as self\_0), this is represented as self test in this study.
-We also used the predict stage of the ``BUBBLE'' to identify a bellwether in each level of hierarchical model, for each project in test\_1 and tested the performance on test\_2 (represented as bellwether\_level0, bellwether\_level1, bellwether\_level respectively).
+We also used the predict stage of the GENERAL to identify a bellwether in each level of hierarchical model, for each project in test\_1 and tested the performance on test\_2 (represented as bellwether\_level0, bellwether\_level1, bellwether\_level respectively).
 Similarly we used the projects in train\_1 to find the bellwether using default bellwether method as mentioned in sec~\ref{Bellwether}, and use that project to build a LR model and test the performance of each project's test\_2 (represented as bellwether0).
@@
 We can see from the figure~\ref{fig:Statistical} that bellwether\_level0 model (i.e.
-the bellwether discovered by ``BUBBLE'' at level 0) performs similar or  better than bellwether0 in most of performance metrics.
+the bellwether discovered by GENERAL at level 0) performs similar or  better than bellwether0 in most of performance metrics.
 Similarly for self\_0 in terms of precision, recall and ifa\_auc bellwether\_level0 scores same rank using statistical significance and effect size test.
@@
 We can see similar results for the global2 results, where bellwether\_level0 performs significantly better.
-Seeing these results we can conclude the ``BUBBLE'' is an effective and fast algorithm to find a exemplary ``Bellwether Projects'', whose predictive performance is comparable with  \textit{bellwether method} proposed by krishna et al.
+Seeing these results we can conclude the GENERAL is an effective and fast algorithm to find a exemplary ``Bellwether Projects'', whose predictive performance is comparable with  \textit{bellwether method} proposed by Krishna et al.
 , local(self test) and global models.
@@
 \begin{result}
-{``BUBBLE'' is a fast and effective algorithm, which can find exemplary ``Bellwether Projects'' with comparable predictive performance.}
+{GENERAL is a fast and effective algorithm, which can find exemplary ``Bellwether Projects'' with comparable predictive performance.}
 \end{result}
@@
 \label{sec:rq4}
-In RQ4, we try to answer the question if learning from too many projects detrimental effect, this question has two parts one on predictive power, other on making general conclusion and conclusion instability.
-Figure~\ref{fig:Statistical} show the results of statistical significance and effect size tests to rank them in order for all the different methods(treatments) used in this experiment.
-In this figure for a performance measure two methods showing same rank means there performance is not statistically significantly different, while a different ranks means they are different, while a smaller rank is better if the performance goal is negative (i.e.
+In RQ4, we try to answer the question if learning from too many projects detrimental effect, this question has two parts, one on predictive power, the other on making general conclusion and conclusion instability.
+Figure~\ref{fig:Statistical} shows the results of statistical significance and effect size tests to rank them in order for all the different methods(treatments) used in this experiment.
+In this figure for a performance measure two methods showing same rank means there performance is not statistically significantly different, while a different ranks mean they are different, while a smaller rank is better if the performance goal is negative (i.e.
 Pf), and higher rank is better in case of positive goal (i.e.
@@
 
-To answer the first part of the question, if learning from too many projects have detrimental effect on predictive power of models, we compare the results of default ``bellwether method'' (a.k.a bellwether0) proposed by krishna et al.
-and ``BUBBLE''(a.k.a BUBBLE\_level0) method.
-The results of scott-knott test shows that for positive goals such as Recall the BUBBLE\_level0 is significantly doing better than Bellwether0 and it is doing as good as or better for precision ans recall.
-While for negative goals such as ifa\_auc BUBBLE\_level0 is doing as good as bellwether0.
-Although in case of Pf they score different ranks with BUBBLE showing higher Pf then bellwether0, it is not by much.
-Similarly while comparing BUBBLE\_level0 with global (which is learning from all the projects) shows although it achieves higher Recall, but it has very high Pf, low precision.
+To answer the first part of the question, if learning from too many projects have detrimental effect on predictive power of models, we compare the results of default ``bellwether method'' (a.k.a bellwether0) proposed by Krishna et al.
+and GENERAL(a.k.a GENERAL\_level0) method.
+The results of scott-knott test shows that for positive goals such as Recall the GENERAL\_level0 is significantly doing better than Bellwether0 and it is doing as good as or better for precision ans recall.
+While for negative goals such as ifa\_auc GENERAL\_level0 is doing as good as bellwether0.
+Although in case of Pf they score different ranks with GENERAL showing higher Pf then bellwether0, it is not by much.
+Similarly while comparing GENERAL\_level0 with global (which is learning from all the projects) shows although it achieves higher Recall, but it has very high Pf, low precision.
 Which answers the first part of the question that learning from too many projects do have detrimental effect on predictive power of models.
@@
 \centering
-\caption{Importance of coefs on \textit{log p} from logistic regression model of ``Bellwether'' shown in fig~\ref{fig:FSS_compare}.
-Here Odds ratio shows one increment in in respective variable increase in the log-odds of being defective.}
 \begin{tabular}{|l|l|l|l|} \hline
@@
 \label{tbl:coefs}
+\caption{Importance of coefs on \textit{log p} from logistic regression model of ``Bellwether'' shown in fig~\ref{fig:FSS_compare}.
+Here Odds ratio shows one increment in in respective variable increase in the log-odds of being defective.}
 \end{table}
 
-Now to answer the second part of the question, that is if learning from too many projects creates conclusion instability, we will look at the figure~\ref{fig:FSS_compare}.
+Now to answer the second part of the question, that is if learning from too many projects creates conclusion instability, we will look at figure~\ref{fig:FSS_compare}.
 Figure~\ref{fig:FSS_compare} show the distribution of attributes selected while building a ML model for defect prediction using local models(a.k.a self\_0), the \textcolor{red}{{\bf red bars}} shows the attributes selected by the ``Bellwether Project''.
@@
 \begin{result}
-{Learning from too many projects have detrimental effect on predictive power, which can be seen on performance difference found between bellwether0 and BUBBLE\_level0, it also introduces conclusion instability.
-By selecting ``Bellwether Project'' using BUBBLE can have better predictive performance as well as it can create generalized model which are explainable and actionable thus minimizing conclusion instability.}
+{Learning from too many projects have detrimental effect on predictive power, which can be seen on performance difference found between bellwether0 and GENERAL\_level0, it also introduces conclusion instability.
+By selecting ``Bellwether Project'' using GENERAL can have better predictive performance as well as it can create generalized model which are explainable and actionable thus minimizing conclusion instability.}
 \end{result}
@@
 
-\subsection*{RQ5: What did we learn?}
+\subsection*{RQ5: What exactly did we learn from all those projects?}
 \label{sec:rq5}
@@
 Using ``Bellwether Project''  minimizes the issue of conclusion instability and thus building trust in the model and deduce better insights about what can be a better indicator of bugs.
-Table~\ref{tbl:coefs} show the attributes selected by the ``Bellwether Project'' and the coefs and Odd ratios for the LR model build using that.
-The insights that we can draw from these results are an increase of 1 in avg\_NPRM can increase the ratio of probability of having a defect and not having a defect by almost 9 times, while an unit increase in total\_NPBM, avg\_NPBM, max\_NPBM, max\_CBO will reduce the ration of probabilities by 0.5, 0.27, 0.33 and 0.53 times respectively.
-an unit increase in total\_ModifiedLOC and avg\_WMC will have almost no effect in Odd ratio.
+Table~\ref{tbl:coefs} shows the attributes selected by the ``Bellwether Project'' and the coefs and Odd ratios for the LR model build using that.
+The insights that we can draw from these results are an increase of 1 in avg\_NPRM can increase the ratio of probability of having a defect and not having a defect by almost 9 times, while a unit increase in total\_NPBM, avg\_NPBM, max\_NPBM, max\_CBO will reduce the ration of probabilities by 0.5, 0.27, 0.33 and 0.53 times respectively.
+a unit increase in total\_ModifiedLOC and avg\_WMC will have almost no effect in Odd ratio.
 From this we can conclude NPRM, NPBM, RFC and CBO are important factor while predicting for defects all of which are interface related metrics in these datasets.
-The learning from these information can be if there is increase in number of private methods in a certain class, developers need to be extra careful as that is a good indicator of introducing bugs in code.
+The learning from these information can be if there is an increase in number of private methods in a certain class, developers need to be extra careful as that is a good indicator of introducing bugs in code.
 In Summary, we can say
@@
 
-(c) \textit{External Validity}: For this study we have relied on data collected by zhang et al.~\cite{zhang15} for their studies.
-The metrics collected for each project was done using an commercialized tool called ``Understand''.
+(c) \textit{External Validity}: For this study we have relied on data collected by Zhang et al.~\cite{zhang15} for their studies.
+The metrics collected for each project were done using an commercialized tool called ``Understand''.
 There is a possibility that calculation of metrics or labeling of defective vs non-defective using other tools or methods may result in different outcome.
-That said, the ``Understand'' is a commercialized tool which has detailed documentation about the metrics calculations and zhang et al.
+That said, the ``Understand'' is a commercialized tool which has detailed documentation about the metrics calculations and Zhang et al.
 has shared their scripts and process to convert the metrics to usable format and has described the approach to label defects.
@@
 
-(e) \textit{Sampling Bias}: Our conclusions are based on the 697 projects collected by zhang et al.~\cite{zhang15} for their studies.
+(e) \textit{Sampling Bias}: Our conclusions are based on the 697 projects collected by Zhang et al.~\cite{zhang15} for their studies.
 It is possible that different initial projects would have lead to different conclusions.
@@
 \label{sec:concl}
-In this paper, we have proposed a new transfer learning ``bellwether method'' to find ``Bellwether effect'' called ``BUBBLE'' and uses this to find generality in Software Engineering by minimizing conclusion instability thus increasing trust and deducing meaningful insights from them which in turn helps in training and tool developments.
+In this paper, we have proposed a new transfer learning ``bellwether method'' to find ``Bellwether effect'' called GENERAL and uses this to find generality in Software Engineering by minimizing conclusion instability thus increasing trust and deducing meaningful insights from them which in turn helps in training and tool developments.
 
@@
 al.
-are computationally very expensive and took long time to discover these bellwethers, e.g.,experimentation took 3 days to find a bellwether project from among the 697 projects.
-
-We showed in this paper, the new algorithm ``BUBBLE'' can find ``Bellwether Project'' order of magnitude faster.
+are computationally very expensive and took long time to discover these bellwethers, e.g., experimentation took 3 days to find a bellwether project from among the 697 projects.
+
+We showed in this paper, the new algorithm GENERAL can find ``Bellwether Project'' order of magnitude faster.
 We show ``Bellwether method'' proposed by krishna et al.
-has a computational complexity of $\approx O(N*2)$ while ``BUBBLE'' has a computational complexity of $\approx O((N*2/m))$ where m is the number of cluster at the leaf level of the CF tree and N is the number of projects.
-``BUBBLE'' only requiring 1.5 hours to run in comparison to 3 days and requires far less comparison 9080 instead of 393129 required for ``Bellwether method'' proposed by krishna et al.
-
-The study also showed the ``BUBBLE'' is a fast and effective algorithm, which can find exemplary ``Bellwether Projects'' with comparable predictive performance.
-The figure~\ref{fig:Statistical} shows ``Bellwether Projects'' discovered by ``BUBBLE'' have similar or better predictive performance while comparing with bellwether0, Self\_0 or global2.
+has a computational complexity of $\approx O(N*2)$ while GENERAL has a computational complexity of $\approx O((N*2/m))$ where m is the number of cluster at the leaf level of the CF tree and N is the number of projects.
+GENERAL only requiring 1.5 hours to run in comparison to 3 days and requires far less comparison 9080 instead of 393129 required for ``Bellwether method'' proposed by Krishna et al.
+
+The study also showed the GENERAL is a fast and effective algorithm, which can find exemplary ``Bellwether Projects'' with comparable predictive performance.
+The figure~\ref{fig:Statistical} shows ``Bellwether Projects'' discovered by GENERAL have similar or better predictive performance while comparing with bellwether0, Self\_0 or global2.
 
@@
 
-Hence, from a  engineering perspective there are two main reasons to use ``BUBBLE'': (a) This is a very fast algorithm to find ``Bellwether project'';  (b) They have comparable predictive performance than its counter parts; and (c) They slow down the pace of conclusion changes and allow users to draw generalized conclusions and meaningful actionable insights .
+Hence, from a  engineering perspective there are two main reasons to use GENERAL: (a) This is a very fast algorithm to find ``Bellwether project'';  (b) They have comparable predictive performance than its counterparts; and (c) They slow down the pace of conclusion changes and allow users to draw generalized conclusions and meaningful actionable insights.
 
@@
 We strongly recommend that when building increasingly complex and expensive  methods, researchers should pause and compare their supposedly more sophisticated method against simpler alternatives.
-Going forward from this paper, we would recommend that the transfer learning community uses ``BUBBLE'' as a baseline method against which they can test more complex methods.
+Going forward from this paper, we would recommend that the transfer learning community uses GENERAL as a baseline method against which they can test more complex methods.
 
@@
 \bibliography{main} 
-\clearpage
+ \balance
 

### 2019-10-22 pseudo.tex
Updates from Overleaf

\renewcommand\thesubfigure{\alph{subfigure}}
\begin{figure*}[ht!]
\centering
\begin{minipage}{.45\linewidth}
\centering
\resizebox{0.925\linewidth}{!}{
\begin{subfigure}[t]{\linewidth}
\inputminted[numbersep=5pt, linenos=true, fontsize=\small]{c}{pseudocode/overall.py}

\caption{The overall framework of \tool}
\label{fig:general_framework}    
\end{subfigure}}\\[0.3em]
\resizebox{0.925\linewidth}{!}{
\begin{subfigure}[t]{\linewidth}
\inputminted[numbersep=5pt, linenos=true, fontsize=\small]{python}{pseudocode/get_cov.py}

\caption{Method to obtain edge coverage}
\label{fig:coverage}    
\end{subfigure}}%~
\end{minipage}\hspace{0.1em}%
\begin{minipage}{.5\linewidth}
\centering
\resizebox{0.925\linewidth}{!}{
\begin{subfigure}{\linewidth}
\inputminted[numbersep=5pt, linenos=true, fontsize=\small]{python}{pseudocode/seed_select.py}
\vspace{-2em}
\caption{Method to perform seed selection with importance sampling.}
\label{fig:seed_selection}    
\end{subfigure}}\\[-0.2em]
\resizebox{0.925\linewidth}{!}{
\begin{subfigure}{\linewidth}
\inputminted[numbersep=5pt, linenos=true, fontsize=\small]{python}{pseudocode/train_adaptive.py}
\vspace{-2em}
\caption{Method to compute adaptive loss for training neural network.}
\label{fig:train_adaptive}    
\end{subfigure}}\\[-0.2em]
\resizebox{0.925\linewidth}{!}{        
\begin{subfigure}{\linewidth}
\inputminted[numbersep=5pt, linenos=true, fontsize=\small]{python}{pseudocode/mutate.py}
\vspace{-2em}
\caption{Method to generate new inputs with gradient ascent.}
\label{fig:mutation}    
\end{subfigure}}
\end{minipage}\\[0.3em]
\caption{{\small Pseudocode of \tool.}}
\label{fig:pseudo}
\end{figure*}

### 2019-10-22 pseudocode/example.c

@@ -1,0 +1,12 @@
+/* libxml2-2.9.9/parser.c:8347 */
+const xmlChar * 
+xmlParseAttribute(xmlParserCtxtPtr ctxt, xmlChar **value) {
+    const xmlChar *name;
+    ...
+    // obtain attribute name from input
+    name = xmlParseName(ctxt);
+    // check if attribute equals to a specification.
+    if (xmlStrEqual(name, "xml:space")){
+        ...
+    }
+}

### 2019-10-22 pseudocode/get_cov.py

@@ -1,0 +1,12 @@
+def get_coverage(inputs):
+  """Get edge coverage.
+  Returns:
+    A dictionary of inputs and corresponding coverage
+  """
+  cov_dict = dict()
+  for test_input in inputs:
+    "Get coverage by running the program"
+    cov = coverage(input)
+    "Update coverage dictionary of test input"
+    cov_dict[test_input] = cov
+  return cov_dict

### 2019-10-22 pseudocode/mutate.py

@@ -1,0 +1,8 @@
+def mutate(sampled_inputs, gradients):
+    "Mutate inputs with gradient ascent"
+    mutated_inputs = []
+    for old_input in sampled_inputs:
+      for i in old_input:
+        new_input[i] = old_input[byte] + step * gradients[i]
+      mutated_inputs.append(new_input)
+    return mutated_inputs

### 2019-10-22 pseudocode/overall.py

@@ -1,0 +1,25 @@
+def FuzzNN(budget, n_rounds):
+  """The main fuzzing framework.
+  Args:
+    budget: Sampling budget for seed selection
+    n_rounds: Termination criteria for the fuzzer
+  """
+  inputs = init_inputs()
+  for round in range(n_rounds):
+    # ----- Input Selection -----
+    "Select inputs with importance sampling"
+    input_samples = sample_inputs(inputs, budget)
+    "Compute the true edge coverage of the inputs"
+    edge_true = get_coverage(input_samples)
+    # ----- Mutation Location Selection -----
+    "Initialize a fully connected Neural Network"
+    NN = Neural_Network(X=input_samples, y=edge_true)
+    "Train neural network with adaptive loss"
+    NN = NN.train(loss=adaptive_loss)    
+    "Compute gradients of edge coverage wrt. inputs"
+    grad_vector = NN.compute_gradients()
+    # ----- Mutation Operation -----
+    "Mutate inputs to generate new inputs"
+    new_inputs = mutate(input_samples, grad_vector)
+    "Add new inputs to the pool of available inputs"
+    inputs += new_inputs

### 2019-10-22 pseudocode/seed_select.py

@@ -1,0 +1,24 @@
+def sample_inputs(all_inputs, max_budget):
+  """Importance sampling based input selection.
+  Returns:
+    A sample of the most important input.
+  """
+  budget = max_budget
+  selected_inputs = []
+  edges = get_coverage(all_inputs)
+  "Sort the inputs from most to least recent" 
+  sorted_inputs = sort_by_recency(all_inputs)
+  "Sort the new edges from most to least rare"
+  important_edges = sort_by_rarity(new_edges) 
+  for edge in important_edges:
+    for input in sorted_inputs:
+        if budget == 0:
+             break
+        if edge_cov[input][edge] == 1:
+            selected_inputs.append(input)
+            budget = budget - 1
+  return selected_inputs
+
+
+
+

### 2019-10-22 pseudocode/soft_label.c

@@ -1,0 +1,8 @@
+void foo(int a) {
+    if (a != 10000) {
+        /* Do something ... */
+    } else
+    {
+        /* VULNERABILITY */
+    }
+}

### 2019-10-22 pseudocode/train_adaptive.py

@@ -1,0 +1,7 @@
+def adaptive_loss(egde_true, edge_pred):
+    "Coverage guided loss function to train Neural Network."
+    penalty = get_neg_pos_ratio()
+    loss = 0
+    for true, pred, b in zip(edge_true, edge_pred, penalty):
+      loss += -(b*true*log(pred) + (1-true)*log((1-pred)))
+    return loss

### 2020-02-12 response.tex
Updates from Overleaf

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                               RESPONSE TO REVIEWERS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\pagebreak
\newpage
\renewcommand*{\thesection}{\Alph{section}}
\nobalance
\section*{RESPONSE TO REVIEWERS}
\section*{Comments from the editor}

\review{I would like to thank the authors for submitting their work to TSE. While all the reviewers agree that the problem addressed is important and the paper has potential, the reviewers also identified several concerns that need to be carefully addressed. The reviewers also agreed that the amount of work needed to address those concerns is beyond a major revision. Thus, after carefully checking the reviewers and in accordance with reviewer’s recommendations, I also recommend “Revise and resubmit as New”.}

Thank you very much for your encouraging comments. We have made appropriate changes to the manuscript taking into careful consideration the recommendations of the reviewers. We hope that this new draft adequately satisfies all the issues raised by the reviewers. To assist the reviewers in tracking all the new changes, where appropriate, we have prefixed the text with \respto{X-XX} to correspond to the reviewers' questions.

Below is the brief summary of our changes:
\be
\item The problem statement needs to be clarified and properly positioned (R1, R3). XXX

\item The novelty of the approach needs to be clarified (R3). XXX (see \bareresp{2-1})

\item The writing needs to be improved (R1, R2, R3).

\item The study needs to include all the details to ensure replicability (R1, R2).

\item The results of the study need to be revisited since the reviewers are not convinced that the results support the claims in the paper (R1, R2, R3).

\item The background on transfer learning needs citations (R2).
\ee

\section*{Reviewer 1}

Thank you very much for your detailed review. We have made some additional corrections, clarifications, and revisions, as directed by your comments. To assist in your review, we refer to specific locations of each of the changes using \respto{1-XX}.

\review{(1.1) 1. Background. The paper builds upon a number of previous studies. However, several key questions have no answer: *What is* the bellwhether? *Why is* this relevant? How does it work when applied to different contexts? Why is this useful in practice? None of these questions are addressed in the paper. This submission should be self-contained and allow a reader to understand its content without reading 10 other papers; in this sense, the submission fails completely. For example, the paper mentions that: "The core intuition of this new approach is that if many projects are similar, then we do not need to run comparisons between all pairs of projects": very good, but where this intuition come from?}

### 2020-02-12 manuscript.tex
Updates from Overleaf

@@
 \usepackage{booktabs}
-\usepackage{minted}
+% \usepackage{minted}
 \usepackage[framemethod=tikz]{mdframed}
@@
 \newcommand{\tab}[1]{Table~\ref{tab:#1}}
+
+\newcommand{\tbl}[1]{Table~\ref{tbl:#1}}
 \definecolor{comment_color}{rgb}{0.5, 0, 1}
@@
 \definecolor{LightCyan}{rgb}{0.88,1,1}
-\definecolor{darkgray}{gray}{0.6}
+\definecolor{darkgray}{gray}{0.7}
 \definecolor{Gray}{rgb}{0.88,1,1}
@@
 \definecolor{lightergray}{rgb}{0.85, 0.85, 0.85}
+\definecolor{darkgray}{rgb}{0.47, 0.47, 0.47}
 \definecolor{lightestgray}{rgb}{0.95, 0.95, 0.95}
@@
 \begin{document}
-\title{  Learning GENERAL Principles \\from Hundreds of     Projects}
+\title{  Learning GENERAL Principles from\\Hundreds of    Software Projects}
 
@@
 \begin{abstract}
-
-This paper seeks scalable methods for learning general lessons from hundreds of software projects.
-When one   exemplar project (the ``bellwether'') offers the best advice, it can be used to offer    advice for
-many others.
-These bellwethers can be used to make quality predictions about new projects (even before there is much experience with those new projects).
-Such general conclusions   simplifies     software quality policies (since the list of quality problems, and their mitigations, is static);   the cost of  training (since ``best practices'' are now constant); and tool development (since it is clear where it is most cost-effective to buy/build tools to mitigate
-for software quality issues).
-
-But finding that bellwether is a slow process since that needs an  analysis of all pairs of projects. 
-Hence,  we  propose GENERAL:  a novel bellwether based on
+When one   exemplar project, which we call the ``bellwether'', offers the best advice
+then
+it can be used to offer    advice for
+many other projects. Such bellwethers can be used to make quality predictions about new projects, even before there is much experience with those new projects. 
+% Such general conclusions   simplifies     software quality policies since the list of quality problems, and their mitigations, is static).
+Also such general conclusions simplify the design and delivery
+% of training programs since, as long as the bellwether offers best advice,
+% then  ``best practices'' will remain  now constant.
+% Lastly, bellwethers simplify tool development
+% since, using the advice from the bellwether,  it is clear where it is most cost-effective to buy/build tools to mitigate
+% for software quality issues.
+
+But  existing  methods  for  bellwether  transfer  are  very slow.  When  applied  to  the  697  projects  studied  here,  they took  60  days  of  CPU  to  find  and  certify  the  bellwethers
+Hence,  we  propose GENERAL:  a novel bellwether detection algorithm based on
   hierarchical clustering. At each level within a tree of clusters, one bellwether is computed from sibling projects, then promoted up the tree. 
@@
 large data sets. 
-For example, the defect prediction models found by GENERAL from
-nearly 700 projects were  just as good as those found via  traditional methods.
+For example, for nearly 700 projects,
+the defect prediction models generated from GENERAL's bellwether  
+were  just as good as those found via  standard methods.
+
+% Having shown that it is
+% possible to transfer lessons learned across
+%  100s of projects, our future work
+%  will be to  achieve ``mega-transfer'';
+%  i.e. to transfer lessons learned between
+%  1000s to 10,000s of projects.
 
@@
 \begin{IEEEkeywords}
-Transfer Learning, Bellwether, Defect Prediction, Scalable Method. 
+Transfer Learning, Bellwether, Defect Prediction, Software Analytics. 
 \end{IEEEkeywords}}
@@
   tremendous practical significance.
-When new projects arrive, then even before there is much experience with those new projects,  lessons learned from other projects can be applied to the new project (just by querying the bellwether),
+When new projects arrive, then even before there is much experience with those new projects,  lessons learned from other projects can be applied to the new project (just by studying the bellwether),
  Further, since the bellwether is equivalent to the other models,
- then when new projects appear, their quality can be evaluated even before there is an extensive experience base within that particular project (just by applying the bellwether).
+ then when new projects appear, their quality can be evaluated even before there is an extensive experience base within that particular project (again, just by studying the bellwether).
  %That is, bellwethers can be queried  to find general lessons about (a)~major quality issues;
@@
 {\em 
-Learning from many other projects is better than learning just from your own project data.
+Learning from many other projects can be better than learning just from your own local project data.
 }\end{quote}
@@
     \centering
-    \includegraphics[width=\linewidth]{figs/cost.png}
+    \includegraphics[width=\linewidth]{figs/cost.pdf}
     \caption{Hypothetical cost comparison between GENERAL and default Bellwether.}
@@
 \end{figure} 
-Using GENERAL, we can  explore five research questions:
-
-\begin{itemize}
-        \item 
-            \textbf{RQ1}:  What are the drawbacks of traditional bellwether  methods?
+Using GENERAL, we can  explore these research questions:
+
+            \textbf{RQ1}:   Can hierarchical clustering tame the complexity of bellwether-based reasoning?
 
             \begin{RQ}{
-                With hundreds of projects, traditional bellwether methods can discover  source datasets which offer general lessons for all the rest.
-But this traditional approach can require hundreds of hours of computations and will not scale to larger data sets.
-}
+               Theoretically and empirically, the 
+hierarchical
+reasoning on GENERAL performs much
+faster than standard bellwether methods.}
             \end{RQ}
 
-        \item 
-            \textbf{RQ2}: How to tame complexity of bellwether?
+           \noindent \textbf{RQ2}:  Is this faster bellwether effective?
 
             \begin{RQ}{
-                The proposed new  transfer learner called GENERAL uses hierarchical data clustering is order of magnitude faster for discovering a source project both in term of number of comparison and run-time.}
+                Measured in terms of predictive performance,
+the effectiveness of hierarchical bellwethers
+is very similar to local learning
+(and these two methods are more effective
+than the other options explored here).}
             \end{RQ}
 
-        \item 
-            \textbf{RQ3}:  Is this faster bellwether effective?
+       \noindent 
+            \textbf{RQ3}: Does learning from too many projects have detrimental effect?
 
             \begin{RQ}{
-                The new transfer learner GENERAL  is statistically as effective as or sometime even better then the default bellwether which is an exhaustive search and local learning. }
+            Assessed in terms of {\em recall},
+it is better to learn bellwethers from more data rather than less.
+But assessed in terms of {\em false alarms}, 
+while learning bellwethers
+from many projects is useful, it is possible to learn from too much data.}
             \end{RQ}
 
-        \item 
-            \textbf{RQ4}: Does learning from too many projects have detrimental effect?
+         \noindent 
+            \textbf{RQ4}: What exactly did we learn from all those projects?
 
             \begin{RQ}{
-                Based on the results seen in this study we can see learning from too many projects does have a detrimental effect in-term of predictive power and shows conclusion instability.}
+                The importance of many key features is not apparent at the local
+level. To fully appreciate the critical impact on defects
+of class interface design,  it is necessary to conduct
+a global analysis across hundreds of projects. }
             \end{RQ}
 
-        \item 
-            \textbf{RQ5}: What exactly did we learn from all those projects?
-
-            \begin{RQ}{
-                Based on the results seen in this study, our best models uses only a fraction of the features in the dataset.
-Looking at the selected metrics, we can conclude that in these 697 projects, code interface issues are the dominant factor on software defects.
-}
-            \end{RQ}
-
-    \end{itemize}
-Overall, the  contributions of this paper are
-\bi
-
-\item \textbf{Hierarchical bellwethers for  transfer learner:} A hierarchical clustering based \textit{bellwether method} algorithm GENERAL to find \textit{bellwether effect} in datasets by finding a source project for the transfer learner.
-The algorithm uses bellwether selection and bellwether promotion (described in section~\ref{GENERAL}) to find bellwether in hierarchical cluster and promote the bellwethers to upper levels in a divide and conquer approach.
-
-\item \textbf{Showing inherent generality in SE}  In this study we discover a source data set for transfer learner from a large number of   projects, hence proving generality in the SE datasets (where some datasets can act as exemplars for the rest of them for defect prediction).
+\noindent Overall, the  contributions of this paper are
+\bi
+
+\item \textbf{Hierarchical bellwethers for  transfer learner:} We
+offer a  novel hierarchical clustering    bellwether algorithm  called GENERAL  (described in section~\ref{GENERAL}) that
+finds bellwether in hierarchical clusters, then promotes those bellwether to upper levels
+The final  project that is promoted to the root of the hierarchy is returned as  ``the'' bellwether.
+
+\item \textbf{Showing inherent generality in SE:}
+In this study we discover a source data set for transfer learner from a large number of   projects, hence proving generality in the SE datasets (where some datasets can act as exemplars for the rest of them for defect prediction).
 
@@
 \ei
-
 The rest of this paper is structured as follows.
-.
 Some background and related work are discussed in section~\ref{sec:literature}.
@@
 
-\begin{figure}[!b]
+\begin{figure}[!t]
     \centering
-    \includegraphics[width=\linewidth]{figs/predictive_power.png}
+    \includegraphics[width=\linewidth]{figs/predictive_power.pdf}
     \caption{Two hypothetical results about how training set size might effect the efficacy of quality prediction for software projects.}
@@
 Just to balance the above argument,
-we add that   sometimes it is possible to learn from
-{\em too much data}.
+we add that   sometimes it is possible to learn from {\em too much data}.
 Petersen and Wohlin~\cite{Petersen2009} argue that for empirical SE, context matters.
@@
 Consider the hypothetical results of Figure~\ref{fig:predictive_power}.
-The \textcolor{ao(english)}{{\bf GREEN}} curve shows some quality predictor that (hypothetically) gets better, the more projects it learns from (i.e.
+The \textcolor{blue}{{\bf BLUE}} curve shows some quality predictor that (hypothetically) gets better, the more projects it learns from (i.e.
 higher levels in the hierarchical cluster).
-After about 2 levels, the \textcolor{ao(english)}{{\bf GREEN}} curve's growth stops and we would say that community size here was around cluster size in level 1.
+After about learning from 1000 projects, the \textcolor{blue}{{\bf BLUE}} curve's growth stops and we would say that community size here was around cluster size in level 1.
 In this case, while we could not offer a single model that covers {\em all} of SE, we could offer a handful of models, each of which would be relevant to project clusters at that level.
-Accordingly, we would say that there are many cases where  wisdom from prior projects can be readily applied to guide future projects and (b)~the generality issues raised are not be so pressing.
+%Accordingly, we would say that there are many cases where  wisdom from prior projects can be readily applied to guide future projects and (b)~the generality issues raised are not be so pressing.
 
@@
 general models outperformed by specialized models localized to particular parts of the data.
-Menzies et al.
-showed in their paper about local vs global learning in defect prediction and effort estimation domain that using a rule based learner locality based learning was much effective than rules learned from the global dataset.
-While Herbold et al.~\cite{herbold2017global} in their study regarding global vs local model for cross-project defect prediction showed evident proof that local models make only a minor difference in comparison to global models.
-While local can cause conclusion instabilities, global models can miss details which are specific to a certain dataset.
-So in this study, we review the evidence that if it is useful to explore more than just the local data.
-This evidence falls into four groups:
+For example.
+Menzies et al. explored local vs global learning in defect prediction and effort estimation~\cite{menzies2012local}  and found that
+ learning rules from specific local data was more
+ effective than learning rules from the global space.
+
+On the other hand,
+Herbold et al.~\cite{herbold2017global}  offered an opposite conclusion.
+In their   study regarding global vs local model for cross-project defect prediction,
+they saw that  local models offered little to no improvement over models learned
+from all the global data.
+One explanation for this discrepancy  is the size of number of projects that they explored.
+Menzies, Herbold et al.
+explored less than two dozen projects which raises issues of external validity in their conclusions.
+Accordingly, here,  we explore nearly 700 projects.
+As shown below, the results of this paper agree  more with Herbold et al.
+than  Menzies et al.
+since we show that one global model (learned from a single bellwether projects) does just as well as anything else.
+
+Apart from the above discrepancy in research results, there are many other reasons to
+explore learning from many projects. Those reasons   falls into four groups:
 
@@
 And how would you draw conclusions from that large set?
+Note that the answers to these questions requires learning from multiple projects.
+Hence, this paper.
 
@@
 \item    
+ \textbf{Heterogeneous Transfer Learning:} This type of transfer learning operates on source and target data that contain the different attributes.
+
+\item
 \textbf{Homogeneous Transfer Learning:} This kind of transfer learning operates on source and target data that contain the same attributes.
-\item    
- \textbf{Heterogeneous Transfer Learning:} This type of transfer learning operates on source and target data that contain the different attributes.
+This paper explores scalable methods for  homogeneous transfer.
 \ei
@@
 Other researchers ~\cite{kocaguneli2012, kocaguneli2011find} doubted that a fixed value of k was appropriate for all data.
-That work recursively bi-clustered the source data, then pruned the cluster sub-trees with greatest ``varianc'' (where the ``variance'' of a sub-tree is the variance of the conclusions in its leaves).
+That work recursively bi-clustered the source data, then pruned the cluster sub-trees with greatest ``variance'' (where the ``variance'' of a sub-tree is the variance of the conclusions in its leaves).
 This method combined row selection with row pruning (of nearby rows with large variance).
@@
 
-% \begin{figure}[!t]
-%     \small
-%      %\begin{lstlisting}[mathescape,linewidth=7.5cm,frame=none,numbers=right]
-%     ~~~~~~\inputminted[numbersep=1pt, linenos=true, fontsize=\scriptsize]{python}{pseudocode/bubble.py}
-%     %\vspace{-0.2cm}
-%     \caption{Pseudo-code of GENERAL Experiment}
-%     \label{fig:GAP_pseudocode} 
-%     %\vspace{-0.3cm}
-% \end{figure}
-
-% \begin{figure}[!t]
-%      %\begin{lstlisting}[mathescape,linewidth=7.5cm,frame=none,numbers=right]
-%         \begin{minipage}{\linewidth}
-%             \inputminted[numbersep=2pt, linenos=true, fontsize=\scriptsize]{python}{pseudocode/heirarchical_bellw.py}
-%         \end{minipage}
-%     %\vspace{-0.2cm}
-%     \caption{Pseudo-code of Hierarchical Bellwether}
-%     \label{fig:GAP_pseudocode} 
-%     %\vspace{-0.3cm}
-% \end{figure}
-
  Our proposed improvement to bellwethers is called GENERAL.
@@
  \be
- \item Sumamrize the projects via {\bf feature extraction} (see \S\ref{sec:fx}).
+ \item Summarize the projects via {\bf feature extraction} (see \S\ref{sec:fx}).
  \item Using some clustering algorithm, group all our data into sets of similar projects.
@@
  \fig{cost} contrasts the computational cost of Equation~\ref{eq:GENERAL} with Equation~\ref{eq:bellwether}   
- (and that figure assumes $m=20$, which is the devision constant we used in these experiments-- see below.).
- As seen in that figure,  the $O(m*(N/m)^2)$ analysis is inherently far more scalable than the $O(N^2)$ analysis  required by standard bellwether.
+ (and that figure assumes $m=20$, which is the division constant we used in these experiments-- see below.).
+ As seen in that figure,  the $O(m*(N/m)^2)$ analysis is inherently   more scalable than the $O(N^2)$ analysis  required by standard bellwether.
 
@@
 The process metrics are computed using the change history in the six-months period before the split date via manual collection of data using scripts.
-
-\begin{figure}
+The data collected for this project is summarized in \fig{lang_projects}
+ and \fig{meta}.
+
+\begin{figure}[!b]
 \centering
@@
     \textbf{Language} & \textbf{Projects} & \\
-    Java & 290 &\rule{41.6pt}{8pt} \\
-    CPP & 241 &\rule{34.5pt}{8pt} \\
-    C & 116 &\rule{16.6pt}{8pt} \\
-    CS & 42 &\rule{6.3pt}{8pt} \\
-    Pascal & 8 &\rule{1.1pt}{8pt} \\
+    Java & 290 &\crule{41.6pt}{8pt} \\
+    CPP & 241 &\crule{34.5pt}{8pt} \\
+    C & 116 &\crule{16.6pt}{8pt} \\
+    CS & 42 &\crule{6.3pt}{8pt} \\
+    Pascal & 8 &\crule{1.1pt}{8pt} \\
      & 
@@
 Many  projects use combinations of languages to
-achieve their results. Here, we show majority language used in the project.}
+achieve their results. Here, we show majority language used in each project.}
 \label{fig:lang_projects}
@@
     \centering
-    \includegraphics[width=\linewidth]{figs/meta.pdf}
+    \includegraphics[width=.8\linewidth]{figs/meta.pdf}
     \caption{Distribution of projects depending on Defect Percentage, Data set Size, Lines of Code and Number of Files.}
@@
 \end{tabular}
-\caption{List of software metrics used in this study}
+\caption{List of software metrics used in this study.}
 \label{tbl:metric}
@@
  Google Scholar reports that  the original  paper proposing BIRCH has been cited over 5,400 times.
-For this experiment we have set BIRCH's branching factor as 20 and  threshold  value  as  0.5.
+For this experiment we used defaults proposed by~\cite{zhang1996birch}; a   branching factor of 20 and  the ``new cluster creation'' threshold  of  0.5.
 
@@
 Each subset is  scored via
-$\mathit{merit}_s = k\overbar{r_{\mathit{cf}}}/\sqrt{k+k(k-1)\overbar{r_{\mathit{ff}}}}$
+$\mathit{merit}_s = kr_{\mathit{cf}}/\sqrt{k+k(k-1)r_{\mathit{ff}}}$
 where
@@
 Note that for this to be maximal, $r_{\mathit{cf}}$  must be large
-and $r_{\mathit{ff}}$ must be small. That is, features have to connect
-more to the class than each other.}. 
+and $r_{\mathit{ff}}$ must be small. That is, features have to connect more to the class than each other.}. 
 \ei
@@
 An alternative to the Zitler indicator is    `boolean domination ''
- that says one thing is better than another it if it no worse on any criteria and better on at least one criteria. We prefer Equattion~\ref{eq:cdom} to boolean domination since we
+ that says one thing is better than another it if it no worse on any criteria and better on at least one criteria. We prefer Equation~\ref{eq:cdom} to boolean domination since we
  have a   5-goal optimization problem and it it is known that boolean domination often  fails for 3 or more goals~\cite{Wagner:2007,Sayyad:2013}.
@@
     \includegraphics[width=\linewidth]{figs/General.pdf}
-    \caption{GENERAL algorithm.}
+    \caption{ Experimental rig for this paper.  In this rig, 
+      bellwethers are
+    learned and tested on {\em separate } projects. Within the test set (denoted ``test1``, above),
+    the data is further divided into ``train2, test2``. To assess the bellwether found from ``train1`` against local learning, data from each project is divided into ``train2,test2``
+    then (a)~local
+    models are learned from   ``train2``; after which time,
+    (b)~the local models from ``train2'' and the bellwether model from ``train1``
+    are both applied to the same data from ``test2``.
+    Note that this process is repeated 20 times, with different random number seeds, to generate 20 different sets of ``train1, train2, test2``.
+    }
     \label{fig:GENERAL}
@@
 
-    \item \textbf{Aovid projects with limited defect data:} Zhang et al.
+    \item \textbf{Avoid projects with limited defect data:} Zhang et al.
 in their study counted the number of fix-inducing and non-fixing commits from a one-year period and removed any projects with 75 \% quantile of the number of fix-inducing and non-fixing commits.
@@
     \item \textbf{Avoid projects with less than 50 rows:} We removed any project with less than 50 rows as they are too small to build a meaningful predictor. 
-       \item \textbf{Avoid pojects with too few errors:}
+       \item \textbf{Avoid projects with too few errors:}
     We pruned  projects which did not  have enough fix-inducing vs non-fixing data points to create a stratified k=5 fold cross-validation an
@@
 These filters resulted in a training set of   697 projects\footnote{\href{http://tiny.cc/bellwether_data}{http://tiny.cc/bellwether\_data}}.
+Fig~\ref{fig:meta} and fig~\ref{fig:lang_projects} shows the Distribution of projects depending on defect percentage, data set size, lines of code, number of files and project languages to confirm the projects selected comes from wide verity and representative of a software community.
 From these selected projects, the data was labeled using issue tracking system and commit messages.
@@
 
-To report the finding and results of this study without any bias, we repeat the experiment 20 times by dividing the dataset randomly into train\_1 and test\_1 as a 90-10 split, the projects in train\_1 was used to find the bellwether in each cluster in the CF Tree, and then each project in test\_1 was divide into train\_2 and test\_2 split.
-We trained a LR model using train\_2 for each project and tested on test\_2, this is represented as self test in this study.
-We also used the predict stage of the GENERAL to identify bellwether for each project in test\_1 and tested the performance on test\_2.
+\fig{GENERAL} illustrates our experimental rig. 
+ The following process was repeated 20 times, with different random seeds used each time.
+ \bi
+ \item
+ Projects were divided
+ randomly into train\_1 and test\_1 as a 90:10 split.
+ \item
+ The projects in train\_1 were used to find the bellwether .
+ \item
+ Each   project in test\_1 was  then divide into train\_2 and test\_2 (using a 2:1 split).
+ \item
+ LR and feature selection and SMOTE were then used
+ to build two models: one from the train\_1 bellwether and one from the train\_2
+ data.
+ \item
+ Both models were then applied to the test\_2 data.
+ \ei
 
@@
 
+\subsection{Learners}\label{mylearners}
+
+In this study, we applied the follow learners:
+
+%
+
+\textbf{Self:} (a.k.a. local learning). This  is the standard method used in software analytics~\cite{menzies2013software,zhang2013software}.
+In this approach, the local project data is divided into a 90\% training set (which we call  train\_2)
+and a 10\% test set (which we call test\_2). After that, some some learner builds a model from the training data
+(using the methods of \S\ref{sec:Experimental}),
+which is then assessed on the test data.
+
+As we shall see, this approach produces competent defect predictors.
+Recalling
+the motivation of this paper: we do not
+seek   better predictor that is (say) more accurate
+than {\bf self}.
+That is, hierarchical bellwethers can be recommended even if they {\em 
+perform  no better  than {\bf self}}. Rather:
+\bi
+\item
+As listed
+in the motivations of
+\S\ref{sec:Motivation}, we seek ways to make conclusions
+across a wide number of projects. 
+\item
+That is, our goal is to test if hierarchical bellwethers
+can quickly  find a  small set of {\em adequate conclusions}
+that hold across a large space 
+of projects. 
+\ei
+So, here, by ``adequate'', we mean conclusions
+that perform no worse than those found by other methods.
+
+\textbf{ZeroR:} 
+In his textbook on ``Empirical AI", Cohen~\cite{Cohen:1995} recommends base-lining new methods against some simpler approach.
+For that purpose, we use {\bf ZeroR} learner. This learner assigns labels every test instance according to
+the majority class of the training data. Note that if anything we do performs worse that ZeroR, then there is no
+point to any of the learning technology explored in this paper.
+
+\textbf{Global:}  Another baseline, against which we compare our methods
+is a {\bf Global} learner build using all the data   train\_1.
+Note that, if this learner performs best, then this  would  mean that we could replace GENERAL with a much simpler system.
+
+\textbf{Bellwether0:} This learner is the  $O(N^2)$ bellwether method  proposed by Krishna et al.~\cite{krishna16a}.
+What will we show is that GENERAL does better than {\bf Bellwether0} is three ways:
+(a) GENERAL is inherently more scalable; (b) GENERAL is (much) faster; and (c) GENERAL produced better predictions.
+That is, our new GENERAL method is a significant improvement over the prior state-of-the-art.
+
+\textbf{GENERAL\_level2:}  GENERAL finds bellwethers at various levels of the BIRCH cluster tree.
+GENERAL\_level2 results show the performance of the model learned from the bellwether found in the leaves of the  BIRCH cluster tree.
+That is these results come from  a bellwether generated from 15 to 30 projects.  
+For this process:
+\bi
+\item
+First, we tag each leaf cluster with its associated bellwether;
+\item
+Second, we use the test procedure built into BIRCH; i.e. a test case is presented to the root
+of the cluster tree and BIRCH returns its {\em relevant  leaf};
+i.e. the cluster closest to that test case.
+\item
+We then apply the bellwether tagged at that leaf.
+\ei
+\textbf{GENERAL\_level1:}  GENERAL\_level1 results show the performance of the model learned from the bellwether found between the root and   the leaves of the  BIRCH cluster tree.
+In practice, BIRCH divides our data only twice
+so there is only one GENERAL\_level1  between root and leaves. For this process,
+we use the same procedure as GENERAL\_level2 but this time, we use the bellwether tagged in the {\em parent}
+cluster of the relevant leaf. Note that these level1 results come from an analysis of between 50 to 200  projects
+(depneding on the shape of the cluster tree genrated via BIRCH).
+
+\textbf{GENERAL\_level0:}  
+In the following,  the  GENERAL\_level0 results show the performance of the model learned from the bellwether found at the root of the BIRCH cluster tree.
+Note that these results come from an analysis of over 600 projects.
+
 \subsection{Statistical Tests}
@@
 For e.g., lists $l,m$ and $n$ of size $ls,ms$ and $ns$ where $l=m\cup n$, Scott-Knott divides the sequence at the break that maximizes:
-
 \begin{equation}
-    E(\Delta)=ms/ls*abs(m.\mu - l.\mu)^2 \\ + ns/ls*abs(n.\mu - l.\mu)^2
+    E(\Delta)=\frac{ms}{ls}\times abs(m.\mu - l.\mu)^2  + \frac{ns}{ls}\times abs(n.\mu - l.\mu)^2
 \end{equation}
-
 Scott-Knott then applies some statistical hypothesis test $H$ to check if $m$ and $n$ are significantly different.
@@
 
+\subsection{Performance Measures}
+\label{sec:Measures}
+
+In this section, we introduce the following 5 evaluation measures used in this study to evaluate the performance of machine learning models.
+Suppose we have a dataset with M changes and N defects.
+After inspecting 20\% LOC, we inspected $m$ changes and found $n$ defects.
+Also, when we find the first defective change, we have inspected k changes.
+Using
+this data, we can define 5 evaluation measures  as follows:
+
+(1) \textbf{Recall:} This is the proportion of inspected defective changes among all the actual defective changes; i.e. $n/N$.
+Recall is used in  many previous studies~\cite{kamei2012large,yang2016effort,yang2017tlel,xia2016collective,yang2015deep}.
+
+(2) \textbf{Precision:} This is the proportion of inspected defective changes among all the inspected changes; i.e.
+$n/m$.
+A low Precision indicates that developers would encounter more false alarms, which may have negative impact on developers' confidence on the prediction model.
+
+(3) \textbf{pf:} This is the proportion of all suggested defective changes which are not actual defective changes among all the suggested defective changes.
+A high {\em pf} suggests developers will encounter more false alarms which may have negative impact on developers' confidence in the prediction model.
+
+(4) \textbf{popt20:} This is the proportion number of suggested defective changes among all suggested defective changes, when when 20\% LOC modified by all changes are inspected. 
+A high {\em popt20} values mean that developers can find most bugs in a small percent of the code.
+To compute Popt20, we divided the test set into the modules predicted to be faulty (set1)
+and predicted to be bug-free (set2). Each set was then sorted in ascending order by lines 
+of code.  We then ran down set1, then set2, till 20\% of the total lines of code
+were reached-- at which point {\em popt20} is the percent of buggy modules seen up to that point.
+
+(5) \textbf{ifa\_auc:} Number of  initial false alarms encountered before we find the first defect.
+Inspired by previous studies on fault localization~\cite{parnin2011automated,kochhar2016practitioners,xia2016automated}, we caution that if the top-k changes recommended by the model are all false alarms, developers would be frustrated and are not likely to continue inspecting the other changes.
+For example, Parnin and Orso ~\cite{parnin2011automated} found that developers would stop inspecting suspicious statements, and turn back to traditional debugging, if they could not get promising results within the first few statements they inspect.
+Using the nomenclature reported
+about {\em Ifa$=k$}.
+In this study we use a modified version of {\em ifa} called ifa\_auc, which calculates {\em ifa} based on efforts spent on inspecting the code.
+We use gradually increment the efforts spent by increasing the total LOC inspected and calculate ifa on each iteration to get the area under the curve (auc), here the x-axis is the percentage of effort spent on inspection and y-axis is {\em ifa}.
+
+\section{Results}
+\label{sec:results}
+
+\subsection*{RQ1: Can hierarchical clustering tame the complexity of bellwether-based reasoning?}
+\label{sec:rq1}
+
+% In the literature, we saw most of the previous studies have shown bellwether effect with very small datasets.
+In order to use bellwether to prove presence of generality in SE domain datasets, we first have to showcase the bellwether method suggested by Krishna et al.
+in their experiment works for large datasets.
+We use our defect prediction dataset with 697 projects for this purpose.
+
+% We divide the dataset in train\_1 and test\_1 set and then performed a $ N*(N-1) $ comparison on all the projects in train\_1 set to find a bellwether, and then dividing each project in test\_1 set into train\_2 and test\_2 using a train\_test split.
+We use the train\_2 to train a LR model and test on test\_2 which is represented as \textit{self} in the figures.
+Similarly we use the bellwether project from train\_1 to train a LR model and test it on test\_2 which is represented as \textit{bellwether0}.
+We use statistical tests mentioned in section~\ref{stats} to compare the performance of \textit{self} vs \textit{bellwether0} for all the performance measures mentioned in section~\ref{sec:Measures}, which is shown
+
+\fig{cost} showed that, theoretically,
+GENERAL is an inherently faster approach than traditional bellwether methods.
+To test that theoretical
+conclusion,
+we ran the rig of \fig{GENERAL} on
+an four core machine running at 2.3GHz with 8GB of RAM.
+
+\begin{figure}[!b]
+    \centering
+    \includegraphics[width=\linewidth]{figs/Time.png}
+    \caption{Mean runtime for for one run of standard bellwether and GENERAL.}
+    \label{fig:time}
+\end{figure}
+
+\fig{time} shows the mean runtimes for one run of GENERAL versus traditional bellwether. For certification purposes, this had to be repeated 20 times. In that certification run:
+\bi
+\item
+The $O(N^2)$ analysis of the traditional {\em bellwether0} approach needed 60 days of CPU time.
+\item 
+The $O(m*(N/m)^2)$ analysis
+of GENERAL needed 30  hours. That is, in empirical
+ result consistent with the theoretical predictions of \fig{cost}, GENERAL runs much faster than traditional bellwether.
+\item All the other methods required
+another 6 hours of computation. 
+\ei
+If we were merely seeking conclusions from one project, then we would recommend ignoring bellwethers
+and just use results from each project. That said, we still endorse bellwether method since  we seek
+lessons that hold across many projects.
+
+In summary, based on these results, we conclude that:
+
+\begin{RQ}{Theoretically and empirically, the  hierarchical reasoning on GENERAL performs much faster than standard bellwether methods.}
+\end{RQ}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%Latex Table%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[!b]
+{\scriptsize
+{\scriptsize \begin{tabular}{p{.1cm}lp{1.5cm}rrc}
+\arrayrulecolor{darkgray}
+\rowcolor[gray]{.9}  & rank & treatment & mean & sd & \\
+ \multirow{5}{*}{\rotatebox[origin=c]{90}{Recall}} 
+  &   1 &      GENERAL\_level2 &    38 &  32 & \quart{22}{38}{32}{16} \\
+  &   1 &      bellwether0 &    39 &  31 & \quart{23}{39}{31}{15} \\
+  &   1 &  ZeroR &    40 &  49 & \quart{16}{40}{49}{25} \\
+  &   2 &      GENERAL\_level1 &    48 &  33 & \quart{31}{48}{33}{16} \\
+  &   3 &      self &    55 &  27 & \quart{41}{55}{27}{12} \\
+  &   3 &      GENERAL\_level0 &    56 &  31 & \quart{42}{56}{31}{16} \\
+  &   4 &      global &    78 &  40 & \quart{57}{78}{40}{20} \\ \hline
+\multirow{5}{*}{\rotatebox[origin=c]{90}{Pf}} 
+  &  1 &      GENERAL\_level2 &    28 &  28 & \quart{14}{28}{28}{13} \\
+  &  1 &      bellwether0 &    28 &  25 & \quart{15}{28}{25}{11} \\
+  &  1 &      self &    30 &  20 & \quart{20}{30}{20}{10} \\
+  &  1 &      GENERAL\_level1 &    35 &  28 & \quart{21}{35}{28}{14} \\
+  &  1 &      ZeroR &    39 &  49 & \quart{15}{39}{49}{25} \\
+  &  2 &      GENERAL\_level0 &    47 &  31 & \quart{31}{47}{31}{15} \\
+  &  3 &      global &    79 &  39 & \quart{59}{79}{39}{19} \\\hline
+\multirow{5}{*}{\rotatebox[origin=c]{90}{Precision}} &   1 &      ZeroR &    21 &  30 & \quart{6}{21}{30}{15} \\
+    &  2 &      global &    35 &  28 & \quart{21}{35}{28}{14} \\
+    &   2 &      GENERAL\_level2 &    39 &  34 & \quart{22}{39}{34}{17} \\
+    &   2 &      bellwether0 &    40 &  33 & \quart{23}{40}{33}{16} \\
+    &   2 &      GENERAL\_level1 &    42 &  31 & \quart{26}{42}{31}{15} \\
+    &   2 &      GENERAL\_level0 &    44 &  30 & \quart{28}{44}{30}{15} \\
+    &   2 &      self &    50 &  30 & \quart{35}{50}{30}{15} \\\hline
+\multirow{5}{*}{\rotatebox[origin=c]{90}{Popt20}} &   1 &      ZeroR &    13 &  16 & \quart{5}{13}{16}{8} \\
+  & 2 &      GENERAL\_level2 &    26 &  22 & \quart{15}{26}{22}{11} \\
+  &  2 &      global &    26 &  13 & \quart{19}{26}{13}{6} \\
+  &  2 &      bellwether0 &    28 &  21 & \quart{17}{28}{21}{9} \\
+  &  2 &      GENERAL\_level0 &    28 &  15 & \quart{22}{28}{15}{8} \\
+  &  2 &      GENERAL\_level1 &    28 &  19 & \quart{19}{28}{19}{9} \\
+  &  3 &      self &    35 &  19 & \quart{26}{35}{19}{10} \\\hline
+\multirow{5}{*}{\rotatebox[origin=c]{90}{ifa\_auc}} &   1 &      ZeroR &    7 &  11 & \quart{1.12}{6.77}{11.29}{5.65} \\
+  &  2 &      global &    19 &  16 & \quart{11.35}{19.38}{16.06}{8.03} \\
+  &  3 &      GENERAL\_level2 &    22 &  14 & \quart{14.48}{21.59}{14.21}{7.10} \\
+  &  3 &      bellwether0 &    23 &  14 & \quart{15.48}{22.56}{14.15}{7.07} \\
+  &  3 &      self &    23 &  12 & \quart{17.09}{22.93}{11.68}{5.84} \\
+  &  3 &      GENERAL\_level1 &    23 &  14 & \quart{16.10}{22.98}{13.74}{6.87} \\
+  &  3 &      GENERAL\_level0 &    25 &  13 & \quart{17.87}{24.51}{13.27}{6.63} \\
+\end{tabular}}
+}
+\caption{Statistical Results comparison. The ``rank`` column at left comes from
+the statistical analysis methods of \S\ref{eval}. Note that for {\em pf}, and {\em ifa} rank=1 is the best rank while for all other performance measures, ranks $\in{3,4}$ are best. 
+}\label{fig:Statistical}
+\end{figure}
+
 {\small 
-\begin{figure*}[ht!]
+\begin{figure*}[!t]
     \centering
-    \begin{tikzpicture}[nodes={draw, circle,fill=pink!50}, ->,sibling distance=.7cm,minimum size=.1cm,scale=.5]
+    \begin{tikzpicture}[nodes={draw, circle,fill=darkgray!60}, ->,sibling distance=.7cm,minimum size=.1cm,scale=.5]
 
@@
 }
-
-\subsection{Performance Measures}
-\label{sec:Measures}
-
-In this section, we introduce the following 5 evaluation measures used in this study to evaluate the performance of machine learning models.
-Suppose we have a dataset with M changes and N defects.
-After inspecting 20\% LOC, we inspected m changes and found n defects.
-Besides, when we find the first defective change, we have inspected k changes.
-Then the 5 evaluation measures are defined and computed as follows:
-
-(1) \textbf{Recall:} Proportion of inspected defective changes among all the actual defective changes.
-This is the evaluation measure used by many previous studies~\cite{kamei2012large,yang2016effort,yang2017tlel,xia2016collective,yang2015deep}.
-They focused on achieving high Recall so that more defective changes could be detected.
-Recall is computed as: $n/N$.
-
-(2) \textbf{Precision:} Proportion of inspected defective changes among all the inspected changes.
-A low Precision indicates that developers would encounter more false alarms, which may have negative impact on developers' confidence on the prediction model.
-Precision is computed as: $n/m$.
-
-(3) \textbf{pf:} Proportion of all suggested defective changes which are not actual defective changes among all the suggested defective changes.
-A high pf suggests developers will encounter more false alarms which may have negative impact on developers' confidence in the prediction model.
-
-(4) \textbf{popt20:} Proportion number of suggested defective changes among all suggested defective changes, when when 20\% LOC modified by all changes are inspected.
-A high popt20 indicates that, under the same number of LOC to inspect, developers will find more bugs, which means developers will be able to fix more defects with the same amount of effort invested.
-
-(5) \textbf{ifa\_auc:} Number of Initial False Alarms encountered before we find the first defect.
-Inspired by previous studies on fault localization~\cite{parnin2011automated,kochhar2016practitioners,xia2016automated}, we assume that if the top-k changes recommended by the model are all false alarms, developers would be frustrated and are not likely to continue inspecting the other changes.
-For example, Parnin and Orso ~\cite{parnin2011automated} found that developers would stop inspecting suspicious statements, and turn back to traditional debugging, if they could not get promising results within the first few statements they inspect.
-ifs is computed as: k.
-In this study we use a modified version of ifa called ifa\_auc, which calculates ifa based on efforts spent on inspecting the code.
-We use gradually increment the efforts spent by increasing the total LOC inspected and calculate ifa on each iteration to get the area under the curve (auc), here the x-axis is the percentage of effort spent on inspection and y-axis is ifa.
-
-\section{Results}
-\label{sec:results}
-
-\subsection*{RQ1: What are the drawbacks of traditional bellwether  methods?}
-\label{sec:rq1}
-
-In the literature, we saw most of the previous studies have shown bellwether effect with very small datasets.
-In order to use bellwether to prove presence of generality in SE domain datasets, we first have to showcase the bellwether method suggested by Krishna et al.
-in their experiment works for large datasets.
-We use our defect prediction dataset with 697 projects for this purpose.
-
-We divide the dataset in train\_1 and test\_1 set and then performed a $ N*(N-1) $ comparison on all the projects in train\_1 set to find a bellwether, and then dividing each project in test\_1 set into train\_2 and test\_2 using a train\_test split.
-We use the train\_2 to train a LR model and test on test\_2 which is represented as \textit{self\_0} in the figures.
-Similarly we use the bellwether project from train\_1 to train a LR model and test it on test\_2 which is represented as \textit{bellwether0}.
-We use statistical tests mentioned in section~\ref{stats} to compare the performance of \textit{self\_0} vs \textit{bellwether0} for all the performance measures mentioned in section~\ref{sec:Measures}, which is shown in figure~\ref{fig:Statistical}.
-
-It is evident that using the \textit{bellwether method} proposed by Krishna et al.
-we were able to find bellwether effect in large dataset with 697 projects.
-This answers this RQ and creates the baseline results for our study.
-In this RQ1 although we are able to find \textit{bellwether effect}, this method is very expensive, requiring a $ N*(N-1) $ comparison, which in our experimental setup took nearly 3 days of computation.
-Which takes us to the next research question.
-In summary, we find that
-
-\begin{result} {Bellwethers are found when studying over 697 software projects.
-However, conventional methods of Krishna et al~\cite{krishna2017learning} take far too long to discover these bellwethers, e.g., experimentation took 3 days to find a bellwether project from among the 697 projects.}
-\end{result}
-
-\subsection*{RQ2: How to tame complexity of bellwether?}
-\label{sec:rq2}
-
-To tame complexity of bellwether in this RQ, we propose a new bellwether method called GENERAL to find bellwether in large datasets.
+%%%%%%%%%%%%%%%%%%%%%%%End Latex Table%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% \subsection*{RQ2: Can hierarchical clustering tame the complexity of bellwether?}
+% \label{sec:rq2}
+
+% While we must deprecate standard bellwether (for learning lessons from large datasets), we can endorse the use of GENERAL.
+% Thoretically, GENERAL
+
+% To tame complexity of bellwether in this RQ, we propose a new bellwether method called GENERAL to find bellwether in large datasets.
 This bellwether method is composed of 6 stages, (a) a feature extraction process to summarize each project into a single representative vector, (b) a hierarchical clustering algorithm, which uses the feature vectors to cluster similar projects into community of increasing size at different levels of cluster, (c) a bellwether selection phase where a $N*(N-1)$ comparison is performed at each leaf level cluster and using a cdom calculation in all the metrics mentioned in~\ref{tbl:metric} a bellwether is selected, (d) a iterative bellwether promotion stage, where bellwether from child clusters are promoted as potential bellwethers at parent cluster, (e) another bellwether selection phase at non-leaf levels, where comparisons are only made among potential bellwethers from leaf node and finally (f) a bellwether prediction phase, which suggests a bellwether based on project similarity when a new project is to be predicted.
@@
 
-In the \textit{bellwether method} proposed by Krishna et al.
+% In the \textit{bellwether method} proposed by Krishna et al.
 if there are N projects in a community it will make $\approx N^2$ comparisons to discover the bellwether.
 While GENERAL different approach to discover bellwether by dividing the data into smaller cluster and finding bellwether among each, here if we assume we have m cluster at leaf level with N projects in each, we will have
-$\approx m*(N/m)^2$ comparisons to discover the bellwether which is m times less comparison.
+% $\approx m*(N/m)^2$ comparisons to discover the bellwether which is m times less comparison.
 For example if we see the example figure~\ref{fig:example tree} for hierarchically cluster a community of 627 projects, if we use the default bellwether method it will require  393,129 comparisons.
@@
 
-\begin{result}
-{GENERAL can find the bellwether project
-an order of magnitude faster than prior work
-(1.5 hours versus 3 days)
-since GENERAL  requires far fewer
- comparisons between projects
- (9,080 instead of 393,129 required for 
- Krishna et al.'s bellwether method). }
-\end{result}
-
-XXXX
-
-\begin{equation}
-\label{eq:GENERAL}
-    {GENERAL\; complexity } =  O(m*(N/m)^2)
-\end{equation}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{figs/time.png}
-    \caption{Runtime for default bellwether and GENERAL.}
-    \label{fig:time}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%Latex Table%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[!t]
-{\scriptsize
-{\scriptsize \begin{tabular}{p{.1cm}lp{1.5cm}rrc}
-\arrayrulecolor{darkgray}
-\rowcolor[gray]{.9}  & rank & treatment & mean & sd & \\
- \multirow{5}{*}{\rotatebox[origin=c]{90}{Recall}} &   1 &      random2 &    40 &  49 & \quart{16}{40}{49}{25} \\
-  &   1 &      GENERAL\_level2 &    38 &  32 & \quart{22}{38}{32}{16} \\
-  &   1 &      bellwether0 &    39 &  31 & \quart{23}{39}{31}{15} \\
-  &   2 &      GENERAL\_level1 &    48 &  33 & \quart{31}{48}{33}{16} \\
-  &   3 &      GENERAL\_level0 &    56 &  31 & \quart{42}{56}{31}{16} \\
-  &   3 &      self\_0 &    55 &  27 & \quart{41}{55}{27}{12} \\
-  &   4 &      global2 &    78 &  40 & \quart{57}{78}{40}{20} \\ \hline
-\multirow{5}{*}{\rotatebox[origin=c]{90}{Pf}} &    1 &      random2 &    39 &  49 & \quart{15}{39}{49}{25} \\
-  &  1 &      random2 &    39 &  49 & \quart{15}{39}{49}{25} \\
-  &  1 &      GENERAL\_level2 &    28 &  28 & \quart{14}{28}{28}{13} \\
-  &  1 &      bellwether0 &    28 &  25 & \quart{15}{28}{25}{11} \\
-  &  1 &      self\_0 &    30 &  20 & \quart{20}{30}{20}{10} \\
-  &  1 &      GENERAL\_level1 &    35 &  28 & \quart{21}{35}{28}{14} \\
-  &  2 &      GENERAL\_level0 &    47 &  31 & \quart{31}{47}{31}{15} \\
-  &  3 &      global2 &    79 &  39 & \quart{59}{79}{39}{19} \\\hline
-\multirow{5}{*}{\rotatebox[origin=c]{90}{Precision}} &   1 &      random2 &    21 &  30 & \quart{6}{21}{30}{15} \\
-    &  2 &      global2 &    35 &  28 & \quart{21}{35}{28}{14} \\
-    &   2 &      bellwether0 &    40 &  33 & \quart{23}{40}{33}{16} \\
-    &   2 &      GENERAL\_level2 &    39 &  34 & \quart{22}{39}{34}{17} \\
-    &   2 &      GENERAL\_level1 &    42 &  31 & \quart{26}{42}{31}{15} \\
-    &   2 &      GENERAL\_level0 &    44 &  30 & \quart{28}{44}{30}{15} \\
-    &   2 &      self\_0 &    50 &  30 & \quart{35}{50}{30}{15} \\\hline
-\multirow{5}{*}{\rotatebox[origin=c]{90}{Popt20}} &   1 &      random2 &    13 &  16 & \quart{5}{13}{16}{8} \\
-  & 2 &      GENERAL\_level2 &    26 &  22 & \quart{15}{26}{22}{11} \\
-  &  2 &      global2 &    26 &  13 & \quart{19}{26}{13}{6} \\
-  &  2 &      bellwether0 &    28 &  21 & \quart{17}{28}{21}{9} \\
-  &  2 &      GENERAL\_level0 &    28 &  15 & \quart{22}{28}{15}{8} \\
-  &  2 &      GENERAL\_level1 &    28 &  19 & \quart{19}{28}{19}{9} \\
-  &  3 &      self\_0 &    35 &  19 & \quart{26}{35}{19}{10} \\\hline
-\multirow{5}{*}{\rotatebox[origin=c]{90}{ifa\_auc}} &   1 &      random2 &    7 &  11 & \quart{1.12}{6.77}{11.29}{5.65} \\
-  &  2 &      global2 &    19 &  16 & \quart{11.35}{19.38}{16.06}{8.03} \\
-  &  3 &      GENERAL\_level2 &    22 &  14 & \quart{14.48}{21.59}{14.21}{7.10} \\
-  &  3 &      bellwether0 &    23 &  14 & \quart{15.48}{22.56}{14.15}{7.07} \\
-  &  3 &      self\_0 &    23 &  12 & \quart{17.09}{22.93}{11.68}{5.84} \\
-  &  3 &      GENERAL\_level1 &    23 &  14 & \quart{16.10}{22.98}{13.74}{6.87} \\
-  &  3 &      GENERAL\_level0 &    25 &  13 & \quart{17.87}{24.51}{13.27}{6.63} \\
-\end{tabular}}
-}
-\caption{Statistical Results comparison
-}\label{fig:Statistical}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%End Latex Table%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection*{RQ3: Is this faster bellwether effective?}
+% \begin{result}
+% {GENERAL can find the bellwether project
+% an order of magnitude faster than prior work
+% (1.5 hours versus 3 days)
+% since GENERAL  requires far fewer
+%  comparisons between projects
+%  (9,080 instead of 393,129 required for 
+%  Krishna et al.'s bellwether method). }
+% \end{result}
+
+% XXXX
+
+% \begin{equation}
+% \label{eq:GENERAL}
+%     {GENERAL\; complexity } =  O(m*(N/m)^2)
+% \end{equation}
+
+\subsection*{RQ2: Is this faster bellwether effective?}
 \label{sec:rq3}
 
-In RQ2, we can see using GENERAL we are able to find bellwether for a large dataset in order of magnitude faster.
-This raises the question is  \textit{bellwether method} GENERAL as effective as \textit{bellwether method} proposed by krishna et al.
-and can it be compared against local(self test) and global models?
-
-To answer this question in this study we have used the defect prediction dataset with 697 projects and divided the projects randomly into train\_1 and test\_1 as a 90-10 split, the projects in train\_1 was used to find the bellwether in each cluster in the CF Tree as mentioned in sec~\ref{GENERAL}, and then each project in test\_1 was divide into train\_2 and test\_2 split.
-We trained a LR model using train\_2 for each project and tested on test\_2 (represented as self\_0), this is represented as self test in this study.
-We also used the predict stage of the GENERAL to identify a bellwether in each level of hierarchical model, for each project in test\_1 and tested the performance on test\_2 (represented as bellwether\_level0, bellwether\_level1, bellwether\_level respectively).
-Similarly we used the projects in train\_1 to find the bellwether using default bellwether method as mentioned in sec~\ref{Bellwether}, and use that project to build a LR model and test the performance of each project's test\_2 (represented as bellwether0).
-And we combined all the data from train\_1, and used that to build a global model and tested on test\_2 (represented as global2).
-We compare the performance of each model described above using statistical tests as mentioned in section~\ref{stats} and if 2 models are ranked different that represents their performance is significantly different.
-
-We can see from the figure~\ref{fig:Statistical} that bellwether\_level0 model (i.e.
-the bellwether discovered by GENERAL at level 0) performs similar or  better than bellwether0 in most of performance metrics.
-Similarly for self\_0 in terms of precision, recall and ifa\_auc bellwether\_level0 scores same rank using statistical significance and effect size test.
-Although for bellwether0 and self\_0 the performance rank for pf and Popt20 is little better than bellwether\_level0, the difference is very small.
-We can see similar results for the global2 results, where bellwether\_level0 performs significantly better.
-Seeing these results we can conclude the GENERAL is an effective and fast algorithm to find a exemplary ``Bellwether Projects'', whose predictive performance is comparable with  \textit{bellwether method} proposed by Krishna et al.
-, local(self test) and global models.
-In summary, we find that
-
-\begin{result}
-{GENERAL is a fast and effective algorithm, which can find exemplary ``Bellwether Projects'' with comparable predictive performance.}
-\end{result}
-
-\subsection*{RQ4: Does learning from too many projects has detrimental effect?}
+The speed improvements reported in {\bf RQ1} are only useful
+of this faster method can also deliver adequate predictions
+(i.e. predictions that are not worse
+than those generated by other methods).
+
+Figure~\ref{fig:Statistical} shows the distribution of
+performance score results seen in
+of \fig{GENERAL}. These results are grouped together by the ``rank'' score
+of the left-hand-side column 
+(and this rank was generated using the statistical methods of
+\S\ref{eval}).
+
+In these results, the {\em ifa\_auc}  and {\em precision} scores
+were mostly uninformative. With the exception of {\em ZeroR},
+there was very little difference in these scores.
+
+As to {\em ZeroR}, we cannot recommend that approach.
+While {\em ZeroR} 
+makes few mistakes (low {\em ifa}s and low {\em pf}s), it scores badly
+on   other measures (very low {\em recall}s  and {\em popt(20)}.
+
+Similarly, we cannot recommend the    {\em global} approach.
+In this approach, quality predictors are learned from   one data set that combines
+data from hundreds of projects. As seen in Figure~\ref{fig:Statistical} 
+that approach generates an unacceptably large false alarm rate ($pf=79\%$).
+
+Another approach we would deprecate is the traditional bellwether approach.
+By all the measures of
+Figure~\ref{fig:Statistical},   the {\em bellwether0} are in the middle of the pack. That is:
+\bi
+\item
+That approach is in no way outstanding. 
+\item
+So, 
+compared to hierarchical bellwether,
+ there is no evidence here of a performance
+benefit from using  traditional bellwether.
+\item
+Given this lack luster performance, 
+and   the {\bf RQ1} results (where traditional bellwether ran very slowly), we therefore  
+deprecate the traditional bellwether approach.
+ \ei
+As to GENERAL vs the local learning results of {\em self}, in many ways their performance in  Figure~\ref{fig:Statistical},
+is indistinguishable:
+\bi
+\item As mentioned above, measured in terms of {\em ifa\_auc}
+and {\em precision}, there is no significant differences.
+\item In terms of {\em recall} there is no statistical difference in the rank
+of  local learning with {\em self} and 
+  {\em GENERAL\_level0}
+(a bellwether
+generated from the root of a BIRCH cluster tree) and 
+\item In terms of {\em pf} (false alarms), some of the GENERAL results are ranked
+the same as {\em self} (and we will expand on this point, below).
+\ei
+Overall, we summarize the Figure~\ref{fig:Statistical} results as follows:
+
+\begin{RQ}
+{Measured in terms of predictive performance,
+the effectiveness of hierarchical bellwethers
+is very similar to local learning
+(and these two methods are more effective
+than the other options explored here). }
+\end{RQ}
+
+When two options have similar predictive
+performance, then other criteria can be used
+to select between them:
+\bi
+\item If the goal is to quickly generate
+conclusions about one project, then we would recommend
+local learning since (as seen above), local learning is five
+times faster than hierarchical bellwether.
+\item
+But, as said at the start
+of \S\ref{sec:results},
+our goal is to quickly generalize across hundreds of
+projects. 
+\ei
+
+\subsection*{RQ3: Does learning from too many projects have detrimental effect?}
 \label{sec:rq4}
-In RQ4, we try to answer the question if learning from too many projects detrimental effect, this question has two parts, one on predictive power, the other on making general conclusion and conclusion instability.
+
+Returning now to \fig{predictive_power}, this
+research question asks if there is such a thing
+as learning from too much data.  What we will see is that
+answers to this question are much more complex than the simplistic
+picture of \fig{predictive_power}. While for some goals it is possible
+to learn from too much data, there are other goals where it seems
+more is always better.
+
+To answer {\bf RQ3}, we first note that when GENERAL
+calls the BIRCH clustering algorithm, it generates the tree
+of clusters shown in  
+\fig{example tree}. In that tree:
+\bi
+\item
+The bellwether found at level 0 of the tree
+(which we call {\em GENERAL\_level0}) is learned from 627 projects.
+\item
+The bellwethers found at level 1 of the tree
+(which we call {\em GENERAL\_level1}) is learned from four sub-groups
+of our projects.
+\item
+The bellwethers found at level 2 of the tree
+(which we call {\em GENERAL\_level2}) is learned from 80
+sub-sub groups of our projects.
+\ei
+That is, to answer {\bf RQ3} we need only compare the predictive performance
+of models learned from these different levels. In that comparison,
+if the level\_$(i+1)$ bellwethers generated better predictions
+that the   level\_$(i)$ bellwethers, then we would conclude that it is best to learn lessons from smaller groups
+of projects.
+
+Figure~\ref{fig:Statistical} lets us
+compare the performance of the bellwethers learned from different 
+levels:
+\bi
+\item The {\em ifa} and {\em Popt20} 
+and {\em precision}  results for the different levels
+are all ranked the same.  Hence we say that, measured in terms of those 
+measures, we cannot distinguish the performance at different levels.
+\item 
+As to {\em recall},   the level2,1,0 bellwether results are 
+respectively ranked worst, better, best. 
+\item
+Slightly different results are offered in the {\em pf} false alarm results. Here,  levels2,1,0 bellwether are respectively ranked best, best, worst.
+\ei
+That is, these results say that:
+
+\begin{RQ}
+{Assessed in terms of {\em recall},
+it is better to learn bellwethers from more data rather than less.
+But assessed in terms of {\em false alarms}, 
+while learning bellwethers
+from many projects is useful, it is possible to learn from too much data.} 
+\end{RQ}
+
+To put that another way, the answer to ``is is possible to learn from too much data'', is ``depends on what you value'':
+\bi
+\item
+For risk-adverse development of mission or safety critical
+systems, it is best to use all data to learn the bellwether
+since that finds most defects.
+\item
+On the other hand, for cost-adverse development of non-critical
+systems (where cutting development cost
+is more important than removing
+bugs), then there seems to be a ``Goldilocks zone'' where
+the bellwether is learned from just enough data (but not too much or too little).
+\ei
+
+% In this section, we return to 
+% In RQ4, we try to answer the question if learning from too many projects detrimental effect, this question has two parts, one on predictive power, the other on making general conclusion and conclusion instability.
 Figure~\ref{fig:Statistical} shows the results of statistical significance and effect size tests to rank them in order for all the different methods(treatments) used in this experiment.
@@
 
-To answer the first part of the question, if learning from too many projects have detrimental effect on predictive power of models, we compare the results of default ``bellwether method'' (a.k.a bellwether0) proposed by Krishna et al.
+% To answer the first part of the question, if learning from too many projects have detrimental effect on predictive power of models, we compare the results of default ``bellwether method'' (a.k.a bellwether0) proposed by Krishna et al.
 and GENERAL(a.k.a GENERAL\_level0) method.
@@
 
+% Now to answer the second part of the question, that is if learning from too many projects creates conclusion instability, we will look at figure~\ref{fig:FSS_compare}.
+Figure~\ref{fig:FSS_compare} show the distribution of attributes selected while building a ML model for defect prediction using local models(a.k.a self), the \textcolor{red}{{\bf red bars}} shows the attributes selected by the ``Bellwether Project''.
+Conclusion instability causes vastly different and often contradicting conclusions to be derived from a data source.
+This sort of instability is very prevalent in several domains of software engineering.
+We can see from figure~\ref{fig:FSS_compare}, when learning from local data, each model selected different sets of attributes and resulted in selecting almost all different attributes.
+That means there is no general conclusion can be drawn for defect prediction models by saying which attributes are important, this results in conclusion instability and that effects the trusts on those models, the insights that can be drawn from them.
+Which farther affects training and tool development as mentioned in sec~\ref{sec:Motivation}.
+From these results we can see learning from too many data can cause conclusion instability and thus affecting generality in SE domain.
+In Summary, we can say
+
+\begin{figure*}[h]
+    \centering
+    \includegraphics[width=\linewidth]{figs/FSS_compare.png}
+    \caption{Distribution of features selected using self model and ``Bellwether'' model.}
+    \label{fig:FSS_compare}
+\end{figure*}
+
+\subsection*{RQ4: What exactly did we learn from all those projects?}
+\label{sec:rq5}
+
+Having demonstrated that we can quickly find bellwethers
+from hundreds of software projects, it is appropriate to ask
+what model was learned from all that data. This is an important question for this research sinceif  we cannot show the lessons
+learned from our 627 projects, then all the above is wasted effort.
+
+Table~\ref{tbl:coefs}  shows the weights learned by logistic
+regression after feature selection using the bellwether project
+selected by {\em GENERAL\_level0}. Note that:
+\bi
+\item
+The number of features that appear in Table~\ref{tbl:coefs}  is much smaller than the list of features shown in Table~\ref{tbl:metric}.
+That is, our bellwether is reporting that only a few features
+are most important for predicting software defects.
+\item
+Table~\ref{tbl:coefs}  is sorted by the absolute value of the weights
+associated with those features. The last two features have near
+zero weights; i.e. they have negligible effect.
+\ei
+Apart from the negligible features, all that is left are NPRM, NPNM, RFC , and CBO. As shown in Table~\ref{tbl:metric}, these features
+all relate to class interface concepts; specifically: 
+\bi
+\item
+The number of public and private methods; 
+\item
+The  average number of methods that respond to an incoming message; 
+\item
+Inter-class coupling. 
+\ei
 \begin{table}[!t]
@@
 \end{tabular}
-\label{tbl:coefs}
-\caption{Importance of coefs on \textit{log p} from logistic regression model of ``Bellwether'' shown in fig~\ref{fig:FSS_compare}.
-Here Odds ratio shows one increment in in respective variable increase in the log-odds of being defective.}
+
+\caption{Importance of coefs on \textit{log p} from logistic regression model of ``Bellwether'' shown in Fig~\ref{fig:FSS_compare}.
+Here Odds ratio shows one increment in in respective variable increase in the log-odds of being defective.}\label{tbl:coefs}
 \end{table}
-
-Now to answer the second part of the question, that is if learning from too many projects creates conclusion instability, we will look at figure~\ref{fig:FSS_compare}.
-Figure~\ref{fig:FSS_compare} show the distribution of attributes selected while building a ML model for defect prediction using local models(a.k.a self\_0), the \textcolor{red}{{\bf red bars}} shows the attributes selected by the ``Bellwether Project''.
-Conclusion instability causes vastly different and often contradicting conclusions to be derived from a data source.
-This sort of instability is very prevalent in several domains of software engineering.
-We can see from figure~\ref{fig:FSS_compare}, when learning from local data, each model selected different sets of attributes and resulted in selecting almost all different attributes.
-That means there is no general conclusion can be drawn for defect prediction models by saying which attributes are important, this results in conclusion instability and that effects the trusts on those models, the insights that can be drawn from them.
-Which farther affects training and tool development as mentioned in sec~\ref{sec:Motivation}.
-From these results we can see learning from too many data can cause conclusion instability and thus affecting generality in SE domain.
-In Summary, we can say
-
-\begin{result}
-{Learning from too many projects have detrimental effect on predictive power, which can be seen on performance difference found between bellwether0 and GENERAL\_level0, it also introduces conclusion instability.
-By selecting ``Bellwether Project'' using GENERAL can have better predictive performance as well as it can create generalized model which are explainable and actionable thus minimizing conclusion instability.}
-\end{result}
-
-\begin{figure*}[h]
-    \centering
-    \includegraphics[width=\linewidth]{figs/FSS_compare.png}
-    \caption{Distribution of attributes selected using self\_0 model and ``Bellwether'' model.}
-    \label{fig:FSS_compare}
-\end{figure*}
-
-\subsection*{RQ5: What exactly did we learn from all those projects?}
-\label{sec:rq5}
-
-In this RQ we show what did we learn by selecting a ``Bellwether Project'' to create defect prediction models.
-Using ``Bellwether Project''  minimizes the issue of conclusion instability and thus building trust in the model and deduce better insights about what can be a better indicator of bugs.
-Table~\ref{tbl:coefs} shows the attributes selected by the ``Bellwether Project'' and the coefs and Odd ratios for the LR model build using that.
-The insights that we can draw from these results are an increase of 1 in avg\_NPRM can increase the ratio of probability of having a defect and not having a defect by almost 9 times, while a unit increase in total\_NPBM, avg\_NPBM, max\_NPBM, max\_CBO will reduce the ration of probabilities by 0.5, 0.27, 0.33 and 0.53 times respectively.
-a unit increase in total\_ModifiedLOC and avg\_WMC will have almost no effect in Odd ratio.
-From this we can conclude NPRM, NPBM, RFC and CBO are important factor while predicting for defects all of which are interface related metrics in these datasets.
-The learning from these information can be if there is an increase in number of private methods in a certain class, developers need to be extra careful as that is a good indicator of introducing bugs in code.
-In Summary, we can say
-
-\begin{result}
-{Learning from ``Bellwether Project'' is very concise, can be used to extract meaningful and actionable insights.
-The insight from this study is interface related metrics collected from these 697 projects are good indicator of bugs in the codebase.
-}
-\end{result}
+\fig{FSS_compare} shows what might be learned with and without
+the methods of this paper. Recall that the learners used in this research used feature selection and  logistic regression.
+\begin{itemize}
+\item  The gray bars in \fig{FSS_compare} show how often the features
+of Table~\ref{tbl:metric} were selected in the models learned from
+local data using {\em self}. 
+\item
+The red bars in \fig{FSS_compare} shows which features
+used in the local models that also appeared in the model learned from the bellwether. 
+  Note that only a very
+small subset of the features seen in the  {\em self} models
+were found useful in the bellwether model of Table~\ref{tbl:coefs}.
+\end{itemize}
+Just to say the obvious:
+when learning
+local models from very many projects, there is a wide range 
+of features used in the model.
+It is far easier to 
+definitively learn lessons from a much smaller range
+of features, such as those listed in Table~\ref{tbl:coefs}.
+For example,
+based on these results
+we can say that for predicting defects, in this sample of  features taken from 627 projects:
+\bi
+\item Issues of inter-class interface are paramount;
+\item While many other  issues are far less important such as file size, depth of inheritance tree, intra-method complexity, file size, revision history, and anything relating to  the other features of Table~\ref{tbl:metric}
+that are not listed in Table~\ref{tbl:coefs}.
+\ei
+In summary:
+
+\begin{RQ}
+{The importance of many key features is not apparent at the local
+project level. To fully appreciate the critical impact on defects
+of class interface design,  it is necessary to conduct
+a global analysis across hundreds of projects. }
+\end{RQ}
+To say that another way, 
+\begin{quote}
+{\em 
+Learning from many other projects can be better than learning just from your own local project data.
+}\end{quote}
 
@@
 (a) \textit{Evaluation Bias}: 
-In  RQ1, RQ2 and RQ3 we have shown the performance of local model, hierarchical bellwether models, default bellwether model and compared them using statistical tests on their performance to make conclusion about presence of generality in SE datasets.
+In  {\bf  RQ1, RQ2} and {\bf RQ3} we have shown the performance of local model, hierarchical bellwether models, default bellwether model and compared them using statistical tests on their performance to make conclusion about presence of generality in SE datasets.
 While those results are true, that conclusion is scoped by the evaluation metrics we used to write this paper.
@@
 \label{sec:concl}
-In this paper, we have proposed a new transfer learning ``bellwether method'' to find ``Bellwether effect'' called GENERAL and uses this to find generality in Software Engineering by minimizing conclusion instability thus increasing trust and deducing meaningful insights from them which in turn helps in training and tool developments.
-
-Our results show that regardless size of software engineering datasets we can still find ``Bellwether'' in those datasets.
-In this study bellwethers were found when studying over 697 software projects.
-However, conventional methods of Krishna et.
-al.
-are computationally very expensive and took long time to discover these bellwethers, e.g., experimentation took 3 days to find a bellwether project from among the 697 projects.
-
-We showed in this paper, the new algorithm GENERAL can find ``Bellwether Project'' order of magnitude faster.
-We show ``Bellwether method'' proposed by krishna et al.
-has a computational complexity of $\approx O(N*2)$ while GENERAL has a computational complexity of $\approx O((N*2/m))$ where m is the number of cluster at the leaf level of the CF tree and N is the number of projects.
-GENERAL only requiring 1.5 hours to run in comparison to 3 days and requires far less comparison 9080 instead of 393129 required for ``Bellwether method'' proposed by Krishna et al.
-
-The study also showed the GENERAL is a fast and effective algorithm, which can find exemplary ``Bellwether Projects'' with comparable predictive performance.
-The figure~\ref{fig:Statistical} shows ``Bellwether Projects'' discovered by GENERAL have similar or better predictive performance while comparing with bellwether0, Self\_0 or global2.
-
-We also try to answer the question if learning from too many projects have detrimental effect, the study showed it can have detrimental effect on predictive performance of models also it introduces conclusion instability.
-We can see local models(a.k.a self tests) although having almost similar predictive performance does not allow us to draw general conclusions and insights for software defect prediction models.
-Thus it is very unlikely users will be able to trust these models and uses them for training, tool development and other related activities.
-Contrast to that, using a ``Bellwether Project'' we are able to make general conclusion about software defect prediction models.
-
-Hence, from a  engineering perspective there are two main reasons to use GENERAL: (a) This is a very fast algorithm to find ``Bellwether project'';  (b) They have comparable predictive performance than its counterparts; and (c) They slow down the pace of conclusion changes and allow users to draw generalized conclusions and meaningful actionable insights.
-
-Finally, we remark that much of the prior work on homogeneous transfer learning have complicated the homogeneous transfer learning process and are computationally expensive.
+In this paper, we have proposed a new transfer learning  bellwether method   called GENERAL.
+While GENERAL only reflects on a small percent of the projects,
+its hierarchical methods find projects which yield models
+whose performance is comparable to anything else we studied
+in this analysis.
+Using GENERAL, we have shown that issues
+of class interface design were the most critical
+issue within a sample of 628 projects.
+
+One reason we recommend GENERAL is its scalabiity.
+Pre-existing
+bellwether methods are very slow. Here, we show
+that a new method based on hierarchical reasoning
+is both must faster (empirically) and can scale to much
+larger sets of projects (theoretically). Such scalability
+is vital to our research since, now that we have shown
+we can reach general conclusions from 100s of projects,
+our next goal is to analyze 1000s to 10,000s of projects.
+
+Finally, we warn that much of the prior work on homogeneous transfer learning many  have complicated the homogeneous transfer learning process with needlessly
+complicated methods.
   We strongly recommend that when building increasingly complex and expensive  methods, researchers should pause and compare their supposedly more sophisticated method against simpler alternatives.
@@
 
+This work was partially funded by NSF Grant \#1908762.
+\balance
 \bibliographystyle{IEEEtran}
 \bibliography{main}
- \balance
-
-% \input{response.tex}
+
+\begin{IEEEbiography}[{\includegraphics[width=1in,clip,keepaspectratio]{figs/suvodeep.JPG}}]{Suvodeep Majumder}
+ is a second year Ph.D. student in Computer Science at North Carolina State University.  
+  His research interests include using large scale data mining and application of big data and artificial intelligence methods to solve problems in software engineering.
+  \url{https://www.suvodeepmajumder.us}.
+\end{IEEEbiography}
+\begin{IEEEbiography}[{\includegraphics[width=1in,clip,keepaspectratio]{figs/krishna.jpg}}]{Rahul Krishna}, (Ph.D. 2019, North
+Carolina State University) is a post-doc at Columbia University.
+His research explores ways in which machine learning and AI can be used for software testing.
+During his Ph.D.
+he worked on actionable analytics for software engineering to  develop algorithms that go beyond prediction to generate insights that can assist decision making.
+\url{http://rkrsn.us}
+\end{IEEEbiography}
+\begin{IEEEbiography}[{\includegraphics[width=1in,clip,keepaspectratio]{figs/tim.png}}]{Tim Menzies} (IEEE Fellow)
+is a Professor in CS at NcState  His research interests include software engineering (SE), data mining, artificial intelligence, search-based SE, and open access science. \url{http://menzies.us}
+\end{IEEEbiography}
+
+\input{response.tex}
 

### 2020-03-03 response.tex
Updates from Overleaf

@@
 
-Thank you very much for your encouraging comments.
+\response{ Thank you very much for your encouraging comments.
 We have made appropriate changes to the manuscript taking into careful consideration the recommendations of the reviewers.
 We hope that this new draft adequately satisfies all the issues raised by the reviewers.
-To assist the reviewers in tracking all the new changes, where appropriate, we have prefixed the text with \respto{X-XX} to correspond to the reviewers' questions.
-
+To assist the reviewers in tracking all the new changes, where appropriate, we have prefixed the text with \respto{X-XX} to correspond to the reviewers' questions.~\\
 Below is the brief summary of our changes:
 \be
-\item The problem statement needs to be clarified and properly positioned (R1, R3). XXX
-
-\item The novelty of the approach needs to be clarified (R3). XXX (see \bareresp{2-1})
-
-\item The writing needs to be improved (R1, R2, R3).
-
-\item The study needs to include all the details to ensure replicability (R1, R2).
-
+\item The problem statement has been  clarified and properly positioned (R1, R3). XXX
+\item The novelty of the approach has  been clarified (R3). XXX (see \bareresp{2-1})
+\item Using comments from  (R1, R2, R3), we have made numerous small editorial improvements.
+\item The study now includes all the details to ensure replicability (R1, R2).
 \item The results of the study need to be revisited since the reviewers are not convinced that the results support the claims in the paper (R1, R2, R3).
-
-\item The background on transfer learning needs citations (R2).
-\ee
+\item The background on transfer learning has been augmented with more  citations (R2).
+\ee}
 
@@
 
-Thank you very much for your detailed review.
+\response{Thank you very much for your detailed review.
 We have made some additional corrections, clarifications, and revisions, as directed by your comments.
-To assist in your review, we refer to specific locations of each of the changes using \respto{1-XX}.
+To assist in your review, we refer to specific locations of each of the changes using \respto{1-XX}.}
 
-\review{(1.1) 1.
-Background.
+\review{(1.1) Background.
 The paper builds upon a number of previous studies.
-However, several key questions have no answer: *What is* the bellwhether?
+However, several key questions have no answer: *What is* the bellwether?
 *Why is* this relevant?
 How does it work when applied to different contexts?
-Why is this useful in practice?
-None of these questions are addressed in the paper.
-This submission should be self-contained and allow a reader to understand its content without reading 10 other papers; in this sense, the submission fails completely.
-For example, the paper mentions that: "The core intuition of this new approach is that if many projects are similar, then we do not need to run comparisons between all pairs of projects": very good, but where this intuition come from?}
+Why is this useful in practice?}
+
+\response{You are quite correct, we did not define bellwether till very late in the prior draft. In this draft, we define bellwether on page 1.
+}
+
+\review{The paper mentions that: "The core intuition of this new approach is that if many projects are similar, then we do not need to run comparisons between all pairs of projects": very good, but where this intuition come from?}
+
+\response{Thank you for that comment.  You a re quite correct-- we did not document the source of our intutuion. We have added the following note to \respto{1-XX}}
+
+\begin{quote}
+\response{``The core intuition of this new approach is two-fold. Firstly,
+many projects are similar in structure. We say this since  Devanbu
+et al.`\cite{hindle2012naturalness}   report that if Markov chains are created for tokens in a program,
+then a remarkably small number of chains capture most of the program. ~\\
+``Secondly, given these similarities,   we can exploit symmetries between different projects in order to learn predictors from one and apply those to another.
+To say that anothe way, given large scale similarities between projects,  then we do not need to run comparisons between all pairs of projects since analyszing just a few pairs should work as well as anything else.''}
+\end{quote}
+
+\review{(1.2)The relevance of the paper.
+This is, unfortunately, unclear.
+According to the abstract and introduction, the main issue treated in the paper is related to scalability.
+Please, provide a clear case study on the performance of bellwether methods.
+The claims on the scalability of the approaches are just claims, no details are reported.
+Abstract and introduction just report that "when applied to the 697 projects studied here, they took 60 days of CPU to find and certify the bellwether".
+As said, the bellwether approach has been applied to several problems (e.g., defect prediction/effort estimation/bad smell detection): are these problems the same?
+When is it needed to apply scalable solutions for bellwether approaches?
+Why?
+Please, explain.}
+
+\response{ need a new RQ0: how slow is standard bellwether. theoretically an empriically its slow (chart on p2. move to RQ0). May need to include results using increasing community size.}
+
+\review{(1.3) Writing style.
+The introduction is, simply, to be completely rewritten.
+I would like to see a paper that is understandable even from non-experts.
+As such, please define the context of the paper, the concepts of (1) software quality - line 1, (2) general models - line 2, (3) many projects - line 2, (4) "scalable approach to learning effective models adapted to the task at hand" - line 2/3, (5) "or does the truth lie somewhere in-between" - line 3.
+These are just of the examples of why the introduction is unclear and does not provide any detail on the reasons behind the paper.
+The same is true for the remaining of the paper, which gives for granted many of the concepts without explaining them properly.}
+
+\response{ frist 3 oaras deled tup to :"funding general lessons"}
+
+\review{(1.4) Please, avoid claims such as "have tremendous practical significance" without providing any practical significant example/citation. (This is just an example)}
+
+\response{ you are right. sueprlatives deleted (including that one)"}
+
+\review{(1.5a) The clarity and replicability of the paper are unclear.
+Here some examples 1) "The logistic regression learner (since it is relatively fast)".
+What does "fast" mean?
+How was "fast" computed?
+}
+
+\response{ you are right. sueprlatives deleted (including that one)"}
+
+\review{(1.5b)
+2) "The SMOTE class imbalance correction algorithm [49], which we run on the training data2". Why is SMOTE needed? Why is the problem unbalanced? Please, explain.
+}
+
+\review{(1.5c)
+3) "and Hall’s CFS feature selector". Which features have been removed and why?
+}
+
+\review{(1.5d)
+4) "As to CFS, we found that without it, our recalls were very low and we could not identify which metrics mattered the most".
+Where can the reader understand this statement?
+Where is the replication data?
+}
+
+\response{how should I answer Where can the reader understand this statement? May need to remove this section as i don't have the results}
+
+\review{(1.5e)
+5) "extensive studies have found that CFS more useful than many other feature subset selection methods such as PCA or InfoGain or RELIEF".
+The paper cites just one paper, how should these studies be "extensive"?
+}
+
+\response{Thank you for that comment.  You are quite correct-- we did not document the all the necessary citations for supporting our claim before. We have added the following note to \respto{1-5e}}
+
+\review{(1.5f)
+5) "Maximize recall and precision and popt(20)": Why should these metrics be maximized?
+What is the practical value, e.g., is high recall always needed in practice, or should we prefer precision in the problems treated by the bellwether?
+What about popt(20)?}
+
+\response{added footnote also there are details in sec 4.5}
+
+\review{(1.5g) "While minimizing false alarms and ifa auc": Again, please explain the practical relevance of the performance metrics employed. }
+
+\response{added footnote also there are details in sec 4.5}
+
+\review{(1.5h) 
+More in general, how can one replicate the performed study? Is there a replication package? If so, where?}
+
+\response{Thank you for that comment.
+You are quite correct-- we did not include in depth steps to replicate the study before.
+We have added a replication package in contribution section \respto{1-5h} as well as more in depth details about the algorithm has been added in \respto{XXXX}}
+
+\review{(1.6a) The analysis of the results should be substantially improved.
+Let consider the case of Section 5 - RQ1.
+The results are reported in less than half column and refer to a figure (Figure 6) which does not explain anything.
+The summary reports that "Theoretically and empirically, the hierarchical reasoning on GENERAL performs much faster than standard bellwether methods": I cannot understand where these "theoretically and empirically" come from, since there is no proof of them.
+}
+
+\response{you are wright, need an RQ0}
+
+\review{(1.6b)
+The same is true for the other research questions. And, in general, there is qualitative analysis: Why are the results the ones reported in the paper? }
+
+\response{you are right,Thank you for that comments. We have added much  quantaitive analusis as
+well as statistical tests to this paper. Please see \fig{XXX7}.}
+
+\review{(1.6c) What makes the reported method scalable?}
+
+RQ0: how slow old better
+
+RQ1: how fast new bellweather.
+
+RQ2: scalabulity (the old RQ1)
+
+RQ3: (as before)
+
+RQ4: (as belfire)
+
+\section*{Reviewer 2squeue}
+
+Many of your comeents take issue with two terms used in this paper "lessons learned" and "trasfer learning".
+We agree with you that our use of "lessons learned" was inappropriate and we have removed all those usages.
+
+As to oir use of "transfer learning", 
+inspired by your commetns we have ckarified what we mean by that term much earlier in the paper (see \cite{XXX}).
+Base don that clarification, we can show that our use of ``transfer learning'' is consistent with its usage by Pan'09 (a paper current 8,220 citations at the time of this writing).
+Also, our usage is consistent with dozens of recent SE research papers on transfer learning~\cite{XXXmanycite}.
+Thank you for enocuraging us to clarify that terminology.
+
+A survey on transfer learning
+SJ Pan, Q Yang - IEEE Transactions on knowledge and data …, 2009 - ieeexplore.ieee.org
+  Cited by 8220 Related articles All 20 versions Web of Science: 3428
+
+% \review{(2.1) [Sec.
+1 and throughout] The paper repeatedly refers to a method for “transferring lessons learned from one project to another.” But the method does NOT transfer lessons learned.
+Lessons learned are identified throughout and formally documented in the project closing process.}
+
+% \response{ u r right. lessons learned are what yu said. what we do pass pom
+% defect predictors from one project to another (and this passage process of data mining results is very different to the lessons learned process you describe).   }
+
+% \review{These lessons learned are reviewed when new projects are being initiated/planned.
+The introduction talks about guiding project management but project management has a process for handling lessons learned that doesn’t require machine learning.
+How does the method help that process?
+Why would you need a “bellwether” to apply lessons learned to a new project?!
+The method does not transfer lessons learned but what it DOES appear to do is associate defect rate profiles for two projects (a so-called “bellwether” and a new project).}
+
+% \response{ ur rught we renamed as you said. }
+
+\review{(2.2) [Sec.
+1] “…the bellwether is equivalent to the other models…” This claim is confusing.
+1) Is “the bellwether” a model or a project?
+2) How is equivalence defined?
+Or do you simply mean “similar”?}
+
+\response{ acts as data poasss on. cjanged to similiar.}
+
+\review{(2.3) [Sec.
+1] “when new projects appear, their quality can be evaluated even before there is an extensive experience base within that particular project (again, just by studying the bellwether).” You take a set of projects…select one project (the “bellwether”)…then use that project to build a model that can—for instance—estimate defect rate.
+So, for the defect estimation case, the model learned from the bellwether won’t tell you where the defects may be (i.e., fault localization), it will just estimate how buggy a new project is.
+Is all of this right?}
+
+\response{ XX.}
+
+\review{(2.4) If the point is to use the bellwether to infer things about a “new” project, then how new can the new project be?
+When (in the new project’s history) can you be sure the model from the bellwether is valid to use?}
+
+\response{Explain the train, test splits and the how you do the exp. then say this is what our model proves, it predicts for projects which it has not seen before XX.}
+
+\review{(2.5) Do you have to find a bellwether for each purpose?
+In other words, if you find a bellwether among 697 projects for defect rate prediction, then is that same bellwether automatically used to build a model for another discrete task (different than defect rate prediction)?
+Or will you have to apply this algorithm for each and every discrete task?}
+
+\response{ clairft}
+
+\review{(2.6) Figure 1 needs to be omitted}
+
+\response{ ciuretainly too confusing for intro. can move to a later section and ducssed in more retchnical detail}
+
+\review{(2.7) The computational complexity $(O(N^2)$ versus $O(m*(N/m^2))$ is both compact appropriate.}
+
+\response{ XXXX}
+
+\review{(2.8) The paper does not evaluate the model’s performance using a pool of 12,000 projects; the evaluation does not even use 1,000 projects.}
+
+\response{ will fix}
+
+\review{(2.9) [Sec.
+1] The box under RQ4 is very confusing.
+We find the bellwether to simply study one project, but this note says we still need to analyze hundreds of projects to understand something like the importance of features.
+Is this right?}
+
+\response{ will fix}
+
+% \review{(2.10a) [Sec. 1] The contributions of this paper.
+% 1) The first contribution claims “bellwethers for transfer learner.” Indeed, the paper repeatedly refers to transfer learning.
+But I do not see where the transfer learning is actually being done when I inspect the procedure at the beginning of Sec.
+3:}
+
+% \review{(2.10b)
+% [A] Step 1 characterizes each project using the same feature space and the paper does not support the fact that data are distributed differently.
+Moreover, the learning task remains the same.
+These facts do not support a transfer learning setting prima facia.}
+
+% \response{(2.10c) with respect, our usage is consistent with how the term is used in the SE literature, see LOTS of ferences~\cite{xxx}.}
+
+% \response{(2.10d) 
+% [B] Steps 2 and 3 involve grouping the projects based on similarity. There is no transfer learning here.}
+
+% \response{(2.10e) 
+% [C] There is no transfer learning done in Steps 4-6.}
+
+% \response{(2.10f) 
+% [D] Aside from inspecting each step in the main procedure, another way to determine whether GENERAL involves transfer learning is the following: This approach does not involve reweighting instances nor does it appear to involve transferring feature representations and/or parameters…and if it does then the paper does not even identify this fact much less argue for it being the case.
+% If something in this rationale [A-D] is not correct, then please clear up the explanation on transfer learning in the paper in terms/language the machine learning community has established to avoid ambiguity.}
+
+\review{2) I do not understand what the second contribution really is.}
+
+yes, we have deletet is
+
+\review{(2.11) [Sec. 2.1] I recommend removing this subsection from Background and condensing it in the motivation in Sec. 1.}
+
+good idea. paper now starts with 2.1
+
+\review{(2.12) [Sec 2.2] Figure 2 needs to be omitted. These “hypothetical” plots are not substantial. (The authors even say as much when discussing the results in Sec. 5.)}
+
+replaced with two dots poiints: descibning this in wors
+
+\review{(2.13) [Sec. 2.2] At least two-thirds of this sub-section is anecdotal. Does the gist of this subsection depend critically on the hypotheticals?}
+
+get rid of 2.2.. delete fig 2
+
+\review{(2.14) [Sec.
+2.3] “Accordingly, here, we explore nearly 700 projects.” But just because 697 (this study) is larger than 24 (previous studies) does not mean external validity concerns are adequately addressed when one considers how complex the task is.
+Please comment.}
+
+\response{with respect, in terms of SE reserch, it it smuch larger thatnanythtngoins eeen before. but your concenr is valud. we have added
+a weaselt sentence at the end saying that we can benever assume generality of all porkect. }
+
+\review{(1.15) [Sec.
+2.3] “If they ask ‘are we sure XYZ causes problems?’, can we say that we have mined enough projects to ensure that XYZ is problematic?” We can say XYZ is probably problematic, but that doesn’t answer the deeper question about causality.
+Do you agree?}
+
+\response{ ur right. we shiuld bneve wsay "cuase'. work removed. is associated, statisitally predicts for.}
+
+% \review{(1.16) [Sec.
+2.4] “This art of moving data and/or lessons learned from one project to another is Transfer Learning.” I do not agree with this definition.
+Please cite this definition or use the definition of transfer learning established by the machine learning community.}
+
+\review{(2.17) [Sec.
+2.4] “Successful transfer learning can have two variants…” Cite these variants.
+This is a software engineering paper—not a machine learning paper—that should reference other work for these fundamental details.}
+
+\response{citations added.}
+
+\review{(2.18) [Sec.
+3.2] “…for large sample datasets…” What is the size of the design matrix?
+Does 21 product metrics and five process metrics mean 26 columns?
+If there are 697 projects and snapshots every six months, then how many rows are there?}
+
+\response{XXX}
+
+\review{(2.19) [Sec. 3.3] “As discussed below, the defect models assessed in these experiments” Incomplete.}
+
+\response{fixed}
+
+\review{(1.20) [Sec. 4.1] “stratified k=5 fold cross-validation an” Incomplete.}
+
+\response{fixed}
+
+\review{(1.21) [Sec.
+5] “To put that another way, the answer to ‘is is [sic] possible to learn from too much data’, is ‘depends on what you value’” How does your concept of learning from too much data relate to the concept of overfitting?
+Same concept?
+Different concepts?
+If so, how are they different?}
+
+\response{timm}
+
+\review{(1.22) [Abstract] “When one exemplar project…offers the best advice then it can be used to offer advice for many other projects.” The word advice is confusing here.
+The so-called bellwether does not offer advice or recommendations.
+It is simply used as a characterization, right?}
+
+\response{predicttions}
+
+\review{(1.23) [Sec. 2.3] “…among developers, there is little agreement on what many issues relating to software.” Please reword.}
+
+\response{fixed}
+
+\review{(1.24) [Sec. 2.3(c)] “For example…” is a run-on sentence.}
+
+\review{(1.25) [Sec. 3] What are the units for dataset size in Fig. 4?}
+
+\review{(1.26) [Sec. 5] Why do you need a figure (Fig. 6) for two numbers?}
+
+\section*{Reviewer 3}
+
+\review{(1.1)What I find irritating is that the manuscript introduces a new approach GENERAL, which just applies hierarchical clustering.
+As far as I understand, hierarchical clustering is a well-known, standard, and largely-evaluated clustering algorithm.
+I don’t really see the need to rebrand it with a new name.
+What is the difference between GENERAL and hierarchical clustering other than the GENERAL is applied to defect prediction?}
+
+\review{(1.2) Figure 1 “shows a hypothetical cost comparison in AWS between standard bellwether and GENERAL.” If the Figure is hypothetical, why do we need it?
+Is it based on real data?
+As far as I understand, the plot is merely speculation and as such is should be included in scientific papers.}
+
+we will remove
+
+\review{(1.3) I am also very concerned about the (unproven) assumption that we can make conclusions that hold across multiple projects.
+While the dataset includes 700 projects, we have no information about the project, the domain applications, criticality (e.g., safety-critical systems vs.
+generic open-source Java libraries).
+I don’t really see how a model trained on dozens of open-source apache libraries can be applied to robotics, medical systems, etc.
+Note that for the latter domains, testing, requirements engineering, and maintenance are different and have peculiar standards (e.g., MC/CD coverage for automotive systems vs.
+statement coverage for non-critical systems).
+See below further comments about the quality of the dataset.}
+
+wirht respect.... but we can
+
+\review{(3.4) Similar to Figure 1, Figure 2 discussed hypothetical results/comparisons.
+Why do we need to speculate on hypothetical data rather than real data?
+The last two paragraphs in Section 2.2 make little sense to me.
+There is no reason to have them, if not for contributing to the overall overselling.}
+
+fig2 remove
+
+\review{(3.5) Up to page 5 (Sections 1-2), the paper broadly discusses the importance of learning models from hundreds of projects to have more generic and more reliable software analytics in a broader sense.
+However, from Section 3 to Section 6, the manuscript focuses on defect prediction ONLY.}
+
+sure. tahts oour case study
+
+\review{(1.6) How can we use one single sub-domain (i.e., defect prediction) to make bold statements that should be valid for software analytics in general?
+This overselling concerns me a lot.
+This manuscript DOES NOT provide any evidence that GENERAL works and is applicable for other contexts other than defect prediction.
+In other words, SE is not only Defect Prediction.}
+
+not in general. cant prove external validity. jsut for our 673 projects. wichi is orders of mangitude larger than anything seen ebfore.
+
+\review{(1.7) Therefore, the title, the abstract, introduction, motivation, and conclusions should mention defect prediction as to the only sub-domain in which GENERAL has been evaluated.
+Any overselling to other domains (or software analytics in a broader sense) should be removed (perhaps mentioned as part of future work) because it is not supported by what is in the empirical study/results.}
+
+we agree. titlte shcnage accouding.
+
+\review{(1.8) As mentioned in one of my comments above, the script seeks to model generalizability looking at the number of projects (and size) as solely dimension to look at.
+But what about the quality attributes, such as the application domain?
+What are the application domains of the projects?
+Are there only open-source projects?
+How about industrial projects, including the financial, automotive, and robotics sectors?
+How many web and mobile applications are in the sample?
+Does the dataset cover these domains?
+If not, how can we claim that 700 projects can bring us to generalizability?}
+
+not in general. cant prove external validity. jsut for our 673 projects. wichi is orders of mangitude larger than anything seen ebfore.
+
+\review{(1.9) Furthermore, the dataset looks quite strange to me.
+Looking at the defect distributions (left-most boxplot in Figure 4), I do see that 75\% of the projects (the last quartile) have more than 60\% of defective modules (classes/methods?).
+Some have a defective percentage above 80\%.
+Do we need machine learning to predict defects in projects where almost all modules are defectives?
+In these projects, a simple, constant classifier would work the best.
+The results also show this for ZeroR in Section 5.}
+
+unclear on this. zeroR tells us that it is not enough to do simple things
+
+\review{(3.10) Throughout the manuscript, the complexity of GENERAL is suggested to be $O(m * (N/m)^2)$.
+But there is proof about the complexity whatsoever.
+Either the manuscript cites proofs from existing papers (e.g., related work on hierarchical clustering) or provides a complete proof (perhaps in an appendix).}
+
+XXXX
+
+\review{(1.11) All the results are summarized in one single table (Figure 7), which shows the mean and the standard deviation of five evaluation metrics, as well as the rank of the statistical tests.
+There are two problems in aggregating the data in this way: (1)I am not sure that the arithmetic mean and the standard deviation are the appropriate metrics to use.
+Are the data normally distributed?
+Do we have many outliers?
+Perhaps, median and IQR are more appropriate as they are less affected by outliers.}
+
+use medians an QRQ
+
+{Maybe, the boxplots would be the most appropriate way to show the distributions.
+(2)The average across 700 projects makes little sense and hides what happens in each project.
+What happens per project?
+In how many projects does GENERAL performs better than the standard bellwether learner?}
+
+xplain
+
+\review{(1.12) Section 5 contains the following recommendation “As to ZeroR, we cannot recommend that approach.
+While ZeroR makes few mistakes (low ifas and low pfs), it scores badly on other measures (very low recalls and popt(20).” This argument does not convince me as ZeroR gets the best results for two metrics (as far as I understand).
+Please elaborate more on why we cannot use ZeroR.
+Besides, ZeroR may work relatively well because of projects with a very large number of defects.
+Perhaps, some in-depth analysis of the correlation between defect distributions and performances of the models would be very useful.}
+
+Xplan
+
+\review{(1.13) Section 5 (RQ3) ends with two recommendations about critical and non-critical systems.
+However, I could not find any analysis that can support these recommendations.
+I also queried the paper looking for the keywords “critical systems,” but I could not find anything except the recommendation with these keywords.
+To address this, there are only two mutually exclusive solutions: either remove the recommendations or add in-depth analysis that can provide empirical evidence to the claims.}
+
+cget rid of critial systems

### 2020-03-03 manuscript.tex
Updates from Overleaf

@@
   keywordstyle=\color{pink}\bfseries\sffamily\fontsize{2.8mm}{0.6em},
-  emph={train, predict, add_samples, FindBellwether, BEETLE, get_cost, sample, get_perf, remove_non_bellwethers, LinearTransform, GPTransform}, 
-  emphstyle=\bfseries\color{black!80} ,
+  emph={train, predict, add_samples, FindBellwether, BEETLE, get_cost, sample, get_perf, remove_non_bellwethers, LinearTransform, GPTransform,General,get_featrures,BIRCH,bellwether,get_bellwethers,O(N)},
+  emphstyle=\bfseries\color{blue!50!black} ,
   stringstyle=\itshape\color{black!50},
@@
 }
+
+\newcommand{\response}[1]{\textcolor{blue}{#1}}
 \usepackage[tikz]{bclogo}
@@
 \begin{document}
-\title{  Learning GENERAL Principles from\\Hundreds of    Software Projects}
+\title{  How to Find GENERAL    Defect Prediction Models  \\
+Amidst Hundreds of    Software Projects}
 
@@
 \begin{abstract}
-When one   exemplar project, which we call the ``bellwether'', offers the best advice
+\respto{2-22}{\color{blue} When one   exemplar project, which we call the ``bellwether'', offers the best prediction
 then
-it can be used to offer    advice for
-many other projects. Such bellwethers can be used to make quality predictions about new projects, even before there is much experience with those new projects. 
+it can be used to offer prediction for
+many other projects. Such bellwethers can be used to make quality predictions about new projects, even before there is much experience with those new projects.}
 % Such general conclusions   simplifies     software quality policies since the list of quality problems, and their mitigations, is static).
@@
 % Is that the best we can do?
-How should we reason about software quality?
+
+% How should we reason about software quality?
 Should we use  general models that hold over many projects?
 Or must we use an ever-changing set of ideas that are   continually adapted to the task at hand?
-Or does the truth lie somewhere in-between?  
-To say that another way:
-\bi
-\item
-Are there general principles we can use to guide project management, software standards, education,   tool development, and legislation about software? 
-\item
-Or is  software engineering some ``patchwork quilt'' of ideas and methods where it only makes sense to reason about specific, specialized, and small sets of  projects?
-\ei
-If the latter were true then
- then there would be no stable conclusions about what is best practice for SE   (since those best practices would keep changing as we move from project to project).
+% Or does the truth lie somewhere in-between?  
+% To say that another way:
+% \bi
+% \item
+% Are there general principles we can use to guide project management, software standards, education,   tool development, and legislation about software? 
+% \item
+% Or is  software engineering some ``patchwork quilt'' of ideas and methods where it only makes sense to reason about specific, specialized, and small sets of  projects?
+% \ei
+% If the latter were true then
+%  then there would be no stable conclusions about what is best practice for SE   (since those best practices would keep changing as we move from project to project).
 As discussed in section~\ref{sec:Motivation}, such conclusion instability has   detrimental implications for {\em generality, trust, insight, training}, and {\em tool development}.
 
+\respto{1-3}{\color{blue}Researchers and industry practitioners makes use of software analytics for many tasks to access software quality, such as:
+\bi
+\item Predicting if a submitted code is likely to buggy or not.
+\item Improving code quality by detecting code smells.
+\item Issue lifetime estimation to enable effective development and maintenance of their software systems.
+\ei
+
+Large organizations and many open source communities uses data-driven decision making, where they learn using large scale data analysis on historical data available to them.
+With large quantity of data available to them, how should they reason about software quality?
+Should they use  general models that hold over many projects?
+Or must they use an ever-changing set of ideas that are   continually adapted to the task at hand?
+If the latter were true then there would be no stable conclusions about what is best practice for SE   (since those best practices would keep changing as we move from project to project).
+As discussed in section~\ref{sec:Motivation}, such conclusion instability has   detrimental implications for {\em generality, trust, insight, training}, and {\em tool development}.}
 %One  explanation for the limited conclusions (so far) from automated analytics is  {\em how much} data we are using for analysis.
@@
 Finding general lessons across multiple projects is a complex task.
-A new approach, that shows much promise,
-is the ``bellwether'' method
- for   transferring conclusions between   projects~\cite{krishna2018bellwethers,krishna16a,mensah18z,mensah2017stratification,mensah2017investigating}  (the bellwether is the  leading sheep of a flock, with a bell on its neck).
-That method:
+A new approach, that shows much promise, is the ``bellwether'' method for transferring conclusions between projects~\cite{krishna2018bellwethers,krishna16a,mensah18z,mensah2017stratification,mensah2017investigating}.
+\respto{1-1}{\color{blue} ``bellwether'' is a project from a community of N projects, whose data yields the best analytic (i.e.
+defect prediction, effort estimation etc) on all others.} (the bellwether is the  leading sheep of a flock, with a bell on its neck).
+This method:
 \bi
@@
 \ei
-This approach has been successfully applied to defect prediction, software effort estimation, bad smell detection, issue lifetime estimation, and configuration optimization. As a 
-method of transferring lessons learned from one project to another, bellwethers have worked better than the Burak filter~\cite{turhan09}, Ma et al.~\cite{Ma2012}'s transfer naive Bayes (TNB); and Nam et al.
+This approach has been successfully applied to defect prediction, software effort estimation, bad smell detection, issue lifetime estimation, and configuration optimization.
+As a method of transferring lessons learned from one project to another, bellwethers have worked better than the Burak filter~\cite{turhan09}, Ma et al.~\cite{Ma2012}'s transfer naive Bayes (TNB); and Nam et al.
 TCA  and TCA+, algorithms~\cite{Nam13,Nam2015}.
 
-In terms of {\em transfer} and {\em lessons learned},  such bellwethers have
-  tremendous practical significance.
+%In terms of {\em transfer} and {\em lessons learned},  such bellwethers have
+ % tremendous practical significance. 
   When new projects arrive, then even before there is much experience with those new projects,  lessons learned from other projects can be applied to the new project (just by studying the bellwether),
- Further, since the bellwether is equivalent to the other models,
- then when new projects appear, their quality can be evaluated even before there is an extensive experience base within that particular project (again, just by studying the bellwether).
+ Further, \respto{2-2}{\color{blue} since the bellwether is an exemplar projects for the community of N projects seen so far},
+ %since the bellwether is similar to the other models
+ then when new projects appear, \respto{2-3}{\color{blue} bugs can be localized for that project} even before there is an extensive experience base within that particular project (again, just by studying the bellwether).
  %That is, bellwethers can be queried  to find general lessons about (a)~major quality issues;
@@
 
-This paper reports a novel approach  that dramatically improves on existing bellwether methods.
+This paper reports a novel approach  that improves on existing bellwether methods.
+%dramatically improves on existing bellwether methods.
  Our GENERAL  method  uses hierarchical clustering model to recursively divide a large number of projects into smaller clusters.
@@
 this means GENERAL will scale up much better than traditional   methods.
-For example:
-\bi
-\item
-This paper applies GENERAL and traditional $O(N^2)$ bellwether to 697 projects.
+For example: This paper applies GENERAL and traditional $O(N^2)$ bellwether to 697 projects.
 GENERAL and the traditional approach terminated in 1.5 and 72 hours (respectively).
-
-\item 
- Figure~\ref{fig:cost} shows a hypothetical cost comparison in AWS between standard bellwethers and   GENERAL when running for 100 to 1,000,000 projects. Note that GENERAL
- is inherently more scalable.
- \ei
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=\linewidth]{figs/cost.pdf}
-    \caption{Hypothetical cost comparison between GENERAL and default Bellwether.}
-    \label{fig:cost}
-\end{figure} 
+% \bi
+% \item
+% This paper applies GENERAL and traditional $O(N^2)$ bellwether to 697 projects.
+% GENERAL and the traditional approach terminated in 1.5 and 72 hours (respectively).
+
+% \item 
+%  Figure~\ref{fig:cost} shows a hypothetical cost comparison in AWS between standard bellwethers and   GENERAL when running for 100 to 1,000,000 projects. Note that GENERAL
+%  is inherently more scalable.
+%  \ei
+% \begin{figure}[!t]
+%     \centering
+%     \includegraphics[width=\linewidth]{figs/cost.pdf}
+%     \caption{Hypothetical cost comparison between GENERAL and default Bellwether.}
+%     \label{fig:cost}
+% \end{figure} 
 Using GENERAL, we can  explore these research questions:
-
-            \textbf{RQ1}:   Can hierarchical clustering tame the complexity of bellwether-based reasoning?
+            \respto{1-6}
+
+            {\color{blue}
+            \textbf{RQ1}:  How slow is conventional bellwether method?
+
+            \begin{RQ}{
+               Conventional bellwether method as proposed by krishna et al~\cite{krishna2018bellwethers,krishna16a} uses a $ O(N^2) $ comparisons to find the ``bellwether'' among a community of N (697 projects in this experiment) projects.
+In this experiment the conventional bellwether method used almost 72 hours to find the ``bellwether''.}
+            \end{RQ}
+
+            \textbf{RQ2}:  How fast is new bellwether method aka GENERAL?
+
+            \begin{RQ}{
+               The new bellwether method (GENERAL), which is a combination of hierarchical clustering and bellwether method took around 1.5 hours find a ``bellwether''.}
+            \end{RQ}
+
+            }
+
+            \textbf{RQ3}:   Can hierarchical clustering tame the complexity of bellwether-based reasoning?
 
@@
 
-           \noindent \textbf{RQ2}:  Is this faster bellwether effective?
+           \noindent \textbf{RQ4}:  Is this faster bellwether effective?
 
@@
        \noindent 
-            \textbf{RQ3}: Does learning from too many projects have detrimental effect?
+            \textbf{RQ5}: Does learning from too many projects have detrimental effect?
 
@@
          \noindent 
-            \textbf{RQ4}: What exactly did we learn from all those projects?
+            \textbf{RQ6}: What exactly did we learn from all those projects?
 
@@
 
-\item \textbf{ Replication Package:} We have made available a  replication package\footnote{\href{http://tiny.cc/bellwether}{http://tiny.cc/bellwether}} .
-The  replication package consists of all the datasets used in this paper, in addition to mechanisms for computation of other statistical measures.
+\item \respto{1-5h}{\color{blue}\textbf{ Replication Package:} We have made available a  replication package\footnote{\href{http://tiny.cc/bellwether}{http://tiny.cc/bellwether}} .
+The  replication package consists of all the datasets used in this paper, in addition to mechanisms for computation of other statistical measures.}
 
@@
 
-\section{Background and Related Work}
-\label{sec:literature}
+\section{Motivation}
+\label{sec:motivation}
 
@@
 
-\begin{figure}[!t]
-    \centering
-    \includegraphics[width=\linewidth]{figs/predictive_power.pdf}
-    \caption{Two hypothetical results about how training set size might effect the efficacy of quality prediction for software projects.}
-    \label{fig:predictive_power}
-\end{figure}
+% \begin{figure}[!t]
+%     \centering
+%     \includegraphics[width=\linewidth]{figs/predictive_power.pdf}
+%     \caption{Two hypothetical results about how training set size might effect the efficacy of quality prediction for software projects.}
+%     \label{fig:predictive_power}
+% \end{figure}
 
@@
 
-The {\em size} of the communities found in this way would have a profound impact on how we should reason about software engineering.
+\respto{2-12}{\color{blue} The {\em size} of the communities found in this way would have a profound impact on how we should reason about software engineering.
+Consider in this experiment of 697 projects, we build a set of defect predictor by learning bellwether from smalls cluster of $\approx10$ projects,  medium clusters of $\approx100$ projects, a large cluster containing $\approx600$ projects and a self test.
+In this scenario if we see the defect prediction models build  using bellwethers from medium set of clusters works better than set smalls clusters as well as the large cluster, then in this case, while we could not offer a single model that covers {\em all} of SE, we could offer a handful of models, each of which would be relevant to project clusters.
+While if we see only self test works in this case and learning from more projects makes quality predictions worse which means the our projects break up into ``communities'' of size one.
+In this case,  (a)~principles about what is ``best practice'' for different software projects would be constantly changing (whenever we jump from small community to small community); and (b)~the generality issues would be becoming open and urgent concerns for the SE analytics community.}
+
+In summary, the above two sections lead to our  research question {\bf  RQ5}:
+does learning from too many projects have detrimental effects. Later in this
+paper, we will return to this issue.
+
+% The {\em size} of the communities found in this way would have a profound impact on how we should reason about software engineering.
 Consider the hypothetical results of Figure~\ref{fig:predictive_power}.
@@
 In this case, while we could not offer a single model that covers {\em all} of SE, we could offer a handful of models, each of which would be relevant to project clusters at that level.
-%Accordingly, we would say that there are many cases where  wisdom from prior projects can be readily applied to guide future projects and (b)~the generality issues raised are not be so pressing.
-
-Now consider the hypothetical \textcolor{red}{{\bf RED}} curve of Figure~\ref{fig:predictive_power}.
+% %Accordingly, we would say that there are many cases where  wisdom from prior projects can be readily applied to guide future projects and (b)~the generality issues raised are not be so pressing.
+
+% Now consider the hypothetical \textcolor{red}{{\bf RED}} curve of Figure~\ref{fig:predictive_power}.
 Here, we see that (hypothetically)  learning from more projects makes quality predictions worse which means the our 10,000 projects break up into ``communities'' of size one.
@@
 
-In summary, the above two sections lead to our  research question {\bf  RQ4}:
-does learning from too many projects have detrimental effects. Later in this
-paper, we will return to this issue.
-
+% In summary, the above two sections lead to our  research question {\bf  RQ4}:
+% does learning from too many projects have detrimental effects. Later in this
+% paper, we will return to this issue.
+
+\section{Background and Related Work}
+\label{sec:literature}
 \subsection{Why Transfer Knowledge?}
@@
 
-\textbf{(a) The lesson on big data is that that the {\em more} training data, the {\em better} the learned model.} Vapnik~\cite{vapnik14} discusses examples where models accuracy improves to nearly 100\%, just by training on $10^2$ times as much data.
+\textbf{(a) The lesson on big data is that that the {\em more} training data, the {\em better} the learned model:} Vapnik~\cite{vapnik14} discusses examples where models accuracy improves to nearly 100\%, just by training on $10^2$ times as much data.
 This effect has yet to be seen in SE data~\cite{menzies2013guest} but that might just mean we have yet to use enough training data (hence, this study).
 
-\textbf{(b) We need to learn from more data since there is very little agreement on what has been learned to far:} Another reason to try generalizing across more SE data is that, among developers, there is little agreement on what many issues relating to software:
+\textbf{(b) We need to learn from more data since there is very little agreement on what has been learned so far:} 
+% Another reason to try generalizing across more SE data is that, among developers, there is little agreement on what many issues relating to software:
+\respto{2-23}{\color{blue} Among developers,  there is little agreement on what is of importance relating to software quality and other aspects of the software development:}
 \bi
@@
 
-It turns out that developers are not the only one's confused about how various factors influence software projects.
+\respto{2-24}{\color{blue} It turns out that developers are not the only one's confused about how various factors influence software projects.
 Much recent research calls into question  the ``established wisdoms'' of SE field.
-For example, here is a list of recent conclusions that contradict prior conclusions:
-
-\bi
-
+
+Here is a list of recent conclusions that contradict prior conclusions:}
+
+\bi
     \item In stark contrast to  much prior research, pre- and post- release failures are not connected~\cite{fenton2000quantitative};
@@
     \item Delayed issues are not exponentially more expensive to fix~\cite{menzies2017delayed};
-
 \ei
@@
 Subsequent research realized that data had to be carefully sub-sampled and possibly transformed before quality predictors from one source are applied to a target project.
-Successful transfer learning can have two variants -
-
-\bi
-\item    
- \textbf{Heterogeneous Transfer Learning:} This type of transfer learning operates on source and target data that contain the different attributes.
+Transfer learning can have two variants -
+
+\bi
+\item    
+ \textbf{Heterogeneous Transfer Learning:} This type of transfer learning operates on source and target data that contain the different attributes~\respto{2-17}{\color{blue}\cite{jing2015heterogeneous,he2014towards,nam2017heterogeneous,cheng2016heterogeneous,yu2017feature}}.
 
@@
 \textbf{Homogeneous Transfer Learning:} This kind of transfer learning operates on source and target data that contain the same attributes.
-This paper explores scalable methods for  homogeneous transfer.
+This paper explores scalable methods for homogeneous transfer~\respto{2-17}{\color{blue}\cite{ma2012transfer,zimmermann2009cross,turhan2009relative,krishna2018bellwethers}}.
 \ei
@@
 
-Considering all the attempts at transfer learning sampled above, suggested a surprising lack of consistency in the choice of datasets, learning methods, and statistical measures while reporting results of transfer learning.
+Considering all the attempts at transfer learning sampled above, suggested a surprising lack of consistency in the choice of source datasets, learning methods, and statistical measures while reporting results of transfer learning.
 This issue was addressed by ``Bellwether'' suggested by Krishna et al.
@@
 
-\section{About GENERAL}\label{sec:Metric Extraction}
+\section{About GENERAL}
+% \label{sec:Metric Extraction}
 \label{GENERAL}
 
+\begin{figure}[!t]
+    \small
+     \begin{lstlisting}[mathescape,numbers=right,frame=None]
+        def General(project):
+            # getting feature vectors for each project
+            # complexity is O(N)
+            feature_vectors = get_features(projects)
+            # hierarchically clustering projects
+            # complexity is O(N)
+            h_clusters = BIRCH(projects,feature_vectors)
+            for level in h_clusters.levels:
+                if level.depth == h_clusters.max_depth:
+                    # finding bellwether for each cluster at leaf-level
+                    # complexity is O(m), assuming m clusters
+                    for cluster in level.clusters:
+                        # finding bellwether for a cluster
+                        # complexity is O(n^2) where n = N/m
+                        level.cluster.bell = bellwether(cluster.projects)
+                else:
+                    for cluster in h_clusters.level.clusters:
+                        bell_projects = cluster.child.get_bellwethers()
+                        level.cluster.bell = bellwether(bell_projects)
+            return h_clusters
+
+            \end{lstlisting} 
+            \vspace{-0.2cm}
+            \caption{Pseudo-code of GENERAL}
+            \label{fig:Pseudo-code} 
+            \vspace{-0.3cm}
+\end{figure}
+
  Our proposed improvement to bellwethers is called GENERAL.
-The core intuition of this new approach is that if many projects are similar, then we do not need to run comparisons between all pairs of projects.
-When such similar projects exist, if may suffice to just compare a small number of   representative examples.
-
- Accordingly, the rest of this paper performs the following experiment:
+The core intuition of this new approach is that if many projects are similar, then we do not need to run comparisons between all pairs of projects.\respto{1-2}{\color{blue} We say this since  Devanbu et al.`\cite{hindle2012naturalness} report that if Markov chains are created for tokens in a program, then a remarkably small number of chains capture most of the program.
+Given these similarities,   we can exploit symmetries between different projects in order to learn predictors from one and apply those to another.
+To say that another way, when such similar projects exist, if may suffice to just compare a small number of representative examples.
+}
+%  When such similar projects exist, if may suffice to just compare a small number of representative examples.
+
+\respto{3-10}{\color{blue}  
+ Accordingly, the rest of this paper performs the following experiment assuming :
  \be
- \item Summarize the projects via {\bf feature extraction} (see \S\ref{sec:fx}).
+ \item Summarize the projects via {\bf feature extraction} (see \S\ref{sec:fx}). Assuming there are N projects, this step has a complexity of $O(N)$.
  \item Using some clustering algorithm, group all our data into sets of similar projects.
- \item The groups are themselves grouped into super-groups, then super-super-groups, etc to form a tree.  This step requires a {\bf hierarchical clustering} algorithm (see \S\ref{sec:hc}).
+ \item The groups are themselves grouped into super-groups, then super-super-groups, etc to form a tree.
+This step requires a {\bf hierarchical clustering} algorithm (see \S\ref{sec:hc}).
+Our hierarchical clustering algorithm BIRCH has a complexity of $O(N)$ where each project is represented by a feature vector from step 1.
  \item Starting at the leaves of that tree,   the best project is discovered by training on each project, and test its model
@@
  and  a comparison method to {\bf select the best model} (see \S\ref{sec:best}).
- \item  Once bellwether from each group is  pushed up the tree, then steps 4,5 are repeated,
+Here if we analyze an average case where $N$ projects is divided into $m$ clusters equally, then each cluster has a complexity of $O((N/m)^2)$ and the total complexity is $O(m*(N/m)^2)$ as there are $m$ clusters.
+ \item  Once bellwether from each group is  pushed up the tree, each super-groups only has projects selected as bellwether from step 5 then steps 4,5 are repeated,
  recursively.
@@
  \ee
- Note that when the clustering algorithm divides the data into $m$ clusters, then the complexity of this method (which we call GENERAL) is: 
+
+ Note that when the clustering algorithm divides the $N$ projects into $m$ clusters at leaf level, then if we analyze the average case complexity of the algorithm using the pseudo-code from \fig{Pseudo-code} average case complexity of this method (which we call GENERAL) is:
  \begin{equation}
@@
 \end{equation}
- \fig{cost} contrasts the computational cost of Equation~\ref{eq:GENERAL} with Equation~\ref{eq:bellwether}   
- (and that figure assumes $m=20$, which is the division constant we used in these experiments-- see below.).
- As seen in that figure,  the $O(m*(N/m)^2)$ analysis is inherently   more scalable than the $O(N^2)$ analysis  required by standard bellwether.
+
+}
+{\color{blue}
+ Comparing the computational cost of Equation~\ref{eq:GENERAL} with Equation~\ref{eq:bellwether}, we can say the $O(m*(N/m)^2)$ analysis is inherently more scalable than the $O(N^2)$ analysis required by standard bellwether as m increases.}
 
@@
 Using the   Understand tool~\cite{visualize},
-we   calculated 21 product and 5 process metrics to build     defect prediction models
+we calculated different variations (i.e. average, max etc.) of 21 product and 5 process metrics to build defect prediction models
  (see Table~\ref{tbl:metric}).
@@
 \item Since some projects have relatively few defects, before learning, 
-some {\em over-sampling} is required to increase the number of defective examples in the training sets
-\item Since one of our research questions ({\bf RQ5}) asks ``what did we learn from all these projects'', we needed a learning method that generate succinct models.
+some {\em over-sampling} is required to increase the number of defective examples in the training sets.
+\item Since one of our research questions ({\bf RQ6}) asks ``what did we learn from all these projects'', we needed a learning method that generate succinct models.
 According, we used {\em feature selection}  to check which subset of Table~\ref{tbl:metric}
@@
 \item
-The logistic regression learner 
-(since it is relatively fast);
-\item
-The SMOTE class imbalance correction algorithm~\cite{Chawla2002},  which we run  on the training data\footnote{  The SMOTE Synthetic Minority Over-Sampling Technique algorithms sub-samples the majority class (i.e., deletes examples) while over-sampling the minority class until all classes have the same frequency.
-To over-sample, new examples are synthesized extrapolating between known examples (of the minority class) and its $k$ nearest neighbors.
- While it is useful
+The logistic regression learner, \respto{1-5a} {\color{blue} since it is widely used in defect prediction~\cite{ghotra2015revisiting,XXX} in software engineering domain and it is relatively fast in terms of model building time than other learners such as Support Vector Machine, Random Forest, Artificial Neural Nets etc.
+tested on defect prediction.~\cite{ghotra2015revisiting};}
+\item
+The SMOTE class imbalance correction algorithm\footnote{  The SMOTE Synthetic Minority Over-Sampling Technique algorithms sub-samples the majority class (i.e., deletes examples) while over-sampling the minority class until all classes have the same frequency.
+To over-sample, new examples are synthesized extrapolating between known examples (of the minority class) and its $k$ nearest neighbors.}~\cite{Chawla2002}, \respto{1-5b} {\color{blue} since many of the projects have relatively very few or large number of defects.
+A model build on project with such skewed class distribution can result in a biased model towards the majority class (Such models can either have low recall or high recall with high pf).
+Thus we run SMOTE on the training data\footnote{While it is useful
   to artificially boost the number of target examples
 in the training data~\cite{Chawla2002,Pelayo2007,mensah2017investigating}, it is a methodological error to also change the distributions in   the test data~\cite{agrawal17}. Hence, for our work,
-we take care to {\em only} resample the training data.};
-\item
-and Hall's
+we take care to {\em only} resample the training data.} to artificially boost the number of target examples in the training data and achieving balanced recall and pf for the minority class test examples};
+\item
+Hall's
 CFS feature selector~\cite{hall1999correlation}\footnote{CFS  is based on the heuristic
@@
 Note that for this to be maximal, $r_{\mathit{cf}}$  must be large
-and $r_{\mathit{ff}}$ must be small. That is, features have to connect more to the class than each other.}. 
+and $r_{\mathit{ff}}$ must be small.
+That is, features have to connect more to the class than each other.}, \respto{1-5c} {\color{blue} to identify features which are highly correlated with the classification, yet uncorrelated to each other.
+The features which are  highly correlated with each other will not add more information while making classification, while the features which are uncorrelated towards the classification also not add more information while making classification.
+The CFS algorithm incrementally picks one feature at a time which adds the most information towards the classification at a given step and stops when there is no more improvement in the score (see footnote 4).
+}
 \ei
@@
 As to CFS, we found that without it, our recalls were very low and we could not identify which metrics mattered the most.
-Also,   extensive studies have found that CFS more useful than many other feature subset selection methods such as  PCA or InfoGain or RELIEF~\cite{hall1999correlation}.
+Also,   extensive studies have found that CFS more useful than many other feature subset selection methods such as  PCA or InfoGain or RELIEF\respto{1-5e} {\color{blue}~\cite{hall1999correlation,challagulla2008empirical,arar2015software,lee2016developer,rodriguez2007attribute,gao2015combining,hosni2017investigating}.
+}
 
 \subsection{Select the Best Model}\label{sec:best}
-As discussed below, the defect models assessed in these experiments
-
-To find the bellwether, our method must compare many models and select the best one.
-As discussed below, we score model performance according to five goals:
-\bi
-\item
-Maximize
-recall and precision and popt(20);
-\item
-While minimizing  false alarms  and
-ifa\_auc.
-\ei
-(For definitions and details for these criteria, and why we selected them, see \S\ref{sec:Measures}.)
+% As discussed below, the defect models assessed in these experiments
+
+To find the bellwether, our method must compare many models and select the best one based on the goals important for that task.
 
@@
 
-An alternative to the Zitler indicator is    `boolean domination ''
- that says one thing is better than another it if it no worse on any criteria and better on at least one criteria. We prefer Equation~\ref{eq:cdom} to boolean domination since we
- have a   5-goal optimization problem and it it is known that boolean domination often  fails for 3 or more goals~\cite{Wagner:2007,Sayyad:2013}.
+An alternative to the Zitler indicator is    `boolean domination '' that says one thing is better than another it if it no worse on any criteria and better on at least one criteria.
+We prefer Equation~\ref{eq:cdom} to boolean domination since we have a   3-goal optimization problem and it it is known that boolean domination often  fails for 2 or more goals~\cite{Wagner:2007,Sayyad:2013}.
+
+As discussed above, model performance can be scored and the best model can be chosen by researchers based on their choice of metrics.
+In this experiment we score model performance according to three goals i.e.
+recall, precision, pf, and chose the best model where we can:
+\bi
+\item
+\respto{1-5f} {\color{blue}Maximize
+recall\footnote{{\color{blue}Recall is the ratio between predicted actual target class examples vs all target class examples.
+In other words recall = $ \frac{TP}{TP+FN} $, which means in an ideal scenario where we identify all the actual target class as target class without missing the recall will be one.
+Thus to make a good predictor we need to maximize the recall}} and precision\footnote{{\color{blue}Precision is the ratio between predicted actual target class examples vs all predicted target class examples.
+In other words precision = $ \frac{TP}{TP+FP} $, so in an ideal scenario where we identify all the actual target class as target class without predicting any non-target class as target class the precision will be one.
+Thus to make a good predictor we need to maximize the precision as well}}
+%and popt(20)\footnote{{\color{blue}popt(20) is a cost sensitive productivity based metric, which represents the percentage of total defect identified by reading 20\% of the code.
+This means more defects we can identify by reading only 20\% of the code is better for the developers to localize and fix the defects.}}
+};
+\item
+\respto{1-5f} {\color{blue} While minimizing  false alarms\footnote{{\color{blue}false alarms (pf) is the ratio between non-target class identified as target class and total number of actual non-target class.
+IN other words false alarm = $ \frac{FP}{FP+TN} $, so in an ideal scenario FP should be zero, thus not identifying and non-defective class as defective and effectively making false alarm as zero.}}
+%and ifa\_auc\footnote{{\color{blue}Need to describe ifa auc XXXX.}}
+.}
+\ei
+(For definitions and details for these criteria, and why we selected them, see \S\ref{sec:Measures}.)
+
+% In such   {\em multi-objective} problems, one model is better than another if it
+%  satisfies a ``domination predicate''.
+%  We use the Zitler indicator dominance
+%  predictor~\cite{zit02} to select our bellwether (since this is known to select better models
+%  for 5-goal optimization~\cite{Sayyad:2013,Sayyad:2013:SPL}).
+% This predicate favors model
+%   $y$ over $x$  model if $x$ ``losses'' most:
+% \begin{equation}\label{eq:cdom}
+% \begin{array}{rcl}
+% \textit{worse}(x,y)& =& \textit{loss}(x,y) > \textit{loss}(y,x)\\
+% \textit{loss}(x,y)& = &\sum_j^n -e^{\Delta(j,x,y,n)}/n\\
+% \Delta(j,x,y,n) & = & w_j(o_{j,x}  - o_{j,y})/n
+% \end{array}
+% \end{equation}
+% where  ``$n$'' is the number of objectives (for us, $n=5$) and $w_j\in \{-1,1\}$ depending on whether
+% we seek to maximize goal $x_j$.
+
+% An alternative to the Zitler indicator is    `boolean domination ''
+%  that says one thing is better than another it if it no worse on any criteria and better on at least one criteria. We prefer Equation~\ref{eq:cdom} to boolean domination since we
+%  have a   5-goal optimization problem and it it is known that boolean domination often  fails for 3 or more goals~\cite{Wagner:2007,Sayyad:2013}.
 
@@
        \item \textbf{Avoid projects with too few errors:}
-    We pruned  projects which did not  have enough fix-inducing vs non-fixing data points to create a stratified k=5 fold cross-validation an
+    We pruned  projects which did not  have enough fix-inducing vs non-fixing data points to create a stratified k=5 fold cross-validation/% an
 
@@
 
-\subsection*{RQ1: Can hierarchical clustering tame the complexity of bellwether-based reasoning?}
-\label{sec:rq1}
+\subsection*{RQ1: How slow is conventional bellwether method? }
+\label{sec:rq3}
+
+\subsection*{RQ2: How  fast  is  new  bellwether  method  aka  GENERAL?}
+\label{sec:rq3}
+
+\subsection*{RQ3: Can hierarchical clustering tame the complexity of bellwether-based reasoning?}
+\label{sec:rq3}
 
@@
 
-{\small 
+% {\small 
+% \begin{figure*}[!t]
+%     \centering
+%     \begin{tikzpicture}[nodes={draw, circle,fill=darkgray!60}, ->,sibling distance=.7cm,minimum size=.1cm,scale=.5]
+
+%     \node{627}
+%         child { node {57}
+%             child {node {9}} 
+%             child {node {9}} 
+%             child {node {7}} 
+%             child {node {17}}
+%             child {node {13}}}
+%         child [missing]
+%         child [missing]
+%         child [missing]
+%         child [missing]
+%         child [missing]
+%         child [missing]
+%         child [missing]
+%         child { node {127} 
+%             child {node {3}} 
+%             child {node {9}} 
+%             child {node {19}} 
+%             child {node {15}}
+%             child {node {4}}
+%             child {node {17}} 
+%             child {node {15}} 
+%             child {node {19}} 
+%             child {node {11}}
+%             child {node {15}}}
+%         child [missing]
+%         child [missing]
+%         child [missing]
+%         child [missing]
+%         child [missing]
+%         child [missing]
+%         child [missing]
+%         child [missing]
+%         child [missing]
+%         child [missing]
+%         child [missing]
+%         child [missing]
+%         child { node {183} 
+%             child {node {8}} 
+%             child {node {3}} 
+%             child {node {12}} 
+%             child {node {16}}
+%             child {node {20}}
+%             child {node {18}} 
+%             child {node {12}} 
+%             child {node {4}} 
+%             child {node {12}}
+%             child {node {16}}
+%             child {node {5}}
+%             child {node {17}} 
+%             child {node {9}} 
+%             child {node {9}} 
+%             child {node {10}}
+%             child {node {14}}}
+%         child [missing]
+%         child [missing]
+%         child [missing]
+%         child [missing]
+%         child [missing]
+%         child [missing]
+%         child [missing]
+%         child [missing]
+%         child [missing]
+%         child [missing]
+%         child [missing]
+%         child [missing]
+%         child [missing]
+%         child [missing]
+%         child [missing]
+%         child [missing]
+%         child [missing]
+%         child { node {260} 
+%             child {node {17}} 
+%             child {node {17}} 
+%             child {node {20}} 
+%             child {node {14}}
+%             child {node {9}}
+%             child {node {13}} 
+%             child {node {18}} 
+%             child {node {10}} 
+%             child {node {18}}
+%             child {node {10}}
+%             child {node {6}} 
+%             child {node {15}} 
+%             child {node {14}} 
+%             child {node {9}}
+%             child {node {10}}
+%             child {node {8}} 
+%             child {node {7}} 
+%             child {node {13}} 
+%             child {node {15}}}
+%             ;
+% \end{tikzpicture}
+%     \caption{Example of Hierarchical Clustering for 627 projects}
+%     \label{fig:example tree}
+% \end{figure*}
+% }
+%%%%%%%%%%%%%%%%%%%%%%%End Latex Table%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure*}[!t]
     \centering
-    \begin{tikzpicture}[nodes={draw, circle,fill=darkgray!60}, ->,sibling distance=.7cm,minimum size=.1cm,scale=.5]
-
-    \node{627}
-        child { node {57}
-            child {node {9}} 
-            child {node {9}} 
-            child {node {7}} 
-            child {node {17}}
-            child {node {13}}}
-        child [missing]
-        child [missing]
-        child [missing]
-        child [missing]
-        child [missing]
-        child [missing]
-        child [missing]
-        child { node {127} 
-            child {node {3}} 
-            child {node {9}} 
-            child {node {19}} 
-            child {node {15}}
-            child {node {4}}
-            child {node {17}} 
-            child {node {15}} 
-            child {node {19}} 
-            child {node {11}}
-            child {node {15}}}
-        child [missing]
-        child [missing]
-        child [missing]
-        child [missing]
-        child [missing]
-        child [missing]
-        child [missing]
-        child [missing]
-        child [missing]
-        child [missing]
-        child [missing]
-        child [missing]
-        child { node {183} 
-            child {node {8}} 
-            child {node {3}} 
-            child {node {12}} 
-            child {node {16}}
-            child {node {20}}
-            child {node {18}} 
-            child {node {12}} 
-            child {node {4}} 
-            child {node {12}}
-            child {node {16}}
-            child {node {5}}
-            child {node {17}} 
-            child {node {9}} 
-            child {node {9}} 
-            child {node {10}}
-            child {node {14}}}
-        child [missing]
-        child [missing]
-        child [missing]
-        child [missing]
-        child [missing]
-        child [missing]
-        child [missing]
-        child [missing]
-        child [missing]
-        child [missing]
-        child [missing]
-        child [missing]
-        child [missing]
-        child [missing]
-        child [missing]
-        child [missing]
-        child [missing]
-        child { node {260} 
-            child {node {17}} 
-            child {node {17}} 
-            child {node {20}} 
-            child {node {14}}
-            child {node {9}}
-            child {node {13}} 
-            child {node {18}} 
-            child {node {10}} 
-            child {node {18}}
-            child {node {10}}
-            child {node {6}} 
-            child {node {15}} 
-            child {node {14}} 
-            child {node {9}}
-            child {node {10}}
-            child {node {8}} 
-            child {node {7}} 
-            child {node {13}} 
-            child {node {15}}}
-            ;
-\end{tikzpicture}
+    \includegraphics[width=\linewidth]{figs/bubble.pdf}
     \caption{Example of Hierarchical Clustering for 627 projects}
@@
 \end{figure*}
-}
-%%%%%%%%%%%%%%%%%%%%%%%End Latex Table%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% \subsection*{RQ2: Can hierarchical clustering tame the complexity of bellwether?}
-% \label{sec:rq2}
-
-% While we must deprecate standard bellwether (for learning lessons from large datasets), we can endorse the use of GENERAL.
-% Thoretically, GENERAL
-
-% To tame complexity of bellwether in this RQ, we propose a new bellwether method called GENERAL to find bellwether in large datasets.
-This bellwether method is composed of 6 stages, (a) a feature extraction process to summarize each project into a single representative vector, (b) a hierarchical clustering algorithm, which uses the feature vectors to cluster similar projects into community of increasing size at different levels of cluster, (c) a bellwether selection phase where a $N*(N-1)$ comparison is performed at each leaf level cluster and using a cdom calculation in all the metrics mentioned in~\ref{tbl:metric} a bellwether is selected, (d) a iterative bellwether promotion stage, where bellwether from child clusters are promoted as potential bellwethers at parent cluster, (e) another bellwether selection phase at non-leaf levels, where comparisons are only made among potential bellwethers from leaf node and finally (f) a bellwether prediction phase, which suggests a bellwether based on project similarity when a new project is to be predicted.
-The details of each phase is mentioned in sec~\ref{GENERAL}.
-
-% In the \textit{bellwether method} proposed by Krishna et al.
-if there are N projects in a community it will make $\approx N^2$ comparisons to discover the bellwether.
-While GENERAL different approach to discover bellwether by dividing the data into smaller cluster and finding bellwether among each, here if we assume we have m cluster at leaf level with N projects in each, we will have
-% $\approx m*(N/m)^2$ comparisons to discover the bellwether which is m times less comparison.
-For example if we see the example figure~\ref{fig:example tree} for hierarchically cluster a community of 627 projects, if we use the default bellwether method it will require  393,129 comparisons.
-On the other hand, if we use the GENERAL algorithm to find the bellwether,  it will require only 9,080 comparisons.
-Using this process we are able to find bellwether in 1.5 hours, which is order of magnitude faster then the bellwether method proposed by Krishna et al.
-In summary, we find that:
-
-% \begin{result}
-% {GENERAL can find the bellwether project
-% an order of magnitude faster than prior work
-% (1.5 hours versus 3 days)
-% since GENERAL  requires far fewer
-%  comparisons between projects
-%  (9,080 instead of 393,129 required for 
-%  Krishna et al.'s bellwether method). }
-% \end{result}
-
-% XXXX
-
-% \begin{equation}
-% \label{eq:GENERAL}
-%     {GENERAL\; complexity } =  O(m*(N/m)^2)
-% \end{equation}
-
-\subsection*{RQ2: Is this faster bellwether effective?}
-\label{sec:rq3}
-
-The speed improvements reported in {\bf RQ1} are only useful
+
+\subsection*{RQ4: Is this faster bellwether effective?}
+\label{sec:rq4}
+
+The speed improvements reported in {\bf RQ3} are only useful
 of this faster method can also deliver adequate predictions
@@
 Given this lack luster performance, 
-and   the {\bf RQ1} results (where traditional bellwether ran very slowly), we therefore  
+and   the {\bf RQ3} results (where traditional bellwether ran very slowly), we therefore  
 deprecate the traditional bellwether approach.
@@
 
-\subsection*{RQ3: Does learning from too many projects have detrimental effect?}
-\label{sec:rq4}
+\subsection*{RQ5: Does learning from too many projects have detrimental effect?}
+\label{sec:rq5}
 
@@
 
-To answer {\bf RQ3}, we first note that when GENERAL
+To answer {\bf RQ5}, we first note that when GENERAL
 calls the BIRCH clustering algorithm, it generates the tree
@@
 \ei
-That is, to answer {\bf RQ3} we need only compare the predictive performance
+That is, to answer {\bf RQ5} we need only compare the predictive performance
 of models learned from these different levels. In that comparison,
@@
 
-\subsection*{RQ4: What exactly did we learn from all those projects?}
-\label{sec:rq5}
+\subsection*{RQ6: What exactly did we learn from all those projects?}
+\label{sec:rq6}
 
@@
 from hundreds of software projects, it is appropriate to ask
-what model was learned from all that data. This is an important question for this research sinceif  we cannot show the lessons
+what model was learned from all that data. This is an important question for this research since if  we cannot show the lessons
 learned from our 627 projects, then all the above is wasted effort.
@@
 (a) \textit{Evaluation Bias}: 
-In  {\bf  RQ1, RQ2} and {\bf RQ3} we have shown the performance of local model, hierarchical bellwether models, default bellwether model and compared them using statistical tests on their performance to make conclusion about presence of generality in SE datasets.
+In  {\bf  RQ3, RQ4} and {\bf RQ5} we have shown the performance of local model, hierarchical bellwether models, default bellwether model and compared them using statistical tests on their performance to make conclusion about presence of generality in SE datasets.
 While those results are true, that conclusion is scoped by the evaluation metrics we used to write this paper.

### 2020-03-03 pseudocode/pseudo_code.py

@@ -1,0 +1,12 @@
+def General(project):
+    feature_vectors = get_featrures(projects)
+    h_clusters = BIRCH(projects,feature_vectors)
+    for level in h_clusters.levels:
+        if level.depth == h_clusters.max_depth:
+            for cluster in level.clusters:
+                level.cluster.bell = bellwether(cluster.projects)
+        else:
+            for cluster in h_clusters.level.clusters:
+                bell_projects = cluster.child.get_bellwethers()
+                level.cluster.bell = bellwether(bell_projects)
+    return h_clusters

### 2020-03-12 response.tex
Updates from Overleaf

@@
 \be
-\item The problem statement has been  clarified and properly positioned (R1, R3). XXX
-\item The novelty of the approach has  been clarified (R3). XXX (see \bareresp{2-1})
+\item The problem statement has been  clarified and properly positioned (R1, R3).
+\item The novelty of the approach has  been clarified (R3). (see \bareresp{3-1})
 \item Using comments from  (R1, R2, R3), we have made numerous small editorial improvements.
@@
 
-\review{(1.1) Background.
+\review{(1.1a) Background.
 The paper builds upon a number of previous studies.
@@
 
-\response{You are quite correct, we did not define bellwether till very late in the prior draft. In this draft, we define bellwether on page 1.
-}
+\response{(1.1b)You are quite correct, we did not define bellwether till very late in the prior draft. In this draft, we define bellwether on page 1\respto{1-1a}}
 
@@
 
-\response{Thank you for that comment.  You a re quite correct-- we did not document the source of our intutuion. We have added the following note to \respto{1-XX}}
+\response{Thank you for that comment.  You a re quite correct-- we did not document the source of our intutuion. We have added the following note to \respto{1-1b}}
 
@@
 ``Secondly, given these similarities,   we can exploit symmetries between different projects in order to learn predictors from one and apply those to another.
-To say that anothe way, given large scale similarities between projects,  then we do not need to run comparisons between all pairs of projects since analyszing just a few pairs should work as well as anything else.''}
+To say that another way, given large scale similarities between projects,  then we do not need to run comparisons between all pairs of projects since analyzing just a few pairs should work as well as anything else.''}
 \end{quote}
@@
 
-\response{ need a new RQ0: how slow is standard bellwether. theoretically an empriically its slow (chart on p2. move to RQ0). May need to include results using increasing community size.}
+\response{ need a new RQ0: how slow is standard bellwether.
+theoretically an empirically its slow (chart on p2.
+move to RQ0).
+May need to include results using increasing community size.XXX including an comparison study with varying size of community to start with.
+Still need to write this}
 
-\review{(1.3) Writing style.
-The introduction is, simply, to be completely rewritten.
-I would like to see a paper that is understandable even from non-experts.
+\review{(1.3a) Writing style. The introduction is, simply, to be completely rewritten}
+
+\response{Thank you for your comment. On review, we found that core problem of conclusion instability
+was not well documented in the introduction. This new draft fixes that problem. Much of the new
+text on page1 takes care to document {\em why }
+we are exploring conclusion instability before
+moving on the {\em how} we do that exploration.}
+
+\review{(1.3a)I would like to see a paper that is understandable even from non-experts.
 As such, please define the context of the paper, the concepts of (1) software quality - line 1, (2) general models - line 2, (3) many projects - line 2, (4) "scalable approach to learning effective models adapted to the task at hand" - line 2/3, (5) "or does the truth lie somewhere in-between" - line 3.
@@
 
-\response{ frist 3 oaras deled tup to :"funding general lessons"}
+\response{Thank you for your comment. We have rewritten the introduction to be more understandable from a non-expert view and added necessary definitions where required.}
 
@@
 
-\response{ you are right. sueprlatives deleted (including that one)"}
+\response{ Thank you for your comment, you are right.In this manuscript we have deleted the  superlatives (including that one)}
 
@@
 
-\response{ you are right. sueprlatives deleted (including that one)"}
+\response{ Thank you for your comment, you are quite right. We had not properly mentioned the reason behind choosing logistics regression. In this draft we have added the reasons to \respto{1-5a}:}
+
+\begin{quote}
+\response{
+"The logistic regression learner,  since it is widely used in defect prediction~\cite{ghotra2015revisiting,XXX} in software engineering domain and it is relatively fast in terms of model building time than other learners such as Support Vector Machine, Random Forest, Artificial Neural Nets etc.
+tested on defect prediction.~\cite{ghotra2015revisiting}}
+\end{quote}
 
@@
 
+\response{You are right, we had not included the reason for using SMOTE in our algorithm and had not explained why the problem is unbalanced.
+In this draft we have added notes to answer those questions \respto{1-5b}:}
+\begin{quote}
+    \response{The SMOTE class imbalance correction algorithm~\cite{Chawla2002}, since many of the projects have relatively very few or large number of defects.
+A model build on project with such skewed class distribution can result in a biased model towards the majority class (Such models can either have low recall or high recall with high pf).
+Thus we run SMOTE on the training data to artificially boost the number of target examples in the training data and achieving balanced recall and pf for the minority class test examples}
+\end{quote}
+
 \review{(1.5c)
@@
 }
+
+\response{You are quite correct, we did not included the details about how the features are being removed and why in the last draft.
+In this draft we have included notes regarding how CFS works and why the features that are not used are removed \respto{1-5b}:}
+
+\begin{quote}
+    \response{Hall's CFS feature selector~\cite{hall1999correlation} is used to identify features which are highly correlated with the classification, yet uncorrelated to each other.
+The features which are  highly correlated with each other will not add more information while making classification, while the features which are uncorrelated towards the classification also not add more information while making classification.
+The CFS algorithm incrementally picks one feature at a time which adds the most information towards the classification at a given step and stops when there is no more improvement in the score.}
+\end{quote}
 
@@
 
-\response{how should I answer Where can the reader understand this statement? May need to remove this section as i don't have the results}
+\response{Thank you for your comment, using the replication package (including data) the experiments can be reproduced.\respto{1-5h}}
 
@@
 
-\response{added footnote also there are details in sec 4.5}
+\response{Thank you for your comment, we didn't explained why these metrics need to be maximized, added necessary details\respto{1-5f} as footnote also there are details in sec 4.5}
 
@@
 
-\response{added footnote also there are details in sec 4.5}
+\response{Thank you for your comment, we didn't explained why these metrics need to be minimized, added necessary details\respto{1-5f} as footnote also there are details in sec 4.5}
 
@@
 
-\response{you are wright, need an RQ0}
+\response{you are right, in the last draft we indeed did not included detailed analysis of the results to show the scalability of our model.
+In this draft \respto{1-2}\respto{1-6a} we have included 2 more research questions (RQ1 and RQ2) to show the conventional bellwether is slower than the new bellwether (aka GENERAL) method.
+We also have updated another research question (RQ3) to compare the methods in-term of number of comparisons and time taken to run the two methods, as can been seen in figure~\ref{fig:compare} and \ref{fig:compare_time}.}
 
 \review{(1.6b)
-The same is true for the other research questions. And, in general, there is qualitative analysis: Why are the results the ones reported in the paper? }
+The same is true for the other research questions. And, in general, there is qualitative analysis: Why are the results the ones reported in the paper?}
 
-\response{you are right,Thank you for that comments. We have added much  quantaitive analusis as
-well as statistical tests to this paper. Please see \fig{XXX7}.}
+\response{you are right,Thank you for that comments. We have added much  quantitative analysis as
+well as statistical tests to this paper. Please see figure~\ref{fig:compare} and \ref{fig:compare_time}. XXXX(do we need more analytics and if so what?)}
 
@@
 
-RQ0: how slow old better
+\response{Thank you for your comment, in this version we have updated the RQ3 to show that our method is scalable.
+We have showcased the analysis of number of comparisons and run time between the two algorithm (conventional bellwether and GENERAL) using various community size.}
 
-RQ1: how fast new bellweather.
+\section*{Reviewer}
 
-RQ2: scalabulity (the old RQ1)
-
-RQ3: (as before)
-
-RQ4: (as belfire)
-
-\section*{Reviewer 2squeue}
-
-Many of your comeents take issue with two terms used in this paper "lessons learned" and "trasfer learning".
+Many of your comments take issue with two terms used in this paper "lessons learned" and "transfer learning".
 We agree with you that our use of "lessons learned" was inappropriate and we have removed all those usages.
 
-As to oir use of "transfer learning", 
-inspired by your commetns we have ckarified what we mean by that term much earlier in the paper (see \cite{XXX}).
+As to our use of "transfer learning", 
+inspired by your comments we have clarified what we mean by that term much earlier in the paper (see \cite{XXX}).
 Base don that clarification, we can show that our use of ``transfer learning'' is consistent with its usage by Pan'09 (a paper current 8,220 citations at the time of this writing).
 Also, our usage is consistent with dozens of recent SE research papers on transfer learning~\cite{XXXmanycite}.
-Thank you for enocuraging us to clarify that terminology.
+Thank you for encouraging us to clarify that terminology.
 
@@
 
-\response{ acts as data poasss on. cjanged to similiar.}
+\response{ Thank you for your comment, in the last draft we did not accurately explain what bellwether is. In this draft we have included the definition of bellwether \respto{1-1}\respto{2-2}:}
+
+\begin{quote}
+    \response{``bellwether'' is a project from a community of N projects, whose data yields the best analytic (i.e.
+defect prediction, effort estimation etc) on all others.
+Also, to answer your second question, ``…the bellwether is equivalent to the other models'' has been replaced with ``....since the bellwether is an exemplar projects for the community of N projects seen so far...''  }
+\end{quote}
 
@@
 
-\response{ XX.}
+\response{Thank you for your comment.
+In the first draft we did not adequately explained the goal of the task we are exploring.
+In this version we have added proper details regarding the task, that is to explore defect prediction to localize bugs in project's codebase  using software quality metrics extracted from the projects and the details has been added at \respto{2-3}.}
 
@@
 
-\response{ clairft}
+\response{Thank you for your comment, it was unclear in the previous manuscript whether we need to find different bellwether for discrete task (different than defect rate prediction).
+For finding bellwether for another task, different from defect prediction, we do need to find another bellwether.
+The reason being, for other tasks the model build using the data will be different, so similarity between models  built using the projects will also be different.}
 
@@
 
-\response{ ciuretainly too confusing for intro. can move to a later section and ducssed in more retchnical detail}
+\response{You are correct, it is certainly confusing for intro. we have removed the hypothetical figure and texts associated with it.}
 
@@
 
-\response{ XXXX}
+\response{Not yet sure what it means}
 
@@
 
-\response{ will fix}
+\response{will fix}
 
@@
 
-\response{ will fix}
+\response{You are correct, the wording of the box under RQ4 was confusing.
+We have added new texts \respto{2-9} to be more clear about the  context about finding bellwether to understand importance of features.
+To be more precise, instead of finding important features for each project (which shows very different results for each project), we find the bellwether (as an exemplary project for all other projects) using GENERAL and check the importance of feature for that project only.}
 
@@
 
-\review{2) I do not understand what the second contribution really is.}
+\review{(2.10) I do not understand what the second contribution really is.}
 
-yes, we have deletet is
+\response{
+Thank you for that comment. Yes you are completely correct.
+ On  review,  we  found that  core  problem  of  conclusion  instability  was  not  well documented  in  the  introduction.
+This  new  draft  fixes  that problem.
+Much of the new text on page1 takes care to document {\em why } we  are  exploring  general SE conclusions  before moving on the
+ {\em how} we do that exploration.}
+
+ \response{
+Note that with that new introduction (that focuses more on {\em why}, then this paper is not  better at contextualizing
+and justifying the need (and value) of the second contribution.}
+
+% yes, we have deleted it. But this is one of the main points, can we answer not it}
 
@@
 
-good idea. paper now starts with 2.1
+\response{Yes! Good idea. We have done that.}
 
@@
 
-replaced with two dots poiints: descibning this in wors
+\response{Thank you for your comments, we have moved [Sec.
+2.1] from background to a new section titled Motivation.
+Also we have removed the hypothetical situation and added actual experimental data to show the difference.
+The details has been added as text in \respto{2-12}.}
 
-\review{(2.13) [Sec. 2.2] At least two-thirds of this sub-section is anecdotal. Does the gist of this subsection depend critically on the hypotheticals?}
+\review{(2.13) [Sec. 2.2] At least two-thirds of this sub-section is anecdotal. Does the gist of this subsection depend critically on the hypothetical?}
 
-get rid of 2.2.. delete fig 2
+\response{Thank you for your comments, we have removed the hypothetical graph and added experimental details for this section.
+The new text has been added to [Sec.
+2.2], which is a part of motivation now \respto{2-12}.}
 
@@
 
-\response{with respect, in terms of SE reserch, it it smuch larger thatnanythtngoins eeen before. but your concenr is valud. we have added
-a weaselt sentence at the end saying that we can benever assume generality of all porkect. }
+\response{with respect, in terms of SE research, it is much larger than any studies seen before. but your concern is valid. we have added
+a weaselt sentence at the end saying that we can never assume generality of all porkect.XXX}
 
-\review{(1.15) [Sec.
+\review{(2.15) [Sec.
 2.3] “If they ask ‘are we sure XYZ causes problems?’, can we say that we have mined enough projects to ensure that XYZ is problematic?” We can say XYZ is probably problematic, but that doesn’t answer the deeper question about causality.
@@
 
-\response{ ur right. we shiuld bneve wsay "cuase'. work removed. is associated, statisitally predicts for.}
+\response{ You are quite right.
+we should never say "cause'.
+We have removed the ambiguous statement and added XYZ is a statistical predictor for bug prone code.
+The changes has been added in this manuscript\respto{2-15} }
 
@@
 
-\response{citations added.}
+\response{Thank you for your comment. We indeed forgot to add the citations in the previous manuscript. We have added the citations in this manuscript \respto{2-17}.}
 
@@
 
-\response{fixed}
+\response{Thank you for your comment, we have fixed the incomplete sentence.}
 
-\review{(1.20) [Sec. 4.1] “stratified k=5 fold cross-validation an” Incomplete.}
+\review{(2.20) [Sec. 4.1] “stratified k=5 fold cross-validation an” Incomplete.}
 
-\response{fixed}
+\response{Thank you for your comment, we have fixed the incomplete sentence. We have also ensured there are no more incomplete sentences in this version.}
 
-\review{(1.21) [Sec.
+\review{(2.21) [Sec.
 5] “To put that another way, the answer to ‘is is [sic] possible to learn from too much data’, is ‘depends on what you value’” How does your concept of learning from too much data relate to the concept of overfitting?
@@
 
-\response{timm}
+\response{
+Over-fitting is a problem that can occur with data of any size. Over-fitting is a well-studies problem that explores bias/variance trade offs.
+But over-fitting is an orthogonal issue to Transfer learning.
+To clarify all that we have added text to XXX:}
+\begin{quote}
+\response{
+\respto{2-XXX}
+This sections ask if conclusions always improve as we learn from more and more data.
+This can be an issue since if a new project
+is fundamentally different to all past projects, then irrelevant ideas from the past will be
+inappropriately applied to the present situation. ~\\
+is a special problem that arises when combining old data/models with new data/models.}
+\end{quote}
 
-\review{(1.22) [Abstract] “When one exemplar project…offers the best advice then it can be used to offer advice for many other projects.” The word advice is confusing here.
+\review{(2.22) [Abstract] “When one exemplar project…offers the best advice then it can be used to offer advice for many other projects.” The word advice is confusing here.
 The so-called bellwether does not offer advice or recommendations.
@@
 
-\response{predicttions}
+\response{Thank you for your comment, you are quite correct the use of ``advice or recommendations'' is rather ambiguous in this context.
+We have changed these references of ``advice or recommendations'' to ``prediction'' in this version of manuscript }
 
-\review{(1.23) [Sec. 2.3] “…among developers, there is little agreement on what many issues relating to software.” Please reword.}
+\review{(2.23) [Sec. 2.3] “…among developers, there is little agreement on what many issues relating to software.” Please reword.}
 
-\response{fixed}
+\response{Thank you for your comment. We have made changes \respto{2-23} to the sentence to be understandable }
 
-\review{(1.24) [Sec. 2.3(c)] “For example…” is a run-on sentence.}
+\review{(2.24) [Sec. 2.3(c)] “For example…” is a run-on sentence.}
 
-\review{(1.25) [Sec. 3] What are the units for dataset size in Fig. 4?}
+\response{Thank you for your comments, we have rechecked the manuscript for such run-on-sentences and fixed them in this version.}
 
-\review{(1.26) [Sec. 5] Why do you need a figure (Fig. 6) for two numbers?}
+\review{(2.25) [Sec. 3] What are the units for dataset size in Fig. 4?}
+
+\response{Thank you for your comment, we forgot to include the unit for dataset size in Fig.
+4 (Now Fig~\ref{fig:meta}) in the last  version.
+The unit for dataset size is number of rows for each dataset and it has been added into the figure as well.}
+
+\review{(2.26) [Sec. 5] Why do you need a figure (Fig. 6) for two numbers?}
+
+\response{Thank you for your comment, the figure Fig.
+6 (now Fig~\ref{fig:time}) is important as this figure shows the difference of time taken for each method.
+XXXXXXX include with updated charts.XXXXXXX}
 
@@
 
-\review{(1.1)What I find irritating is that the manuscript introduces a new approach GENERAL, which just applies hierarchical clustering.
+\review{(3.1)What I find irritating is that the manuscript introduces a new approach GENERAL, which just applies hierarchical clustering.
 As far as I understand, hierarchical clustering is a well-known, standard, and largely-evaluated clustering algorithm.
@@
 
-\review{(1.2) Figure 1 “shows a hypothetical cost comparison in AWS between standard bellwether and GENERAL.” If the Figure is hypothetical, why do we need it?
+\response{Thank you for your comment.
+There were indeed lack of clarity regarding the explanation of how GENERAL works, we have added more details about GENERAL\respto{XXXXXX}.
+The algorithm GENERAL uses hierarchical clustering to cluster projects into smaller groups based on similarity and doesn't help with actually predicting the defect.
+GENERAL uses the hierarchical clustering to group the projects, then bellwether method is applied at the leaf nodes of the hierarchical clustering tree to find bellwether for each leaf, then a approximation is applied and only the bellwethers are pushed up to the tree to find bellwether in upper levels.
+This process goes on until we find bellwether for the root node.
+After we have found bellwethers , we build models for predicting defect.}
+
+\review{(3.2) Figure 1 “shows a hypothetical cost comparison in AWS between standard bellwether and GENERAL.” If the Figure is hypothetical, why do we need it?
 Is it based on real data?
@@
 
-we will remove
+\response{Thank you for your comments.
+We have removed the hypothetical scenarios from sec~\ref{sec:motivation}.
+We have removed all the hypothetical graphs and added data from actucal experiment in this version of manuscript\respto{3-2}.}
 
-\review{(1.3) I am also very concerned about the (unproven) assumption that we can make conclusions that hold across multiple projects.
-While the dataset includes 700 projects, we have no information about the project, the domain applications, criticality (e.g., safety-critical systems vs.
+\review{(3.3) I am also very concerned about the (unproven) assumption that we can make conclusions that hold across multiple projects.
+While the dataset includes 700 projects, we have no information about the project, the domain applications, critically (e.g., safety-critical systems vs.
 generic open-source Java libraries).
@@
 
-wirht respect.... but we can
+\response{with respect.... but we can}
 
@@
 
-fig2 remove
+\response{Thank you for your comments.
+We have removed the hypothetical scenarios from sec~\ref{sec:motivation}.
+We have removed all the hypothetical graphs and added data from actual experiment in this version of manuscript\respto{3-2}.}
 
@@
 
-sure. tahts oour case study
+\response{Thank you for your comment.
+In this paper, we discussed about a broader impact of learning from large number of projects to find a general conclusion.
+We indeed didn't emphasized on mentioning, we are using defect prediction as our case study for this paper.
+We have added details\respto{3-5} about using defect prediction in this paper as a case study for showing the importance of learning models from hundreds of projects.}
 
-\review{(1.6) How can we use one single sub-domain (i.e., defect prediction) to make bold statements that should be valid for software analytics in general?
+\review{(3.6) How can we use one single sub-domain (i.e., defect prediction) to make bold statements that should be valid for software analytics in general?
 This overselling concerns me a lot.
@@
 
-not in general. cant prove external validity. jsut for our 673 projects. wichi is orders of mangitude larger than anything seen ebfore.
+\response{Thank you for your comment.
+We indeed can not say that in general and can not prove external validity, but just for the projects used in this paper.
+which is orders of magnitude larger than anything seen before.}
 
-\review{(1.7) Therefore, the title, the abstract, introduction, motivation, and conclusions should mention defect prediction as to the only sub-domain in which GENERAL has been evaluated.
+% not in general. cant prove external validity. jsut for our 673 projects. wichi is orders of mangitude larger than anything seen ebfore.
+
+\review{(3.7) Therefore, the title, the abstract, introduction, motivation, and conclusions should mention defect prediction as to the only sub-domain in which GENERAL has been evaluated.
 Any overselling to other domains (or software analytics in a broader sense) should be removed (perhaps mentioned as part of future work) because it is not supported by what is in the empirical study/results.}
 
-we agree. titlte shcnage accouding.
+\response{Thank you for your comment.
+We have changed title, the abstract, introduction, motivation, and conclusions to be more specific towards defect prediction rather than software analytics for this version.}
 
-\review{(1.8) As mentioned in one of my comments above, the script seeks to model generalizability looking at the number of projects (and size) as solely dimension to look at.
+\review{(3.8) As mentioned in one of my comments above, the script seeks to model generalizability looking at the number of projects (and size) as solely dimension to look at.
 But what about the quality attributes, such as the application domain?
@@
 
-not in general. cant prove external validity. jsut for our 673 projects. wichi is orders of mangitude larger than anything seen ebfore.
+\response{not in general. cant prove external validity. just for our 673 projects. which is orders of magnitude larger than anything seen before.XXXX}
 
-\review{(1.9) Furthermore, the dataset looks quite strange to me.
+\review{(3.9) Furthermore, the dataset looks quite strange to me.
 Looking at the defect distributions (left-most boxplot in Figure 4), I do see that 75\% of the projects (the last quartile) have more than 60\% of defective modules (classes/methods?).
@@
 
-unclear on this. zeroR tells us that it is not enough to do simple things
+\response{unclear on this. zeroR tells us that it is not enough to do simple things. Not sure how to answer.XXXX}
 
@@
 
-XXXX
+\response{Thank you for your comment, we didn't included detailed analysis of complexity of our method in the last manuscript.
+We have added much details and an step by step analysis\respto{3-10} of complexity of the algorithm shown in Fig~\ref{fig:Pseudo-code}.}
 
-\review{(1.11) All the results are summarized in one single table (Figure 7), which shows the mean and the standard deviation of five evaluation metrics, as well as the rank of the statistical tests.
+\review{(3.11a) All the results are summarized in one single table (Figure 7), which shows the mean and the standard deviation of five evaluation metrics, as well as the rank of the statistical tests.
 There are two problems in aggregating the data in this way: (1)I am not sure that the arithmetic mean and the standard deviation are the appropriate metrics to use.
@@
 
-use medians an QRQ
+\response{Thank you for your comment, you are quite correct.
+We used arithmetic mean and standard deviation as our metrics to showcase our result in the last manuscript, which may be affected by outliers and skew the results.
+In this manuscript, we have replaced arithmetic mean and standard deviation with median and IQR in figure~\ref{fig:Statistical}.}
 
-{Maybe, the boxplots would be the most appropriate way to show the distributions.
+\review{(3.11b)Maybe, the boxplots would be the most appropriate way to show the distributions.
 (2)The average across 700 projects makes little sense and hides what happens in each project.
@@
 
-xplain
+\response{Thank you for your comments.
+The Fig~\ref{fig:Statistical} is a form of boxplot, where the black dot represents the median and the spread of the black line represents the 25th and 75th percentile of the data.
+Alternatively we can include all the results instead of just showing the median and IQR, but it will occupy too much space.}
 
-\review{(1.12) Section 5 contains the following recommendation “As to ZeroR, we cannot recommend that approach.
+\review{(3.12) Section 5 contains the following recommendation “As to ZeroR, we cannot recommend that approach.
 While ZeroR makes few mistakes (low ifas and low pfs), it scores badly on other measures (very low recalls and popt(20).” This argument does not convince me as ZeroR gets the best results for two metrics (as far as I understand).
@@
 
-Xplan
+\response{Thank you for your comments, in the last manuscript we did not properly explained why the model ZeroR can not be recommend.
+We have updated the figure~\ref{fig:Statistical} to replace arithmetic mean and standard deviation with median and IQR.
+We can see from the figure~\ref{fig:Statistical}, the ZeroR model has a recall and pf of zero with IQR diff between 75th and 25th percentile as 100, which signifies as the model either predicts everything as defective or non-defective it will not be able to predict any defective module at all if the defect ratio is less than 50\%, while for projects with defect ratio is more than 50\% it will predict everything as defective with high false positive.XXXX}
 
-\review{(1.13) Section 5 (RQ3) ends with two recommendations about critical and non-critical systems.
+\review{(3.13) Section 5 (RQ3) ends with two recommendations about critical and non-critical systems.
 However, I could not find any analysis that can support these recommendations.
@@
 
-cget rid of critial systems
+\response{Thank you for your valuable comments, the text for section~\ref{sec:rq6} was indeed confusing, we have made appropriate changes to better explain our analysis of a general defect prediction model learned by analyzing 627 projects.
+We have also removed any ambiguous keyword which might not be appropriate in this context.
+The changes has been added in \respto{3-13}.}

### 2020-03-12 manuscript.tex
Updates from Overleaf

@@
 large data sets. 
-For example, for nearly 700 projects,
+For nearly 700 projects,
 the defect prediction models generated from GENERAL's bellwether  
@@
 
+\respto{1-3}{\color{blue}Researchers and industry practitioners makes use of data-driven decision making for defect prediction by generating software quality models(defect predictor) from project data comprises of software quality metrics (Commonly used software metrics for defect prediction are complexity metrics (such as lines of code, Halstead metrics, McCabe’s cyclometic complexity, and CK metrics) and process metrics (such as number of revisions, lines added and deleted) These defect predictors are used for predicting defects in new set of changes and to learn what are the important metrics that are responsible for finding these defects.
+These quality metrics can be collected with much ease from the code base of different software systems from large organizations and open source community, and can be used for large scale data-driven decision making.}
+
+{\color{blue} But what is the external validity of the conclusions reached  via
+the above data mining methods?
+ If we cannot offer general rules across a large number of software projects, then it is   difficult to demonstrate such generality.
+ Hassan~\cite{Hassan17} cautions that managers lose faith in software analytics if its models keep changing since  the assumptions used to make prior policy decisions may no longer hold.
+Also, Kim et al.~\cite{Kim2016}, notes  that the aim of software analytics is to obtain actionable insights that help practitioners accomplish software development goals.
+Many other researchers agree.
+For example,
+Tan et al.~\cite{tan2016defining} say that such   insights  are a core deliverable.
+Sawyer et al.
+agree, saying that  insights are the key driver for businesses to invest in data analytics initiatives~\cite{sawyer2013bi}.
+Also,
+Bird, Zimmermann, et al.~\cite{Bird:2015} argue that such  insights occur when users reflect, and react, to the output of a model generated via software analytics.
+But if  new models keep being generated in new projects, then that exhausts the ability of  users to draw insight from  new data.}
+
+{\color{blue} Apart from the above,  are several other reasons to seek general conclusions in SE. For example, 
+if we are unsure what factors most influence quality, it is difficult to design and implement and deploy tools that can successfully improve that quality.
+Also,
+consider the task of training a   novice software engineers or newcomers to a project If our models are not stable, then it hard to teach what factors  most influence software quality.}
+
+%Many Large organizations and many open source communities are using large scale data analysis on historical data available to them.
+With large quantity of data available to them, how should they reason about software quality?
+Should they use general defect prediction models that hold over many projects?
+Or must they use an ever-changing set of defect prediction models that are continually build and adapted to the task at hand?
+If the latter were true then there would be no stable models and conclusions about what is best practice for SE for avoiding defects (since those best practices would keep changing as we move from project to project).
+As discussed in section~\ref{sec:Motivation}, such conclusion instability has detrimental implications for {\em generality, trust, insight, training}, and {\em tool development}.}
+
+% Researchers and industry practitioners makes use of different machine learning models to automatically generate software quality models(defect predictor) from project data comprises of software quality metrics (Commonly used software metrics for defect prediction are complexity metrics (such as lines of code, Halstead metrics, McCabe’s cyclometic complexity, and CK metrics) and process metrics(such as Number of revisions, lines added and deleted)) .
+Researches and industry practitioners use these defect predictors to predict for defect in new set of changes and to learn what are the important metrics that are responsible for finding these defects.
+These quality metrics can be collected with much ease from the code base of different software systems from large organizations and open source community, and
+
 %   After a decade of intensive research into automated software analytics, what general principles have we learned?
-While that work has generated specific results about specific projects~\cite{Bird:2015,menzies2013software}, it has failed (so far) to deliver general principles that are demonstrably useful across many projects~\cite{menzies2013guest} (for an example of how {\em more} data can lead to {\em less} general conclusions, see below in {\S}2a).
+While that work has generated specific results about specific projects~\cite{Bird:-24015,menzies2013software}, it has failed (so far) to deliver general principles that are demonstrably useful across many projects~\cite{menzies2013guest} (for an example of how {\em more} data can lead to {\em less} general conclusions, see below in {\S}2a).
 
@@
 
-\respto{1-3}{\color{blue}Researchers and industry practitioners makes use of software analytics for many tasks to access software quality, such as:
-\bi
-\item Predicting if a submitted code is likely to buggy or not.
-\item Improving code quality by detecting code smells.
-\item Issue lifetime estimation to enable effective development and maintenance of their software systems.
-\ei
-
-Large organizations and many open source communities uses data-driven decision making, where they learn using large scale data analysis on historical data available to them.
+% \respto{1-3}{\color{blue}Researchers and industry practitioners makes use of software analytics for many tasks to access software quality, such as:
+% \bi
+% \item Predicting if a submitted code is likely to buggy or not.
+% \item Improving code quality by detecting code smells.
+% \item Issue lifetime estimation to enable effective development and maintenance of their software systems.
+% \ei
+
+% Large organizations and many open source communities uses data-driven decision making, where they learn using large scale data analysis on historical data available to them.
 With large quantity of data available to them, how should they reason about software quality?
@@
 
-Finding general lessons across multiple projects is a complex task.
+{\color{blue} Finding general defect prediction models  across multiple projects is a complex task.
+There are many recent examples of supposed ``general'' SE conclusions that are
+now questionable. For example, Fenton warns
+that, in stark contrast to  much prior research, pre- and post- release failures are not connected~\cite{fenton2000quantitative}.
+Also, Nagappan et al. have found that the language construct GOTO, as used in contemporary practice, is rarely considered harmful~\cite{nagappan2015empirical};
+Similiary, Fucci et al. report that test-driven development is not any better than "test last"~\cite{fucci2017dissection};
+ Further, in our own work, we have seen that
+ delayed issues are not exponentially more expensive to fix~\cite{menzies2017delayed}.
+ For a long list of other conclusions that were found to be  unstable across multiple projects, see~\cite{Me13}.
+This problem is so endemic in software engineering that other journals have devoted entire special issues t the topic~\cite{Menzies2012}.
+}
+
+{\color{blue} Given all these examples of SE conclusions whose generality we must now question, it is timely
+to ask what methods are available for finding general results that hold across multiple projects?}
 A new approach, that shows much promise, is the ``bellwether'' method for transferring conclusions between projects~\cite{krishna2018bellwethers,krishna16a,mensah18z,mensah2017stratification,mensah2017investigating}.
-\respto{1-1}{\color{blue} ``bellwether'' is a project from a community of N projects, whose data yields the best analytic (i.e.
+\respto{1-1a}{\color{blue} ``bellwether'' is a project from a community of N projects, whose data yields the best analytic (i.e.
 defect prediction, effort estimation etc) on all others.} (the bellwether is the  leading sheep of a flock, with a bell on its neck).
@@
 \ei
-This approach has been successfully applied to defect prediction, software effort estimation, bad smell detection, issue lifetime estimation, and configuration optimization.
-As a method of transferring lessons learned from one project to another, bellwethers have worked better than the Burak filter~\cite{turhan09}, Ma et al.~\cite{Ma2012}'s transfer naive Bayes (TNB); and Nam et al.
-TCA  and TCA+, algorithms~\cite{Nam13,Nam2015}.
-
-%In terms of {\em transfer} and {\em lessons learned},  such bellwethers have
- % tremendous practical significance. 
-  When new projects arrive, then even before there is much experience with those new projects,  lessons learned from other projects can be applied to the new project (just by studying the bellwether),
+\respto{3-5}{\color{blue}This approach has been successfully applied to defect prediction, software effort estimation, bad smell detection, issue lifetime estimation, and configuration optimization (In this paper we only explore defect prediction).
+As a method of transfer learning from one project to another, bellwethers have worked better than the Burak filter~\cite{turhan09}, Ma et al.~\cite{Ma2012}'s transfer naive Bayes (TNB); and Nam et al.
+TCA  and TCA+, algorithms~\cite{Nam13,Nam2015}}.
+
+When new projects arrive, then even before there is much experience with those new projects,  models learned from other projects can be applied to the new project (just by studying the bellwether),
  Further, \respto{2-2}{\color{blue} since the bellwether is an exemplar projects for the community of N projects seen so far},
@@
 this means GENERAL will scale up much better than traditional   methods.
-For example: This paper applies GENERAL and traditional $O(N^2)$ bellwether to 697 projects.
+This paper applies GENERAL and traditional $O(N^2)$ bellwether to 697 projects.
 GENERAL and the traditional approach terminated in 1.5 and 72 hours (respectively).
@@
                Conventional bellwether method as proposed by krishna et al~\cite{krishna2018bellwethers,krishna16a} uses a $ O(N^2) $ comparisons to find the ``bellwether'' among a community of N (697 projects in this experiment) projects.
-In this experiment the conventional bellwether method used almost 72 hours to find the ``bellwether''.}
+In this experiment the conventional bellwether method is very expensive to find the ``bellwether''.}
             \end{RQ}
@@
             \begin{RQ}{
-               The new bellwether method (GENERAL), which is a combination of hierarchical clustering and bellwether method took around 1.5 hours find a ``bellwether''.}
+               The new bellwether method (GENERAL), which is a combination of hierarchical clustering and bellwether method achieves  a computational complexity of $O(m*(N/m)^2)$, which is much faster than conventional bellwether.}
             \end{RQ}
@@
             \begin{RQ}{
-                The importance of many key features is not apparent at the local
-level. To fully appreciate the critical impact on defects
-of class interface design,  it is necessary to conduct
-a global analysis across hundreds of projects. }
+                \respto{2-9}\respto{3-13} {\color{blue}The importance of many key features is not apparent at the local
+project level.
+To fully understand the effect of certain attributes (key features) on defect prediction and bug localization, it is necessary to analyze hundreds of projects together to identify a single bellwether.
+This bellwether will act as an exemplary model to identify such key features in defect prediction models.}}
             \end{RQ}
@@
 
-\subsection{Why Seek Generality?}
-\label{sec:Motivation}
-There are many reasons to seek stable general conclusions in software engineering.
-If our conclusions about best practices for SE projects keep changing, that will be detrimental to generality, trust, insight, training, and tool development.
-
-\textbf{Generality:} Data science for software engineering cannot be called a ``science'' unless it makes general conclusions that hold across  multiple  projects.
-If we cannot offer general rules across a large number of software projects, then it is   difficult to demonstrate such generality.
-
-\textbf{Trust:} Hassan~\cite{Hassan17} cautions that managers lose faith in software analytics if its models keep changing since  the assumptions used to make prior policy decisions may no longer hold.
-
-\textbf{Insight:} Kim et al.~\cite{Kim2016}, say  that the aim of software analytics is to obtain actionable insights that help practitioners accomplish software development goals.
-For Tan et al.~\cite{tan2016defining}, such   insights  are a core deliverable.
-Sawyer et al.
-agree, saying that  insights are the key driver for businesses to invest in data analytics initiatives~\cite{sawyer2013bi}.
-Bird, Zimmermann, et al.~\cite{Bird:2015} say that such  insights occur when users reflect, and react, to the output of a model generated via software analytics.
-But if  new models keep being generated in new projects, then that exhausts the ability of  users to draw insight from  new data.
-
-\textbf{Training:} Another concern is what do we train novice software engineers or newcomers to a project?
-If our models are not stable, then it hard to teach what factors  most influence software quality.
-
-\textbf{Tool development:} Further to the last point--- if we are unsure what factors most influence quality, it is difficult to design and implement and deploy tools that can successfully improve that quality.
+%If our conclusions about best practices for SE projects keep changing, that will be detrimental to generality, trust, insight, training, and tool development.
 
@@
 
-\subsection{Why Shun Generality?}
-Just to balance the above argument,
-we add that   sometimes it is possible to learn from {\em too much data}.
+\subsection{A Note on Context}
+%Just to balance the above argument,
+%we add that   sometimes it is possible to learn from {\em too much data}.
 Petersen and Wohlin~\cite{Petersen2009} argue that for empirical SE, context matters.
@@
 
-\respto{2-12}{\color{blue} The {\em size} of the communities found in this way would have a profound impact on how we should reason about software engineering.
+\respto{2-12}\respto{3-2}{\color{blue} The {\em size} of the communities found in this way would have a profound impact on how we should reason about software engineering.
 Consider in this experiment of 697 projects, we build a set of defect predictor by learning bellwether from smalls cluster of $\approx10$ projects,  medium clusters of $\approx100$ projects, a large cluster containing $\approx600$ projects and a self test.
@@
 The good news is that using software analytics, we can correct the above misconceptions.
-If data mining shows that doing  XYZ is bug prone, then we could  guide developers to avoid XYZ.
+\respto{2-15}{\color{blue} If data mining shows that higher or lower XYZ is cause for code to be  bug prone, then we could  guide developers to avoid having higher or lower XYZ.
 But will developers listen to us?
-If they ask ``are we sure  XYZ causes problems?'', can we say that we have mined enough projects to ensure that XYZ is problematic?
-
-\respto{2-24}{\color{blue} It turns out that developers are not the only one's confused about how various factors influence software projects.
+If they ask ``are we sure having higher or lower XYZ is a statistical predictor for bug prone code?'', can we say that we have mined enough projects to ensure that XYZ is a statistical predictor for bug prone code?}
+
+%\respto{2-24}{\color{blue} It turns out that developers are not the only one's confused about how various factors influence software projects.
 Much recent research calls into question  the ``established wisdoms'' of SE field.
 
-Here is a list of recent conclusions that contradict prior conclusions:}
-
-\bi
-    \item In stark contrast to  much prior research, pre- and post- release failures are not connected~\cite{fenton2000quantitative};
-
-    \item Static code analyzers perform no better than simple statistical predictors~\cite{Fa13};
-
-    \item The language construct GOTO, as used in contemporary practice, is rarely considered harmful~\cite{nagappan2015empirical};
-
-    \item Strongly typed languages are not associated with successful projects~\cite{ray2014large};
-
-    \item Test-driven development is not any better than "test last"~\cite{fucci2017dissection};
-
-    \item Delayed issues are not exponentially more expensive to fix~\cite{menzies2017delayed};
-\ei
-Note that if the reader disputes any of the above, then we ask how would you challenge the items on this list?
+%Note that if the reader disputes any of the above, then we ask how would you challenge the items on this list?
 Where would you get the data, from enough projects, to   successfully refute the above?
@@
 \textbf{(c) Imported data can be more useful than local data:} Another benefit of  importing data from other projects is that, sometimes, that imported data can be better than the local information.
-For example, Rees-Jones reports in one study that while building predictors
+Rees-Jones reports in one study that while building predictors
 for Github close time  for open source projects~\cite{rees2017better} using data from other projects performs much better then building models using {\em local learning} (because there is better  information {\em there} than {\em here}).
@@
 \textbf{(d) When there is insufficient local data, learning from other projects is very useful:} When developing new software in  novel areas, it is useful to draw on the relevant  experience  from related areas with a larger experience base.This is particularly true when developers are doing something that is novel to them, but has been widely applied elsewhere
-For example, Clark and Madachy~\cite{clark15} discuss 65 types of software they see        under-development by the US Defense Department in 2015.
+, Clark and Madachy~\cite{clark15} discuss 65 types of software they see        under-development by the US Defense Department in 2015.
 Some of these types are very common (e.g.
@@
  \textbf{Similarity-Based Approaches:} In this approach we can transfer some/all subset of the rows or columns of data from source to target.
-For example, the Burak filter~\cite{turhan09} builds its training sets by finding the k = 10 nearest code modules in S for every $ t \in T $.
+The Burak filter~\cite{turhan09} builds its training sets by finding the k = 10 nearest code modules in S for every $ t \in T $.
 However, the Burak filter suffered from the all too common instability problem (here, whenever the source or target is updated, data miners will learn a new model since different code modules will satisfy the k = 10 nearest neighbor criteria).
@@
     \small
-     \begin{lstlisting}[mathescape,numbers=right,frame=None]
+     \begin{lstlisting}[mathescape,numbers=left,frame=None]
         def General(project):
@@
  Our proposed improvement to bellwethers is called GENERAL.
-The core intuition of this new approach is that if many projects are similar, then we do not need to run comparisons between all pairs of projects.\respto{1-2}{\color{blue} We say this since  Devanbu et al.`\cite{hindle2012naturalness} report that if Markov chains are created for tokens in a program, then a remarkably small number of chains capture most of the program.
+The core intuition of this new approach is that if many projects are similar, then we do not need to run comparisons between all pairs of projects.\respto{1-1b}{\color{blue} We say this since  Devanbu et al.`\cite{hindle2012naturalness} report that if Markov chains are created for tokens in a program, then a remarkably small number of chains capture most of the program.
 Given these similarities,   we can exploit symmetries between different projects in order to learn predictors from one and apply those to another.
@@
 Thus to make a good predictor we need to maximize the recall}} and precision\footnote{{\color{blue}Precision is the ratio between predicted actual target class examples vs all predicted target class examples.
-In other words precision = $ \frac{TP}{TP+FP} $, so in an ideal scenario where we identify all the actual target class as target class without predicting any non-target class as target class the precision will be one.
+In other words precision = $ \frac{TP}{TP+FP} $, therefore in an ideal scenario where we identify all the actual target class as target class without predicting any non-target class as target class the precision will be one.
 Thus to make a good predictor we need to maximize the precision as well}}
@@
 \respto{1-5f} {\color{blue} While minimizing  false alarms\footnote{{\color{blue}false alarms (pf) is the ratio between non-target class identified as target class and total number of actual non-target class.
-IN other words false alarm = $ \frac{FP}{FP+TN} $, so in an ideal scenario FP should be zero, thus not identifying and non-defective class as defective and effectively making false alarm as zero.}}
+IN other words false alarm = $ \frac{FP}{FP+TN} $, thus in an ideal scenario FP should be zero, thus not identifying and non-defective class as defective and effectively making false alarm as zero.}}
 %and ifa\_auc\footnote{{\color{blue}Need to describe ifa auc XXXX.}}
@@
 (5) \textbf{ifa\_auc:} Number of  initial false alarms encountered before we find the first defect.
-Inspired by previous studies on fault localization~\cite{parnin2011automated,kochhar2016practitioners,xia2016automated}, we caution that if the top-k changes recommended by the model are all false alarms, developers would be frustrated and are not likely to continue inspecting the other changes.
-For example, Parnin and Orso ~\cite{parnin2011automated} found that developers would stop inspecting suspicious statements, and turn back to traditional debugging, if they could not get promising results within the first few statements they inspect.
-Using the nomenclature reported
-about {\em Ifa$=k$}.
+Inspired by previous studies on fault localization~\cite{parnin2011automated, kochhar2016practitioners, xia2016automated}, we caution that if the top-k changes recommended by the model are all false alarms, developers would be frustrated and are not likely to continue inspecting the other changes.
+Parnin and Orso ~\cite{parnin2011automated} found that developers would stop inspecting suspicious statements, and turn back to traditional debugging, if they could not get promising results within the first few statements they inspect.
+Using the nomenclature reported about {\em ifa$=k$}.
 In this study we use a modified version of {\em ifa} called ifa\_auc, which calculates {\em ifa} based on efforts spent on inspecting the code.
@@
 
+{\color{blue} 
 \subsection*{RQ1: How slow is conventional bellwether method? }
 \label{sec:rq3}
-
+\respto{1-2}\respto{1-6a} Conventional bellwether as proposed by Krishna et al.
+compares all projects in a given community with all others to build defect prediction models and compare with each other.
+This operation is quite expensive, which has a $ O(n^2) $ computational complexity.
+In this experiment we used this conventional bellwether to make a baseline comparison with 627 projects (697 in total) in the community.
+Figure~\ref{fig:compare} showed that, the conventional bellwether did a total of {\em 393129} comparisons, while taking {\em 72} hours (with SMOTE and CFS) or {\em 10648} seconds (without SMOTE and CFS) to complete.
+In summary we conclude
+
+\begin{RQ}{Conventional bellwether method as proposed by krishna et al~\cite{krishna2018bellwethers,krishna16a} uses a $ O(N^2) $ comparisons to find the ``bellwether'' among a community of N (697 projects in this experiment) projects.
+In this experiment the conventional bellwether method is very expensive to find the ``bellwether''.}
+\end{RQ}
+}
+
+{\color{blue} 
 \subsection*{RQ2: How  fast  is  new  bellwether  method  aka  GENERAL?}
 \label{sec:rq3}
+The new bellwether method proposed in this paper uses a hierarchical clustering, then finds bellwether at leaf level clusters and pushes up bellwethers to parent nodes for comparisons.
+This process reduces the computational complexity to $O(m*(N/m)^2)$ on an average case (assuming the hierarchical clustering creates m cluster at leaf level).
+When compared with conventional bellwether, figure~\ref{fig:compare} shows the new bellwether only requires {\em 9583} comparisons\, which is order of magnitude less comparisons.
+Figure~\ref{fig:compare_time} and \ref{fig:time} shows the new method only takes {\em 362} seconds (without SMOTE and CFS) to complete and {\em 1.5} hours (with SMOTE and CFS).
+In summary we can say
+
+\begin{RQ}{The new bellwether method (GENERAL), which is a combination of hierarchical clustering and bellwether method achieves  a computational complexity of $O(m*(N/m)^2)$, which is much faster than conventional bellwether.}
+\end{RQ}
+}
 
@@
 
-\fig{cost} showed that, theoretically,
+\respto{1-6c}\fig{Pseudo-code} showed that, theoretically,
 GENERAL is an inherently faster approach than traditional bellwether methods.
@@
     \includegraphics[width=\linewidth]{figs/Time.png}
-    \caption{Mean runtime for for one run of standard bellwether and GENERAL.}
+    \caption{Mean runtime for for one run of standard bellwether and GENERAL (With SMOTE and CFS).}
     \label{fig:time}
@@
 
-\fig{time} shows the mean runtimes for one run of GENERAL versus traditional bellwether. For certification purposes, this had to be repeated 20 times. In that certification run:
+\begin{figure}[!b]
+    \centering
+    \includegraphics[width=\linewidth]{figs/Time_Compare.pdf}
+    \caption{Mean runtime for for one run of standard bellwether and GENERAL with different community size.}
+    \label{fig:compare_time}
+\end{figure}
+
+\begin{figure}[!b]
+    \centering
+    \includegraphics[width=\linewidth]{figs/compare.pdf}
+    \caption{Number of comparison one run of standard bellwether and GENERAL with different community size.}
+    \label{fig:compare}
+\end{figure}
+
+\fig{compare} shows the mean number of comparisons required for finding a bellwether using conventional bellwether versus GENERAL for different community size .
+
+\fig{time} shows the mean run times for one run of GENERAL versus traditional bellwether. For certification purposes, this had to be repeated 20 times. In that certification run:
+
 \bi
@@
 The $O(m*(N/m)^2)$ analysis
-of GENERAL needed 30  hours. That is, in empirical
- result consistent with the theoretical predictions of \fig{cost}, GENERAL runs much faster than traditional bellwether.
-\item All the other methods required
-another 6 hours of computation. 
-\ei
-If we were merely seeking conclusions from one project, then we would recommend ignoring bellwethers
-and just use results from each project. That said, we still endorse bellwether method since  we seek
-lessons that hold across many projects.
+of GENERAL needed 30  hours. That is, in empirical result consistent with the theoretical predictions of \fig{cost}, GENERAL runs much faster than traditional bellwether.
+\item 
+All the other methods required another 6 hours of computation. 
+\ei
+
+If we were merely seeking conclusions from one project, then we would recommend ignoring bellwethers and just use results from each project.
+That said, we still endorse bellwether method since  we seek lessons that hold across many projects.
 
@@
 \end{RQ}
+
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%Latex Table%%%%%%%%%%%%%%%%%%%%%%%%%
+% \begin{figure}[!b]
+% {\scriptsize
+% {\scriptsize \begin{tabular}{p{.1cm}lp{1.5cm}rrc}
+% \arrayrulecolor{darkgray}
+% \rowcolor[gray]{.9}  & rank & treatment & mean & sd & \\
+%  \multirow{5}{*}{\rotatebox[origin=c]{90}{Recall}} 
+%   &   1 &      GENERAL\_level2 &    38 &  32 & \quart{22}{38}{32}{16} \\
+%   &   1 &      bellwether0 &    39 &  31 & \quart{23}{39}{31}{15} \\
+%   &   1 &  ZeroR &    40 &  49 & \quart{16}{40}{49}{25} \\
+%   &   2 &      GENERAL\_level1 &    48 &  33 & \quart{31}{48}{33}{16} \\
+%   &   3 &      self &    55 &  27 & \quart{41}{55}{27}{12} \\
+%   &   3 &      GENERAL\_level0 &    56 &  31 & \quart{42}{56}{31}{16} \\
+%   &   4 &      global &    78 &  40 & \quart{57}{78}{40}{20} \\ \hline
+% \multirow{5}{*}{\rotatebox[origin=c]{90}{Pf}} 
+%   &  1 &      GENERAL\_level2 &    28 &  28 & \quart{14}{28}{28}{13} \\
+%   &  1 &      bellwether0 &    28 &  25 & \quart{15}{28}{25}{11} \\
+%   &  1 &      self &    30 &  20 & \quart{20}{30}{20}{10} \\
+%   &  1 &      GENERAL\_level1 &    35 &  28 & \quart{21}{35}{28}{14} \\
+%   &  1 &      ZeroR &    39 &  49 & \quart{15}{39}{49}{25} \\
+%   &  2 &      GENERAL\_level0 &    47 &  31 & \quart{31}{47}{31}{15} \\
+%   &  3 &      global &    79 &  39 & \quart{59}{79}{39}{19} \\\hline
+% \multirow{5}{*}{\rotatebox[origin=c]{90}{Precision}} &   1 &      ZeroR &    21 &  30 & \quart{6}{21}{30}{15} \\
+%     &  2 &      global &    35 &  28 & \quart{21}{35}{28}{14} \\
+%     &   2 &      GENERAL\_level2 &    39 &  34 & \quart{22}{39}{34}{17} \\
+%     &   2 &      bellwether0 &    40 &  33 & \quart{23}{40}{33}{16} \\
+%     &   2 &      GENERAL\_level1 &    42 &  31 & \quart{26}{42}{31}{15} \\
+%     &   2 &      GENERAL\_level0 &    44 &  30 & \quart{28}{44}{30}{15} \\
+%     &   2 &      self &    50 &  30 & \quart{35}{50}{30}{15} \\\hline
+% \multirow{5}{*}{\rotatebox[origin=c]{90}{Popt20}} &   1 &      ZeroR &    13 &  16 & \quart{5}{13}{16}{8} \\
+%   & 2 &      GENERAL\_level2 &    26 &  22 & \quart{15}{26}{22}{11} \\
+%   &  2 &      global &    26 &  13 & \quart{19}{26}{13}{6} \\
+%   &  2 &      bellwether0 &    28 &  21 & \quart{17}{28}{21}{9} \\
+%   &  2 &      GENERAL\_level0 &    28 &  15 & \quart{22}{28}{15}{8} \\
+%   &  2 &      GENERAL\_level1 &    28 &  19 & \quart{19}{28}{19}{9} \\
+%   &  3 &      self &    35 &  19 & \quart{26}{35}{19}{10} \\\hline
+% \multirow{5}{*}{\rotatebox[origin=c]{90}{ifa\_auc}} &   1 &      ZeroR &    7 &  11 & \quart{1.12}{6.77}{11.29}{5.65} \\
+%   &  2 &      global &    19 &  16 & \quart{11.35}{19.38}{16.06}{8.03} \\
+%   &  3 &      GENERAL\_level2 &    22 &  14 & \quart{14.48}{21.59}{14.21}{7.10} \\
+%   &  3 &      bellwether0 &    23 &  14 & \quart{15.48}{22.56}{14.15}{7.07} \\
+%   &  3 &      self &    23 &  12 & \quart{17.09}{22.93}{11.68}{5.84} \\
+%   &  3 &      GENERAL\_level1 &    23 &  14 & \quart{16.10}{22.98}{13.74}{6.87} \\
+%   &  3 &      GENERAL\_level0 &    25 &  13 & \quart{17.87}{24.51}{13.27}{6.63} \\
+% \end{tabular}}
+% }
+% \caption{Statistical Results comparison. The ``rank`` column at left comes from
+% the statistical analysis methods of \S\ref{eval}. Note that for {\em pf}, and {\em ifa} rank=1 is the best rank while for all other performance measures, ranks $\in{3,4}$ are best. 
+% }\label{fig:Statistical}
+% \end{figure}
 
@@
 {\scriptsize
-{\scriptsize \begin{tabular}{p{.1cm}lp{1.5cm}rrc}
+{\scriptsize 
+\resizebox{.48\textwidth}{!}{
+\begin{tabular}{p{.1cm}lp{1.5cm}rrc}
 \arrayrulecolor{darkgray}
-\rowcolor[gray]{.9}  & rank & treatment & mean & sd & \\
+\rowcolor[gray]{.9}  & rank & treatment & median & IQR & \\
  \multirow{5}{*}{\rotatebox[origin=c]{90}{Recall}} 
-  &   1 &      GENERAL\_level2 &    38 &  32 & \quart{22}{38}{32}{16} \\
-  &   1 &      bellwether0 &    39 &  31 & \quart{23}{39}{31}{15} \\
-  &   1 &  ZeroR &    40 &  49 & \quart{16}{40}{49}{25} \\
-  &   2 &      GENERAL\_level1 &    48 &  33 & \quart{31}{48}{33}{16} \\
-  &   3 &      self &    55 &  27 & \quart{41}{55}{27}{12} \\
-  &   3 &      GENERAL\_level0 &    56 &  31 & \quart{42}{56}{31}{16} \\
-  &   4 &      global &    78 &  40 & \quart{57}{78}{40}{20} \\ \hline
+  & 1 &      ZeroR &    0 &  100 & \quart{0}{0}{100}{100} \\
+  & 1 &      BUBBLE\_level2 &    33 &  63 & \quart{0}{33}{63}{30} \\
+  & 1 &      bellwether0 &    38 &  55 & \quart{5}{38}{55}{22} \\
+  & 2 &      BUBBLE\_level1 &    50 &  54 & \quart{20}{50}{54}{24} \\
+  & 3 &      BUBBLE\_level0 &    57 &  47 & \quart{36}{57}{47}{25} \\
+  & 3 &      self &    57 &  34 & \quart{41}{57}{34}{17} \\
+  & 4 &      global &    100 &  12 & \quart{88}{100}{12}{0} \\ \hline
 \multirow{5}{*}{\rotatebox[origin=c]{90}{Pf}} 
-  &  1 &      GENERAL\_level2 &    28 &  28 & \quart{14}{28}{28}{13} \\
-  &  1 &      bellwether0 &    28 &  25 & \quart{15}{28}{25}{11} \\
-  &  1 &      self &    30 &  20 & \quart{20}{30}{20}{10} \\
-  &  1 &      GENERAL\_level1 &    35 &  28 & \quart{21}{35}{28}{14} \\
-  &  1 &      ZeroR &    39 &  49 & \quart{15}{39}{49}{25} \\
-  &  2 &      GENERAL\_level0 &    47 &  31 & \quart{31}{47}{31}{15} \\
-  &  3 &      global &    79 &  39 & \quart{59}{79}{39}{19} \\\hline
-\multirow{5}{*}{\rotatebox[origin=c]{90}{Precision}} &   1 &      ZeroR &    21 &  30 & \quart{6}{21}{30}{15} \\
-    &  2 &      global &    35 &  28 & \quart{21}{35}{28}{14} \\
-    &   2 &      GENERAL\_level2 &    39 &  34 & \quart{22}{39}{34}{17} \\
-    &   2 &      bellwether0 &    40 &  33 & \quart{23}{40}{33}{16} \\
-    &   2 &      GENERAL\_level1 &    42 &  31 & \quart{26}{42}{31}{15} \\
-    &   2 &      GENERAL\_level0 &    44 &  30 & \quart{28}{44}{30}{15} \\
-    &   2 &      self &    50 &  30 & \quart{35}{50}{30}{15} \\\hline
-\multirow{5}{*}{\rotatebox[origin=c]{90}{Popt20}} &   1 &      ZeroR &    13 &  16 & \quart{5}{13}{16}{8} \\
-  & 2 &      GENERAL\_level2 &    26 &  22 & \quart{15}{26}{22}{11} \\
-  &  2 &      global &    26 &  13 & \quart{19}{26}{13}{6} \\
-  &  2 &      bellwether0 &    28 &  21 & \quart{17}{28}{21}{9} \\
-  &  2 &      GENERAL\_level0 &    28 &  15 & \quart{22}{28}{15}{8} \\
-  &  2 &      GENERAL\_level1 &    28 &  19 & \quart{19}{28}{19}{9} \\
-  &  3 &      self &    35 &  19 & \quart{26}{35}{19}{10} \\\hline
-\multirow{5}{*}{\rotatebox[origin=c]{90}{ifa\_auc}} &   1 &      ZeroR &    7 &  11 & \quart{1.12}{6.77}{11.29}{5.65} \\
-  &  2 &      global &    19 &  16 & \quart{11.35}{19.38}{16.06}{8.03} \\
-  &  3 &      GENERAL\_level2 &    22 &  14 & \quart{14.48}{21.59}{14.21}{7.10} \\
-  &  3 &      bellwether0 &    23 &  14 & \quart{15.48}{22.56}{14.15}{7.07} \\
-  &  3 &      self &    23 &  12 & \quart{17.09}{22.93}{11.68}{5.84} \\
-  &  3 &      GENERAL\_level1 &    23 &  14 & \quart{16.10}{22.98}{13.74}{6.87} \\
-  &  3 &      GENERAL\_level0 &    25 &  13 & \quart{17.87}{24.51}{13.27}{6.63} \\
-\end{tabular}}
+  & 1 &      ZeroR &    0 &  100 & \quart{0}{0}{100}{100} \\
+  & 1 &      BUBBLE\_level2 &    21 &  43 & \quart{0}{21}{43}{22} \\
+  & 1 &      bellwether0 &    25 &  45 & \quart{0}{25}{45}{20} \\
+  & 1 &      self &    25 &  23 & \quart{17}{25}{23}{15} \\
+  & 1 &      BUBBLE\_level1 &    33 &  41 & \quart{10}{33}{41}{18} \\
+  & 2 &      BUBBLE\_level0 &    45 &  43 & \quart{24}{45}{43}{22} \\
+  & 3 &      global &    100 &  17 & \quart{83}{100}{17}{0} \\ \hline
+\multirow{5}{*}{\rotatebox[origin=c]{90}{Precision}} 
+  & 1 &      ZeroR &    0 &  45 & \quart{0}{0}{45}{45} \\
+  & 2 &      global &    33 &  45 & \quart{11}{33}{45}{23} \\
+  & 2 &      bellwether0 &    36 &  63 & \quart{4}{36}{63}{31} \\
+  & 2 &      BUBBLE\_level2 &    36 &  65 & \quart{0}{36}{65}{29} \\
+  & 2 &      BUBBLE\_level1 &    41 &  54 & \quart{13}{41}{54}{26} \\
+  & 2 &      BUBBLE\_level0 &    41 &  47 & \quart{20}{41}{47}{26} \\
+  & 2 &      self &    50 &  44 & \quart{28}{50}{44}{23} \\ \hline
+\multirow{5}{*}{\rotatebox[origin=c]{90}{Popt20}} 
+  & 1 &      ZeroR &    0 &  28 & \quart{0}{0}{28}{28} \\
+  & 2 &      BUBBLE\_level2 &    28 &  41 & \quart{0}{28}{41}{12} \\
+  & 2 &      global &    28 &  14 & \quart{20}{28}{14}{5} \\
+  & 2 &      bellwether0 &    31 &  42 & \quart{0}{31}{42}{11} \\
+  & 2 &      BUBBLE\_level0 &    31 &  16 & \quart{23}{31}{16}{8} \\
+  & 2 &      BUBBLE\_level1 &    31 &  23 & \quart{17}{31}{23}{9} \\
+  & 3 &      self &    36 &  20 & \quart{27}{36}{20}{11} \\ \hline
+\multirow{5}{*}{\rotatebox[origin=c]{90}{ifa\_auc}} 
+  & 1 &      ZeroR &    0 &  11 & \quart{0}{0}{11}{11} \\
+  & 2 &      global &    15 &  29 & \quart{6}{15}{29}{20} \\
+  & 3 &      BUBBLE\_level2 &    21 &  21 & \quart{11}{21}{21}{11} \\
+  & 3 &      bellwether0 &    22 &  21 & \quart{13}{22}{20}{11} \\
+  & 3 &      self &    22 &  17 & \quart{15}{22}{17}{9} \\
+  & 3 &      BUBBLE\_level1 &    23 &  20 & \quart{14}{23}{20}{11} \\
+  & 3 &      BUBBLE\_level0 &    24 &  21 & \quart{14}{24}{21}{12} \\
+\end{tabular}}}
 }
@@
 
-Returning now to \fig{predictive_power}, this
-research question asks if there is such a thing
-as learning from too much data.  What we will see is that
-answers to this question are much more complex than the simplistic
-picture of \fig{predictive_power}. While for some goals it is possible
-to learn from too much data, there are other goals where it seems
-more is always better.
+This sections ask if conclusions always improve as we learn from more and more data.
+This can be an issue since if a new project
+is fundamentally different to all past projects, then irrelevant ideas from the past will be
+inappropriately applied to the present situation.
 
@@
 of features, such as those listed in Table~\ref{tbl:coefs}.
-For example,
-based on these results
+Based on these results
 we can say that for predicting defects, in this sample of  features taken from 627 projects:
@@
 \begin{RQ}
-{The importance of many key features is not apparent at the local
-project level. To fully appreciate the critical impact on defects
-of class interface design,  it is necessary to conduct
-a global analysis across hundreds of projects. }
+{\respto{2-9}\respto{3-13} {\color{blue}The importance of many key features is not apparent at the local
+project level.
+To fully understand the effect of certain attributes (key features) on defect prediction and bug localization, it is necessary to analyze hundreds of projects together to identify a single bellwether.
+This bellwether will act as an exemplary model to identify such key features in defect prediction models.}}
+
+% To fully appreciate the critical impact on defects
+% of class interface design,  it is necessary to conduct
+% a global analysis across hundreds of projects. }
 \end{RQ}

### 2020-03-19 response.tex
Updates from Overleaf

@@
 
-\response{ Thank you very much for your encouraging comments.
-We have made appropriate changes to the manuscript taking into careful consideration the recommendations of the reviewers.
-We hope that this new draft adequately satisfies all the issues raised by the reviewers.
-To assist the reviewers in tracking all the new changes, where appropriate, we have prefixed the text with \respto{X-XX} to correspond to the reviewers' questions.~\\
-Below is the brief summary of our changes:
+\response{ Thank you very much for your encouraging comments. We find that the prior draft made
+several mistakes, that have been fixed here.
+\bi
+\item We assumed that the  core motivation for this work
+was widely known and accepted in the community. That was a mistake. This draft completely rewrites the Introduction
+to include much more background information on the 
+presence of the problem studied here.
+\item Cascading on from that first mistake, we made several
+mistakes with how we framed   our research questions. This
+draft fixes those errors. This has the added benefit
+of clarifying our discussion
+along the way.
+\ei
+Apart from these two points we have also addressed
+the many helpful and detailed comments from the reviewers:
 \be
@@
 \item Using comments from  (R1, R2, R3), we have made numerous small editorial improvements.
-\item The study now includes all the details to ensure replicability (R1, R2).
+\item The study now includes all the details to ensure 
+replicability   (R1, R2).
 \item The results of the study need to be revisited since the reviewers are not convinced that the results support the claims in the paper (R1, R2, R3).
 \item The background on transfer learning has been augmented with more  citations (R2).
-\ee}
+\ee
+}
 
@@
 \response{Thank you very much for your detailed review.
+As we said to the associated editor, the previous draft made the following mistake:
+\bi
+\item We assumed that the  core motivation for this work
+was widely known and accepted in the community. That was a mistake. 
+\item
+Consequently,this draft completely rewrites the Introduction
+to include much more background information on the 
+presence of the problem studied here.
+\ei
 We have made some additional corrections, clarifications, and revisions, as directed by your comments.
@@
 
-\response{(1.1b)You are quite correct, we did not define bellwether till very late in the prior draft. In this draft, we define bellwether on page 1\respto{1-1a}}
+\response{(1.1b)You are quite correct, we did not define bellwether till very late in the prior draft. In this draft, we define bellwether on page 1\citeresp{1-1a}}
+
+\begin{quote}
+    \response{``bellwether'' is a project from a community of N projects, whose data yields the best analytic (i.e.
+defect prediction, effort estimation etc) on all others.
+(the bellwether is the  leading sheep of a flock, with a bell on its neck)}
+\end{quote}
 
@@
 
-\response{Thank you for that comment.  You a re quite correct-- we did not document the source of our intutuion. We have added the following note to \respto{1-1b}}
+\response{Thank you for that comment.  You are quite correct-- we did not document the source of our intuition. We have added the following note to \citeresp{1-1b}}
 
@@
 \response{``The core intuition of this new approach is two-fold. Firstly,
-many projects are similar in structure. We say this since  Devanbu
-et al.`\cite{hindle2012naturalness}   report that if Markov chains are created for tokens in a program,
-then a remarkably small number of chains capture most of the program. ~\\
-``Secondly, given these similarities,   we can exploit symmetries between different projects in order to learn predictors from one and apply those to another.
-To say that another way, given large scale similarities between projects,  then we do not need to run comparisons between all pairs of projects since analyzing just a few pairs should work as well as anything else.''}
+many projects are similar in structure. We came to this
+intuition based on the writing
+of    Devanbu
+et al.`\cite{hindle2012naturalness}   who showed that a remarkably
+small number of Markov chains 
+capture the repeated patterns
+of tokens in a program~\\
+When such similarities
+exist, then we   exploit symmetries between different projects in order to learn predictors from one and apply those to another.
+Specifically: assuming inter-project symmetry,   we do not need to run comparisons between all pairs of projects since analyzing just a few pairs should work as well as anything else.''}
 \end{quote}
@@
 
-\response{ need a new RQ0: how slow is standard bellwether.
+\response{Thank you for your comments.
+ On review, we found that core problem of conclusion instability
+was not well documented in the introduction. This new draft fixes that problem with a completely new
+introduction that better focuses the work on conclusion instability and scalability.}
+
+% {need a new RQ0: how slow is standard bellwether.
 theoretically an empirically its slow (chart on p2.
@@
 
-\response{Thank you for your comment. On review, we found that core problem of conclusion instability
-was not well documented in the introduction. This new draft fixes that problem. Much of the new
+\response{Thank you for your comment. We agree.   Much of the new
 text on page1 takes care to document {\em why }
@@
 
-\response{Thank you for your comment. We have rewritten the introduction to be more understandable from a non-expert view and added necessary definitions where required.}
+\response{Thank you for your comment.
+We have deleted much of that confusing terminology from the introduction since, as you say, it introduces too many ideas in a confusing way, all at once.
+Please see \citeresp{1-3}.}
 
@@
 
-\response{ Thank you for your comment, you are right.In this manuscript we have deleted the  superlatives (including that one)}
+\response{ Thank you for your comment, You are right.In this manuscript we have deleted the  superlatives (including that one)}
 
@@
 
-\response{ Thank you for your comment, you are quite right. We had not properly mentioned the reason behind choosing logistics regression. In this draft we have added the reasons to \respto{1-5a}:}
+\response{ Thank you for your comment, you are quite right. We had not properly mentioned the reason behind choosing logistics regression.  In this draft we have added the reasons to \citeresp{1-5a}:}
 
@@
 \response{
-"The logistic regression learner,  since it is widely used in defect prediction~\cite{ghotra2015revisiting,XXX} in software engineering domain and it is relatively fast in terms of model building time than other learners such as Support Vector Machine, Random Forest, Artificial Neural Nets etc.
-tested on defect prediction.~\cite{ghotra2015revisiting}}
+"The logistic regression learner,  since it is widely used in defect prediction~\cite{ghotra2015revisiting} in   the  software engineering domain and, in our experience,
+in runs much faster (in terms of model building time) than many other learners such as Support Vector Machine, Random Forest, Artificial Neural Nets etc. (when tested on defect prediction).}
 \end{quote}
 
-\review{(1.5b)
-2) "The SMOTE class imbalance correction algorithm [49], which we run on the training data2". Why is SMOTE needed? Why is the problem unbalanced? Please, explain.
+\review{(1.5b) "The SMOTE class imbalance correction algorithm [49], which we run on the training data2". Why is SMOTE needed? Why is the problem unbalanced? Please, explain.
 }
@@
 \response{You are right, we had not included the reason for using SMOTE in our algorithm and had not explained why the problem is unbalanced.
-In this draft we have added notes to answer those questions \respto{1-5b}:}
+In this draft we have added notes to answer those questions \citeresp{1-5b}:}
 \begin{quote}
@@
 
-\review{(1.5c)
-3) "and Hall’s CFS feature selector". Which features have been removed and why?
+\review{(1.5c) "and Hall’s CFS feature selector". Which features have been removed and why?
 }
@@
 \response{You are quite correct, we did not included the details about how the features are being removed and why in the last draft.
-In this draft we have included notes regarding how CFS works and why the features that are not used are removed \respto{1-5b}:}
+In this draft we have included notes regarding how CFS works and why the features that are not used are removed \citeresp{1-5b}:}
 
@@
 
-\review{(1.5d)
-4) "As to CFS, we found that without it, our recalls were very low and we could not identify which metrics mattered the most".
+\response{As to what attributes were selected, please see Figure~\ref{fig:FSS_compare}. As to what of
+the selected figures were most important, please see Table~\ref{tbl:coefs}.}
+
+\review{(1.5d) "As to CFS, we found that without it, our recalls were very low and we could not identify which metrics mattered the most".
 Where can the reader understand this statement?
-Where is the replication data?
+Where is the replication data?}
+
+\response{Thank you for your comment, using the replication package (including data) the experiments can be reproduced.\citeresp{1-5d}.  Also, we have added in specific numbers to that sentence:
+\begin{quote}
+As to CFS, we found that without it, our recalls were very low (less than 20\%).
+\end{quote}
 }
 
-\response{Thank you for your comment, using the replication package (including data) the experiments can be reproduced.\respto{1-5h}}
+\review{(1.5e) "extensive studies have found that CFS more useful than many other feature subset selection methods such as PCA or InfoGain or RELIEF".
+The paper cites just one paper, how should these studies be "extensive"?}
 
-\review{(1.5e)
-5) "extensive studies have found that CFS more useful than many other feature subset selection methods such as PCA or InfoGain or RELIEF".
-The paper cites just one paper, how should these studies be "extensive"?
-}
+\response{Thank you for that comment.  You are quite correct-- we did not document the all the necessary citations for supporting our claim before. We have added the following note to \citeresp{1-5e}}
 
-\response{Thank you for that comment.  You are quite correct-- we did not document the all the necessary citations for supporting our claim before. We have added the following note to \respto{1-5e}}
-
-\review{(1.5f)
-5) "Maximize recall and precision and popt(20)": Why should these metrics be maximized?
+\review{(1.5f) "Maximize recall and precision and popt(20)": Why should these metrics be maximized?
 What is the practical value, e.g., is high recall always needed in practice, or should we prefer precision in the problems treated by the bellwether?
@@
 
-\response{Thank you for your comment, we didn't explained why these metrics need to be maximized, added necessary details\respto{1-5f} as footnote also there are details in sec 4.5}
+\response{Thank you for your comment, we didn't explained why these metrics need to be maximized, added necessary details\citeresp{1-5f}.}
 
@@
 
-\response{Thank you for your comment, we didn't explained why these metrics need to be minimized, added necessary details\respto{1-5f} as footnote also there are details in sec 4.5}
+\response{Thank you for your comment, we didn't explained why these metrics need to be minimized, added necessary details\citeresp{1-5f}.}
 
@@
 You are quite correct-- we did not include in depth steps to replicate the study before.
-We have added a replication package in contribution section \respto{1-5h} as well as more in depth details about the algorithm has been added in \respto{XXXX}}
+We have added a replication package in contribution section \citeresp{1-5h} as well as more in depth details about the algorithm has been added in figure~\ref{fig:Pseudo-code} and section~\ref{GENERAL}.}
 
@@
 
-\response{you are right, in the last draft we indeed did not included detailed analysis of the results to show the scalability of our model.
-In this draft \respto{1-2}\respto{1-6a} we have included 2 more research questions (RQ1 and RQ2) to show the conventional bellwether is slower than the new bellwether (aka GENERAL) method.
+\response{You are quite correct.
+In the last draft we indeed did not included detailed analysis of the results to show the scalability of our model.
+In this draft \citeresp{1-2}\citeresp{1-6a} we have included 2 more research questions (RQ1 and RQ2) to show the conventional bellwether is slower than the new bellwether (aka GENERAL) method.
 We also have updated another research question (RQ3) to compare the methods in-term of number of comparisons and time taken to run the two methods, as can been seen in figure~\ref{fig:compare} and \ref{fig:compare_time}.}
@@
 
-\response{you are right,Thank you for that comments. We have added much  quantitative analysis as
-well as statistical tests to this paper. Please see figure~\ref{fig:compare} and \ref{fig:compare_time}. XXXX(do we need more analytics and if so what?)}
+\response{You are right,Thank you for that comments. We have added much  quantitative analysis as
+well as statistical tests to this paper. Please see Figures~\ref{fig:compare_time} and ~\ref{fig:compare}.}
 
@@
 
-\section*{Reviewer}
+\section*{Reviewer 2}
 
-Many of your comments take issue with two terms used in this paper "lessons learned" and "transfer learning".
-We agree with you that our use of "lessons learned" was inappropriate and we have removed all those usages.
+\response{Thank you very much for your detailed review.
+As we said to the associated editor, the previous draft made the following mistake:
+\bi
+\item We assumed that the  core motivation for this work
+was widely known and accepted in the community. That was a mistake. 
+\item
+Consequently,this draft completely rewrites the Introduction
+to include much more background information on the 
+presence of the problem studied here.
+\ei
+We have made some additional corrections, clarifications, and revisions, as directed by your comments.
+To assist in your review, we refer to specific locations of each of the changes using the notation \respto{1-XX}.}
 
-As to our use of "transfer learning", 
-inspired by your comments we have clarified what we mean by that term much earlier in the paper (see \cite{XXX}).
-Base don that clarification, we can show that our use of ``transfer learning'' is consistent with its usage by Pan'09 (a paper current 8,220 citations at the time of this writing).
-Also, our usage is consistent with dozens of recent SE research papers on transfer learning~\cite{XXXmanycite}.
+% Many of your comments take issue with two terms used in this paper "lessons learned" and "transfer learning".
+% We agree with you that our use of "lessons learned" was inappropriate and we have removed all those usages.
+
+% As to our use of "transfer learning", 
+% inspired by your comments we have clarified what we mean by that term much earlier in the paper (see \cite{XXX}).
+Base don that clarification, we can show that our use of ``transfer learning'' is consistent with its usage by Pan'09 (a paper current 8,220 citations at the time of this writing)~\cite{pan2009survey}.
+Also, our usage is consistent with dozens of recent SE research papers on transfer learning~\cite{pan2009survey,kocaguneli2015transfer,jing2015heterogeneous,ma2012transfer,nam2013transfer,jamshidi2017transfer,qing2015cross,cao2015software,tong2016heterogeneous,nam2017heterogeneous,li2018cost,zhang2016cross,jing2015heterogeneous}.
 Thank you for encouraging us to clarify that terminology.
 
-A survey on transfer learning
-SJ Pan, Q Yang - IEEE Transactions on knowledge and data …, 2009 - ieeexplore.ieee.org
-  Cited by 8220 Related articles All 20 versions Web of Science: 3428
+% A survey on transfer learning
+% SJ Pan, Q Yang - IEEE Transactions on knowledge and data …, 2009 - ieeexplore.ieee.org
+%   Cited by 8220 Related articles All 20 versions Web of Science: 3428
 
@@
 
-\response{ Thank you for your comment, in the last draft we did not accurately explain what bellwether is. In this draft we have included the definition of bellwether \respto{1-1}\respto{2-2}:}
+\response{ Thank you for your comment, in the last draft we did not accurately explain what bellwether is. In this draft we have included the definition of bellwether \citeresp{1-1a}\citeresp{2-2}:}
 
 \begin{quote}
-    \response{``bellwether'' is a project from a community of N projects, whose data yields the best analytic (i.e.
-defect prediction, effort estimation etc) on all others.
-Also, to answer your second question, ``…the bellwether is equivalent to the other models'' has been replaced with ``....since the bellwether is an exemplar projects for the community of N projects seen so far...''  }
+    \response{``bellwether'' is a project from a community of N projects, whose data yields the best analytic (i.e. defect prediction, effort estimation etc) on all others.} 
+\end{quote}
+\begin{quote}
+    \response{Also, to answer your second question, ``…the bellwether is equivalent to the other models'' has been replaced with ``....since the bellwether is an exemplar projects for the community of N projects seen so far...''  }
 \end{quote}
@@
 \review{(2.3) [Sec.
-1] “when new projects appear, their quality can be evaluated even before there is an extensive experience base within that particular project (again, just by studying the bellwether).” You take a set of projects…select one project (the “bellwether”)…then use that project to build a model that can—for instance—estimate defect rate.
-So, for the defect estimation case, the model learned from the bellwether won’t tell you where the defects may be (i.e., fault localization), it will just estimate how buggy a new project is.
-Is all of this right?}
+1] “when new projects appear, their quality can be evaluated even before there is an extensive experience base within that particular project (again, just by studying the bellwether).” }
 
-\response{Thank you for your comment.
-In the first draft we did not adequately explained the goal of the task we are exploring.
-In this version we have added proper details regarding the task, that is to explore defect prediction to localize bugs in project's codebase  using software quality metrics extracted from the projects and the details has been added at \respto{2-3}.}
+\response{Thank you for your comment, this was a needless complexity that we deleted from this draft.}
 
@@
 
-\response{Explain the train, test splits and the how you do the exp. then say this is what our model proves, it predicts for projects which it has not seen before XX.}
+\response{Thank you for your comment.
+To answer the first question, the projects can be completely new projects, without any historical data collected for reference.
+To answer the second question, in this research the experiments has been designed to simulate a situation, where there are known projects in a large community as well as a set of new projects which are not part of the community.
+We do this by dividing the 697 projects into two sets 1) {\em Train 1}: a community 627 projects, from which we will select a bellwether and 2) {\em Train 2}: a set of 70 new projects, which will be tested using bellwether.}
+
+% \response{Explain the train, test splits and the how you do the exp. then say this is what our model proves, it predicts for projects which it has not seen before XX.}
 
@@
 
-\response{Thank you for your comment, it was unclear in the previous manuscript whether we need to find different bellwether for discrete task (different than defect rate prediction).
-For finding bellwether for another task, different from defect prediction, we do need to find another bellwether.
-The reason being, for other tasks the model build using the data will be different, so similarity between models  built using the projects will also be different.}
+\response{Thank you for your comment. 
+As you point out, the prior draft
+was too value on this point.
+This paper now focuses on defect prediction (see the new title).}
+
+\response{ But to answer
+your question (about whether
+or not the the bellwether changes
+per goal), it is possible that another
+task will require another bellwether.
+Accordingly,
+we assert it is vital that the
+bellwether method is fast. Hence this paper.}
 
@@
 
-\response{You are correct, it is certainly confusing for intro. we have removed the hypothetical figure and texts associated with it.}
+\response{You are correct. Deleted. }
 
@@
 
-\response{Not yet sure what it means}
+\response{In practice, the difference
+between the runtimes associated with these two  approaches is a 
+very large difference (as witnessed
+by P  Figures~\ref{fig:compare_time} and ~\ref{fig:compare}.) }
 
@@
 
-\response{will fix}
+\response{All our current numbers now say 697.}
 
@@
 
-\response{You are correct, the wording of the box under RQ4 was confusing.
-We have added new texts \respto{2-9} to be more clear about the  context about finding bellwether to understand importance of features.
-To be more precise, instead of finding important features for each project (which shows very different results for each project), we find the bellwether (as an exemplary project for all other projects) using GENERAL and check the importance of feature for that project only.}
+\response{You are correct. We have reworded the wording of the box under RQ4, which was confusing. We have simpler text now \citeresp{2-9}.}
 
@@
 \response{
-Thank you for that comment. Yes you are completely correct.
- On  review,  we  found that  core  problem  of  conclusion  instability  was  not  well documented  in  the  introduction.
-This  new  draft  fixes  that problem.
-Much of the new text on page1 takes care to document {\em why } we  are  exploring  general SE conclusions  before moving on the
- {\em how} we do that exploration.}
+Thank you for that comment. We deleted it.}
 
- \response{
-Note that with that new introduction (that focuses more on {\em why}, then this paper is not  better at contextualizing
-and justifying the need (and value) of the second contribution.}
+%  \response{
+% Note that with that new introduction (that focuses more on {\em why}, then this paper is not  better at contextualizing
+% and justifying the need (and value) of the second contribution.}
 
@@
 
-\response{Thank you for your comments, we have moved [Sec.
-2.1] from background to a new section titled Motivation.
-Also we have removed the hypothetical situation and added actual experimental data to show the difference.
-The details has been added as text in \respto{2-12}.}
+\response{Thank you for your comments. We have deleted it.}
 
@@
 
-\response{Thank you for your comments, we have removed the hypothetical graph and added experimental details for this section.
-The new text has been added to [Sec.
-2.2], which is a part of motivation now \respto{2-12}.}
+\response{Thank you for your comments. As you suggested, we have removed it.}
 
@@
 
-\response{with respect, in terms of SE research, it is much larger than any studies seen before. but your concern is valid. we have added
-a weaselt sentence at the end saying that we can never assume generality of all porkect.XXX}
+\response{Please see our new comments at end of introduction.
+Clearly, we oversold our case before.
+Our conclusions are not general to all projects.
+However, and this has not be achieved before.
+our conclusions are general to hundreds
+of project.}
 
@@
 
-\response{ You are quite right.
-we should never say "cause'.
-We have removed the ambiguous statement and added XYZ is a statistical predictor for bug prone code.
-The changes has been added in this manuscript\respto{2-15} }
+\response{You are quite right.
+Probabilistic data miner results  should never claim causality.
+We have removed the ambiguous statement and added XYZ is a statistical predictor for bug prone code \citeresp{2-15}.}
 
@@
 
-\response{Thank you for your comment. We indeed forgot to add the citations in the previous manuscript. We have added the citations in this manuscript \respto{2-17}.}
+\response{Thank you for your comment. We indeed forgot to add the citations in the previous manuscript. We have added the citations in this manuscript \citeresp{2-17}.}
 
@@
 
-\response{XXX}
+\response{Thank you for your comment, the previous manuscript did not included all the details regarding the design matrix.
+In this manuscript we have included much details regarding the design matrix in \citeresp{2-18}.
+\fig{meta} shows the distribution of number of rows in each projects, which is a snapshots of the projects from 6 months back of the last commit.
+We can see from the \fig{meta} median number of rows is around 120 in this group of 697 projects explored.}
+
+\begin{quote}
+    \response{Using the   Understand tool~\cite{visualize},
+we calculated different variations (i.e. average, max etc.) of 21 product and 5 process metrics, with a total 66 attributes/columns to build defect prediction models
+ (see Table~\ref{tbl:metric}).
+These product  metrics are calculated from snapshots of the projects from 6 months back of the last commit.
+The process metrics are computed using the change history in the six-months period before the split date via manual collection of data using scripts.}
+\end{quote}
 
@@
 Over-fitting is a problem that can occur with data of any size. Over-fitting is a well-studies problem that explores bias/variance trade offs.
-But over-fitting is an orthogonal issue to Transfer learning.
-To clarify all that we have added text to XXX:}
+But over-fitting is an orthogonal issue to negative
+transfer learning.
+To clarify all that we have added text to \citeresp{2-21}:}
 \begin{quote}
 \response{
-\respto{2-XXX}
 This sections ask if conclusions always improve as we learn from more and more data.
@@
 inappropriately applied to the present situation. ~\\
-is a special problem that arises when combining old data/models with new data/models.}
+This is a special problem that arises when combining old data  with new data.}
 \end{quote}
@@
 \response{Thank you for your comment, you are quite correct the use of ``advice or recommendations'' is rather ambiguous in this context.
-We have changed these references of ``advice or recommendations'' to ``prediction'' in this version of manuscript }
+We have changed these references of ``advice or recommendations'' to ``prediction'' in this version of manuscript.}
 
@@
 
-\response{Thank you for your comment. We have made changes \respto{2-23} to the sentence to be understandable }
+\response{Thank you for your comment. We have made changes \citeresp{2-23} to the sentence to be understandable }
 
@@
 
-\review{(3.1)What I find irritating is that the manuscript introduces a new approach GENERAL, which just applies hierarchical clustering.
+\response{Thank you very much for your detailed review.
+As we said to the associated editor, the previous draft made the following mistake:
+\bi
+\item We assumed that the  core motivation for this work
+was widely known and accepted in the community. That was a mistake. 
+\item
+Consequently,this draft completely rewrites the Introduction
+to include much more background information on the 
+presence of the problem studied here.
+\ei
+We have made some additional corrections, clarifications, and revisions, as directed by your comments.
+To assist in your review, we refer to specific locations of each of the changes using \respto{1-XX}.}
+
+\review{(3.1)The manuscript introduces a new approach GENERAL, which just applies hierarchical clustering.
 As far as I understand, hierarchical clustering is a well-known, standard, and largely-evaluated clustering algorithm.
@@
 
-\response{Thank you for your comment.
-There were indeed lack of clarity regarding the explanation of how GENERAL works, we have added more details about GENERAL\respto{XXXXXX}.
-The algorithm GENERAL uses hierarchical clustering to cluster projects into smaller groups based on similarity and doesn't help with actually predicting the defect.
-GENERAL uses the hierarchical clustering to group the projects, then bellwether method is applied at the leaf nodes of the hierarchical clustering tree to find bellwether for each leaf, then a approximation is applied and only the bellwethers are pushed up to the tree to find bellwether in upper levels.
-This process goes on until we find bellwether for the root node.
-After we have found bellwethers , we build models for predicting defect.}
+\response{Thank you for your comment. We have added detailed notes on how GENERAL and each of its component works. To clarify, GENERAL
+does several things, only one of which is a standard
+hierarchical clusterer. First, it clusters using the BIRCH clusterer
+as a sub-routine. Secondly, it walks over the cluster tree generated
+from BIRCH conducting experiments to see what best local model works for a subbranch. As part of those experiments: (2a) it builds models using a data mining on data from a sub-tree; (2b) it compares
+different models from sibling trees using a multi-objective domination predicate. Note that this second part is not part of standard BIRCH. For full details on this process, please  \citeresp{3-1}.}
 
@@
 
-\response{Thank you for your comments.
-We have removed the hypothetical scenarios from sec~\ref{sec:motivation}.
-We have removed all the hypothetical graphs and added data from actucal experiment in this version of manuscript\respto{3-2}.}
+\response{Thank you for your comments.   We have removed all the hypothetical graphs and added data from actual experiment in this version of manuscript.}
 
@@
 statement coverage for non-critical systems).
-See below further comments about the quality of the dataset.}
+}
 
-\response{with respect.... but we can}
+\response{With respect, we are unclear on this comment. As shown by our precision, recall, false alarm, etc results what this paper
+shows is that we can make general conclusions across this space of projects. And, elsewhere, bellwethers have worked to generate
+configurations for cloud-based tools~\cite{krishna2019whence},
+effort estimation, predicting Github issue close time, and
+code bad smell detection~\cite{krishna2018bellwethers,krishna2017simpler, nair19a, krishna16, krishna16a}.
+So we would characterize bellwethers as method that has been demonstrated useful in many domains.
+However, and this is the point of this paper, the existing  method does not scale to large data sets.
+Hence, this paper.}
 
@@
 
-\response{Thank you for your comments.
-We have removed the hypothetical scenarios from sec~\ref{sec:motivation}.
-We have removed all the hypothetical graphs and added data from actual experiment in this version of manuscript\respto{3-2}.}
+\response{Thank you for your comments. In the last draft, Figure 1 and Figure 2 were indeed based on hypothetical data.  We have removed the hypothetical Figure 1 and Figure 2 in this draft.}
 
@@
 
-\response{Thank you for your comment.
-In this paper, we discussed about a broader impact of learning from large number of projects to find a general conclusion.
-We indeed didn't emphasized on mentioning, we are using defect prediction as our case study for this paper.
-We have added details\respto{3-5} about using defect prediction in this paper as a case study for showing the importance of learning models from hundreds of projects.}
+\response{Thank you for your comment. You are correct. The paper
+is now focused on defect prediction (see our new title). }
 
@@
 \response{Thank you for your comment.
-We indeed can not say that in general and can not prove external validity, but just for the projects used in this paper.
-which is orders of magnitude larger than anything seen before.}
+If you are asking ``does bellwether work for multiple domains'', then we would say ``yes'' as shown by Krishna et al.'s TSE and ASE paper~\cite{krishna2018bellwethers,krishna2017simpler, krishna16, krishna16a} (see our comment for 3.3).}
+
+\response{But if you are asking ``are these conclusions general across the space of all projects, we would agree with you that the answer must be ``no''.
+The prior draft reached too far on this point.
+Our new end to the introduction \citeresp{3-6}  makes it clear that we are talking about ``more generalizable to more projects'' rather than ``general to all projects''.}
 
@@
 
-\response{not in general. cant prove external validity. just for our 673 projects. which is orders of magnitude larger than anything seen before.XXXX}
+\response{Please see comment 3.3 and 3.6}
 
@@
 \response{Thank you for your comment, we didn't included detailed analysis of complexity of our method in the last manuscript.
-We have added much details and an step by step analysis\respto{3-10} of complexity of the algorithm shown in Fig~\ref{fig:Pseudo-code}.}
+We have added much details and an step by step analysis \citeresp{3-10} of complexity of the algorithm shown in Fig~\ref{fig:Pseudo-code}.}
 
@@
 The Fig~\ref{fig:Statistical} is a form of boxplot, where the black dot represents the median and the spread of the black line represents the 25th and 75th percentile of the data.
-Alternatively we can include all the results instead of just showing the median and IQR, but it will occupy too much space.}
+Also note that the ranks we offer in that figure (in the left-hand-column) are generated via non-parametric statistics
+(bootstrap and the A12 effect size test) that do not assume gaususians.}
 
@@
 We have updated the figure~\ref{fig:Statistical} to replace arithmetic mean and standard deviation with median and IQR.
-We can see from the figure~\ref{fig:Statistical}, the ZeroR model has a recall and pf of zero with IQR diff between 75th and 25th percentile as 100, which signifies as the model either predicts everything as defective or non-defective it will not be able to predict any defective module at all if the defect ratio is less than 50\%, while for projects with defect ratio is more than 50\% it will predict everything as defective with high false positive.XXXX}
+We can see from the figure~\ref{fig:Statistical}, the ZeroR model has a recall and pf of zero with IQR diff between 75th and 25th percentile as 100, which signifies as the model either predicts everything as defective or non-defective it will not be able to predict any defective module at all if the defect ratio is less than 50\%, while for projects with defect ratio is more than 50\% it will predict everything as defective with high false positive.}
 
@@
 We have also removed any ambiguous keyword which might not be appropriate in this context.
-The changes has been added in \respto{3-13}.}
+The changes has been added in \citeresp{3-13}.}

### 2020-03-19 manuscript.tex
Updates from Overleaf

@@
 \begin{document}
-\title{  How to Find GENERAL    Defect Prediction Models  \\
-Amidst Hundreds of    Software Projects}
+\title{   Finding GENERAL    Defect Prediction Models   
+Within Hundreds  of   Software Projects}
 
@@
 \begin{abstract}
-\respto{2-22}{\color{blue} When one   exemplar project, which we call the ``bellwether'', offers the best prediction
-then
-it can be used to offer prediction for
-many other projects. Such bellwethers can be used to make quality predictions about new projects, even before there is much experience with those new projects.}
-% Such general conclusions   simplifies     software quality policies since the list of quality problems, and their mitigations, is static).
-Also such general conclusions simplify the design and delivery
-% of training programs since, as long as the bellwether offers best advice,
-% then  ``best practices'' will remain  now constant.
-% Lastly, bellwethers simplify tool development
-% since, using the advice from the bellwether,  it is clear where it is most cost-effective to buy/build tools to mitigate
-% for software quality issues.
-
-But  existing  methods  for  bellwether  transfer  are  very slow.  When  applied  to  the  697  projects  studied  here,  they took  60  days  of  CPU  to  find  and  certify  the  bellwethers
-Hence,  we  propose GENERAL:  a novel bellwether detection algorithm based on
-  hierarchical clustering. At each level within a tree of clusters, one bellwether is computed from sibling projects, then promoted up the tree. 
+% \respto{2-22}{\color{blue}Given a group of software projects,
+% there often exists  one   exemplar project
+% that offers the best prediction for all others.
+% Such ``bellwether projects''
+% can be used to make quality predictions that are general
+% to that group.}
+% Existing  methods  for  finding bellwether  are  very slow.
+When  applied  to  the  697  projects  studied  here, standard bellwether methods   took  60  days  of  CPU  to  find  and  certify  the  bellwethers
+% Hence,we  propose a faster way to find bellwethers. 
+% GENERAL applies hierarchical clustering to groups of project data.
+At each level within a tree of clusters, one bellwether is computed from sibling projects, then promoted up the tree.
 This hierarchical method is a scalable approach to learning effective models from very
-large data sets. 
-For nearly 700 projects,
-the defect prediction models generated from GENERAL's bellwether  
-were  just as good as those found via  standard methods.
-
-% Having shown that it is
-% possible to transfer lessons learned across
-%  100s of projects, our future work
-%  will be to  achieve ``mega-transfer'';
-%  i.e. to transfer lessons learned between
-%  1000s to 10,000s of projects.
+% large data sets. For  hundreds of projects, the defect prediction models generated from GENERAL's bellwether were just as good as those found via  standard methods.
+
+\respto{2-22}{\color{blue}Given a group of software projects, there often exists  one   exemplar project that offers the best prediction for all others.
+Such ``bellwether projects'' can be used to make quality predictions that are general to that group.} Existing  methods  for  finding bellwether  are  very slow.
+When  applied  to  the  697  projects  studied  here, standard bellwether methods   took  60  days  of  CPU  to  find  and  certify  the  bellwethers.
+Also among a large group of software projects there may be subgroup of projects which are more similar to each other then other subgroups and can have a bellwether for each such subgroup of projects.
+Existing bellwether methods does not take this into consideration to find multiple bellwether.
+Hence, we  propose a faster and better  way to find bellwethers.
+GENERAL applies hierarchical clustering to groups of project data.
+At each level within a tree of clusters, one bellwether is computed from sibling projects, then promoted up the tree.
+This hierarchical method is a scalable approach to learning effective models from very large data sets.
+For  hundreds of projects, the defect prediction models generated from GENERAL's bellwether were just as good as those found via standard methods.
 
@@
 
-\respto{1-3}{\color{blue}Researchers and industry practitioners makes use of data-driven decision making for defect prediction by generating software quality models(defect predictor) from project data comprises of software quality metrics (Commonly used software metrics for defect prediction are complexity metrics (such as lines of code, Halstead metrics, McCabe’s cyclometic complexity, and CK metrics) and process metrics (such as number of revisions, lines added and deleted) These defect predictors are used for predicting defects in new set of changes and to learn what are the important metrics that are responsible for finding these defects.
-These quality metrics can be collected with much ease from the code base of different software systems from large organizations and open source community, and can be used for large scale data-driven decision making.}
+\respto{1-2}\respto{1-3}{\color{blue} Researchers and industry practitioners makes use of data-driven decision making data mining algorithms build software quality models from project data.For example, many research and industrial groups generate defect predictors from software metrics~\cite{ghotra2015revisiting, zimm09 ,okutan2014software, he13, Zhang16aa, nam2017heterogeneous, Me13, Tantithamthavorn18, me09b, me10a, peters2015lace2, nam2018heterogeneous, menzies2011local, zimmermann09}.
+These metrics can take  forms including process metrics (that describe how and who updates the code) and product metrics (such as number of methods per class, lines of codes, etc).
+One advantage of this approach is that the collection of these metrics is very fast.
+Also,  the subsequent data mining (to generate the quality models) can be fully automated and can scale to a large number of projects.
+Hence, data-driven decision making  is widely used in   SE research and   industrial practice.~\cite{tosun2010ai,kim2015remi,wan2018perceptions} }
+
+\begin{table*}
+\begin{center}
+\includegraphics[width=14cm]{figs/istable.png}
+\end{center}
+\caption{Contradictory conclusions from OO-metrics studies for defect prediction.
+From~\cite{menzies2012local}, Studies report significant (``+'') or irrelevant (``-'') metrics verified by univariate prediction models.
+Blank entries indicate that the corresponding metric is not evaluated in that particular study.
+CBO = coupling between objects; RFC = response for class (number of methods executed by arriving messages); LCOM = lack of cohesion (pairs of methods referencing one instance variable, different definitions of LCOM are aggregated); NOC = number of children (immediate subclasses); WMC = number os methods per class.
+For more details on these examples, and references to the papers containing these studies, see~\cite{menzies2012local}.}
+\label{unstable}
+\end{table*}
 
 {\color{blue} But what is the external validity of the conclusions reached  via
-the above data mining methods?
- If we cannot offer general rules across a large number of software projects, then it is   difficult to demonstrate such generality.
+the these data mining methods?
+Prior to this paper, the usual result is that such conclusions are not general to multiple projects.
+For example, Table~\ref{unstable} summarizes the results of dozens of studies.
+In that table we observe that, from project to project, very different attributes are most associated with defect prediction.
+This is troubling since,   as
+Sawyer et al. argue,   project-general
+insights are the key driver for businesses to invest in data analytics.
+If  new models keep being generated whenever we switch to  new projects, then that exhausts the ability of  users to draw insight from  new data.
 Hassan~\cite{Hassan17} cautions that managers lose faith in software analytics if its models keep changing since  the assumptions used to make prior policy decisions may no longer hold. 
-Also, Kim et al.~\cite{Kim2016}, notes  that the aim of software analytics is to obtain actionable insights that help practitioners accomplish software development goals.
-Many other researchers agree.
-For example,
-Tan et al.~\cite{tan2016defining} say that such   insights  are a core deliverable.
-Sawyer et al.
-agree, saying that  insights are the key driver for businesses to invest in data analytics initiatives~\cite{sawyer2013bi}.
-Also,
-Bird, Zimmermann, et al.~\cite{Bird:2015} argue that such  insights occur when users reflect, and react, to the output of a model generated via software analytics.
-But if  new models keep being generated in new projects, then that exhausts the ability of  users to draw insight from  new data.}
-
-{\color{blue} Apart from the above,  are several other reasons to seek general conclusions in SE. For example, 
+ Further,
 if we are unsure what factors most influence quality, it is difficult to design and implement and deploy tools that can successfully improve that quality.
-Also,
-consider the task of training a   novice software engineers or newcomers to a project If our models are not stable, then it hard to teach what factors  most influence software quality.}
+Lastly,
+consider the task of training a   novice software engineers or newcomers to a project. If our models are not stable, then it hard to teach what factors  most influence software quality.}
 
@@
 
-{\color{blue} Finding general defect prediction models  across multiple projects is a complex task.
-There are many recent examples of supposed ``general'' SE conclusions that are
-now questionable. For example, Fenton warns
-that, in stark contrast to  much prior research, pre- and post- release failures are not connected~\cite{fenton2000quantitative}.
-Also, Nagappan et al. have found that the language construct GOTO, as used in contemporary practice, is rarely considered harmful~\cite{nagappan2015empirical};
-Similiary, Fucci et al. report that test-driven development is not any better than "test last"~\cite{fucci2017dissection};
- Further, in our own work, we have seen that
- delayed issues are not exponentially more expensive to fix~\cite{menzies2017delayed}.
- For a long list of other conclusions that were found to be  unstable across multiple projects, see~\cite{Me13}.
-This problem is so endemic in software engineering that other journals have devoted entire special issues t the topic~\cite{Menzies2012}.
-}
-
-{\color{blue} Given all these examples of SE conclusions whose generality we must now question, it is timely
-to ask what methods are available for finding general results that hold across multiple projects?}
-A new approach, that shows much promise, is the ``bellwether'' method for transferring conclusions between projects~\cite{krishna2018bellwethers,krishna16a,mensah18z,mensah2017stratification,mensah2017investigating}.
-\respto{1-1a}{\color{blue} ``bellwether'' is a project from a community of N projects, whose data yields the best analytic (i.e.
-defect prediction, effort estimation etc) on all others.} (the bellwether is the  leading sheep of a flock, with a bell on its neck).
-This method:
+%{\color{blue} Finding general defect predictors  across many projects is a complex task.  
+ %For a long list of   conclusions that were found to be  unstable across multiple projects, see~\cite{Me13}.
+This problem is so endemic in software engineering that other journals have devoted entire special issues to the topic~\cite{Menzies2012}.}
+
+A new approach for transferring conclusions
+across multiple projects
+is     the ``bellwether'' method~\cite{krishna2018bellwethers,krishna16a,mensah18z,mensah2017stratification,mensah2017investigating}.\respto{1-1a}\respto{2-2}{\color{blue} Given a community of projects developed by the same organization,
+a ``bellwether'' is the   whose data yields the best analytic (i.e. defect prediction, effort estimation etc) on all others} (and we call that the ``bellwether'' since that is the
+name of the  leading sheep of a flock, with a bell on its neck).  This method:
 \bi
@@
 \ei
-\respto{3-5}{\color{blue}This approach has been successfully applied to defect prediction, software effort estimation, bad smell detection, issue lifetime estimation, and configuration optimization (In this paper we only explore defect prediction).
-As a method of transfer learning from one project to another, bellwethers have worked better than the Burak filter~\cite{turhan09}, Ma et al.~\cite{Ma2012}'s transfer naive Bayes (TNB); and Nam et al.
-TCA  and TCA+, algorithms~\cite{Nam13,Nam2015}}.
-
-When new projects arrive, then even before there is much experience with those new projects,  models learned from other projects can be applied to the new project (just by studying the bellwether),
- Further, \respto{2-2}{\color{blue} since the bellwether is an exemplar projects for the community of N projects seen so far},
- %since the bellwether is similar to the other models
- then when new projects appear, \respto{2-3}{\color{blue} bugs can be localized for that project} even before there is an extensive experience base within that particular project (again, just by studying the bellwether).
+{\color{blue} \respto{1-1a}\respto{3-5}This approach is useful since bellwethers can generate
+models that hold across multiple data sets.
+Also,   bellwether are a better
+way to transfer lessons between software projects~\cite{krishna2018bellwethers,krishna2017simpler, nair19a, krishna16, krishna16a}  than many other methods including
+the Burak filter~\cite{turhan09}, Ma et al.~\cite{Ma2012}'s transfer naive Bayes (TNB); and Nam et al.'s  TCA  and TCA+, algorithms~\cite{Nam13,Nam2015}.}
+
+% When new projects arrive, then even before there is much experience with those new projects,  models learned from other projects can be applied to the new project (just by studying the bellwether),
+%  Further, \respto{2-2}{\color{blue} since the bellwether is an exemplar projects for the community of N projects seen so far},
+%  %since the bellwether is similar to the other models
+%  then when new projects appear, \respto{2-3}{\color{blue} bugs can be localized for that project} even before there is an extensive experience base within that particular project (again, just by studying the bellwether).
  %That is, bellwethers can be queried  to find general lessons about (a)~major quality issues;
@@
 
-But existing  methods for bellwether transfer are very slow.
-When applied to the 697 projects studied here, they took 60 days of CPU to find and certify the bellwethers.
-There are many reasons for that including how the models were certified (20 repeats  with different train/test sets)
-and the complexity of the analysis procedure (which includes fixing class imbalance and feature selection).
+But existing  methods for bellwether transfer are very slow. When applied to the 697 projects studied here, they took 60 days of CPU to find and certify the bellwethers.
+%There are many reasons for that including how the models were certified (20 repeats  with different train/test sets)
+%and the complexity of the analysis procedure (which includes fixing class imbalance and feature selection).
 But the major cause of this slow down was that those   methods  required an $O(N^2)$ comparison between   $N=697$ projects.
 
-This paper reports a novel approach  that improves on existing bellwether methods.
+Accordingly, this paper explores a novel approach that can find  bellwethers much faster than standard methods.    
 %dramatically improves on existing bellwether methods.
- Our GENERAL  method  uses hierarchical clustering model to recursively divide a large number of projects into smaller clusters.
+ {\color{blue}\respto{1-3a} Our GENERAL    algorithm uses hierarchical clustering  to recursively divide a large number of projects into smaller clusters. 
  Starting at the leaves of that tree of clusters, GENERAL finds the    bellwethers within sibling projects.
@@
 The output of GENERAL is the project promoted to the top of the tree of clusters.
-
- This paper evaluates the model built from the project   found by GENERAL. 
- We will find that  the predictions
- from this model  are as good, or better,
- than those found  via ``within'' learning (where models are trained and tested on local data)
- or ``all-pairs'' learning (where models are found after building models from all pairs of projects).
-   That is
-\begin{quote}
-{\em 
-Learning from many other projects can be better than learning just from your own local project data.
-}\end{quote}
-GENERAL's clustering methods divide $N$ projects into $m$ groups. In that space,   GENERAL only needs
-to compare $O(m*(N/m)^2)$  projects to find the bellwether. Theoretically and empirically, 
-this means GENERAL will scale up much better than traditional   methods.
-This paper applies GENERAL and traditional $O(N^2)$ bellwether to 697 projects.
-GENERAL and the traditional approach terminated in 1.5 and 72 hours (respectively).
+}
+%Note that  GENERAL only needs
+%to compare $O(m*(N/m)^2)$  projects to find the bellwether.
+
+  GENERAL has two advantages over standard bellwether methods.
+Firstly, 
+according to several of the criteria studied here, GENERAL
+can produce better predictors for software quality.  Secondly, it is much  
+faster than standard bellwethers
+(and scales to larger sets of data).
+
 % \bi
@@
 % GENERAL and the traditional approach terminated in 1.5 and 72 hours (respectively).
-
 % \item 
@@
 % \end{figure} 
-Using GENERAL, we can  explore these research questions:
+To present GENERAL and to assess its value, this
+paper asks and answers the following questions:
             \respto{1-6}
@@
 
+            As a starting point for this research,  we need to document the problems associated with existing bellwether methods. RQ1 offers the following theoretical result:
             \begin{RQ}{
-               Conventional bellwether method as proposed by krishna et al~\cite{krishna2018bellwethers,krishna16a} uses a $ O(N^2) $ comparisons to find the ``bellwether'' among a community of N (697 projects in this experiment) projects.
-In this experiment the conventional bellwether method is very expensive to find the ``bellwether''.}
+               Conventional bellwether method as proposed by Krishna et al~\cite{krishna2018bellwethers,krishna16a} uses a $ O(N^2) $ comparisons to find the ``bellwether'' among a community of N (697 projects in this experiment) projects.}
             \end{RQ}
 
-            \textbf{RQ2}:  How fast is new bellwether method aka GENERAL?
+            \textbf{RQ2}:  How fast is GENERAL bellwether?
+
+            RQ2 explains the RQ1 result:
 
             \begin{RQ}{
-               The new bellwether method (GENERAL), which is a combination of hierarchical clustering and bellwether method achieves  a computational complexity of $O(m*(N/m)^2)$, which is much faster than conventional bellwether.}
+            In theory, 
+             GENERAL is much faster since
+             its computational complexity is  $O(m*(N/m)^2)$.}
             \end{RQ}
@@
 
-            \textbf{RQ3}:   Can hierarchical clustering tame the complexity of bellwether-based reasoning?
-
+            \textbf{RQ3}:   In practice,
+            can the hierarchical clustering of GENERAL tame slow runtimes seen in   bellwether-based reasoning?
+
+            This research question checks if our new method tames the runtime complexity of standard bellwether. We find that:
             \begin{RQ}{
-               Theoretically and empirically, the 
-hierarchical
-reasoning on GENERAL performs much
-faster than standard bellwether methods.}
+                When learning
+bellwethers from 697 projects,  GENERAL and   traditional   approaches terminated in 1.5 and 72 hours (respectively).}
             \end{RQ}
+That is to say,  GENERAL is far faster
+than standard bellwether methods.
 
@@
 
+            Sometimes,  a faster method   comes at the cost of a less effective analysis. Hence, this research question compares
+             standard and the GENERAL bellwether methods. We find that:
+
             \begin{RQ}{
-                Measured in terms of predictive performance,
-the effectiveness of hierarchical bellwethers
-is very similar to local learning
-(and these two methods are more effective
-than the other options explored here).}
+                Across multiple performance criteria, the faster GENERAL bellwether algorithm never performs worse that standard bellwether.
+And measured in terms of recall and false alarm, GENERAL performs statistically much better.}
             \end{RQ}
@@
 
+            We ask this since Petersen and Wohlin~\cite{Petersen2009} argue that for empirical SE, context matters.  They
+would say that   it is  a mistake
+to learn from too much data, since that can inappropriately combine 
+data from difference contexts. 
+What we will show is that:
             \begin{RQ}{
-            Assessed in terms of {\em recall},
+            ZXXXAssessed in terms of {\em recall},
 it is better to learn bellwethers from more data rather than less.
@@
 while learning bellwethers
-from many projects is useful, it is possible to learn from too much data.}
+from many projects is useful,
+as predicted by Petersen and Wohlin, it is possible to learn from too much data. }
             \end{RQ}
@@
             \begin{RQ}{
-                \respto{2-9}\respto{3-13} {\color{blue}The importance of many key features is not apparent at the local
-project level.
-To fully understand the effect of certain attributes (key features) on defect prediction and bug localization, it is necessary to analyze hundreds of projects together to identify a single bellwether.
-This bellwether will act as an exemplary model to identify such key features in defect prediction models.}}
+                \respto{2-9}\respto{3-13} {\color{blue}
+                In terms of defect prediction,
+issues of inter-class interface are paramount.
+Many other  issues are far less important such as file size, depth of inheritance tree, intra-method complexity, file size, revision history.}}
             \end{RQ}
@@
 \item \textbf{Showing inherent generality in SE:}
-In this study we discover a source data set for transfer learner from a large number of   projects, hence proving generality in the SE datasets (where some datasets can act as exemplars for the rest of them for defect prediction).
-
-\item \textbf{ Lessons   about software quality that are general
+In this study we discover a source data set for transfer learner from a large number of   projects, hence proving generality in the SE datasets (where some datasets can act as exemplars for the hundreds of other projects).
+
+\item \textbf{Showing when ``enough is enough'': }
+In this study 
+Learning from  a few hundred  projects is better
+than learning from just a few dozens   projects.
+But after 200 projects (approx) the learned
+model start degrading. 
+This is to say that 
+there is an limit beyond
+which more data is actually detrimental to learning software quality models.
+
+\item \textbf{Lessons   about software quality that are general
 to hundreds of software projects:}
@@
 
-\item \respto{1-5h}{\color{blue}\textbf{ Replication Package:} We have made available a  replication package\footnote{\href{http://tiny.cc/bellwether}{http://tiny.cc/bellwether}} .
-The  replication package consists of all the datasets used in this paper, in addition to mechanisms for computation of other statistical measures.}
+\item \respto{1-5d} \respto{1-5h}{\color{blue}\textbf{ Replication Package:} Our  replication package\footnote{\href{http://tiny.cc/bellwether}{http://tiny.cc/bellwether}}   contains  all the datasets and scripts used in this paper.}
 
@@
 
-\section{Motivation}
-\label{sec:motivation}
+\respto{3-6}{\color{blue}  Before beginning, we offer
+a clarification on our use of the term ``general conclusions''. 
+ Like Petersen and Wohlin~\cite{Petersen2009}, we doubt
+ that all projects are so similar that a single
+ model describes them all.  
+ Accordingly, our goal
+is conclusions that hold over 
+{\em many} projects, but not
+necessarily {\em all projects}.
+The achievement documented here is that:
+\bi
+\item
+We can
+ generate one defect predictors across
+ hundreds of projects.
+  \item
+  That 
+  predictor performs   just as well as those found via  standard methods.
+  \ei
+  There are two important features of the conclusions reached via the methods of this paper:
+  \bi
+  \item
+  Our single
+  model offers 
+  external  valid conclusions
+  that are stable across hundreds of projects. As argued above, such a result
+has not been previously reported in SE.
+\item
+the conclusions reached in this way used automatic data mining methods applied to open source data. That is, our results   can be repeated/ improved/ refuted by other research teams.
+\ei
+We are unaware of any other repeatable/refutable result in SE that can be shown to hold over so many projects.}
 
@@
 
-\subsection{A Note on Context}
 %Just to balance the above argument,
 %we add that   sometimes it is possible to learn from {\em too much data}.
-Petersen and Wohlin~\cite{Petersen2009} argue that for empirical SE, context matters.
-That is, they would predict that one model  will \underline{not}  cover all  projects and that tools that report  generality  over many software projects need to also know the {\em communities} within which those conclusions   apply.
-Hence, this work divides into (a)~automated methods for finding sets of projects in the same {\em community}; and (b)~within each {\em community}, find the model that works best.
-
-\respto{2-12}\respto{3-2}{\color{blue} The {\em size} of the communities found in this way would have a profound impact on how we should reason about software engineering.
+
+%Hence, this work divides into (a)~automated methods for finding sets of projects in the same {\em community}; and (b)~within each {\em community}, find the model that works best.
+
+%\respto{2-12}\respto{3-2}{\color{blue} The {\em size} of the communities found in this way would have a profound impact on how we should reason about software engineering.
 Consider in this experiment of 697 projects, we build a set of defect predictor by learning bellwether from smalls cluster of $\approx10$ projects,  medium clusters of $\approx100$ projects, a large cluster containing $\approx600$ projects and a self test.
@@
 In this case,  (a)~principles about what is ``best practice'' for different software projects would be constantly changing (whenever we jump from small community to small community); and (b)~the generality issues would be becoming open and urgent concerns for the SE analytics community.}
-
-In summary, the above two sections lead to our  research question {\bf  RQ5}:
-does learning from too many projects have detrimental effects. Later in this
-paper, we will return to this issue.
 
@@
 One explanation for this discrepancy  is the size of number of projects that they explored.
-Menzies, Herbold et al.
+\respto{2-14}Menzies, Herbold et al.
 explored less than two dozen projects which raises issues of external validity in their conclusions.
@@
 
-\textbf{(d) When there is insufficient local data, learning from other projects is very useful:} When developing new software in  novel areas, it is useful to draw on the relevant  experience  from related areas with a larger experience base.This is particularly true when developers are doing something that is novel to them, but has been widely applied elsewhere
-, Clark and Madachy~\cite{clark15} discuss 65 types of software they see        under-development by the US Defense Department in 2015.
+\textbf{(d) When there is insufficient local data, learning from other projects is very useful:} When developing new software in  novel areas, it is useful to draw on the relevant  experience  from related areas with a larger experience base.This is particularly true when developers are doing something that is novel to them, but has been widely applied elsewhere, Clark and Madachy~\cite{clark15} discuss 65 types of software they see        under-development by the US Defense Department in 2015.
 Some of these types are very common (e.g.
@@
  Our proposed improvement to bellwethers is called GENERAL.
-The core intuition of this new approach is that if many projects are similar, then we do not need to run comparisons between all pairs of projects.\respto{1-1b}{\color{blue} We say this since  Devanbu et al.`\cite{hindle2012naturalness} report that if Markov chains are created for tokens in a program, then a remarkably small number of chains capture most of the program.
-Given these similarities,   we can exploit symmetries between different projects in order to learn predictors from one and apply those to another.
-To say that another way, when such similar projects exist, if may suffice to just compare a small number of representative examples.
+The core intuition of this new approach is that if many projects are similar, then we do not need to run comparisons between all pairs of projects.\respto{1-1b}{\color{blue}
+   We came to this
+intuition based on the writing
+of    Devanbu
+et al.`\cite{hindle2012naturalness}   who showed that a remarkably
+small number of Markov chains 
+capture the repeated patterns
+of tokens in a program~\\
+When such similarities
+exist, then we   exploit symmetries between different projects in order to learn predictors from one and apply those to another.
+Specifically: assuming inter-project symmetry,   we do not need to run comparisons between all pairs of projects since analyzing just a few pairs should work as well as anything else.
 }
@@
 
-\respto{3-10}{\color{blue}  
- Accordingly, the rest of this paper performs the following experiment assuming :
+\respto{3-1}\respto{3-10}{\color{blue}  
+ Accordingly, the rest of this paper performs the following experiment :
  \be
@@
 Our hierarchical clustering algorithm BIRCH has a complexity of $O(N)$ where each project is represented by a feature vector from step 1.
+ \item Implement evaluation criteria (see \S\ref{sec:Measures}).
  \item Starting at the leaves of that tree,   the best project is discovered by training on each project, and test its model
@@
  \ee
-
  Note that when the clustering algorithm divides the $N$ projects into $m$ clusters at leaf level, then if we analyze the average case complexity of the algorithm using the pseudo-code from \fig{Pseudo-code} average case complexity of this method (which we call GENERAL) is:
@@
 
-To operationalize steps 1,2,3,4,5 listed above, we need to make some lower-level engineering decisions. The rest of this section documents those decisions.
-
-\subsection{Feature Extraction}\label{sec:fx}
+To operationalize steps 1,2,3,4,5,6,7 listed above, we need to make some lower-level engineering decisions. The rest of this section documents those decisions.
+
+\subsection{Feature Extraction}
+\label{sec:fx}
 
@@
 about the  development process (e.g.    number of file revisions).
-Using the   Understand tool~\cite{visualize},
-we calculated different variations (i.e. average, max etc.) of 21 product and 5 process metrics to build defect prediction models
+ \respto{2-18}{\color{blue} Using the   Understand tool~\cite{visualize},
+we calculated different variations (i.e. average, max etc.) of 21 product and 5 process metrics, with a total 66 attributes/columns to build defect prediction models
  (see Table~\ref{tbl:metric}).
 These product  metrics are
- calculated from snapshots from every 6 months of the data.
-The process metrics are computed using the change history in the six-months period before the split date via manual collection of data using scripts.
-The data collected for this project is summarized in \fig{lang_projects}
+ calculated from snapshots of the projects from 6 months back of the last commit.
+The process metrics are computed using the change history in the six-months period before the split date via manual collection of data using scripts.} The data collected for this project is summarized in \fig{lang_projects}
  and \fig{meta}.
@@
 \subsection{Data Mining}\label{sec:dm}
-The bellwether analysis of step3 requires a working data miner. Three requirements for that learner are:
-\bi
-\item Since it will be called thousands of times, it must run quickly. Hence, we did not use any methods
+The bellwether analysis of step3 requires a working data miner framework. Three requirements for that data miner framework are:
+\bi
+\item Since it will be called thousands of times, the learner must run quickly. Hence, we did not use any methods
 that require  neural nets or ensembles. 
@@
 \item Since one of our research questions ({\bf RQ6}) asks ``what did we learn from all these projects'', we needed a learning method that generate succinct models.
-According, we used {\em feature selection}  to check which subset of Table~\ref{tbl:metric}
+Accordingly, we used {\em feature selection}  to check which subset of Table~\ref{tbl:metric}
 mattered the most.
 \ei
-According, this study used:
-\bi
-\item
-The logistic regression learner, \respto{1-5a} {\color{blue} since it is widely used in defect prediction~\cite{ghotra2015revisiting,XXX} in software engineering domain and it is relatively fast in terms of model building time than other learners such as Support Vector Machine, Random Forest, Artificial Neural Nets etc.
-tested on defect prediction.~\cite{ghotra2015revisiting};}
+In this study, we used:
+\bi
+\item
+The logistic regression learner, \respto{1-5a} {\color{blue} since it is widely used in defect prediction~\cite{ghotra2015revisiting,XXX} in the software engineering domain and, in our experience,
+in runs much faster (in terms of model building time) than many other learners such as Support Vector Machine, Random Forest, Artificial Neural Nets etc.
+(when tested on defect prediction).~\cite{ghotra2015revisiting};}
 \item
@@
 A model build on project with such skewed class distribution can result in a biased model towards the majority class (Such models can either have low recall or high recall with high pf).
-Thus we run SMOTE on the training data\footnote{While it is useful
+Thus we run SMOTE~\cite{tan2015online,wang2013using,sun2012using,khoshgoftaar2010attribute} on the training data\footnote{While it is useful
   to artificially boost the number of target examples
@@
 is endorsed by recent ICSE papers~\cite{Rahman:2013,ghotra2015revisiting,agrawal17}.
-As to CFS, we found that without it, our recalls were very low and we could not identify which metrics mattered the most.
+As to CFS, we found that without it, our recalls were very low (less than 20\%).
 Also,   extensive studies have found that CFS more useful than many other feature subset selection methods such as  PCA or InfoGain or RELIEF\respto{1-5e} {\color{blue}~\cite{hall1999correlation,challagulla2008empirical,arar2015software,lee2016developer,rodriguez2007attribute,gao2015combining,hosni2017investigating}.
@@
 
+\subsection{Implement Evaluation Criteria}
+\label{sec:Measures}
+
+In this section, we introduce the following 5 evaluation measures used in this study to evaluate the performance of machine learning models.
+Suppose we have a dataset with M changes and N defects.
+After inspecting 20\% LOC, we inspected $m$ changes and found $n$ defects.
+Also, when we find the first defective change, we have inspected k changes.
+Using
+this data, we can define 5 evaluation measures  as follows:
+{\color{blue}\respto{1-5f} 
+(1) \textbf{Recall:} This is the proportion of inspected defective changes among all the actual defective changes; i.e.
+$n/N$.
+This implicates in an ideal scenario where we identify all the actual target class as target class without missing the recall will be one.
+When recall is maximal, we are finding all  the target class.
+Recall is used in  many previous studies~\cite{kamei2012large,yang2016effort,yang2017tlel,xia2016collective,yang2015deep}.
+
+(2) \textbf{Precision:} This is the proportion of inspected defective changes among all the inspected changes; i.e.
+$n/m$.
+A low Precision indicates that developers would encounter more false alarms, which may have negative impact on developers' confidence on the prediction model.
+When precision is maximal, all the reports of defect modules are actually buggy (so the users waste no time looking at results that do not matter to them)
+
+(3) \textbf{pf:} This is the proportion of all suggested defective changes which are not actual defective changes among all the suggested defective changes.
+A high {\em pf} suggests developers will encounter more false alarms which may have negative impact on developers' confidence in the prediction model.
+
+(4) \textbf{popt20:} This is the proportion number of suggested defective changes among all suggested defective changes, when when 20\% LOC modified by all changes are inspected.
+A high {\em popt20} values mean that developers can find most bugs in a small percent of the code, thus effectively reducing the effort required to find bugs.
+To compute Popt20, we divided the test set into the modules predicted to be faulty (set1) and predicted to be bug-free (set2).
+Each set was then sorted in ascending order by lines of code.
+We then ran down set1, then set2, till 20\% of the total lines of code were reached-- at which point {\em popt20} is the percent of buggy modules seen up to that point.
+
+(5) \textbf{ifa\_auc:} Number of  initial false alarms encountered before we find the first defect.
+Inspired by previous studies on fault localization~\cite{parnin2011automated, kochhar2016practitioners, xia2016automated}, we caution that if the top-k changes recommended by the model are all false alarms, developers would be frustrated and are not likely to continue inspecting the other changes.
+Parnin and Orso ~\cite{parnin2011automated} found that developers would stop inspecting suspicious statements, and turn back to traditional debugging, if they could not get promising results within the first few statements they inspect.
+Using the nomenclature reported about {\em ifa$=k$}.
+In this study we use a modified version of {\em ifa} called ifa\_auc, which calculates {\em ifa} based on efforts spent on inspecting the code.
+We use gradually increment the efforts spent by increasing the total LOC inspected and calculate ifa on each iteration to get the area under the curve (auc), here the x-axis is the percentage of effort spent on inspection and y-axis is {\em ifa}.}
+
 \subsection{Select the Best Model}\label{sec:best}
@@
 
-To find the bellwether, our method must compare many models and select the best one based on the goals important for that task.
-
-In such   {\em multi-objective} problems, one model is better than another if it
+The previous section listed numerous goals that could be used to guide the learning. Combining
+numerous goals is often implemented as a multi-objective optimization predicate  one model is better than another if it
  satisfies a ``domination predicate''.
@@
  predictor~\cite{zit02} to select our bellwether (since this is known to select better models
- for 5-goal optimization~\cite{Sayyad:2013,Sayyad:2013:SPL}).
+ for multi-goal optimization in SE~\cite{Sayyad:2013,Sayyad:2013:SPL}).
 This predicate favors model
@@
 
-As discussed above, model performance can be scored and the best model can be chosen by researchers based on their choice of metrics.
-In this experiment we score model performance according to three goals i.e.
-recall, precision, pf, and chose the best model where we can:
-\bi
-\item
-\respto{1-5f} {\color{blue}Maximize
-recall\footnote{{\color{blue}Recall is the ratio between predicted actual target class examples vs all target class examples.
-In other words recall = $ \frac{TP}{TP+FN} $, which means in an ideal scenario where we identify all the actual target class as target class without missing the recall will be one.
-Thus to make a good predictor we need to maximize the recall}} and precision\footnote{{\color{blue}Precision is the ratio between predicted actual target class examples vs all predicted target class examples.
-In other words precision = $ \frac{TP}{TP+FP} $, therefore in an ideal scenario where we identify all the actual target class as target class without predicting any non-target class as target class the precision will be one.
-Thus to make a good predictor we need to maximize the precision as well}}
-%and popt(20)\footnote{{\color{blue}popt(20) is a cost sensitive productivity based metric, which represents the percentage of total defect identified by reading 20\% of the code.
-This means more defects we can identify by reading only 20\% of the code is better for the developers to localize and fix the defects.}}
-};
-\item
-\respto{1-5f} {\color{blue} While minimizing  false alarms\footnote{{\color{blue}false alarms (pf) is the ratio between non-target class identified as target class and total number of actual non-target class.
-IN other words false alarm = $ \frac{FP}{FP+TN} $, thus in an ideal scenario FP should be zero, thus not identifying and non-defective class as defective and effectively making false alarm as zero.}}
-%and ifa\_auc\footnote{{\color{blue}Need to describe ifa auc XXXX.}}
-.}
-\ei
-(For definitions and details for these criteria, and why we selected them, see \S\ref{sec:Measures}.)
-
+{\color{blue}\respto{1-5f} As discussed above, model performance can be scored and the best model can be chosen by researchers based on their choice of metrics.
+In this experiment we score model performance according to the goals mentioned in \S\ref{sec:Measures}.
+Here when assessing models, we  chose the best model that:}
+% \bi
+% \item {\color{blue}Recall is the ratio between predicted actual target class examples vs all target class examples; i.e.
+$ \frac{TP}{TP+FN} $, which means in an ideal scenario where we identify all the actual target class as target class without missing the recall will be one.
+% When recall is maximal, we are finding all  the target class.}
+% \item  {\color{blue} Precision is the ratio between predicted actual target class examples vs all predicted target class examples; i.e.
+$ \frac{TP}{TP+FP} $.
+When precision is maximal, all the reports of defect modules are
+% actually buggy (so the users waste no time looking at results that do not matter to them).}
+% \item {\color{blue}popt(20) is a cost sensitive productivity based metric, which represents the percentage of total defect identified by reading 20\% of the code.
+This means more defects we can identify by reading only 20\% of the code is better for the developers to localize and fix the defects.}
+% \item {\color{blue}ifa\_auc  is  XXX.}
+% \ei
+\bi
+\item
+{\color{blue}Maximize
+recall and precision and popt(20)}
+\item {\color{blue} Minimizes false alarm and ifa\_auc.}
+\ei
 % In such   {\em multi-objective} problems, one model is better than another if it
@@
 
+To Summarize, the algorithm works as follows -
+\bi
+\item The feature extraction algorithm extracts feature vectors for each project.
+\item A hierarchical clustering algorithm BIRCH, uses the feature vectors for each project as representative for the project to create a hierarchical cluster.
+This returns a clustering tree, which includes information regarding which projects are in a certain cluster, each clusters child clusters and parent clusters.
+\item Use the clustering tree to find clusters in leaf level of the tree, to run a all pair comparison within each cluster to select a best model aka ``Bellwether''. 
+\item We push up and store the bellwether found at leaf level to its parents.
+\item On the parent clusters we find the best models pushed from child nodes to run a all pair comparison between them to find the ``Bellwether'' in the parent clusters.
+\item We repeat the last 2 steps until we reach the root node.
+\item When we predict defects for a new project, we first check which cluster in each level it should belong to based on the BIRCH algorithm and then we predict the new project using that cluster's ``Bellwether'' at each level.
+\ei
+
 \section{Experimental Methods}
@@
 That is, hierarchical bellwethers can be recommended even if they {\em 
-perform  no better  than {\bf self}}. Rather:
-\bi
-\item
-As listed
-in the motivations of
-\S\ref{sec:Motivation}, we seek ways to make conclusions
-across a wide number of projects. 
-\item
-That is, our goal is to test if hierarchical bellwethers
+perform  no better  than {\bf self}}. Rather, our goal is to test if hierarchical bellwethers
 can quickly  find a  small set of {\em adequate conclusions}
 that hold across a large space 
-of projects. 
-\ei
-So, here, by ``adequate'', we mean conclusions
-that perform no worse than those found by other methods.
+of projects
+(and here, by ``adequate'', we mean conclusions
+that perform no worse than those found by other methods).
 
@@
 
-\subsection{Performance Measures}
-\label{sec:Measures}
-
-In this section, we introduce the following 5 evaluation measures used in this study to evaluate the performance of machine learning models.
+% \subsection{Performance Measures}
+% \label{sec:Measures}
+
+% In this section, we introduce the following 5 evaluation measures used in this study to evaluate the performance of machine learning models.
 Suppose we have a dataset with M changes and N defects.
@@
 Using
-this data, we can define 5 evaluation measures  as follows:
-
-(1) \textbf{Recall:} This is the proportion of inspected defective changes among all the actual defective changes; i.e. $n/N$.
-Recall is used in  many previous studies~\cite{kamei2012large,yang2016effort,yang2017tlel,xia2016collective,yang2015deep}.
-
-(2) \textbf{Precision:} This is the proportion of inspected defective changes among all the inspected changes; i.e.
+% this data, we can define 5 evaluation measures  as follows:
+
+% (1) \textbf{Recall:} This is the proportion of inspected defective changes among all the actual defective changes; i.e. $n/N$.
+% Recall is used in  many previous studies~\cite{kamei2012large,yang2016effort,yang2017tlel,xia2016collective,yang2015deep}.
+
+% (2) \textbf{Precision:} This is the proportion of inspected defective changes among all the inspected changes; i.e.
 $n/m$.
@@
 
-(3) \textbf{pf:} This is the proportion of all suggested defective changes which are not actual defective changes among all the suggested defective changes.
+% (3) \textbf{pf:} This is the proportion of all suggested defective changes which are not actual defective changes among all the suggested defective changes.
 A high {\em pf} suggests developers will encounter more false alarms which may have negative impact on developers' confidence in the prediction model.
 
-(4) \textbf{popt20:} This is the proportion number of suggested defective changes among all suggested defective changes, when when 20\% LOC modified by all changes are inspected. 
-A high {\em popt20} values mean that developers can find most bugs in a small percent of the code.
-To compute Popt20, we divided the test set into the modules predicted to be faulty (set1)
-and predicted to be bug-free (set2). Each set was then sorted in ascending order by lines 
-of code.  We then ran down set1, then set2, till 20\% of the total lines of code
-were reached-- at which point {\em popt20} is the percent of buggy modules seen up to that point.
-
-(5) \textbf{ifa\_auc:} Number of  initial false alarms encountered before we find the first defect.
+% (4) \textbf{popt20:} This is the proportion number of suggested defective changes among all suggested defective changes, when when 20\% LOC modified by all changes are inspected. 
+% A high {\em popt20} values mean that developers can find most bugs in a small percent of the code.
+% To compute Popt20, we divided the test set into the modules predicted to be faulty (set1)
+% and predicted to be bug-free (set2). Each set was then sorted in ascending order by lines 
+% of code.  We then ran down set1, then set2, till 20\% of the total lines of code
+% were reached-- at which point {\em popt20} is the percent of buggy modules seen up to that point.
+
+% (5) \textbf{ifa\_auc:} Number of  initial false alarms encountered before we find the first defect.
 Inspired by previous studies on fault localization~\cite{parnin2011automated, kochhar2016practitioners, xia2016automated}, we caution that if the top-k changes recommended by the model are all false alarms, developers would be frustrated and are not likely to continue inspecting the other changes.
@@
 {\color{blue} 
-\subsection*{RQ2: How  fast  is  new  bellwether  method  aka  GENERAL?}
+\subsection*{RQ2: How fast is GENERAL bellwether?}
 \label{sec:rq3}
@@
 
-\subsection*{RQ3: Can hierarchical clustering tame the complexity of bellwether-based reasoning?}
+\subsection*{RQ3: In practice,
+            can the hierarchical clustering of GENERAL tame slow runtimes seen in   bellwether-based reasoning?}
 \label{sec:rq3}
@@
 
-\fig{compare} shows the mean number of comparisons required for finding a bellwether using conventional bellwether versus GENERAL for different community size .
-
-\fig{time} shows the mean run times for one run of GENERAL versus traditional bellwether. For certification purposes, this had to be repeated 20 times. In that certification run:
+\fig{compare} shows the mean number of comparisons required for finding a bellwether using conventional bellwether versus GENERAL for different community size of 45,90, 180, 360 and 627 projects.
+We can see from the \fig{compare} for increasing community size the number of comparisons required increases rapidly for conventional bellwether, while with GENERAL the number of comparisons required are comparatively small.
+This shows the new bellwether method (aka GENERAL) is scalable with increasing community size.
+
+similarly \fig{compare_time} shows the mean run times for one run of GENERAL versus traditional bellwether for different community size of 45,90, 180, 360 and 627 projects.
+It is evident from the figure with growing community size the new bellwether method takes lesser amount of time ($\approx 4$ times faster in community size of 50 while $\approx 30$ times faster in a community size of 627 projects ).
+
+\fig{time} shows the mean run times for one run of GENERAL versus traditional bellwether (with SMOTE and CFS) for a community size of 627 projects .
+For certification purposes, this had to be repeated 20 times.
+In that certification run:
 
@@
 The $O(m*(N/m)^2)$ analysis
-of GENERAL needed 30  hours. That is, in empirical result consistent with the theoretical predictions of \fig{cost}, GENERAL runs much faster than traditional bellwether.
+of GENERAL needed 30  hours. That is, in empirical result consistent with the theoretical predictions of figure~\ref{fig:Pseudo-code}, GENERAL runs much faster than traditional bellwether.
 \item 
@@
   & 1 &      ZeroR &    0 &  100 & \quart{0}{0}{100}{100} \\
-  & 1 &      BUBBLE\_level2 &    33 &  63 & \quart{0}{33}{63}{30} \\
+  & 1 &      GENERAL\_level2 &    33 &  63 & \quart{0}{33}{63}{30} \\
   & 1 &      bellwether0 &    38 &  55 & \quart{5}{38}{55}{22} \\
-  & 2 &      BUBBLE\_level1 &    50 &  54 & \quart{20}{50}{54}{24} \\
-  & 3 &      BUBBLE\_level0 &    57 &  47 & \quart{36}{57}{47}{25} \\
+  & 2 &      GENERAL\_level1 &    50 &  54 & \quart{20}{50}{54}{24} \\
+  & 3 &      GENERAL\_level0 &    57 &  47 & \quart{36}{57}{47}{25} \\
   & 3 &      self &    57 &  34 & \quart{41}{57}{34}{17} \\
@@
   & 1 &      ZeroR &    0 &  100 & \quart{0}{0}{100}{100} \\
-  & 1 &      BUBBLE\_level2 &    21 &  43 & \quart{0}{21}{43}{22} \\
+  & 1 &      GENERAL\_level2 &    21 &  43 & \quart{0}{21}{43}{22} \\
   & 1 &      bellwether0 &    25 &  45 & \quart{0}{25}{45}{20} \\
   & 1 &      self &    25 &  23 & \quart{17}{25}{23}{15} \\
-  & 1 &      BUBBLE\_level1 &    33 &  41 & \quart{10}{33}{41}{18} \\
-  & 2 &      BUBBLE\_level0 &    45 &  43 & \quart{24}{45}{43}{22} \\
+  & 1 &      GENERAL\_level1 &    33 &  41 & \quart{10}{33}{41}{18} \\
+  & 2 &      GENERAL\_level0 &    45 &  43 & \quart{24}{45}{43}{22} \\
   & 3 &      global &    100 &  17 & \quart{83}{100}{17}{0} \\ \hline
@@
   & 2 &      bellwether0 &    36 &  63 & \quart{4}{36}{63}{31} \\
-  & 2 &      BUBBLE\_level2 &    36 &  65 & \quart{0}{36}{65}{29} \\
-  & 2 &      BUBBLE\_level1 &    41 &  54 & \quart{13}{41}{54}{26} \\
-  & 2 &      BUBBLE\_level0 &    41 &  47 & \quart{20}{41}{47}{26} \\
+  & 2 &      GENERAL\_level2 &    36 &  65 & \quart{0}{36}{65}{29} \\
+  & 2 &      GENERAL\_level1 &    41 &  54 & \quart{13}{41}{54}{26} \\
+  & 2 &      GENERAL\_level0 &    41 &  47 & \quart{20}{41}{47}{26} \\
   & 2 &      self &    50 &  44 & \quart{28}{50}{44}{23} \\ \hline
@@
   & 1 &      ZeroR &    0 &  28 & \quart{0}{0}{28}{28} \\
-  & 2 &      BUBBLE\_level2 &    28 &  41 & \quart{0}{28}{41}{12} \\
+  & 2 &      GENERAL\_level2 &    28 &  41 & \quart{0}{28}{41}{12} \\
   & 2 &      global &    28 &  14 & \quart{20}{28}{14}{5} \\
   & 2 &      bellwether0 &    31 &  42 & \quart{0}{31}{42}{11} \\
-  & 2 &      BUBBLE\_level0 &    31 &  16 & \quart{23}{31}{16}{8} \\
-  & 2 &      BUBBLE\_level1 &    31 &  23 & \quart{17}{31}{23}{9} \\
+  & 2 &      GENERAL\_level0 &    31 &  16 & \quart{23}{31}{16}{8} \\
+  & 2 &      GENERAL\_level1 &    31 &  23 & \quart{17}{31}{23}{9} \\
   & 3 &      self &    36 &  20 & \quart{27}{36}{20}{11} \\ \hline
@@
   & 2 &      global &    15 &  29 & \quart{6}{15}{29}{20} \\
-  & 3 &      BUBBLE\_level2 &    21 &  21 & \quart{11}{21}{21}{11} \\
+  & 3 &      GENERAL\_level2 &    21 &  21 & \quart{11}{21}{21}{11} \\
   & 3 &      bellwether0 &    22 &  21 & \quart{13}{22}{20}{11} \\
   & 3 &      self &    22 &  17 & \quart{15}{22}{17}{9} \\
-  & 3 &      BUBBLE\_level1 &    23 &  20 & \quart{14}{23}{20}{11} \\
-  & 3 &      BUBBLE\_level0 &    24 &  21 & \quart{14}{24}{21}{12} \\
+  & 3 &      GENERAL\_level1 &    23 &  20 & \quart{14}{23}{20}{11} \\
+  & 3 &      GENERAL\_level0 &    24 &  21 & \quart{14}{24}{21}{12} \\
 \end{tabular}}}
@@
 \caption{Statistical Results comparison. The ``rank`` column at left comes from
-the statistical analysis methods of \S\ref{eval}. Note that for {\em pf}, and {\em ifa} rank=1 is the best rank while for all other performance measures, ranks $\in{3,4}$ are best. 
+the statistical analysis methods of \S\ref{eval}.
+Note that for {\em pf}, and {\em ifa}, which we want to minimize, low rank (i.e.
+rank=1) is the best rank while for other performance measures where we want to maximize, ranks  such as $\in{3,4}$ are better.
 }\label{fig:Statistical}
@@
 
+%XXX GL1: worse at nothing, statistically better of recall and pf
+
+% 5XXX RQ5 is very short.
+
 \begin{RQ}
@@
 
+\respto{2-21}{\color{blue}
 This sections ask if conclusions always improve as we learn from more and more data.
@@
 inappropriately applied to the present situation.  
+This is a special problem that arises when combining old data  with new data.}
 
@@
 \ei
+
+To put that another way, the answer to ``is is possible to learn from too much data'', is ``depends on what you value'':
+\respto{3-13}{\color{blue}
+\bi
+\item
+For risk-adverse development, it is best to use all data to learn the bellwether
+since that finds most defects.
+\item
+On the other hand, for cost-adverse development (where cutting development cost
+is more important than removing
+bugs), then there seems to be a ``Goldilocks zone'' where
+the bellwether is learned from just enough data (but not too much or too little).
+\ei
+}
 That is, these results say that:
@@
 \end{RQ}
-
-To put that another way, the answer to ``is is possible to learn from too much data'', is ``depends on what you value'':
-\bi
-\item
-For risk-adverse development of mission or safety critical
-systems, it is best to use all data to learn the bellwether
-since that finds most defects.
-\item
-On the other hand, for cost-adverse development of non-critical
-systems (where cutting development cost
-is more important than removing
-bugs), then there seems to be a ``Goldilocks zone'' where
-the bellwether is learned from just enough data (but not too much or too little).
-\ei
 
@@
 we can say that for predicting defects, in this sample of  features taken from 627 projects:
-\bi
-\item Issues of inter-class interface are paramount;
-\item While many other  issues are far less important such as file size, depth of inheritance tree, intra-method complexity, file size, revision history, and anything relating to  the other features of Table~\ref{tbl:metric}
-that are not listed in Table~\ref{tbl:coefs}.
-\ei
 In summary:
@@
 \begin{RQ}
-{\respto{2-9}\respto{3-13} {\color{blue}The importance of many key features is not apparent at the local
-project level.
-To fully understand the effect of certain attributes (key features) on defect prediction and bug localization, it is necessary to analyze hundreds of projects together to identify a single bellwether.
-This bellwether will act as an exemplary model to identify such key features in defect prediction models.}}
-
-% To fully appreciate the critical impact on defects
-% of class interface design,  it is necessary to conduct
-% a global analysis across hundreds of projects. }
+{\respto{2-9} {\color{blue}In terms of defect prediction,
+issues of inter-class interface are paramount.
+Many other  issues are far less important such as file size, depth of inheritance tree, intra-method complexity, file size, revision history.}}
 \end{RQ}
-To say that another way, 
-\begin{quote}
-{\em 
-Learning from many other projects can be better than learning just from your own local project data.
-}\end{quote}
 
@@
 This work was partially funded by NSF Grant \#1908762.
-\balance
+
 \bibliographystyle{IEEEtran}
 \bibliography{main} 
-
+\newpage
+\begin{minipage}{\linewidth}
 \begin{IEEEbiography}[{\includegraphics[width=1in,clip,keepaspectratio]{figs/suvodeep.JPG}}]{Suvodeep Majumder}
@@
 \end{IEEEbiography}
-
+\end{minipage}
+
+\newpage
 \input{response.tex}

### 2020-04-17 response.tex
Updates from Overleaf

@@
 several mistakes, that have been fixed here.
-\bi
-\item We assumed that the  core motivation for this work
-was widely known and accepted in the community. That was a mistake. This draft completely rewrites the Introduction
+For example,  we assumed that the  core motivation for this work
+was widely known and accepted in the community. That was a mistake so this draft completely rewrites the Introduction
 to include much more background information on the 
-presence of the problem studied here.
-\item Cascading on from that first mistake, we made several
-mistakes with how we framed   our research questions. This
-draft fixes those errors. This has the added benefit
-of clarifying our discussion
-along the way.
-\ei
-Apart from these two points we have also addressed
+presence of the problem studied here.}
+
+\response{Next, using reviewer feedback, we can now better frame
+our  research questions (this has the added benefit
+of clarifying our discussion).}
+
+\response{Apart from these two points, we have also addressed
 the many helpful and detailed comments from the reviewers:
@@
 \item The problem statement has been  clarified and properly positioned (R1, R3).
-\item The novelty of the approach has  been clarified (R3). (see \bareresp{3-1})
-\item Using comments from  (R1, R2, R3), we have made numerous small editorial improvements.
+\item The novelty of the approach has  been clarified (R3). (see our comments to Reviewer3, in \bareresp{3-1},
+below)
 \item The study now includes all the details to ensure 
 replicability   (R1, R2).
-\item The results of the study need to be revisited since the reviewers are not convinced that the results support the claims in the paper (R1, R2, R3).
-\item The background on transfer learning has been augmented with more  citations (R2).
+\item The results of the study were   be revisited and clarified. 
+\item The background on transfer learning has been augmented, with more  citations (R2).
+\item Using comments from  (R1, R2, R3), we have made numerous small editorial improvements.
 \ee
@@
 \item
-Consequently,this draft completely rewrites the Introduction
+Consequently, this draft completely rewrites the Introduction
 to include much more background information on the 
@@
 
-\response{(1.1b)You are quite correct, we did not define bellwether till very late in the prior draft. In this draft, we define bellwether on page 1\citeresp{1-1a}}
+\response{You are quite correct, we did not define bellwether till very late in the prior draft. In this draft, we define bellwether on page 1\citeresp{1-1a}} where we say:
 
 \begin{quote}
-    \response{``bellwether'' is a project from a community of N projects, whose data yields the best analytic (i.e.
-defect prediction, effort estimation etc) on all others.
-(the bellwether is the  leading sheep of a flock, with a bell on its neck)}
+    \response{Given a community of projects developed by the same organization,
+the ``bellwether'' is a project or a handful of projects
+whose data yields the best analytic (i.e. defect prediction, effort estimation, etc) on all others}\footnote{We call that the ``bellwether'' since that is the
+name of the  leading sheep of a flock, with a bell on its neck.}
 \end{quote}
@@
 \response{Thank you for your comments.
- On review, we found that core problem of conclusion instability
-was not well documented in the introduction. This new draft fixes that problem with a completely new
-introduction that better focuses the work on conclusion instability and scalability.}
+ On review, we found that the core problem of conclusion instability
+was not well documented in the introduction.
+This new draft fixes that problem with an extensively revised introduction~\citeresp{1-2} that better focuses the work on conclusion instability and scalability.}
 
@@
 \response{Thank you for your comment. We agree.   Much of the new
-text on page1 takes care to document {\em why }
+text on page1 ~\citeresp{1-3a} takes care to document {\em why }
 we are exploring conclusion instability before
@@
 
-\response{ Thank you for your comment, You are right.In this manuscript we have deleted the  superlatives (including that one)}
+\response{ Thank you for your comment, You are right. In this manuscript, we have deleted the  superlatives (including that one)}
 
@@
 
-\response{ Thank you for your comment, you are quite right. We had not properly mentioned the reason behind choosing logistics regression.  In this draft we have added the reasons to \citeresp{1-5a}:}
+\response{ Thank you for your comment, you are quite right.
+We had not properly mentioned the reason behind choosing logistics regression.
+In this draft, we have added the reasons to \citeresp{1-5a}:}
 
@@
 \response{
-"The logistic regression learner,  since it is widely used in defect prediction~\cite{ghotra2015revisiting} in   the  software engineering domain and, in our experience,
-in runs much faster (in terms of model building time) than many other learners such as Support Vector Machine, Random Forest, Artificial Neural Nets etc. (when tested on defect prediction).}
+"The logistic regression learner,  since it is widely used in defect prediction~\cite{ghotra2015revisiting,zhang2017data,he2012investigation,nam2013transfer,pan2010domain} in   the  software engineering domain and, in our experience,
+it runs much faster (in terms of model building time) than many other learners such as Support Vector Machine, Random Forest, Artificial Neural Nets etc, (when tested on defect prediction).}
 \end{quote}
@@
 \response{You are right, we had not included the reason for using SMOTE in our algorithm and had not explained why the problem is unbalanced.
-In this draft we have added notes to answer those questions \citeresp{1-5b}:}
+In this draft, we have added notes to answer those questions \citeresp{1-5b}:}
 \begin{quote}
-    \response{The SMOTE class imbalance correction algorithm~\cite{Chawla2002}, since many of the projects have relatively very few or large number of defects.
-A model build on project with such skewed class distribution can result in a biased model towards the majority class (Such models can either have low recall or high recall with high pf).
+    \response{(we used)...
+The SMOTE class imbalance correction algorithm~\cite{Chawla2002} since many of the projects have relatively very few or a large number of defects.
+A model built on a project with such skewed class distribution can result in a biased model towards the majority class (Such models can either have a low recall or a high recall with high pf).
 Thus we run SMOTE on the training data to artificially boost the number of target examples in the training data and achieving balanced recall and pf for the minority class test examples}
@@
 
-\response{You are quite correct, we did not included the details about how the features are being removed and why in the last draft.
-In this draft we have included notes regarding how CFS works and why the features that are not used are removed \citeresp{1-5b}:}
+\response{You are quite correct, we did not include the details about how the features are being removed and why in the last draft.
+In this draft, we have included notes regarding how CFS works and why the features that are not used are removed \citeresp{1-5b}:}
 
@@
 The features which are  highly correlated with each other will not add more information while making classification, while the features which are uncorrelated towards the classification also not add more information while making classification.
-The CFS algorithm incrementally picks one feature at a time which adds the most information towards the classification at a given step and stops when there is no more improvement in the score.}
+The CFS algorithm incrementally picks one feature at a time which add the most information towards the classification at a given step and stops when there is no more improvement in the score.}
 \end{quote}
 
-\response{As to what attributes were selected, please see Figure~\ref{fig:FSS_compare}. As to what of
-the selected figures were most important, please see Table~\ref{tbl:coefs}.}
+\response{As to what attributes were selected, please see Figure~\ref{fig:FSS_level1}. As to what of
+the selected figures were most important, please see Table~\ref{tbl:coefs_4}.}
 
@@
 
-\response{Thank you for your comment, using the replication package (including data) the experiments can be reproduced.\citeresp{1-5d}.  Also, we have added in specific numbers to that sentence:
+\response{Thank you for your comment, using the replication package (including data) the experiments can be reproduced \citeresp{1-5d}.  Also, we have added in specific numbers to that sentence:
 \begin{quote}
@@
 
-\response{Thank you for that comment.  You are quite correct-- we did not document the all the necessary citations for supporting our claim before. We have added the following note to \citeresp{1-5e}}
+\response{Thank you for that comment.  You are quite correct-- we did not document all the necessary citations for supporting our claim before. We have added the following note to \citeresp{1-5e}}
+
+\begin{quote}
+    {\color{blue}Also,   extensive studies have found that CFS more useful than many other feature subset selection methods such as  PCA or InfoGain or RELIEF\respto{1-5e} ~\cite{hall1999correlation,challagulla2008empirical,arar2015software,lee2016developer,rodriguez2007attribute,gao2015combining,hosni2017investigating}.
+}
+\end{quote}
 
@@
 
-\response{Thank you for your comment, we didn't explained why these metrics need to be maximized, added necessary details\citeresp{1-5f}.}
+\response{Thank you for your comment, we didn't explain why these metrics need to be maximized, For those notes, please see \citeresp{1-5f} and \citeresp{1-5g}.}
 
@@
 
-\response{Thank you for your comment, we didn't explained why these metrics need to be minimized, added necessary details\citeresp{1-5f}.}
+\response{Thank you for your comment, we didn't explain why these metrics need to be maximized, For those notes, please see  \citeresp{1-5f} and \citeresp{1-5g}.}
 
@@
 \response{Thank you for that comment.
-You are quite correct-- we did not include in depth steps to replicate the study before.
-We have added a replication package in contribution section \citeresp{1-5h} as well as more in depth details about the algorithm has been added in figure~\ref{fig:Pseudo-code} and section~\ref{GENERAL}.}
+You are quite correct-- we did not include in-depth steps to replicate the study before.
+We have added a replication package in contribution section \citeresp{1-5h} as well as more in-depth details about the algorithm has been added in Figure~\ref{fig:Pseudo-code} and section~\ref{GENERAL}.}
 
@@
 \response{You are quite correct.
-In the last draft we indeed did not included detailed analysis of the results to show the scalability of our model.
+In the last draft we indeed did not include a detailed analysis of the results to show the scalability of our model.
 In this draft \citeresp{1-2}\citeresp{1-6a} we have included 2 more research questions (RQ1 and RQ2) to show the conventional bellwether is slower than the new bellwether (aka GENERAL) method.
-We also have updated another research question (RQ3) to compare the methods in-term of number of comparisons and time taken to run the two methods, as can been seen in figure~\ref{fig:compare} and \ref{fig:compare_time}.}
+We also have updated another research question (RQ3) to compare the methods in-term of number of comparisons and time taken to run the two methods, as can been seen in Figures~\ref{fig:compare_time} and
+\ref{fig:compare}.}
 
-\review{(1.6b)
-The same is true for the other research questions. And, in general, there is qualitative analysis: Why are the results the ones reported in the paper?}
-
-\response{You are right,Thank you for that comments. We have added much  quantitative analysis as
-well as statistical tests to this paper. Please see Figures~\ref{fig:compare_time} and ~\ref{fig:compare}.}
-
-\review{(1.6c) What makes the reported method scalable?}
+\review{(1.6b) What makes the reported method scalable?}
 
 \response{Thank you for your comment, in this version we have updated the RQ3 to show that our method is scalable.
-We have showcased the analysis of number of comparisons and run time between the two algorithm (conventional bellwether and GENERAL) using various community size.}
+We have showcased the analysis of number of comparisons and run time between the two algorithms (conventional bellwether and GENERAL) using various community sizes.}
 
@@
 \response{Thank you very much for your detailed review.
-As we said to the associated editor, the previous draft made the following mistake:
-\bi
-\item We assumed that the  core motivation for this work
-was widely known and accepted in the community. That was a mistake. 
+As we said to the associated editor, the prior draft  assumed that the core motivation for this work was widely known and accepted in the community.
+That was a mistake so this draft completely rewrites the Introduction to include much more background information on the presence of the problem studied here.
+Also, thanks to your feedback,
+we have made some additional corrections, clarifications, and revisions, as directed by your comments.
+Please note that to assist in your review, we refer to specific locations of each of the changes using the notation \respto{2-XX}.}
+
+\response{Before going on, we need to ask you one thing.
+\begin{itemize}
 \item
-Consequently,this draft completely rewrites the Introduction
-to include much more background information on the 
-presence of the problem studied here.
-\ei
-We have made some additional corrections, clarifications, and revisions, as directed by your comments.
-To assist in your review, we refer to specific locations of each of the changes using the notation \respto{1-XX}.}
-
-% Many of your comments take issue with two terms used in this paper "lessons learned" and "transfer learning".
-% We agree with you that our use of "lessons learned" was inappropriate and we have removed all those usages.
+Several   of your comments take issue with two terms used in this paper ``lessons learned'' and "transfer learning".
+We agree with you that our use of ``lessons learned" was inappropriate and we have removed all terms from this paper.
+\item
+But as to your argument that our use of ``transfer learning'' is  incorrect, that is not clear to us. 
+As near as we can tell, our use of transfer learning is compatible with standard definitions in that field, both outside
+of SE (e.g. Pan's paper~\cite{pan2009survey})
+and within the SE literature~\cite{ma2012transfer,zimmermann2009cross,turhan2009relative,krishna2018bellwethers,jing2015heterogeneous,he2014towards,nam2017heterogeneous,cheng2016heterogeneous,yu2017feature}.
+Also, reading through your comments, one thing that strikes us is that perhaps you are reserving the use of ``transfer learning''   only  to heterogeneous learning (where the source and target have different attributes)?
+If so, then perhaps
+  \S\ref{tion:how1} is relevant since, in that section, we carefully define and distinguish between homogeneous and heterogeneous transfer learning and clearly state that this paper 
+is about homogeneous learning, where the attributes are the same in source and target.   
+\item
+That said, we want to work with you on this point. Is there another term you would accept that is not ``lessons learned'' or ``transfer learning''?
+Would the terms ``generalize'' or ``extend'' work for you? Please advise.
+\end{itemize}}
 
@@
 \begin{quote}
-    \response{``bellwether'' is a project from a community of N projects, whose data yields the best analytic (i.e. defect prediction, effort estimation etc) on all others.} 
+    \response{(a) `Given a community of projects developed by the same organization,
+the ``bellwether'' is a project or  a handful of projects
+whose data yields the best analytic (i.e. defect prediction, effort estimation, etc) on all others.} 
 \end{quote}
 \begin{quote}
-    \response{Also, to answer your second question, ``…the bellwether is equivalent to the other models'' has been replaced with ``....since the bellwether is an exemplar projects for the community of N projects seen so far...''  }
+    \response{Also, to answer your second question, ``…the bellwether is equivalent to the other models'' means ``bellwether is an exemplar project for the community of N projects seen so far''  }
 \end{quote}
@@
 To answer the first question, the projects can be completely new projects, without any historical data collected for reference.
-To answer the second question, in this research the experiments has been designed to simulate a situation, where there are known projects in a large community as well as a set of new projects which are not part of the community.
+To answer the second question, in this research the experiments have been designed to simulate a situation, where there are known projects in a large community as well as a set of new projects which are not part of the community.
 We do this by dividing the 697 projects into two sets 1) {\em Train 1}: a community 627 projects, from which we will select a bellwether and 2) {\em Train 2}: a set of 70 new projects, which will be tested using bellwether.}
@@
 As you point out, the prior draft
-was too value on this point.
+was too vague on this point.
 This paper now focuses on defect prediction (see the new title).}
@@
 your question (about whether
-or not the the bellwether changes
+or not the bellwether changes
 per goal), it is possible that another
@@
 
-\response{You are correct. Deleted. }
+\response{You are correct. We have deleted Figure 1 from this manuscript. }
 
@@
 very large difference (as witnessed
-by P  Figures~\ref{fig:compare_time} and ~\ref{fig:compare}.) }
+by  Figures~\ref{fig:compare_time} and ~\ref{fig:compare}.) }
 
@@
 
-\response{All our current numbers now say 697.}
+\response{Yes, are correct. That was our mistake. All our current numbers now say 697.}
 
@@
 
-\response{You are correct. We have reworded the wording of the box under RQ4, which was confusing. We have simpler text now \citeresp{2-9}.}
+\response{You are correct-- that text was confusing. In this reworked version, that text is removed. .}
 
@@
 \response{
-Thank you for that comment. We deleted it.}
+Thank you for that comment. We have deleted it.}
 
@@
 \fig{meta} shows the distribution of number of rows in each projects, which is a snapshots of the projects from 6 months back of the last commit.
-We can see from the \fig{meta} median number of rows is around 120 in this group of 697 projects explored.}
+We can see from the \fig{meta} median number of rows is around 120 in this group of 697 projects explored.
+We have also added following notes to~\citeresp{2-18} to explain the metrics collected:}
 
 \begin{quote}
-    \response{Using the   Understand tool~\cite{visualize},
+    \response{...using the   Understand tool~\cite{visualize},
 we calculated different variations (i.e. average, max etc.) of 21 product and 5 process metrics, with a total 66 attributes/columns to build defect prediction models
@@
 
-\response{Thank you for your comment, the figure Fig.
-6 (now Fig~\ref{fig:time}) is important as this figure shows the difference of time taken for each method.
-XXXXXXX include with updated charts.XXXXXXX}
+\response{Thank you for your comment, the Figure Figure 6 has been removed from this version.
+We have included Figure~\ref{fig:compare_time} which shows the time taken by traditional bellwether and GENERAL (without CFS and SMOTE) with increasing project community size.
+these two figures are important to showcase the scalability of the new bellwether method aka GENERAL.}
 
@@
 \response{Thank you very much for your detailed review.
-As we said to the associated editor, the previous draft made the following mistake:
-\bi
-\item We assumed that the  core motivation for this work
-was widely known and accepted in the community. That was a mistake. 
-\item
-Consequently,this draft completely rewrites the Introduction
-to include much more background information on the 
-presence of the problem studied here.
-\ei
-We have made some additional corrections, clarifications, and revisions, as directed by your comments.
-To assist in your review, we refer to specific locations of each of the changes using \respto{1-XX}.}
+As we said to the associated editor, the prior draft  assumed that the core motivation for this work was widely known and accepted in the community.
+That was a mistake so this draft completely rewrites the Introduction to include much more background information on the presence of the problem studied here.
+Also, thanks to your feedback,
+we have made some additional corrections, clarifications, and revisions, as directed by your comments.
+Please note that to assist in your review, we refer to specific locations of each of the changes using the notation \respto{3-XX}.}
 
@@
 As far as I understand, hierarchical clustering is a well-known, standard, and largely-evaluated clustering algorithm.
-I don’t really see the need to rebrand it with a new name.
+I don’t really see the need to re brand it with a new name.
 What is the difference between GENERAL and hierarchical clustering other than the GENERAL is applied to defect prediction?}
@@
 
-\response{With respect, we are unclear on this comment. As shown by our precision, recall, false alarm, etc results what this paper
-shows is that we can make general conclusions across this space of projects. And, elsewhere, bellwethers have worked to generate
-configurations for cloud-based tools~\cite{krishna2019whence},
-effort estimation, predicting Github issue close time, and
-code bad smell detection~\cite{krishna2018bellwethers,krishna2017simpler, nair19a, krishna16, krishna16a}.
-So we would characterize bellwethers as method that has been demonstrated useful in many domains.
-However, and this is the point of this paper, the existing  method does not scale to large data sets.
-Hence, this paper.}
+\response{We are not very clear on this comment.
+In our view,   bellwethers are a method that has been demonstrated useful in many domains. 
+As shown by our precision, recall, false alarm, etc results, this paper
+shows that we can make general conclusions across this space of projects.}
+
+\response{Also, in other papers\cite{krishna2018bellwethers,krishna2017simpler, nair19a, krishna16, krishna16a}, we have shown that
+ bellwethers have worked to generate:
+\begin{itemize}
+\item
+configurations for cloud-based tools~\cite{krishna2019whence}
+(this recently got accepted to TSE);
+\item 
+effort estimation;
+\item
+predicting Github issue close time, 
+\item
+code bad smell detection.
+\end{itemize}
+}
+
+\response{
+However, and this is the point of this paper, the existing  method does not scale to large data sets. Hence, this paper.}
 
@@
 
-\response{unclear on this. zeroR tells us that it is not enough to do simple things. Not sure how to answer.XXXX}
+\response{Thank you for your comment.
+In this study, ZeroR is a method where we predict everything as majority class.
+This effectively means for any project where in the training data majority of the modules are defective, all test data will be predicted as defective (increasing pf and lower precision) and vice-versa if majority of the modules are non-defective.
+The dataset we are working with more then 50\% of the projects has less than 50\% defective modules.
+So ZeroR will detect no defects in all these projects (Figure~\ref{fig:Statistical} show the median recall is zero precisely for this reason).
+This is the reason we can't use ZeroR as a recommended model.
+We have added notes on that in \S\ref{sec:isk} and \citeresp{3-9}.}
 
@@
 We used arithmetic mean and standard deviation as our metrics to showcase our result in the last manuscript, which may be affected by outliers and skew the results.
-In this manuscript, we have replaced arithmetic mean and standard deviation with median and IQR in figure~\ref{fig:Statistical}.}
+In this manuscript, we have replaced arithmetic mean and standard deviation with median and IQR in Figure~\ref{fig:Statistical}.}
 
@@
 \response{Thank you for your comments.
-The Fig~\ref{fig:Statistical} is a form of boxplot, where the black dot represents the median and the spread of the black line represents the 25th and 75th percentile of the data.
+The Fig~\ref{fig:Statistical} is a form of box-plot, where the black dot represents the median and the spread of the black line represents the 25th and 75th percentile of the data.
 Also note that the ranks we offer in that figure (in the left-hand-column) are generated via non-parametric statistics
-(bootstrap and the A12 effect size test) that do not assume gaususians.}
+(bootstrap and the A12 effect size test) that do not assume Gaussian.}
 
@@
 \response{Thank you for your comments, in the last manuscript we did not properly explained why the model ZeroR can not be recommend.
-We have updated the figure~\ref{fig:Statistical} to replace arithmetic mean and standard deviation with median and IQR.
-We can see from the figure~\ref{fig:Statistical}, the ZeroR model has a recall and pf of zero with IQR diff between 75th and 25th percentile as 100, which signifies as the model either predicts everything as defective or non-defective it will not be able to predict any defective module at all if the defect ratio is less than 50\%, while for projects with defect ratio is more than 50\% it will predict everything as defective with high false positive.}
+We have updated the Figure~\ref{fig:Statistical} to replace arithmetic mean and standard deviation with median and IQR.
+Figure~\ref{fig:Statistical} shows ZeroR model has a median recall and pf of zero with IQR diff between 75th and 25th percentile as 100.
+This result signifies the model either predicts everything as defective or non-defective.
+This is because ZeroR is a method where we predict everything as majority class.
+This effectively means for any project where in the training data majority of the modules are defective, all test data will be predicted as defective (increasing pf and lower precision) and vice-versa if majority of the modules are non-defective.
+In the dataset that we have used more then 50\% of the projects has less than 50\% defective modules, thus in result the median recall, precision and pf is zero.}
 
@@
 
-\response{Thank you for your valuable comments, the text for section~\ref{sec:rq6} was indeed confusing, we have made appropriate changes to better explain our analysis of a general defect prediction model learned by analyzing 627 projects.
-We have also removed any ambiguous keyword which might not be appropriate in this context.
-The changes has been added in \citeresp{3-13}.}
+\response{Thank you for your valuable comments, the text for section~\ref{sec:rq6} was indeed confusing. We have removed that confusing terminology.}

### 2020-04-17 manuscript.tex
Updates from Overleaf

@@
 %\usepackage{cleveref}
-\usepackage{colortbl}
+% \usepackage{colortbl}
 \newmdenv[
@@
 \usepackage{colortbl} 
-\usepackage{subcaption}
+% \usepackage{subcaption}
 \usepackage{blindtext, graphicx}
 \usepackage{textcomp}
-\usepackage{mathtools}
+% \usepackage{mathtools}
 \usepackage[hidelinks]{hyperref}
@@
 \usepackage[final]{listings}
-\usepackage{graphicx} 
-\usepackage{multirow}
+% \usepackage{graphicx} 
+% \usepackage{multirow}
 \usepackage{balance}
@@
 \DeclarePairedDelimiter\abs{\lvert}{\rvert}%
-\usepackage{array}
+% \usepackage{array}
 \usepackage{makecell}
@@
 \usepackage[export]{adjustbox}
-\usepackage{mathtools}
+% \usepackage{mathtools}
 \setlength{\belowcaptionskip}{-10pt}
@@
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
-\definecolor{lightgray}{gray}{0.8}
+% \definecolor{lightgray}{gray}{0.8}
 \definecolor{LightCyan}{rgb}{0.88,1,1}
@@
 \definecolor{MyDarkBlue}{rgb}{0,0.08,0.45} 
-\definecolor{pink}{RGB}{231,95,110}
+\definecolor{pink}{rgb}{231,95,110}
 \definecolor{lightergray}{rgb}{0.85, 0.85, 0.85}
@@
   keywordstyle=\color{pink}\bfseries\sffamily\fontsize{2.8mm}{0.6em},
-  emph={train, predict, add_samples, FindBellwether, BEETLE, get_cost, sample, get_perf, remove_non_bellwethers, LinearTransform, GPTransform,General,get_featrures,BIRCH,bellwether,get_bellwethers,O(N)},
+  emph={train, predict, add_samples, FindBellwether, BEETLE, get_cost, sample, get_perf, remove_non_bellwethers, LinearTransform, GPTransform,General,get_featrures,BIRCH,bellwether,get_bellwethers,O(N), if, else, in,for, return},
   emphstyle=\bfseries\color{blue!50!black} ,
@@
 
+\newcommand{\bluecheck}{}%
+\DeclareRobustCommand{\bluecheck}{%
+  \tikz\fill[scale=0.4, color=blue]
+  (0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;%
+}
+
 \newcommand{\response}[1]{\textcolor{blue}{#1}}
@@
 \begin{bclogo}[couleur=gray!20,%
-                arrondi=0.1,logo=\bctrombone,% 
+                arrondi=0,logo=\none,% 
                 ombre=true%
@@
 \newcommand{\flash}{{\sc Flash}\xspace}
-\usepackage{soul}
+% \usepackage{soul}
 \usepackage{color}
@@
 
-\usepackage{amsmath}
+% \usepackage{amsmath}
 \definecolor{Gray}{gray}{0.95}
-\definecolor{LightGray}{gray}{0.975}
+% \definecolor{LightGray}{gray}{0.975}
 
@@
 
+\usepackage{tcolorbox}
+\newtcolorbox{blockquote}{colback=black!5,boxrule=0.4pt,colframe=black,fonttitle=\bfseries}
+
 \begin{document}
@@
 \begin{abstract}
-% \respto{2-22}{\color{blue}Given a group of software projects,
-% there often exists  one   exemplar project
-% that offers the best prediction for all others.
-% Such ``bellwether projects''
-% can be used to make quality predictions that are general
-% to that group.}
-% Existing  methods  for  finding bellwether  are  very slow.
-When  applied  to  the  697  projects  studied  here, standard bellwether methods   took  60  days  of  CPU  to  find  and  certify  the  bellwethers
-% Hence,we  propose a faster way to find bellwethers. 
-% GENERAL applies hierarchical clustering to groups of project data.
-At each level within a tree of clusters, one bellwether is computed from sibling projects, then promoted up the tree.
-This hierarchical method is a scalable approach to learning effective models from very
-% large data sets. For  hundreds of projects, the defect prediction models generated from GENERAL's bellwether were just as good as those found via  standard methods.
-
-\respto{2-22}{\color{blue}Given a group of software projects, there often exists  one   exemplar project that offers the best prediction for all others.
-Such ``bellwether projects'' can be used to make quality predictions that are general to that group.} Existing  methods  for  finding bellwether  are  very slow.
+
+\respto{2-22}{\color{blue}Given a large group of software projects, there often exists  a few   exemplar project(s) that offers the best prediction for all others.
+Such ``bellwether projects'' can be used to make quality predictions that are general to many other projects.}
+
+Existing  methods  for  finding bellwether  have two problems.
+Firstly, they are  very slow.
 When  applied  to  the  697  projects  studied  here, standard bellwether methods   took  60  days  of  CPU  to  find  and  certify  the  bellwethers.
-Also among a large group of software projects there may be subgroup of projects which are more similar to each other then other subgroups and can have a bellwether for each such subgroup of projects.
-Existing bellwether methods does not take this into consideration to find multiple bellwether.
-Hence, we  propose a faster and better  way to find bellwethers.
+Secondly, they assume that only one bellwether exists and, amongst hundreds of projects, they may exist  subgroups, each of which requires their own bellwether.
+
+GENERAL is a new bellwether method that addresses both problems.
 GENERAL   applies hierarchical clustering to groups of project data.
 At each level within a tree of clusters, one bellwether is computed from sibling projects, then promoted up the tree.
-This hierarchical method is a scalable approach to learning effective models from very large data sets.
-For  hundreds of projects, the defect prediction models generated from GENERAL's bellwether were just as good as those found via standard methods.
+In this way, GENERAL can find multiple
+bellwethers, if they exist. Also, GENERAL's hierarchical decomposition runs much faster (and scales better) than standard
+bellwether methods.
 
@@
 \begin{IEEEkeywords}
-Transfer Learning, Bellwether, Defect Prediction, Software Analytics. 
+Transfer Learning, Bellwether, Defect Prediction, Software Analytics, Logistic Regression. 
 \end{IEEEkeywords}}
@@
 
-\respto{1-2}\respto{1-3}{\color{blue} Researchers and industry practitioners makes use of data-driven decision making data mining algorithms build software quality models from project data.For example, many research and industrial groups generate defect predictors from software metrics~\cite{ghotra2015revisiting, zimm09 ,okutan2014software, he13, Zhang16aa, nam2017heterogeneous, Me13, Tantithamthavorn18, me09b, me10a, peters2015lace2, nam2018heterogeneous, menzies2011local, zimmermann09}.
-These metrics can take  forms including process metrics (that describe how and who updates the code) and product metrics (such as number of methods per class, lines of codes, etc).
-One advantage of this approach is that the collection of these metrics is very fast.
-Also,  the subsequent data mining (to generate the quality models) can be fully automated and can scale to a large number of projects.
-Hence, data-driven decision making  is widely used in   SE research and   industrial practice.~\cite{tosun2010ai,kim2015remi,wan2018perceptions} }
+\respto{1-2}\respto{1-3}{\color{blue} Researchers and industry practitioners make use of data-driven decision making data mining algorithms to build software quality models from project data.
+Many research and industrial groups generate defect predictors from software metrics~\cite{ghotra2015revisiting, zimm09 ,okutan2014software, he13, Zhang16aa, nam2017heterogeneous, Me13, Tantithamthavorn18, me09b, me10a, peters2015lace2, nam2018heterogeneous, menzies2011local, zimmermann09}.
+These metrics can take  forms including process metrics (that describe how and who updates the code) and product metrics (such as the number of methods per class, lines of codes, etc).
+When the creation of such models is fully automated
+(using data mining), then this approach scales a large number of projects.
+Hence, data-driven decision making  is widely used in   SE research and   industrial~\cite{tosun2010ai,kim2015remi,wan2018perceptions}.
+}
 
@@
 
-{\color{blue} But what is the external validity of the conclusions reached  via
-the these data mining methods?
+{\color{blue} But what is the external validity of the conclusions reached  via these data mining methods?
 Prior to this paper, the usual result is that such conclusions are not general to multiple projects.
-For example, Table~\ref{unstable} summarizes the results of dozens of studies.
-In that table we observe that, from project to project, very different attributes are most associated with defect prediction.
+Table~\ref{unstable} summarizes the results of dozens of studies.
+In that table, from project to project, very different attributes are most associated with defect prediction.
 This is troubling since,   as
@@
  Further,
-if we are unsure what factors most influence quality, it is difficult to design and implement and deploy tools that can successfully improve that quality.
+if we are unsure of what factors most influence quality, it is difficult to design and implement and deploy tools that can successfully improve that quality.
 Lastly,
 consider the task of training a   novice software engineers or newcomers to a project. If our models are not stable, then it hard to teach what factors  most influence software quality.}
-
-%Many Large organizations and many open source communities are using large scale data analysis on historical data available to them.
-With large quantity of data available to them, how should they reason about software quality?
-Should they use general defect prediction models that hold over many projects?
-Or must they use an ever-changing set of defect prediction models that are continually build and adapted to the task at hand?
-If the latter were true then there would be no stable models and conclusions about what is best practice for SE for avoiding defects (since those best practices would keep changing as we move from project to project).
-As discussed in section~\ref{sec:Motivation}, such conclusion instability has detrimental implications for {\em generality, trust, insight, training}, and {\em tool development}.}
-
-% Researchers and industry practitioners makes use of different machine learning models to automatically generate software quality models(defect predictor) from project data comprises of software quality metrics (Commonly used software metrics for defect prediction are complexity metrics (such as lines of code, Halstead metrics, McCabe’s cyclometic complexity, and CK metrics) and process metrics(such as Number of revisions, lines added and deleted)) .
-Researches and industry practitioners use these defect predictors to predict for defect in new set of changes and to learn what are the important metrics that are responsible for finding these defects.
-These quality metrics can be collected with much ease from the code base of different software systems from large organizations and open source community, and
-
-%   After a decade of intensive research into automated software analytics, what general principles have we learned?
-While that work has generated specific results about specific projects~\cite{Bird:-24015,menzies2013software}, it has failed (so far) to deliver general principles that are demonstrably useful across many projects~\cite{menzies2013guest} (for an example of how {\em more} data can lead to {\em less} general conclusions, see below in {\S}2a).
-
-% Is that the best we can do?
-
-% How should we reason about software quality?
-Should we use  general models that hold over many projects?
-Or must we use an ever-changing set of ideas that are   continually adapted to the task at hand?
-% Or does the truth lie somewhere in-between?  
-% To say that another way:
-% \bi
-% \item
-% Are there general principles we can use to guide project management, software standards, education,   tool development, and legislation about software? 
-% \item
-% Or is  software engineering some ``patchwork quilt'' of ideas and methods where it only makes sense to reason about specific, specialized, and small sets of  projects?
-% \ei
-% If the latter were true then
-%  then there would be no stable conclusions about what is best practice for SE   (since those best practices would keep changing as we move from project to project).
-As discussed in section~\ref{sec:Motivation}, such conclusion instability has   detrimental implications for {\em generality, trust, insight, training}, and {\em tool development}.
-
-% \respto{1-3}{\color{blue}Researchers and industry practitioners makes use of software analytics for many tasks to access software quality, such as:
-% \bi
-% \item Predicting if a submitted code is likely to buggy or not.
-% \item Improving code quality by detecting code smells.
-% \item Issue lifetime estimation to enable effective development and maintenance of their software systems.
-% \ei
-
-% Large organizations and many open source communities uses data-driven decision making, where they learn using large scale data analysis on historical data available to them.
-With large quantity of data available to them, how should they reason about software quality?
-Should they use  general models that hold over many projects?
-Or must they use an ever-changing set of ideas that are   continually adapted to the task at hand?
-If the latter were true then there would be no stable conclusions about what is best practice for SE   (since those best practices would keep changing as we move from project to project).
-As discussed in section~\ref{sec:Motivation}, such conclusion instability has   detrimental implications for {\em generality, trust, insight, training}, and {\em tool development}.}
-%One  explanation for the limited conclusions (so far) from automated analytics is  {\em how much} data we are using for analysis.
-A typical software analytics research paper uses less than a few dozen projects  (exceptions: see~\cite{krishna18a, zhao17, agrawal18}).
-Such small samples can never represent something as diverse as software engineering.
-
-%{\color{blue} Finding general defect predictors  across many projects is a complex task.  
- %For a long list of   conclusions that were found to be  unstable across multiple projects, see~\cite{Me13}.
-This problem is so endemic in software engineering that other journals have devoted entire special issues to the topic~\cite{Menzies2012}.}
 
@@
 is     the ``bellwether'' method~\cite{krishna2018bellwethers,krishna16a,mensah18z,mensah2017stratification,mensah2017investigating}.\respto{1-1a}\respto{2-2}{\color{blue} Given a community of projects developed by the same organization,
-a ``bellwether'' is the   whose data yields the best analytic (i.e. defect prediction, effort estimation etc) on all others} (and we call that the ``bellwether'' since that is the
-name of the  leading sheep of a flock, with a bell on its neck).  This method:
-\bi
-\item Finds a  ``bellwether'' project that is exemplar for the rest;
-\item Draw conclusions from  that project.
+the ``bellwether'' is a project or  a handful of projects
+whose data yields the best analytic (i.e. defect prediction, effort estimation, etc) on all others}\footnote{We call that the ``bellwether'' since that is the
+name of the  leading sheep of a flock, with a bell on its neck.}. In this  method:
+\bi
+\item We find a few exemplar ``bellwethers'';
+\item We draw conclusions from  those projects.
 \ei
@@
 models that hold across multiple data sets.
-Also,   bellwether are a better
-way to transfer lessons between software projects~\cite{krishna2018bellwethers,krishna2017simpler, nair19a, krishna16, krishna16a}  than many other methods including
+Also, bellwethers are a better
+way to transfer models between  projects~\cite{krishna2018bellwethers,krishna2017simpler, nair19a, krishna16, krishna16a}  than many other methods including
 the Burak filter~\cite{turhan09}, Ma et al.~\cite{Ma2012}'s transfer naive Bayes (TNB); and Nam et al.'s  TCA  and TCA+, algorithms~\cite{Nam13,Nam2015}.}
@@
 
-But existing  methods for bellwether transfer are very slow. When applied to the 697 projects studied here, they took 60 days of CPU to find and certify the bellwethers.
-%There are many reasons for that including how the models were certified (20 repeats  with different train/test sets)
-%and the complexity of the analysis procedure (which includes fixing class imbalance and feature selection).
-But the major cause of this slow down was that those   methods  required an $O(N^2)$ comparison between   $N=697$ projects.
-
-Accordingly, this paper explores a novel approach that can find  bellwethers much faster than standard methods.    
-%dramatically improves on existing bellwether methods.
+Existing  methods  for  finding bellwether  have two problems.
+Firstly, they are  very slow.
+When  applied  to  the  697  projects  studied  here, standard bellwether methods   took  60  days  of  CPU  to  find  and  certify  the  bellwethers.
+Secondly, they assume that only one bellwether exists and, amongst hundreds of projects, they may exist  subgroups, each of which requires their own bellwether.
+
+GENERAL is a new bellwether method addresses both problems.  
  {\color{blue}\respto{1-3a} Our GENERAL    algorithm uses hierarchical clustering  to recursively divide a large number of projects into smaller clusters. 
- Starting at the leaves of that tree of clusters, GENERAL finds the    bellwethers within sibling projects.
-That bellwether is then promoted up the tree.
-The output of GENERAL is the project promoted to the top of the tree of clusters.
-}
+ Starting at the leaves of that tree of clusters, GENERAL finds the    bellwethers within sibling projects. That bellwether is then promoted up the tree.}
 %Note that  GENERAL only needs
@@
 
-  GENERAL has two advantages over standard bellwether methods.
+  GENERAL has three advantages over standard bellwether methods.
 Firstly, 
@@
 (and scales to larger sets of data).
-
-% \bi
-% \item
-% This paper applies GENERAL and traditional $O(N^2)$ bellwether to 697 projects.
-% GENERAL and the traditional approach terminated in 1.5 and 72 hours (respectively).
-% \item 
-%  Figure~\ref{fig:cost} shows a hypothetical cost comparison in AWS between standard bellwethers and   GENERAL when running for 100 to 1,000,000 projects. Note that GENERAL
-%  is inherently more scalable.
-%  \ei
-% \begin{figure}[!t]
-%     \centering
-%     \includegraphics[width=\linewidth]{figs/cost.pdf}
-%     \caption{Hypothetical cost comparison between GENERAL and default Bellwether.}
-%     \label{fig:cost}
-% \end{figure} 
+Thirdly, as shown below, GENERAL can find multiple bellwethers (if they are needed).
+
 To present GENERAL and to assess its value, this
-paper asks and answers the following questions:
-            \respto{1-6}
-
-            {\color{blue}
-            \textbf{RQ1}:  How slow is conventional bellwether method?
-
-            As a starting point for this research,  we need to document the problems associated with existing bellwether methods. RQ1 offers the following theoretical result:
-            \begin{RQ}{
-               Conventional bellwether method as proposed by Krishna et al~\cite{krishna2018bellwethers,krishna16a} uses a $ O(N^2) $ comparisons to find the ``bellwether'' among a community of N (697 projects in this experiment) projects.}
-            \end{RQ}
-
-            \textbf{RQ2}:  How fast is GENERAL bellwether?
-
-            RQ2 explains the RQ1 result:
-
-            \begin{RQ}{
-            In theory, 
-             GENERAL is much faster since
-             its computational complexity is  $O(m*(N/m)^2)$.}
-            \end{RQ}
-
-            }
-
-            \textbf{RQ3}:   In practice,
-            can the hierarchical clustering of GENERAL tame slow runtimes seen in   bellwether-based reasoning?
-
-            This research question checks if our new method tames the runtime complexity of standard bellwether. We find that:
-            \begin{RQ}{
-                When learning
-bellwethers from 697 projects,  GENERAL and   traditional   approaches terminated in 1.5 and 72 hours (respectively).}
-            \end{RQ}
-That is to say,  GENERAL is far faster
-than standard bellwether methods.
-
-           \noindent \textbf{RQ4}:  Is this faster bellwether effective?
-
-            Sometimes,  a faster method   comes at the cost of a less effective analysis. Hence, this research question compares
-             standard and the GENERAL bellwether methods. We find that:
-
-            \begin{RQ}{
-                Across multiple performance criteria, the faster GENERAL bellwether algorithm never performs worse that standard bellwether.
+paper asks and answers the following questions.
+\newpage         
+             \noindent {\color{blue}
+            \textbf{RQ1}: {\bf  How slow are   conventional bellwether methods?} \respto{1-6}
+            As a starting point for this research,  we need to document the problems associated with existing bellwether methods. RQ1 offers the following theoretical result:}
+           \vspace{-3mm}\begin{quote}
+           \item {\em
+              The conventional bellwether method as proposed by Krishna et al~\cite{krishna2018bellwethers,krishna16a} is slow since it requires  $ O(N^2) $ comparisons to find   one bellwether within a community of N  projects.}
+        \end{quote}
+
+            \noindent \textbf{RQ2}:  {\bf In theory, how much faster is GENERAL's hierarchical clustering?}        
+            \begin{quote}
+               {\em              GENERAL is theoretically much faster since
+             its computational complexity is  $O(m*(N/m)^2)$.
+            }\end{quote}
+            \noindent \textbf{RQ3}:  {\bf  In practice,
+            how fast is  GENERAL?} This research question checks if GENERAL tames the run-time complexity of standard bellwether. We find that:
+            \begin{quote}
+              \noindent {\em    
+                When learning bellwethers from 697 projects,  GENERAL and   traditional   approaches terminated in 1.5 and 72 hours (respectively).
+That is to say,  GENERAL is far faster than standard bellwether methods.}
+            \end{quote}
+           \noindent \textbf{RQ4}: {\bf  Is this faster bellwether effective?}
+            Sometimes,  a faster method   comes at a cost of less effective analysis. Hence, {\bf RQ4} compares
+             standard and the GENERAL bellwether method. We  find that:
+            \begin{quote}
+              \noindent {\em  
+                Across multiple performance criteria, the faster GENERAL bellwether algorithm never performs worse than standard bellwether.
 And measured in terms of recall and false alarm, GENERAL performs statistically much better.}
-            \end{RQ}
-
+            \end{quote}
        \noindent 
-            \textbf{RQ5}: Does learning from too many projects have detrimental effect?
-
-            We ask this since Petersen and Wohlin~\cite{Petersen2009} argue that for empirical SE, context matters.  They
-would say that   it is  a mistake
-to learn from too much data, since that can inappropriately combine 
-data from difference contexts. 
-What we will show is that:
-            \begin{RQ}{
-            ZXXXAssessed in terms of {\em recall},
-it is better to learn bellwethers from more data rather than less.
-But assessed in terms of {\em false alarms}, 
-while learning bellwethers
-from many projects is useful,
-as predicted by Petersen and Wohlin, it is possible to learn from too much data. }
-            \end{RQ}
-
-         \noindent 
-            \textbf{RQ6}: What exactly did we learn from all those projects?
-
-            \begin{RQ}{
-                \respto{2-9}\respto{3-13} {\color{blue}
-                In terms of defect prediction,
-issues of inter-class interface are paramount.
-Many other  issues are far less important such as file size, depth of inheritance tree, intra-method complexity, file size, revision history.}}
-            \end{RQ}
-
-\noindent Overall, the  contributions of this paper are
-\bi
-
-\item \textbf{Hierarchical bellwethers for  transfer learner:} We
-offer a  novel hierarchical clustering    bellwether algorithm  called GENERAL  (described in section~\ref{GENERAL}) that
-finds bellwether in hierarchical clusters, then promotes those bellwether to upper levels
-The final  project that is promoted to the root of the hierarchy is returned as  ``the'' bellwether.
-
-\item \textbf{Showing inherent generality in SE:}
-In this study we discover a source data set for transfer learner from a large number of   projects, hence proving generality in the SE datasets (where some datasets can act as exemplars for the hundreds of other projects).
-
-\item \textbf{Showing when ``enough is enough'': }
-In this study 
+            \textbf{RQ5}: {\bf Does learning from too many projects have detrimental effects?}
+          In the case of GENERAL's hierarchical clustering, we show that it is a mistake to  learn quality models from the very top of the cluster tree (where data is combined from all projects).
+Rather, it is best to use  models seen   one level down from the root.
+That is:
+             \begin{quote}
+              \noindent {\em  
             Learning from  a few hundred  projects is better
-than learning from just a few dozens   projects.
-But after 200 projects (approx) the learned
-model start degrading. 
-This is to say that 
-there is an limit beyond
-which more data is actually detrimental to learning software quality models.
-
-\item \textbf{Lessons   about software quality that are general
-to hundreds of software projects:}
-  As said above,    in  this sample of  697  projects,  we find that code  interface issues are the dominant factor on software defects.
-
-\item \respto{1-5d} \respto{1-5h}{\color{blue}\textbf{ Replication Package:} Our  replication package\footnote{\href{http://tiny.cc/bellwether}{http://tiny.cc/bellwether}}   contains  all the datasets and scripts used in this paper.}
-
-\ei
+than learning from just a few dozens of projects.
+But after generalizing over 200 projects (approx), the learned
+model starts degrading.  
+  }\end{quote} 
+\noindent To say that another way,   when learning from a very large number of projects (hundreds), they may be useful
+to learn a handful of bellwethers, each of which covers (say) just a few hundred projects. In this regard,
+GENERAL is better than prior bellwether algorithms
+since GENERAL can find multiple bellwethers while
+older methods only ever find one.
+
 The rest of this paper is structured as follows.
 Some background and related work are discussed in section~\ref{sec:literature}.
-Our algorithm GENERAL is described in section~\ref{GENERAL}.
+Our algorithm GENERAL is described in section~\ref{GENERAL} along with performance measures in section~\ref{sec:Measures}.
 Data collection and experimental setup are in section~\ref{sec:Data Collection}.
-Followed by evaluation criteria in section~\ref{eval} and performance measures in section~\ref{sec:Measures}.
-The results and answers to the research questions are presented in section~\ref{sec:results}, which is followed by threats to validity in section~\ref{sec:validity}.
-Finally the conclusion is provided in section~\ref{sec:concl}.
+Followed by evaluation criteria in section~\ref{eval}.
+The results and answers to the research questions are presented in section~\ref{sec:results}.
+Discussion in section~\ref{sec:rq6}, which is followed by threats to validity in section~\ref{sec:validity}.
+Finally, the conclusion is provided in section~\ref{sec:concl}.
+
+ \respto{1-5d} \respto{1-5h}{\color{blue} Note that our  replication package\footnote{\href{http://tiny.cc/general\_bellwether}{http://tiny.cc/general\_bellwether}}   contains  all the datasets and scripts used in this paper.}
 
@@
   \item
-  That 
-  predictor performs   just as well as those found via  standard methods.
+  Those 
+  predictors perform  just as well as those found via  standard methods.
   \ei
@@
 \item
-the conclusions reached in this way used automatic data mining methods applied to open source data. That is, our results   can be repeated/ improved/ refuted by other research teams.
-\ei
-We are unaware of any other repeatable/refutable result in SE that can be shown to hold over so many projects.}
-
-%If our conclusions about best practices for SE projects keep changing, that will be detrimental to generality, trust, insight, training, and tool development.
-
-% \begin{figure}[!t]
-%     \centering
-%     \includegraphics[width=\linewidth]{figs/predictive_power.pdf}
-%     \caption{Two hypothetical results about how training set size might effect the efficacy of quality prediction for software projects.}
-%     \label{fig:predictive_power}
-% \end{figure}
-
-%Just to balance the above argument,
-%we add that   sometimes it is possible to learn from {\em too much data}.
-
-%Hence, this work divides into (a)~automated methods for finding sets of projects in the same {\em community}; and (b)~within each {\em community}, find the model that works best.
-
-%\respto{2-12}\respto{3-2}{\color{blue} The {\em size} of the communities found in this way would have a profound impact on how we should reason about software engineering.
-Consider in this experiment of 697 projects, we build a set of defect predictor by learning bellwether from smalls cluster of $\approx10$ projects,  medium clusters of $\approx100$ projects, a large cluster containing $\approx600$ projects and a self test.
-In this scenario if we see the defect prediction models build  using bellwethers from medium set of clusters works better than set smalls clusters as well as the large cluster, then in this case, while we could not offer a single model that covers {\em all} of SE, we could offer a handful of models, each of which would be relevant to project clusters.
-While if we see only self test works in this case and learning from more projects makes quality predictions worse which means the our projects break up into ``communities'' of size one.
-In this case,  (a)~principles about what is ``best practice'' for different software projects would be constantly changing (whenever we jump from small community to small community); and (b)~the generality issues would be becoming open and urgent concerns for the SE analytics community.}
-
-% The {\em size} of the communities found in this way would have a profound impact on how we should reason about software engineering.
-Consider the hypothetical results of Figure~\ref{fig:predictive_power}.
-The \textcolor{blue}{{\bf BLUE}} curve shows some quality predictor that (hypothetically) gets better, the more projects it learns from (i.e.
-higher levels in the hierarchical cluster).
-After about learning from 1000 projects, the \textcolor{blue}{{\bf BLUE}} curve's growth stops and we would say that community size here was around cluster size in level 1.
-In this case, while we could not offer a single model that covers {\em all} of SE, we could offer a handful of models, each of which would be relevant to project clusters at that level.
-% %Accordingly, we would say that there are many cases where  wisdom from prior projects can be readily applied to guide future projects and (b)~the generality issues raised are not be so pressing.
-
-% Now consider the hypothetical \textcolor{red}{{\bf RED}} curve of Figure~\ref{fig:predictive_power}.
-Here, we see that (hypothetically)  learning from more projects makes quality predictions worse which means the our 10,000 projects break up into ``communities'' of size one.
-In this case,  (a)~principles about what is ``best practice'' for different software projects would be constantly changing (whenever we jump from small community to small community); and (b)~the generality issues would be becoming open and urgent concerns for the SE analytics community.
-
-% In summary, the above two sections lead to our  research question {\bf  RQ4}:
-% does learning from too many projects have detrimental effects. Later in this
-% paper, we will return to this issue.
+The conclusions reached in this way used automatic data mining methods applied to open source data. That is, our results   can be repeated/ improved/ refuted by other research teams.
+\ei}
 
@@
 
-In this section, we ask ``Why even bother to transfer lessons learned between projects?''.
-In several recent studies ~\cite{bettenburg2012think, menzies2012local, posnett2011ecological} with readily-available data from SE repositories, numerous authors report the locality effect in SE; i.e.
-general models outperformed by specialized models localized to particular parts of the data.
-For example.
-Menzies et al. explored local vs global learning in defect prediction and effort estimation~\cite{menzies2012local}  and found that
- learning rules from specific local data was more
- effective than learning rules from the global space.
-
-On the other hand,
-Herbold et al.~\cite{herbold2017global}  offered an opposite conclusion.
-In their   study regarding global vs local model for cross-project defect prediction,
-they saw that  local models offered little to no improvement over models learned
-from all the global data.
-One explanation for this discrepancy  is the size of number of projects that they explored.
-\respto{2-14}Menzies, Herbold et al.
-explored less than two dozen projects which raises issues of external validity in their conclusions.
-Accordingly, here,  we explore nearly 700 projects.
-As shown below, the results of this paper agree  more with Herbold et al.
-than  Menzies et al.
-since we show that one global model (learned from a single bellwether projects) does just as well as anything else.
-
-Apart from the above discrepancy in research results, there are many other reasons to
-explore learning from many projects. Those reasons   falls into four groups:
-
-\textbf{(a) The lesson on big data is that that the {\em more} training data, the {\em better} the learned model:} Vapnik~\cite{vapnik14} discusses examples where models accuracy improves to nearly 100\%, just by training on $10^2$ times as much data.
+There are many other reasons to
+explore learning from many projects. Those reasons   fall into four groups:
+
+\textbf{(a) The lesson on big data is that that the {\em more} training data, the {\em better} the learned model:} Vapnik~\cite{vapnik14} discusses examples where the model's accuracy improves to nearly 100\%, just by training on $10^2$ times as much data.
 This effect has yet to be seen in SE data~\cite{menzies2013guest} but that might just mean we have yet to use enough training data (hence, this study).
@@
 % Another reason to try generalizing across more SE data is that, among developers, there is little agreement on what many issues relating to software:
-\respto{2-23}{\color{blue} Among developers,  there is little agreement on what is of importance relating to software quality and other aspects of the software development:}
-\bi
-    \item
-    According to Passos et al.~\cite{passos11},  developers often  assume that the lessons they learn from a few past projects are general to all their future projects.
+\respto{2-23}{\color{blue} Among developers,  there is little agreement on what is of importance relating to software quality and other aspects of software development:}
+\bi
+    \item
+    According to Passos et al.~\cite{passos11},  developers often  assume that the knowledge they learn from a few past projects are general to all their future projects.
 They comment, ``past experiences were taken into account without much consideration for their context'' ~\cite{passos11}.
@@
 	J{\o}rgensen \& Gruschke~\cite{Jo09} offer a similar warning.
-They report that the suppose software engineering ``gurus'' rarely use lessons from past projects to improve their future reasoning and that such poor past advice can be detrimental to new projects.~\cite{Jo09}.
+They report that the suppose software engineering ``gurus'' rarely use knowledge from past projects to improve their future reasoning and that such poor past advice can be detrimental to new projects.~\cite{Jo09}.
     \item 
@@
 
-%\respto{2-24}{\color{blue} It turns out that developers are not the only one's confused about how various factors influence software projects.
-Much recent research calls into question  the ``established wisdoms'' of SE field.
-
-%Note that if the reader disputes any of the above, then we ask how would you challenge the items on this list?
-Where would you get the data, from enough projects, to   successfully refute the above?
-And where would you get that data?
-And how would you draw conclusions from that large set?
-Note that the answers to these questions requires learning from multiple projects.
-Hence, this paper.
-
 \textbf{(c) Imported data can be more useful than local data:} Another benefit of  importing data from other projects is that, sometimes, that imported data can be better than the local information.
 Rees-Jones reports in one study that while building predictors
-for Github close time  for open source projects~\cite{rees2017better} using data from other projects performs much better then building models using {\em local learning} (because there is better  information {\em there} than {\em here}).
-
-\textbf{(d) When there is insufficient local data, learning from other projects is very useful:} When developing new software in  novel areas, it is useful to draw on the relevant  experience  from related areas with a larger experience base.This is particularly true when developers are doing something that is novel to them, but has been widely applied elsewhere, Clark and Madachy~\cite{clark15} discuss 65 types of software they see        under-development by the US Defense Department in 2015.
+for Github close time  for open source projects~\cite{rees2017better} using data from other projects performs much better than building models using {\em local learning} (because there is better  information {\em there} than {\em here}).
+
+\textbf{(d) When there is insufficient local data, learning from other projects is very useful:} When developing new software in  novel areas, it is useful to draw on the relevant  experience  from related areas with a larger experience base.
+This is particularly true when developers are doing something that is novel to them but has been widely applied elsewhere, Clark and Madachy~\cite{clark15} discuss 65 types of software they see        under-development by the US Defense Department in 2015.
 Some of these types are very common (e.g.
@@
 (e.g.
-workers on   flight avionics   might check for lessons learned from ground-based communications).
+workers on   flight avionics   might check for knowledge  from ground-based communications).
 Developers  working in an uncommon area (e.g.
-avionics communications) might want to transfer in lessons from more common areas (e.g.
+avionics communications) might want to transfer knowledge from more common areas (e.g.
 ground-based communication).
 
-\subsection{ How to  Transfer Knowledge}
-This     art of moving data and/or lessons learned from one project or another is {\em Transfer Learning}.
-When there is insufficient current data to apply data miners to learn defect predictors, transfer learning can be used to transfer lessons learned from other source projects S to the target project T .
+\subsection{ How to  Transfer Knowledge}\label{tion:how1}
+This     art of moving data and/or knowledge  from one project or another is {\em Transfer Learning}.
+When there is insufficient current data to apply data miners to learn defect predictors, transfer learning can be used to transfer knowledge from other source projects S to the target project T.
 
@@
 
- \textbf{Similarity-Based Approaches:} In this approach we can transfer some/all subset of the rows or columns of data from source to target.
+ \textbf{Similarity-Based Approaches:} In this approach, we can transfer some/all subset of the rows or columns of data from source to target.
 The Burak filter~\cite{turhan09} builds its training sets by finding the k = 10 nearest code modules in S for every $ t \in T $.
 However, the Burak filter suffered from the all too common instability problem (here, whenever the source or target is updated, data miners will learn a new model since different code modules will satisfy the k = 10 nearest neighbor criteria).
-Other researchers ~\cite{kocaguneli2012, kocaguneli2011find} doubted that a fixed value of k was appropriate for all data.
-That work recursively bi-clustered the source data, then pruned the cluster sub-trees with greatest ``variance'' (where the ``variance'' of a sub-tree is the variance of the conclusions in its leaves).
-This method combined row selection with row pruning (of nearby rows with large variance).
-Other similarity methods~\cite{Zhang16aa} combine domain knowledge with automatic processing: e.g.
-data is partitioned using engineering judgment before automatic tools cluster the data.
-To address variations of software metrics between different projects, the original metric values were discretized by rank transformation according to similar degree of context factors.
 
@@
 
+\textbf{The Bellwether Method:}
 Considering all the attempts at transfer learning sampled above, suggested a surprising lack of consistency in the choice of source datasets, learning methods, and statistical measures while reporting results of transfer learning.
@@
     \item \textbf{The Bellwether method} is where we search for the exemplar bellwether project and construct a transfer learner with it.
-This transfer learner is then used to predict for effects in future data for that community.
-
-\ei
-
-In their paper Krishna et al.
-performed experiment with communities of 3, 5 and 10 projects in each, and showed that (a)~bellwethers are not rare, (b)~their prediction performance is better than local learning, and (c)~they do fairly well when compared with
+This transfer learner is then used to predict for defects in future data for that community.
+
+\ei
+
+In their paper, Krishna et al.
+performed experiments with communities of 3, 5 and 10 projects in each, and showed that (a)~bellwethers are not rare, (b)~their prediction performance is better than local learning, and (c)~they do fairly well when compared with
 the state-of-the-art transfer learning methods discussed above.
@@
 
-That said,  Krishna et al. warn that in order to find bellwether we need to do a $ N*(N-1) $ comparison; i.e. standard bellwethers
-have complexity $ O(N^2) $ (N being the number of projects in community).
+There are two drawbacks with bellwethers, as seen in prior work.
+Firstly, that prior work assumes that one bellwether will work for many projects. While such a solo-bellwether approach worked well
+in studies over five to 20 projects, we show below that hundreds of projects might actually require more than one bellwether.
+
+Secondly, standard bellwether algorithms are   slow.
+ Krishna et al. warn that in order to find bellwether we need to do a $ N*(N-1) $ comparison; i.e. standard bellwethers
+have complexity $ O(N^2) $ (N being the number of projects in the community).
 
@@
 
-\begin{figure}[!t]
+\begin{figure}[!b]
     \small
-     \begin{lstlisting}[mathescape,numbers=left,frame=None]
+     \begin{lstlisting}[mathescape,numbers=right,frame=None]
         def General(project):
@@
             \vspace{-0.2cm}
-            \caption{Pseudo-code of GENERAL}
+            \caption{Pseudo-code of GENERAL.
+Unlike traditional bellwethers (that require an $O(N^2)$ analysis of all pairs of $N$ projects, GENERAL first hierarchically generates a tree of  clusters with $m$ leaves.
+It  then reasons  within each cluster.
+This means  that GENERAL's complexity is $O(m*(N/m)^2)$.}
             \label{fig:Pseudo-code} 
@@
 
- Our proposed improvement to bellwethers is called GENERAL.
+ Our proposed improvement to the existing bellwether method is called GENERAL.
 The core intuition of this new approach is that if many projects are similar, then we do not need to run comparisons between all pairs of projects.\respto{1-1b}{\color{blue}
@@
  and  a comparison method to {\bf select the best model} (see \S\ref{sec:best}).
-Here if we analyze an average case where $N$ projects is divided into $m$ clusters equally, then each cluster has a complexity of $O((N/m)^2)$ and the total complexity is $O(m*(N/m)^2)$ as there are $m$ clusters.
+Here if we analyze an average case scenario where $N$ projects are divided into $m$ clusters equally, then each cluster has a complexity of $O((N/m)^2)$ and the total complexity is $O(m*(N/m)^2)$ as there are $m$ clusters.
  \item  Once bellwether from each group is  pushed up the tree, each super-groups only has projects selected as bellwether from step 5 then steps 4,5 are repeated,
@@
 
-To operationalize steps 1,2,3,4,5,6,7 listed above, we need to make some lower-level engineering decisions. The rest of this section documents those decisions.
+To operationalize steps 1,2,3,4,5,6,7 listed above, we need to make some lower-level engineering decisions about:
+\bi
+\item Feature extraction;
+\item Hierarchical clustering;
+\item Data mining;
+\item Evaluation criteria;
+\item Selecting the best model.
+\ei
+The rest of this section documents those decisions.
 
@@
 
-Prior to anything else, we must summarize our projects.  Xenos \cite{Xenos} distinguishes
+Prior to anything else, we must summarize our projects as a set of metrics. Xenos \cite{Xenos} distinguishes
 between {\em product metrics} (e.g.  counts of lines
 of code );  and  {\em process metrics} 
-about the  development process (e.g.    number of file revisions).
- \respto{2-18}{\color{blue} Using the   Understand tool~\cite{visualize},
-we calculated different variations (i.e. average, max etc.) of 21 product and 5 process metrics, with a total 66 attributes/columns to build defect prediction models
+about the  development process (e.g.
+number of file revisions).
+Product metrics are properties of the code such as size, complexity, design features collected by analyzing the code, while the process metrics are properties of revision history of files collected by analyzing git history.
+ \respto{2-18}{\color{blue} Here using the   Understand tool~\cite{visualize},
+we calculated different variations (i.e. average, max, etc.) of 21 product and 5 process metrics, with a total of 66 attributes/columns to build defect prediction models
  (see Table~\ref{tbl:metric}).
-These product  metrics are
+ The Understand tool is  widely used   in software analytics~\cite{Zhang16aa,gizas2012comparative,fontana2011experience,orru2015curated,pattison2008talk,malloy2002testing}.
+Using that tool, our product  metrics are
  calculated from snapshots of the projects from 6 months back of the last commit.
-The process metrics are computed using the change history in the six-months period before the split date via manual collection of data using scripts.} The data collected for this project is summarized in \fig{lang_projects}
- and \fig{meta}.
-
-\begin{figure}[!b]
+Also, our process metrics are computed using the change history in the six-months period before the split date via manual collection of data using scripts.} The data collected for this project is summarized in \fig{lang_projects}  and \fig{meta}.
+Using the metrics (process and product) collected for each project we use Hall's CFS feature selector~\cite{hall1999correlation} to summarize the projects into feature vectors for the next phase of the algorithm.
+
+\begin{figure}[!t]
 \centering
-{\small \renewcommand{\baselinestretch}{0.7}
+{\scriptsize \renewcommand{\baselinestretch}{0.7}
 \begin{tabular}{rrl}
@@
 \caption{Distribution of projects depending on languages.
-Many  projects use combinations of languages to
-achieve their results. Here, we show majority language used in each project.}
+Many  projects use combinations of languages so  we show the majority language of  each project.}
 \label{fig:lang_projects}
@@
 
-\begin{figure*}[!h]
-    \centering
-    \includegraphics[width=.8\linewidth]{figs/meta.pdf}
+\begin{figure}[!t]
+\vspace{-15mm}
+    \includegraphics[angle=270,width=\linewidth]{figs/meta.pdf}
+    \vspace{-15mm}
     \caption{Distribution of projects depending on Defect Percentage, Data set Size, Lines of Code and Number of Files.} 
     \label{fig:meta}
-\end{figure*}
-
-Understand is a widely used tool in software analytics~\cite{Zhang16aa,gizas2012comparative,fontana2011experience,orru2015curated,pattison2008talk,malloy2002testing}.
- The advantage of using this tool is that much of the tooling needed for this kind of large scale analysis is already available.
-On the other hand, it also means that we can only reason about the features that Understand can report-- which could be  a threat to the validity of the conclusions reached.
-As shown below, the Table~\ref{tbl:metric} metrics were shown to be effective for our task.
-Nevertheless, in future work, this study needs to be repeated whenever new tools allow for the widespread collection of different kinds of features.
+\end{figure}
 
 \begin{table}[!t]
+
+~\\
 
@@
 \end{table}
-\subsection{Hierarchical Clustering}\label{sec:hc}
+\subsection{Hierarchical Clustering}
+\label{sec:hc}
 
@@
 some {\em over-sampling} is required to increase the number of defective examples in the training sets.
-\item Since one of our research questions ({\bf RQ6}) asks ``what did we learn from all these projects'', we needed a learning method that generate succinct models.
+\item Since one of our motivation is to asks ``what did we learn from all these projects'', we needed a learning method that generates succinct models.
 Accordingly, we used {\em feature selection}  to check which subset of Table~\ref{tbl:metric}
@@
 \item
-The logistic regression learner, \respto{1-5a} {\color{blue} since it is widely used in defect prediction~\cite{ghotra2015revisiting,XXX} in the software engineering domain and, in our experience,
-in runs much faster (in terms of model building time) than many other learners such as Support Vector Machine, Random Forest, Artificial Neural Nets etc.
-(when tested on defect prediction).~\cite{ghotra2015revisiting};}
-\item
-The SMOTE class imbalance correction algorithm\footnote{  The SMOTE Synthetic Minority Over-Sampling Technique algorithms sub-samples the majority class (i.e., deletes examples) while over-sampling the minority class until all classes have the same frequency.
-To over-sample, new examples are synthesized extrapolating between known examples (of the minority class) and its $k$ nearest neighbors.}~\cite{Chawla2002}, \respto{1-5b} {\color{blue} since many of the projects have relatively very few or large number of defects.
-A model build on project with such skewed class distribution can result in a biased model towards the majority class (Such models can either have low recall or high recall with high pf).
-Thus we run SMOTE~\cite{tan2015online,wang2013using,sun2012using,khoshgoftaar2010attribute} on the training data\footnote{While it is useful
+Logistic regression;
+\item
+The SMOTE class imbalance correction algorithm;
+\item
+And Hall's CFS feature selector. 
+\ei
+We selected these tools
+since   in the domain of software analytics,
+the use of LR (logistic regression) and SMOTE
+is endorsed by recent ICSE papers~\cite{Rahman:2013,ghotra2015revisiting,agrawal17}.
+As to CFS, we found that without it, our recalls were very low (less than 20\%).
+Also,   extensive studies have found that CFS more useful than many other feature subset selection methods such as  PCA or InfoGain or RELIEF\respto{1-5e} {\color{blue}~\cite{hall1999correlation,challagulla2008empirical,arar2015software,lee2016developer,rodriguez2007attribute,gao2015combining,hosni2017investigating}.
+}
+The rest of this sub-section offers some low-level notes
+on each tool.
+
+Logistic regression  \respto{1-5a} {\color{blue}  is widely used in defect prediction~\cite{ghotra2015revisiting,zhang2017data,he2012investigation,nam2013transfer,pan2010domain} in the software engineering domain and, in our experience,
+it runs much faster (in terms of model building time) than many other learners such as Support Vector Machine, Random Forest, Artificial Neural Nets etc, (when tested on defect prediction).}
+
+\respto{1-5b} {\color{blue} The SMOTE class imbalance correction algorithm sub-samples the majority class (i.e., deletes examples) while over-sampling the minority class until all classes have the same frequency.
+To over-sample, new examples are synthesized extrapolating between known examples (of the minority class) and its $k$ nearest neighbors~\cite{Chawla2002}.
+We use SMOTE since many of the projects have relatively very few or large number of defects.
+A model built on a project with such skewed class distribution can result in a biased model towards the majority class (Such models can either have a low recall or high recall with high pf).
+Thus we run SMOTE~\cite{tan2015online,wang2013using,sun2012using,khoshgoftaar2010attribute} on the training data\footnote{Technical aside: While it is useful
   to artificially boost the number of target examples
 in the training data~\cite{Chawla2002,Pelayo2007,mensah2017investigating}, it is a methodological error to also change the distributions in   the test data~\cite{agrawal17}. Hence, for our work,
-we take care to {\em only} resample the training data.} to artificially boost the number of target examples in the training data and achieving balanced recall and pf for the minority class test examples};
-\item
-Hall's
-CFS feature selector~\cite{hall1999correlation}\footnote{CFS  is based on the heuristic
+we take care to {\em only} resample the training data.}}.
+
+\respto{1-5c} {\color{blue} Hall's
+CFS feature selector~\cite{hall1999correlation} 
+is based on the heuristic
 that ``good feature subsets contain features highly correlated with the classification, yet uncorrelated to each other''. Using this heuristic,
@@
 Note that for this to be maximal, $r_{\mathit{cf}}$  must be large
-and $r_{\mathit{ff}}$ must be small.
-That is, features have to connect more to the class than each other.}, \respto{1-5c} {\color{blue} to identify features which are highly correlated with the classification, yet uncorrelated to each other.
+and $r_{\mathit{ff}}$ must be small (that is, features have to connect more to the class than each other).
+We use CFS  to identify features that are highly correlated with the classification, yet uncorrelated to each other.
 The features which are  highly correlated with each other will not add more information while making classification, while the features which are uncorrelated towards the classification also not add more information while making classification.
-The CFS algorithm incrementally picks one feature at a time which adds the most information towards the classification at a given step and stops when there is no more improvement in the score (see footnote 4).
-}
-\ei
-We selected  use these tools
-since   in the domain of software analytics,
-the use of LR (logistic regression) and SMOTE
-is endorsed by recent ICSE papers~\cite{Rahman:2013,ghotra2015revisiting,agrawal17}.
-As to CFS, we found that without it, our recalls were very low (less than 20\%).
-Also,   extensive studies have found that CFS more useful than many other feature subset selection methods such as  PCA or InfoGain or RELIEF\respto{1-5e} {\color{blue}~\cite{hall1999correlation,challagulla2008empirical,arar2015software,lee2016developer,rodriguez2007attribute,gao2015combining,hosni2017investigating}.
+Our  CFS   incrementally picks one feature at a time, stopping when there is no more improvement in the score.
 }
@@
 Using
-this data, we can define 5 evaluation measures  as follows:
+this data, we can define 5 evaluation measures  as follows.
+
 {\color{blue}\respto{1-5f} 
@@
 $n/N$.
-This implicates in an ideal scenario where we identify all the actual target class as target class without missing the recall will be one.
+This implicates in an ideal scenario where we identify all the actual target class as the target class without missing the recall will be one.
 When recall is maximal, we are finding all  the target class.
@@
 $n/m$.
-A low Precision indicates that developers would encounter more false alarms, which may have negative impact on developers' confidence on the prediction model.
+A low Precision indicates that developers would encounter more false alarms, which may have a negative impact on developers' confidence in the prediction model.
 When precision is maximal, all the reports of defect modules are actually buggy (so the users waste no time looking at results that do not matter to them)
 
-(3) \textbf{pf:} This is the proportion of all suggested defective changes which are not actual defective changes among all the suggested defective changes.
-A high {\em pf} suggests developers will encounter more false alarms which may have negative impact on developers' confidence in the prediction model.
-
-(4) \textbf{popt20:} This is the proportion number of suggested defective changes among all suggested defective changes, when when 20\% LOC modified by all changes are inspected.
+(3) \textbf{Pf:} This is the proportion of all suggested defective changes which are not actual defective changes among all the suggested defective changes.
+A high {\em pf} suggests developers will encounter more false alarms which may have a negative impact on developers' confidence in the prediction model.
+
+(4) \textbf{Popt20:} This is the proportion number of suggested defective changes among all suggested defective changes, when 20\% LOC modified by all changes are inspected.
 A high {\em popt20} values mean that developers can find most bugs in a small percent of the code, thus effectively reducing the effort required to find bugs.
@@
 Each set was then sorted in ascending order by lines of code.
-We then ran down set1, then set2, till 20\% of the total lines of code were reached-- at which point {\em popt20} is the percent of buggy modules seen up to that point.
-
-(5) \textbf{ifa\_auc:} Number of  initial false alarms encountered before we find the first defect.
+We then ran down set1, then set2, till 20\% of the total lines of code was reached-- at which point {\em popt20} is the percent of buggy modules seen up to that point.
+
+(5) \textbf{Ifa\_auc:} Number of  initial false alarms encountered before we find the first defect.
 Inspired by previous studies on fault localization~\cite{parnin2011automated, kochhar2016practitioners, xia2016automated}, we caution that if the top-k changes recommended by the model are all false alarms, developers would be frustrated and are not likely to continue inspecting the other changes.
-Parnin and Orso ~\cite{parnin2011automated} found that developers would stop inspecting suspicious statements, and turn back to traditional debugging, if they could not get promising results within the first few statements they inspect.
+Parnin and Orso ~\cite{parnin2011automated} found that developers would stop inspecting suspicious statements, and turn back to traditional debugging if they could not get promising results within the first few statements they inspect.
 Using the nomenclature reported about {\em ifa$=k$}.
-In this study we use a modified version of {\em ifa} called ifa\_auc, which calculates {\em ifa} based on efforts spent on inspecting the code.
+In this study, we use a modified version of {\em ifa} called ifa\_auc, which calculates {\em ifa} based on efforts spent on inspecting the code.
 We use gradually increment the efforts spent by increasing the total LOC inspected and calculate ifa on each iteration to get the area under the curve (auc), here the x-axis is the percentage of effort spent on inspection and y-axis is {\em ifa}.}
@@
 
-{\color{blue}\respto{1-5f} As discussed above, model performance can be scored and the best model can be chosen by researchers based on their choice of metrics.
-In this experiment we score model performance according to the goals mentioned in \S\ref{sec:Measures}.
+{\color{blue}\respto{1-5g} As discussed above, model performance can be scored and the best model can be chosen by researchers based on their choice of metrics.
+In this experiment, we score model performance according to the goals mentioned in \S\ref{sec:Measures}.
 Here when assessing models, we  chose the best model that:}
-% \bi
-% \item {\color{blue}Recall is the ratio between predicted actual target class examples vs all target class examples; i.e.
-$ \frac{TP}{TP+FN} $, which means in an ideal scenario where we identify all the actual target class as target class without missing the recall will be one.
-% When recall is maximal, we are finding all  the target class.}
-% \item  {\color{blue} Precision is the ratio between predicted actual target class examples vs all predicted target class examples; i.e.
-$ \frac{TP}{TP+FP} $.
-When precision is maximal, all the reports of defect modules are
-% actually buggy (so the users waste no time looking at results that do not matter to them).}
-% \item {\color{blue}popt(20) is a cost sensitive productivity based metric, which represents the percentage of total defect identified by reading 20\% of the code.
-This means more defects we can identify by reading only 20\% of the code is better for the developers to localize and fix the defects.}
-% \item {\color{blue}ifa\_auc  is  XXX.}
-% \ei
+
 \bi
@@
 \ei
-% In such   {\em multi-objective} problems, one model is better than another if it
-%  satisfies a ``domination predicate''.
-%  We use the Zitler indicator dominance
-%  predictor~\cite{zit02} to select our bellwether (since this is known to select better models
-%  for 5-goal optimization~\cite{Sayyad:2013,Sayyad:2013:SPL}).
-% This predicate favors model
-%   $y$ over $x$  model if $x$ ``losses'' most:
-% \begin{equation}\label{eq:cdom}
-% \begin{array}{rcl}
-% \textit{worse}(x,y)& =& \textit{loss}(x,y) > \textit{loss}(y,x)\\
-% \textit{loss}(x,y)& = &\sum_j^n -e^{\Delta(j,x,y,n)}/n\\
-% \Delta(j,x,y,n) & = & w_j(o_{j,x}  - o_{j,y})/n
-% \end{array}
-% \end{equation}
-% where  ``$n$'' is the number of objectives (for us, $n=5$) and $w_j\in \{-1,1\}$ depending on whether
-% we seek to maximize goal $x_j$.
-
-% An alternative to the Zitler indicator is    `boolean domination ''
-%  that says one thing is better than another it if it no worse on any criteria and better on at least one criteria. We prefer Equation~\ref{eq:cdom} to boolean domination since we
-%  have a   5-goal optimization problem and it it is known that boolean domination often  fails for 3 or more goals~\cite{Wagner:2007,Sayyad:2013}.
-
-% The above equation is actually Pearson's correlation  where
-% all variables have been standardized.  To be applied
-% for discrete class learning (as done by KDP and this paper),
-% Hall et al. employ the Fayyad Irani discretizer~\cite{FayIra93Multi} then apply the following
-% entropy-based measure to infer $r$ (the degree of associations
-% between  discrete sets $X$ and $Y$):
-
-% \begin{equation}\label{eq:cfs}
-% r_{\mathit{xy}}=2\times \left[ \frac{H(x) + H(y) - H(x,y)}{H(y)+H(x)} \right]
-% \end{equation}
-% where $H$ is the standard information gain measure used in 
-% decision tree learning.
-% \lstset{language=Python}
-% \lstset{frame=lines} 
-% \lstset{label={lst:code_direct}}
-% \lstset{basicstyle=\footnotesize}
-% \begin{center}\begin{minipage}{2.5in}\begin{lstlisting}
-% def CFS(data):
-%   features = []
-%   score = -1
-%   while True:
-%     best = None
-%     for feature in range(data.features):
-%       features += [feature]
-%       tmp = merit( data, features) # see above equation
-%       if tmp > score:
-%         score = tmp
-%         bests = features
-%       features.pop()
-%     features += bests
-%     if not improve(score): break
-%   return features
-% \end{lstlisting}
-% \end{minipage}\end{center}
-% \end{figure}
-
-%  This algorithm works is  works in 6 stages.
-
-%     (1) \textbf{Feature Extraction:} In this stage the whole dataset is used to extract features from each project.
-This is done using the FSS algorithm as shown in~\ref{subsec:FSS}.
-Here each project is sent to the FSS and the FSS returns most suitable features for building models, we do this for every project and that information as a vector (i.e.
-a vector or length equal to total number of features, where 0,1 represents a feature being absent,selected) that represents each project.
-By performing this we have a vector representation of each project in the dataset.
-GENERAL uses this information to create the hierarchical clusters to find the communities.
-We perceive this is a good representation of community, as in this work we try to find community which has similar information distribution according to the attributes.
-Thus 2 projects with similar features selected have much higher chance of building similar models.
-
-%     (2) \textbf{Cluster Creation:} After the feature extraction has been done, the data is sent to a modified BIRCH algorithm.
-The algorithm requires a branching factor (i.e.
-Maximum number of CF sub-clusters in each node) and threshold value (i.e.
-when to form a new cluster based on radius).
-For this experiment we have set the branching factor as 20 and threshold value as 0.5.
-Using this version of BIRCH algorithm we build the hierarchical cluster, while storing all necessary details about the cluster like parent-child node, data points, level information, etc.
-This stage returns a Clustering Feature Tree (CF Tree) with all this information, which is passed to the next phase of experiment.
-
-%     (3) \textbf{Bellwether selection phase 1:} The CF Tree from the last phase is passed to the hierarchical bellwether.
-In this phase we use \textit{bellwether method} to identify bellwether at the leaf level.
-Using the CF Tree, we identify the clusters at the leaf level where each cluster represents the smallest community produced by the BIRCH algorithm in the last phase.
-Here we use the default ``Bellwether'' to perform a $ N*(N-1) $ comparison at each cluster.
-Here we select each project in the cluster one by one as a source dataset for transfer learning apply SMOTE as mentioned in sec~\ref{subsec:SMOTE} to handle any data imbalance and then use the FSS algorithm to get rid of any unnecessary attributes as mentioned in sec~\ref{subsec:FSS}.
-This informative and balanced dataset is used to build a LR model as mentioned in sec~\ref{subsec:LR} and we measure the performance of all other projects in the community (cluster).
-The performance measures that are used are mentioned in sec~\ref{sec:Measures}.
-To find the bellwether in each community we use cdom function to find the best source dataset among each cluster considering all performance measures.
-This phase returns a bellwether for each cluster at the leaf level of the CF Tree.
-
-%     (4) \textbf{Bellwether promotion:} In this phase of the algorithm is an iterative process, here we receive the selected bellwethers from the child clusters of each cluster in the level.
-This is called the bellwether promotion.
-Here each parent cluster instead of being represented by all projects within them, they are represented by only the bellwethers in them.
-
-%     (5) \textbf{Bellwether selection phase 2:} In this phase instead of finding a bellwether for each cluster at the level by performing a $ N*(N-1) $ comparison, we select the projects which represented as bellwether at the child nodes and then try to find a bellwether among them.
-So at each cluster at the level we perform a $ M*(M-1) $ comparison at each cluster where M is the selected bellwether from child clusters.
-This creates an order of magnitude faster \textbf{bellwether method}.
-This is again an iterative process, and the end of all the iterations, we will have a bellwether at each cluster at every level.
-
-%     (6) \textbf{Bellwether Prediction:} This is the transfer learning phase, when a new project is evaluated, we will use the FSS algorithm to get its features, then use the feature vectors to identify which cluster it belongs and use that cluster's bellwether as the transfer learning model.
-
-To Summarize, the algorithm works as follows -
+
+{\color{blue}
+\noindent
+To summarize, the algorithm works as follows -
 \bi
@@
 \item A hierarchical clustering algorithm BIRCH, uses the feature vectors for each project as representative for the project to create a hierarchical cluster.
-This returns a clustering tree, which includes information regarding which projects are in a certain cluster, each clusters child clusters and parent clusters.
-\item Use the clustering tree to find clusters in leaf level of the tree, to run a all pair comparison within each cluster to select a best model aka ``Bellwether''. 
+This returns a clustering tree, which includes information regarding which projects are in a certain cluster, each cluster's child clusters and parent cluster.
+\item Use the clustering tree to find clusters in leaf level of the tree, to run an all pair comparison within each cluster to select a best model aka ``Bellwether''. 
 \item We push up and store the bellwether found at leaf level to its parents.
-\item On the parent clusters we find the best models pushed from child nodes to run a all pair comparison between them to find the ``Bellwether'' in the parent clusters.
+\item On the parent clusters, we find the best models pushed from child nodes to run an all pair comparison between them to find the ``Bellwether'' in the parent clusters.
 \item We repeat the last 2 steps until we reach the root node.
@@
 \ei
+}
 
@@
 
-    \item \textbf{Avoid projects with lifespan less than one year:} Zhang et al. filtered out any  projects with a lifespan less than one year.
+    \item \textbf{Avoid projects with a lifespan of less than one year:} Zhang et al. filtered out any  projects with a lifespan of less than one year.
 
@@
 \ei
-These filters resulted in a training set of   697 projects\footnote{\href{http://tiny.cc/bellwether_data}{http://tiny.cc/bellwether\_data}}.
+These filters resulted in a training set of   697 projects\footnote{\href{http://tiny.cc/general\_data}{http://tiny.cc/general\_data}}.
 Fig~\ref{fig:meta} and fig~\ref{fig:lang_projects} shows the Distribution of projects depending on defect percentage, data set size, lines of code, number of files and project languages to confirm the projects selected comes from wide verity and representative of a software community.
@@
  Projects were divided
- randomly into train\_1 and test\_1 as a 90:10 split.
- \item
- The projects in train\_1 were used to find the bellwether .
- \item
- Each   project in test\_1 was  then divide into train\_2 and test\_2 (using a 2:1 split).
+ randomly into train\_1 and test\_1 as a 90:10 split (from a total of 697 projects, 627 projects are for train\_1 and remaining 70 for test\_1).
+ \item
+ The projects in train\_1 were used to find the bellwether.
+ \item
+ Each   project in test\_1 was  then divided into train\_2 and test\_2 (using a 2:1 split).
  \item
@@
 
-% \begin{figure}[!t]
-%     \centering
-%     \includegraphics[width=\linewidth]{figs/BUBBLE.png}
-%     \caption{GENERAL algorithm.}
-%     \label{fig:GENERAL}
-% \end{figure}
-
-% In this study we try to establish the presence of generality in SE datasets.
-We do this by analyzing the presence of bellwether incrementally by adding more and more projects and how the bellwether's predictive power changes.
-In this case to show the presence of generality in SE datasets the predictive power of the bellwether should look like the \textcolor{ao(english)}{GREEN} in figure~\ref{fig:predictive_power}, that is the predictive power of bellwether should increase or remains same, if our results look like the \textcolor{red}{RED} curve, that will show absence of generality in SE datasets.
-
-% In order to achieve this, we try to explore the \textit{bellwether effect} as mentioned in ~\ref{sec:related}.
-We know the default \textit{bellwether method} is very expensive ($ O(N^2) $).
-Thus in this paper we proposes an alternative transfer learning method (GENERAL), that explores \textit{bellwether effect} by exploring an order of magnitude faster \textit{bellwether method}.
-Our approach has three key components:
-
-% \bi
-
-%     \item A feature extractor to find a representation of each project, which will be used for clustering the projects.
-
-%     \item A hierarchical clustering model to use the features extracted from previous step to build the hierarchical cluster.
-
-%     \item A transfer learning model to identify bellwether in the hierarchical cluster.
-
-% \ei
-
-% GENERAL employs a few different algorithms to complete and compose it's 4 different components -
-
-% \subsubsection{\textbf{Feature Subset Selection (FSS):}}
-% \label{subsec:FSS}
-% To extract features from each dataset, we use a feature selector algorithm called Feature Subset Selection(FSS)~\cite{hall1999correlation,hall1997feature}.
-Which is a process of identifying and removing as much irrelevant and redundant information as possible.
-This is achieved using a correlation based feature evolution strategy to evaluate importance of an attribute and a best first search strategy with backtracking that moves through the search space by making local changes to the current feature subset.
-Here if the path being explored begins to look less promising, the best first search can back-track to a more promising previous subset and continue the search from there.
-Given enough time, a best first search will explore the entire search space, so it uses a stopping criterion (i.e.
-no improvement for five consecutive attributes).
-
-% {\small 
-% \begin{figure}[]
-%     \small 
-%     \inputminted[numbersep=2pt, linenos=true, fontsize=\small]{python}{pseudocode/cfs.py}
-%     \vspace{-0.2cm}
-%     \caption{Pseudo-code of Feature Subset Selection}
-%     \label{fig:GAP_pseudocode} 
-%     \vspace{-0.3cm}
-% \end{figure}
-% }
-
 \subsection{Learners}\label{mylearners}
 
-In this study, we applied the follow learners:
+In this study, we applied the following learners:
 
@@
 In this approach, the local project data is divided into a 90\% training set (which we call  train\_2)
-and a 10\% test set (which we call test\_2). After that, some some learner builds a model from the training data
+and a 10\% test set (which we call test\_2). After that, some learner builds a model from the training data
 (using the methods of \S\ref{sec:Experimental}),
@@
 the motivation of this paper: we do not
-seek   better predictor that is (say) more accurate
+seek a better predictor that is (say) more accurate
 than {\bf self}.
@@
 the majority class of the training data. Note that if anything we do performs worse that ZeroR, then there is no
-point to any of the learning technology explored in this paper.
+point in any of the learning technology explored in this paper.
 
@@
 What will we show is that GENERAL does better than {\bf Bellwether0} is three ways:
-(a) GENERAL is inherently more scalable; (b) GENERAL is (much) faster; and (c) GENERAL produced better predictions.
+(a) GENERAL is inherently more scalable; (b) GENERAL is (much) faster, and; (c) GENERAL produced better predictions.
 That is, our new GENERAL method is a significant improvement over the prior state-of-the-art.
@@
 cluster of the relevant leaf. Note that these level1 results come from an analysis of between 50 to 200  projects
-(depneding on the shape of the cluster tree genrated via BIRCH).
+(depending on the shape of the cluster tree generated via BIRCH).
 
@@
 \subsection{Statistical Tests}
-\label{stats}\label{eval}
-
-When comparing the results different models in this study, we used a statistical significance test and an effect size test. Significance test is useful for detecting if two populations
+% \label{stats}
+\label{eval}
+
+When comparing the results of different models in this study, we used a statistical significance test and an effect size test:
+\bi
+\item
+Significance test is useful for detecting if two populations
 differ merely by random noise. 
-Also, effect sizes are useful for checking that two populations differ by more than just a trivial amount.
+\item
+Effect sizes are useful for checking that two populations differ by more than just a trivial amount.
+\ei
 For the significance test,  we use the Scott-Knott procedure  recommended at TSE'13~\cite{mittas2013ranking} and ICSE'15~\cite{ghotra2015revisiting}.
 This technique recursively bi-clusters a sorted set of numbers.
-If any two clusters are statistically indistinguishable, Scott-Knott reports them both as one group.
-Scott-Knott first looks for a break in the sequence that maximizes the expected values in the difference in the means before and after the break.
+If any two clusters are statistically indistinguishable, Scott-Knott reports them both as belonging to the same ``rank''.
+
+To generate these ranks, Scott-Knott first looks for a break in the sequence that maximizes the expected values in the difference in the means before and after the break.
 More specifically,  it  splits $l$ values into sub-lists $m$ and $n$ in order to maximize the expected value of differences  in the observed performances before and after divisions.
-For e.g., lists $l,m$ and $n$ of size $ls,ms$ and $ns$ where $l=m\cup n$, Scott-Knott divides the sequence at the break that maximizes:
+For e.g., lists $l,m$ and $n$ of size $ls,ms$ and, $ns$ where $l=m\cup n$, Scott-Knott divides the sequence at the break that maximizes:
 \begin{equation}
@@
 
-% \subsection{Performance Measures}
-% \label{sec:Measures}
-
-% In this section, we introduce the following 5 evaluation measures used in this study to evaluate the performance of machine learning models.
-Suppose we have a dataset with M changes and N defects.
-After inspecting 20\% LOC, we inspected $m$ changes and found $n$ defects.
-Also, when we find the first defective change, we have inspected k changes.
-Using
-% this data, we can define 5 evaluation measures  as follows:
-
-% (1) \textbf{Recall:} This is the proportion of inspected defective changes among all the actual defective changes; i.e. $n/N$.
-% Recall is used in  many previous studies~\cite{kamei2012large,yang2016effort,yang2017tlel,xia2016collective,yang2015deep}.
-
-% (2) \textbf{Precision:} This is the proportion of inspected defective changes among all the inspected changes; i.e.
-$n/m$.
-A low Precision indicates that developers would encounter more false alarms, which may have negative impact on developers' confidence on the prediction model.
-
-% (3) \textbf{pf:} This is the proportion of all suggested defective changes which are not actual defective changes among all the suggested defective changes.
-A high {\em pf} suggests developers will encounter more false alarms which may have negative impact on developers' confidence in the prediction model.
-
-% (4) \textbf{popt20:} This is the proportion number of suggested defective changes among all suggested defective changes, when when 20\% LOC modified by all changes are inspected. 
-% A high {\em popt20} values mean that developers can find most bugs in a small percent of the code.
-% To compute Popt20, we divided the test set into the modules predicted to be faulty (set1)
-% and predicted to be bug-free (set2). Each set was then sorted in ascending order by lines 
-% of code.  We then ran down set1, then set2, till 20\% of the total lines of code
-% were reached-- at which point {\em popt20} is the percent of buggy modules seen up to that point.
-
-% (5) \textbf{ifa\_auc:} Number of  initial false alarms encountered before we find the first defect.
-Inspired by previous studies on fault localization~\cite{parnin2011automated, kochhar2016practitioners, xia2016automated}, we caution that if the top-k changes recommended by the model are all false alarms, developers would be frustrated and are not likely to continue inspecting the other changes.
-Parnin and Orso ~\cite{parnin2011automated} found that developers would stop inspecting suspicious statements, and turn back to traditional debugging, if they could not get promising results within the first few statements they inspect.
-Using the nomenclature reported about {\em ifa$=k$}.
-In this study we use a modified version of {\em ifa} called ifa\_auc, which calculates {\em ifa} based on efforts spent on inspecting the code.
-We use gradually increment the efforts spent by increasing the total LOC inspected and calculate ifa on each iteration to get the area under the curve (auc), here the x-axis is the percentage of effort spent on inspection and y-axis is {\em ifa}.
+\subsubsection{Interpreting the Scott-Knott Results}\label{sec:isk}
+
+{\color{blue} Scott-Knott divides a set of sorted numbers into ranks $1..x$  from lowest to the highest value.
+These ranks have a different interpretation, depending on whether we seek to minimize or maximize those numbers.
+For our purposes:
+\bi
+\item The first rank=1 is {\em worst} for recall, precision, Popt20 since we want to {\em maximize} these numbers.
+\item
+The first rank=1 is {\em best} for false alarms and ifa\_auc since we want to {\em minimize} those kinds of errors
+\ei
+\respto{3-9}
+Note one special case of the above.
+In the following results, we will see that ZeroR rarely predicts anything as defective.
+hence, it has a very low recall (median=0\%) but {\em also} a  very low false alarm and very low ifa\_auc rate.
+That is to say, ZeroR makes no mistakes since it rarely suggests anything at all.
+Accordingly, we will not be recommending ZeroR for defect prediction.}
 
@@
 {\color{blue} 
-\subsection*{RQ1: How slow is conventional bellwether method? }
-\label{sec:rq3}
-\respto{1-2}\respto{1-6a} Conventional bellwether as proposed by Krishna et al.
+\subsection*{RQ1:  How slow are   conventional bellwether methods? }
+\label{sec:rq1}
+\respto{1-6a} Conventional bellwether as proposed by Krishna et al.
 compares all projects in a given community with all others to build defect prediction models and compare with each other.
-This operation is quite expensive, which has a $ O(n^2) $ computational complexity.
-In this experiment we used this conventional bellwether to make a baseline comparison with 627 projects (697 in total) in the community.
-Figure~\ref{fig:compare} showed that, the conventional bellwether did a total of {\em 393129} comparisons, while taking {\em 72} hours (with SMOTE and CFS) or {\em 10648} seconds (without SMOTE and CFS) to complete.
+This operation is quite expensive, which has an $ O(n^2) $ computational complexity.
+In this experiment, we used this conventional bellwether to make a baseline comparison with 697 projects (627 projects in training and 70 projects in testing) in the community.
+Figure~\ref{fig:compare} showed that the conventional bellwether did a total of {\em 393129} comparisons, while taking {\em 72} hours (with SMOTE and CFS) or {\em 10648} seconds (without SMOTE and CFS) to complete.
 In summary we conclude
 
-\begin{RQ}{Conventional bellwether method as proposed by krishna et al~\cite{krishna2018bellwethers,krishna16a} uses a $ O(N^2) $ comparisons to find the ``bellwether'' among a community of N (697 projects in this experiment) projects.
-In this experiment the conventional bellwether method is very expensive to find the ``bellwether''.}
-\end{RQ}
-}
+\vspace{2mm}
+   \begin{blockquote}
+              \noindent {\bf
+              The conventional bellwether method as proposed by Krishna et al~\cite{krishna2018bellwethers,krishna16a} is slow since it requires  $ O(N^2) $ comparisons to find   one bellwethers within a community of N  projects.}
+            \end{blockquote}}
 
 {\color{blue} 
-\subsection*{RQ2: How fast is GENERAL bellwether?}
-\label{sec:rq3}
+\subsection*{RQ2: In theory, how much faster is GENERAL's hierarchical clustering?}
+\label{sec:rq2}
 The new bellwether method proposed in this paper uses a hierarchical clustering, then finds bellwether at leaf level clusters and pushes up bellwethers to parent nodes for comparisons.
 This process reduces the computational complexity to $O(m*(N/m)^2)$ on an average case (assuming the hierarchical clustering creates m cluster at leaf level).
-When compared with conventional bellwether, figure~\ref{fig:compare} shows the new bellwether only requires {\em 9583} comparisons\, which is order of magnitude less comparisons.
-Figure~\ref{fig:compare_time} and \ref{fig:time} shows the new method only takes {\em 362} seconds (without SMOTE and CFS) to complete and {\em 1.5} hours (with SMOTE and CFS).
-In summary we can say
-
-\begin{RQ}{The new bellwether method (GENERAL), which is a combination of hierarchical clustering and bellwether method achieves  a computational complexity of $O(m*(N/m)^2)$, which is much faster than conventional bellwether.}
-\end{RQ}
-}
+In theory, this is faster than the $O(N^2)$ computation reported for {\bf RQ1}.
+When compared with conventional bellwether, Figure~\ref{fig:compare} shows the new bellwether only requires {\em 9583} comparisons\, which is an order of magnitude fewer comparisons.
+Figure~\ref{fig:compare_time}   shows the new method only takes {\em 362} seconds (without SMOTE and CFS) to complete and {\em 1.5} hours (with SMOTE and CFS).
+In summary, we can say:}
+
+\begin{blockquote}
+              \noindent {\bf              GENERAL is theoretically much faster since
+             its computational complexity is  $O(m*(N/m)^2)$.
+            }\end{blockquote}
 
 \subsection*{RQ3:  In practice,
-            can the hierarchical clustering of GENERAL tame slow runtimes seen in   bellwether-based reasoning?}
+            how fast is  GENERAL?}
 \label{sec:rq3}
 
-% In the literature, we saw most of the previous studies have shown bellwether effect with very small datasets.
-In order to use bellwether to prove presence of generality in SE domain datasets, we first have to showcase the bellwether method suggested by Krishna et al.
-in their experiment works for large datasets.
-We use our defect prediction dataset with 697 projects for this purpose.
-
-% We divide the dataset in train\_1 and test\_1 set and then performed a $ N*(N-1) $ comparison on all the projects in train\_1 set to find a bellwether, and then dividing each project in test\_1 set into train\_2 and test\_2 using a train\_test split.
-We use the train\_2 to train a LR model and test on test\_2 which is represented as \textit{self} in the figures.
-Similarly we use the bellwether project from train\_1 to train a LR model and test it on test\_2 which is represented as \textit{bellwether0}.
-We use statistical tests mentioned in section~\ref{stats} to compare the performance of \textit{self} vs \textit{bellwether0} for all the performance measures mentioned in section~\ref{sec:Measures}, which is shown
-
-\respto{1-6c}\fig{Pseudo-code} showed that, theoretically,
+\respto{1-6b}{\color{blue} \fig{Pseudo-code} showed that, theoretically,
 GENERAL is an inherently faster approach than traditional bellwether methods.
@@
 we ran the rig of \fig{GENERAL} on
-an four core machine running at 2.3GHz with 8GB of RAM.
-
-\begin{figure}[!b]
-    \centering
-    \includegraphics[width=\linewidth]{figs/Time.png}
-    \caption{Mean runtime for for one run of standard bellwether and GENERAL (With SMOTE and CFS).}
-    \label{fig:time}
-\end{figure}
-
-\begin{figure}[!b]
+a four core machine running at 2.3GHz with 8GB of RAM.}
+
+\begin{figure}[!t]
     \centering
     \includegraphics[width=\linewidth]{figs/Time_Compare.pdf}
-    \caption{Mean runtime for for one run of standard bellwether and GENERAL with different community size.}
+    \caption{Mean run-time required for finding a bellwether in a single run of standard bellwether and GENERAL with different community size.}
     \label{fig:compare_time}
@@
 
-\begin{figure}[!b]
+\begin{figure}[!t]
     \centering
     \includegraphics[width=\linewidth]{figs/compare.pdf}
-    \caption{Number of comparison one run of standard bellwether and GENERAL with different community size.}
+    \caption{Number of comparisons required for finding a bellwether in a single run of standard bellwether and GENERAL with different community sizes.}
     \label{fig:compare}
@@
 
-\fig{compare} shows the mean number of comparisons required for finding a bellwether using conventional bellwether versus GENERAL for different community size of 45,90, 180, 360 and 627 projects.
-We can see from the \fig{compare} for increasing community size the number of comparisons required increases rapidly for conventional bellwether, while with GENERAL the number of comparisons required are comparatively small.
+{\color{blue}\fig{compare_time} and \fig{compare} shows the mean number of comparisons and mean run time required for finding a bellwether, using conventional bellwether method versus GENERAL for different community size of 45,90, 180, 360 and 627 projects.
+We can see from \fig{compare_time} and \fig{compare} for increasing community size the number of comparisons and time required increases rapidly for conventional bellwether method, while with GENERAL the number of comparisons required is relatively small.
 This shows the new bellwether method (aka GENERAL) is scalable with increasing community size.
-
-similarly \fig{compare_time} shows the mean run times for one run of GENERAL versus traditional bellwether for different community size of 45,90, 180, 360 and 627 projects.
-It is evident from the figure with growing community size the new bellwether method takes lesser amount of time ($\approx 4$ times faster in community size of 50 while $\approx 30$ times faster in a community size of 627 projects ).
-
-\fig{time} shows the mean run times for one run of GENERAL versus traditional bellwether (with SMOTE and CFS) for a community size of 627 projects .
-For certification purposes, this had to be repeated 20 times.
+}
+
+In this study, we also recorded the mean run times for a single run of GENERAL versus traditional bellwether (with SMOTE and CFS) for a community size of 627 projects.
+For certification purposes, all experiments had to be repeated 20 times.
 In that certification run:
@@
 The $O(m*(N/m)^2)$ analysis
-of GENERAL needed 30  hours. That is, in empirical result consistent with the theoretical predictions of figure~\ref{fig:Pseudo-code}, GENERAL runs much faster than traditional bellwether.
+of GENERAL needed 30  hours. That is, in empirical results consistent with the theoretical predictions of Figure~\ref{fig:Pseudo-code}, GENERAL runs much faster than the traditional bellwether.
 \item 
@@
 If we were merely seeking conclusions from one project, then we would recommend ignoring bellwethers and just use results from each project.
-That said, we still endorse bellwether method since  we seek lessons that hold across many projects.
+That said, we still endorse bellwether method since  we seek knowledge that holds across many projects.
 
@@
 
-\begin{RQ}{Theoretically and empirically, the  hierarchical reasoning on GENERAL performs much faster than standard bellwether methods.}
-\end{RQ}
-
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %%%%%%%%%%%%%%%%%%%%%%%Latex Table%%%%%%%%%%%%%%%%%%%%%%%%%
-% \begin{figure}[!b]
-% {\scriptsize
-% {\scriptsize \begin{tabular}{p{.1cm}lp{1.5cm}rrc}
-% \arrayrulecolor{darkgray}
-% \rowcolor[gray]{.9}  & rank & treatment & mean & sd & \\
-%  \multirow{5}{*}{\rotatebox[origin=c]{90}{Recall}} 
-%   &   1 &      GENERAL\_level2 &    38 &  32 & \quart{22}{38}{32}{16} \\
-%   &   1 &      bellwether0 &    39 &  31 & \quart{23}{39}{31}{15} \\
-%   &   1 &  ZeroR &    40 &  49 & \quart{16}{40}{49}{25} \\
-%   &   2 &      GENERAL\_level1 &    48 &  33 & \quart{31}{48}{33}{16} \\
-%   &   3 &      self &    55 &  27 & \quart{41}{55}{27}{12} \\
-%   &   3 &      GENERAL\_level0 &    56 &  31 & \quart{42}{56}{31}{16} \\
-%   &   4 &      global &    78 &  40 & \quart{57}{78}{40}{20} \\ \hline
-% \multirow{5}{*}{\rotatebox[origin=c]{90}{Pf}} 
-%   &  1 &      GENERAL\_level2 &    28 &  28 & \quart{14}{28}{28}{13} \\
-%   &  1 &      bellwether0 &    28 &  25 & \quart{15}{28}{25}{11} \\
-%   &  1 &      self &    30 &  20 & \quart{20}{30}{20}{10} \\
-%   &  1 &      GENERAL\_level1 &    35 &  28 & \quart{21}{35}{28}{14} \\
-%   &  1 &      ZeroR &    39 &  49 & \quart{15}{39}{49}{25} \\
-%   &  2 &      GENERAL\_level0 &    47 &  31 & \quart{31}{47}{31}{15} \\
-%   &  3 &      global &    79 &  39 & \quart{59}{79}{39}{19} \\\hline
-% \multirow{5}{*}{\rotatebox[origin=c]{90}{Precision}} &   1 &      ZeroR &    21 &  30 & \quart{6}{21}{30}{15} \\
-%     &  2 &      global &    35 &  28 & \quart{21}{35}{28}{14} \\
-%     &   2 &      GENERAL\_level2 &    39 &  34 & \quart{22}{39}{34}{17} \\
-%     &   2 &      bellwether0 &    40 &  33 & \quart{23}{40}{33}{16} \\
-%     &   2 &      GENERAL\_level1 &    42 &  31 & \quart{26}{42}{31}{15} \\
-%     &   2 &      GENERAL\_level0 &    44 &  30 & \quart{28}{44}{30}{15} \\
-%     &   2 &      self &    50 &  30 & \quart{35}{50}{30}{15} \\\hline
-% \multirow{5}{*}{\rotatebox[origin=c]{90}{Popt20}} &   1 &      ZeroR &    13 &  16 & \quart{5}{13}{16}{8} \\
-%   & 2 &      GENERAL\_level2 &    26 &  22 & \quart{15}{26}{22}{11} \\
-%   &  2 &      global &    26 &  13 & \quart{19}{26}{13}{6} \\
-%   &  2 &      bellwether0 &    28 &  21 & \quart{17}{28}{21}{9} \\
-%   &  2 &      GENERAL\_level0 &    28 &  15 & \quart{22}{28}{15}{8} \\
-%   &  2 &      GENERAL\_level1 &    28 &  19 & \quart{19}{28}{19}{9} \\
-%   &  3 &      self &    35 &  19 & \quart{26}{35}{19}{10} \\\hline
-% \multirow{5}{*}{\rotatebox[origin=c]{90}{ifa\_auc}} &   1 &      ZeroR &    7 &  11 & \quart{1.12}{6.77}{11.29}{5.65} \\
-%   &  2 &      global &    19 &  16 & \quart{11.35}{19.38}{16.06}{8.03} \\
-%   &  3 &      GENERAL\_level2 &    22 &  14 & \quart{14.48}{21.59}{14.21}{7.10} \\
-%   &  3 &      bellwether0 &    23 &  14 & \quart{15.48}{22.56}{14.15}{7.07} \\
-%   &  3 &      self &    23 &  12 & \quart{17.09}{22.93}{11.68}{5.84} \\
-%   &  3 &      GENERAL\_level1 &    23 &  14 & \quart{16.10}{22.98}{13.74}{6.87} \\
-%   &  3 &      GENERAL\_level0 &    25 &  13 & \quart{17.87}{24.51}{13.27}{6.63} \\
-% \end{tabular}}
-% }
-% \caption{Statistical Results comparison. The ``rank`` column at left comes from
-% the statistical analysis methods of \S\ref{eval}. Note that for {\em pf}, and {\em ifa} rank=1 is the best rank while for all other performance measures, ranks $\in{3,4}$ are best. 
-% }\label{fig:Statistical}
-% \end{figure}
+\begin{blockquote}
+              \noindent {\bf    
+                When learning bellwethers from 697 projects,  GENERAL and   traditional   approaches terminated in 1.5 and 72 hours (respectively).
+That is to say,  GENERAL is far faster than standard bellwether methods.}
+            \end{blockquote}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%Latex Table%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%Latex Table%%%%%%%%%%%%%%%%%%%%%%%%% \rowcolor[gray]{.9}
 \begin{figure}[!b]
@@
 \arrayrulecolor{darkgray}
-\rowcolor[gray]{.9}  & rank & treatment & median & IQR & \\
+\rowcolor[HTML]{C0C0C0}  & rank & treatment & median & IQR & \\ 
  \multirow{5}{*}{\rotatebox[origin=c]{90}{Recall}} 
@@
   & 3 &      self &    57 &  34 & \quart{41}{57}{34}{17} \\
-  & 4 &      global &    100 &  12 & \quart{88}{100}{12}{0} \\ \hline
+  &\rowcolor[gray]{0.9} 4 &      global &    100 &  12 & \quart{88}{100}{12}{0} \\ \hline
 \multirow{5}{*}{\rotatebox[origin=c]{90}{Pf}} 
@@
   & 1 &      self &    25 &  23 & \quart{17}{25}{23}{15} \\
-  & 1 &      GENERAL\_level1 &    33 &  41 & \quart{10}{33}{41}{18} \\
+  &\rowcolor[gray]{.9} 1 &      GENERAL\_level1 &    33 &  41 & \quart{10}{33}{41}{18} \\
   & 2 &      GENERAL\_level0 &    45 &  43 & \quart{24}{45}{43}{22} \\
@@
   & 2 &      GENERAL\_level2 &    36 &  65 & \quart{0}{36}{65}{29} \\
-  & 2 &      GENERAL\_level1 &    41 &  54 & \quart{13}{41}{54}{26} \\
+  &\rowcolor[gray]{.9} 2 &      GENERAL\_level1 &    41 &  54 & \quart{13}{41}{54}{26} \\
   & 2 &      GENERAL\_level0 &    41 &  47 & \quart{20}{41}{47}{26} \\
@@
   & 2 &      GENERAL\_level1 &    31 &  23 & \quart{17}{31}{23}{9} \\
-  & 3 &      self &    36 &  20 & \quart{27}{36}{20}{11} \\ \hline
+  &\rowcolor[gray]{.9} 3 &      self &    36 &  20 & \quart{27}{36}{20}{11} \\ \hline
 \multirow{5}{*}{\rotatebox[origin=c]{90}{ifa\_auc}} 
-  & 1 &      ZeroR &    0 &  11 & \quart{0}{0}{11}{11} \\
+  &\rowcolor[gray]{.9} 1 &      ZeroR &    0 &  11 & \quart{0}{0}{11}{11} \\
   & 2 &      global &    15 &  29 & \quart{6}{15}{29}{20} \\
@@
 the statistical analysis methods of \S\ref{eval}.
-Note that for {\em pf}, and {\em ifa}, which we want to minimize, low rank (i.e.
-rank=1) is the best rank while for other performance measures where we want to maximize, ranks  such as $\in{3,4}$ are better.
+In this figure, the {\bf best} ranks are highlighted in gray,
+As discussed in \S\ref{sec:isk}, since we want to minimize {\em pf}, and {\em ifa\_auc} then the {\em lowest ranks} (i.e. rank=1) are   {\em best}. But for other measures,
+which we want to maximize (recall, precision, Popt20), the {\em largest ranks} are {\em best}. 
 }\label{fig:Statistical}
@@
 
-% {\small 
-% \begin{figure*}[!t]
-%     \centering
-%     \begin{tikzpicture}[nodes={draw, circle,fill=darkgray!60}, ->,sibling distance=.7cm,minimum size=.1cm,scale=.5]
-
-%     \node{627}
-%         child { node {57}
-%             child {node {9}} 
-%             child {node {9}} 
-%             child {node {7}} 
-%             child {node {17}}
-%             child {node {13}}}
-%         child [missing]
-%         child [missing]
-%         child [missing]
-%         child [missing]
-%         child [missing]
-%         child [missing]
-%         child [missing]
-%         child { node {127} 
-%             child {node {3}} 
-%             child {node {9}} 
-%             child {node {19}} 
-%             child {node {15}}
-%             child {node {4}}
-%             child {node {17}} 
-%             child {node {15}} 
-%             child {node {19}} 
-%             child {node {11}}
-%             child {node {15}}}
-%         child [missing]
-%         child [missing]
-%         child [missing]
-%         child [missing]
-%         child [missing]
-%         child [missing]
-%         child [missing]
-%         child [missing]
-%         child [missing]
-%         child [missing]
-%         child [missing]
-%         child [missing]
-%         child { node {183} 
-%             child {node {8}} 
-%             child {node {3}} 
-%             child {node {12}} 
-%             child {node {16}}
-%             child {node {20}}
-%             child {node {18}} 
-%             child {node {12}} 
-%             child {node {4}} 
-%             child {node {12}}
-%             child {node {16}}
-%             child {node {5}}
-%             child {node {17}} 
-%             child {node {9}} 
-%             child {node {9}} 
-%             child {node {10}}
-%             child {node {14}}}
-%         child [missing]
-%         child [missing]
-%         child [missing]
-%         child [missing]
-%         child [missing]
-%         child [missing]
-%         child [missing]
-%         child [missing]
-%         child [missing]
-%         child [missing]
-%         child [missing]
-%         child [missing]
-%         child [missing]
-%         child [missing]
-%         child [missing]
-%         child [missing]
-%         child [missing]
-%         child { node {260} 
-%             child {node {17}} 
-%             child {node {17}} 
-%             child {node {20}} 
-%             child {node {14}}
-%             child {node {9}}
-%             child {node {13}} 
-%             child {node {18}} 
-%             child {node {10}} 
-%             child {node {18}}
-%             child {node {10}}
-%             child {node {6}} 
-%             child {node {15}} 
-%             child {node {14}} 
-%             child {node {9}}
-%             child {node {10}}
-%             child {node {8}} 
-%             child {node {7}} 
-%             child {node {13}} 
-%             child {node {15}}}
-%             ;
-% \end{tikzpicture}
-%     \caption{Example of Hierarchical Clustering for 627 projects}
-%     \label{fig:example tree}
-% \end{figure*}
-% }
 %%%%%%%%%%%%%%%%%%%%%%%End Latex Table%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[!t]
+\begin{figure*}[!b]
     \centering
-    \includegraphics[width=\linewidth]{figs/bubble.pdf}
+    \includegraphics[width=.9\linewidth]{figs/bubble.pdf}
     \caption{Example of Hierarchical Clustering for 627 projects}
@@
 Figure~\ref{fig:Statistical} shows the distribution of
-performance score results seen in
-of \fig{GENERAL}. These results are grouped together by the ``rank'' score
+performance score results seen in \fig{GENERAL}. These results are grouped together by the ``rank'' score
 of the left-hand-side column 
@@
 As to {\em ZeroR}, we cannot recommend that approach.
-While {\em ZeroR} 
-makes few mistakes (low {\em ifa}s and low {\em pf}s), it scores badly
-on   other measures (very low {\em recall}s  and {\em popt(20)}.
+ZeroR is a method where we predict everything as the majority class.
+In Figure~\ref{fig:Statistical}, ZeroR model has a median recall, precision and pf of zero. 
+That is, this method has very few errors since it offers very few suggestions on what might be defective.
+As discussed at the end of   \S\ref{sec:isk}, we cannot recommend such a method.
 
@@
 By all the measures of
-Figure~\ref{fig:Statistical},   the {\em bellwether0} are in the middle of the pack. That is:
+Figure~\ref{fig:Statistical},   the {\em bellwether0} is in the middle of the pack. That is:
 \bi
@@
 compared to hierarchical bellwether,
- there is no evidence here of a performance
-benefit from using  traditional bellwether.
-\item
-Given this lack luster performance, 
-and   the {\bf RQ3} results (where traditional bellwether ran very slowly), we therefore  
+ there is no evidence here of better performance
+  from    traditional bellwethers.
+\item
+Given this weak performance, 
+and   the {\bf RQ3} results (where traditional bellwether ran very slowly), we, therefore,  
 deprecate the traditional bellwether approach.
@@
 and {\em precision}, there is no significant differences.
-\item In terms of {\em recall} there is no statistical difference in the rank
+\item For {\em recall} there is no statistical difference in the rank
 of  local learning with {\em self} and 
@@
 (a bellwether
-generated from the root of a BIRCH cluster tree) and 
-\item In terms of {\em pf} (false alarms), some of the GENERAL results are ranked
+generated from the root of a BIRCH cluster tree); 
+\item In terms of {\em pf} (false alarms) and Popt20, some of the GENERAL results are ranked
 the same as {\em self} (and we will expand on this point, below).
 \ei
-Overall, we summarize the Figure~\ref{fig:Statistical} results as follows:
+In part, we summarize Figure~\ref{fig:Statistical} results as follows:
 
@@
 
-\begin{RQ}
-{Measured in terms of predictive performance,
-the effectiveness of hierarchical bellwethers
-is very similar to local learning
-(and these two methods are more effective
-than the other options explored here). }
-\end{RQ}
-
-When two options have similar predictive
-performance, then other criteria can be used
-to select between them:
-\bi
-\item If the goal is to quickly generate
-conclusions about one project, then we would recommend
-local learning since (as seen above), local learning is five
-times faster than hierarchical bellwether.
-\item
-But, as said at the start
-of \S\ref{sec:results},
-our goal is to quickly generalize across hundreds of
-projects. 
-\ei
+ \begin{blockquote}
+              \noindent {\bf  
+                Across multiple performance criteria, the faster GENERAL bellwether algorithm never performs worse that standard bellwether.
+And measured in terms of recall and false alarm, GENERAL performs statistically much better.}
+            \end{blockquote}
+
+ This summary does not address an important issue, discussed in {\bf RQ5}.
+
+\begin{figure*}[!b]
+    \centering
+    \includegraphics[width=\linewidth]{figs/fss.pdf}
+    \caption{Distribution of features selected using self model and ``Bellwether'' model. Bars in red denote features found in the GENERAL\_level1 models (see Table~\ref{tbl:coefs_4}). }
+    \label{fig:FSS_level1}
+\end{figure*}
 
@@
 \respto{2-21}{\color{blue}
-This sections ask if conclusions always improve as we learn from more and more data.
+This section ask if conclusions always improve as we learn from more and more data.
 This can be an issue since if a new project
-is fundamentally different to all past projects, then irrelevant ideas from the past will be
+is fundamentally different from all past projects, then irrelevant ideas from the past will be
 inappropriately applied to the present situation.  
@@
 \item
-The bellwether found at level 0 of the tree
-(which we call {\em GENERAL\_level0}) is learned from 627 projects.
+The bellwether found at level 0 of the tree (which we call {\em GENERAL\_level0}) is learned from 627 projects.
 \item
 The bellwethers found at level 1 of the tree
-(which we call {\em GENERAL\_level1}) is learned from four sub-groups
-of our projects.
+(which we call {\em GENERAL\_level1}) is learned from four  groups
+of   projects.
 \item
 The bellwethers found at level 2 of the tree
-(which we call {\em GENERAL\_level2}) is learned from 80
-sub-sub groups of our projects.
-\ei
-That is, to answer {\bf RQ5} we need only compare the predictive performance
-of models learned from these different levels. In that comparison,
-if the level\_$(i+1)$ bellwethers generated better predictions
-that the   level\_$(i)$ bellwethers, then we would conclude that it is best to learn lessons from smaller groups
-of projects.
-
-Figure~\ref{fig:Statistical} lets us
-compare the performance of the bellwethers learned from different 
-levels:
+(which we call {\em GENERAL\_level2}) are learned from 58   groups of   projects.
+
+\ei
+From this list, we make two comments:
+\bi
+\item Firstly, we note if we just use the results from  
+{\em GENERAL\_level0} then we are returning just one model. However, if we use the results from {\em GENERAL\_level1}, then we will return a  handful
+of bellwethers. In this regard, GENERAL is different from traditional bellwethers since this new method can return multiple models, each specialized for a different set of projects.
+\item
+Second, we note that to answer {\bf RQ5} we need only compare the predictive performance of models learned from these different levels.
+In that comparison, if the level\_$(i+1)$ bellwethers generated better predictions that the   level\_$(i)$ bellwethers, then we would conclude that it is best to learn knowledge from smaller groups of projects.
+\ei
+Figure~\ref{fig:Statistical} lets us compare the performance of the bellwethers learned from different levels:
 \bi
@@
 \item
-Slightly different results are offered in the {\em pf} false alarm results. Here,  levels2,1,0 bellwether are respectively ranked best, best, worst.
-\ei
-
-To put that another way, the answer to ``is is possible to learn from too much data'', is ``depends on what you value'':
-\respto{3-13}{\color{blue}
-\bi
-\item
-For risk-adverse development, it is best to use all data to learn the bellwether
-since that finds most defects.
-\item
-On the other hand, for cost-adverse development (where cutting development cost
-is more important than removing
-bugs), then there seems to be a ``Goldilocks zone'' where
-the bellwether is learned from just enough data (but not too much or too little).
-\ei
-}
-That is, these results say that:
-
-\begin{RQ}
-{Assessed in terms of {\em recall},
-it is better to learn bellwethers from more data rather than less.
-But assessed in terms of {\em false alarms}, 
-while learning bellwethers
-from many projects is useful, it is possible to learn from too much data.} 
-\end{RQ}
-
-% In this section, we return to 
-% In RQ4, we try to answer the question if learning from too many projects detrimental effect, this question has two parts, one on predictive power, the other on making general conclusion and conclusion instability.
-Figure~\ref{fig:Statistical} shows the results of statistical significance and effect size tests to rank them in order for all the different methods(treatments) used in this experiment.
-In this figure for a performance measure two methods showing same rank means there performance is not statistically significantly different, while a different ranks mean they are different, while a smaller rank is better if the performance goal is negative (i.e.
-Pf), and higher rank is better in case of positive goal (i.e.
-Recall).
-
-% To answer the first part of the question, if learning from too many projects have detrimental effect on predictive power of models, we compare the results of default ``bellwether method'' (a.k.a bellwether0) proposed by Krishna et al.
-and GENERAL(a.k.a GENERAL\_level0) method.
-The results of scott-knott test shows that for positive goals such as Recall the GENERAL\_level0 is significantly doing better than Bellwether0 and it is doing as good as or better for precision ans recall.
-While for negative goals such as ifa\_auc GENERAL\_level0 is doing as good as bellwether0.
-Although in case of Pf they score different ranks with GENERAL showing higher Pf then bellwether0, it is not by much.
-Similarly while comparing GENERAL\_level0 with global (which is learning from all the projects) shows although it achieves higher Recall, but it has very high Pf, low precision.
-Which answers the first part of the question that learning from too many projects do have detrimental effect on predictive power of models.
-
-% Now to answer the second part of the question, that is if learning from too many projects creates conclusion instability, we will look at figure~\ref{fig:FSS_compare}.
-Figure~\ref{fig:FSS_compare} show the distribution of attributes selected while building a ML model for defect prediction using local models(a.k.a self), the \textcolor{red}{{\bf red bars}} shows the attributes selected by the ``Bellwether Project''.
-Conclusion instability causes vastly different and often contradicting conclusions to be derived from a data source.
-This sort of instability is very prevalent in several domains of software engineering.
-We can see from figure~\ref{fig:FSS_compare}, when learning from local data, each model selected different sets of attributes and resulted in selecting almost all different attributes.
-That means there is no general conclusion can be drawn for defect prediction models by saying which attributes are important, this results in conclusion instability and that effects the trusts on those models, the insights that can be drawn from them.
-Which farther affects training and tool development as mentioned in sec~\ref{sec:Motivation}.
-From these results we can see learning from too many data can cause conclusion instability and thus affecting generality in SE domain.
-In Summary, we can say
-
-\begin{figure*}[h]
-    \centering
-    \includegraphics[width=\linewidth]{figs/FSS_compare.png}
-    \caption{Distribution of features selected using self model and ``Bellwether'' model.}
-    \label{fig:FSS_compare}
-\end{figure*}
-
-\subsection*{RQ6: What exactly did we learn from all those projects?}
+Worse results are seen in the {\em pf} false alarm rates using models learned from the top of the cluster tree.
+\ei
+In summary, measured in terms of false alarm rates,
+our results say that it is possible to learn from too much data. Based on Figure~\ref{fig:Statistical}, we say that it is better to use the multiple models generated by
+{\em GENERAL\_level1} since this has a lower false alarm
+rate than the single model
+generated by {\em GENERAL\_level0}. Hence, for this research question, we conclude:
+
+   \begin{blockquote}
+              \noindent {\bf  
+            Learning from  a few hundred  projects is better
+than learning from just a few dozens   projects.
+But after generalizing over 200 projects (approx), the learned
+model start degrading.  
+  }\end{blockquote}
+
+To say that another way,   when learning from a very large number of projects (hundreds), they may be useful
+to learn a handful of bellwethers, each of which covers (say) just a few hundred projects. In this regard,
+GENERAL is better than prior bellwether algorithms
+since GENERAL can find multiple bellwethers while
+older methods only ever find one.
+
+\section{Discussion}
 \label{sec:rq6}
 
-Having demonstrated that we can quickly find bellwethers
-from hundreds of software projects, it is appropriate to ask
-what model was learned from all that data. This is an important question for this research since if  we cannot show the lessons
-learned from our 627 projects, then all the above is wasted effort.
-
-Table~\ref{tbl:coefs}  shows the weights learned by logistic
-regression after feature selection using the bellwether project
-selected by {\em GENERAL\_level0}. Note that:
-\bi
-\item
-The number of features that appear in Table~\ref{tbl:coefs}  is much smaller than the list of features shown in Table~\ref{tbl:metric}.
-That is, our bellwether is reporting that only a few features
-are most important for predicting software defects.
-\item
-Table~\ref{tbl:coefs}  is sorted by the absolute value of the weights
-associated with those features. The last two features have near
-zero weights; i.e. they have negligible effect.
-\ei
-Apart from the negligible features, all that is left are NPRM, NPNM, RFC , and CBO. As shown in Table~\ref{tbl:metric}, these features
-all relate to class interface concepts; specifically: 
-\bi
-\item
-The number of public and private methods; 
-\item
-The  average number of methods that respond to an incoming message; 
-\item
-Inter-class coupling. 
-\ei
+One lesson learned from this work is that
+features that seem useful (based on some local analysis),
+may not actually be generally useful
+(based on a more global analysis).
+To see this, we need to compare the
+features seen in
+Table~\ref{tbl:coefs_4} and
+\fig{FSS_level1}
+
+  Table~\ref{tbl:coefs_4} 
+ shows what  features were generally
+ ``globally important'' 
+ Here, by ``globally important'' we mean that the features were found in
+  one of the four models generated from  {\em GENERAL\_level1}. Also,
+  the $\beta$ coefficient on those features was not  close to zero (where ``close'' means $-0.1 \le \beta \le 0.1$).
+We   say that the  features  of Table~\ref{tbl:coefs_4}   are ``globally important''
+  since our analysis shows that, across many data sets,
+  they are the ones that most predict for defects.
+
+\fig{FSS_level1} shows what features were found to be ``locally important'' within specific data sets. 
+ Recalling \S\ref{sec:dm}, we say that a feature is
+ ``locally important'' if the CFS feature selection algorithm found that it was amongst the features
+ that best presented for defects within each data set. This figure counts how often a particular feature was selected across our 697 projects. 
+ We call these features   ``locally important''
+ since these results come from an analysis that is restricted to just one data set.
+
 \begin{table}[!t]
 \centering
-\begin{tabular}{|l|l|l|l|} \hline
-Rank & Attr               & coef  & Odds ratio \\ \hline
-1    & avg\_NPRM          & 2.23  & 9.26      \\ \hline
-2    & avg\_NPBM          & -1.31 & 0.27      \\ \hline
-3    & max\_NPBM          & -1.12 & 0.33      \\ \hline
-4    & max\_RFC           & 0.74  & 2.09      \\ \hline 
-5    & total\_NPBM        & -0.70 & 0.50      \\ \hline
-6    & max\_CBO           & -0.64 & 0.53      \\ \hline
-7    & total\_ModifiedLOC & 0.10  & 1.10      \\ \hline
-8    & avg\_WMC           & 0.07  & 1.07     \\ \hline
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+\rowcolor[HTML]{C0C0C0} 
+Attributes & Cluster 1 & Cluster 2 & Cluster 3 & Cluster 4 \\ \hline
+NRev       & \bluecheck         &           &           &           \\ \hline
+NFix       &           & \bluecheck         &           &           \\ \hline
+LOC        & \bluecheck         & \bluecheck         &           &           \\ \hline
+CC         & \bluecheck         &           &           &           \\ \hline
+NIV        & \bluecheck         &           & \bluecheck         &           \\ \hline
+NPM        & \bluecheck         &           & \bluecheck         &           \\ \hline
+CBO        &           & \bluecheck         &           &           \\ \hline
+FANOUT     &           &           & \bluecheck         &           \\ \hline
+CL         &           &           & \bluecheck         & \bluecheck         \\ \hline
+RCC        &           &           &           & \bluecheck         \\ \hline
+NOC        &           &           & \bluecheck         & \bluecheck         \\ \hline
 \end{tabular}
-
-\caption{Importance of coefs on \textit{log p} from logistic regression model of ``Bellwether'' shown in Fig~\ref{fig:FSS_compare}.
-Here Odds ratio shows one increment in in respective variable increase in the log-odds of being defective.}\label{tbl:coefs}
+\caption{Important features in the four   GENERAL\_level1 models found by this study. 
+Features are included here only if
+their $\beta$ coefficients  are   not   ``close'' to zero (where ``close'' means $-0.1 \le \beta \le 0.1$).}
+\label{tbl:coefs_4}
 \end{table}
-\fig{FSS_compare} shows what might be learned with and without
-the methods of this paper. Recall that the learners used in this research used feature selection and  logistic regression.
-\begin{itemize}
-\item  The gray bars in \fig{FSS_compare} show how often the features
-of Table~\ref{tbl:metric} were selected in the models learned from
-local data using {\em self}. 
-\item
-The red bars in \fig{FSS_compare} shows which features
-used in the local models that also appeared in the model learned from the bellwether. 
-  Note that only a very
-small subset of the features seen in the  {\em self} models
-were found useful in the bellwether model of Table~\ref{tbl:coefs}.
-\end{itemize}
-Just to say the obvious:
-when learning
-local models from very many projects, there is a wide range 
-of features used in the model.
-It is far easier to 
-definitively learn lessons from a much smaller range
-of features, such as those listed in Table~\ref{tbl:coefs}.
-Based on these results
-we can say that for predicting defects, in this sample of  features taken from 627 projects:
-In summary:
-
-\begin{RQ}
-{\respto{2-9} {\color{blue}In terms of defect prediction,
-issues of inter-class interface are paramount.
-Many other  issues are far less important such as file size, depth of inheritance tree, intra-method complexity, file size, revision history.}}
-\end{RQ}
+
+To make it easy to compare these locally and globally important features,  we color in \textcolor{red}{{\bf RED}}
+all the bars of \fig{FSS_level1} that come from features
+also found in  Table~\ref{tbl:coefs_4}. Note that only a small subset of the locally important
+features are actually globally important.
+
+Note also that, at first glance, there  seems to be some agreement on what is both locally and globally important.
+On the left-hand side of  \fig{FSS_level1}, we see that six of the top ten locally important features are colored red; i.e.
+they are also globally important.
+
+On the other hand, a more careful analysis shows things that it is not wise to simply assume that the most locally important features are usually important for most projects:
+\bi
+\item
+Consider the top four most common locally important features: NFix, NRev, CL, RCC. These features appear in  25\%, 25\%, 50\%, 25\% 
+(respectively) of the clusters shown in Table~\ref{tbl:coefs_4}. 
+\item
+Also, consider the height of the bars in \fig{FSS_level1}. Nearly all the locally important features are important in less than 25\% of projects.
+\ei
+That is,  it is a mistake to assume that something that is  important for a few local projects is globally useful to dozens to hundreds of projects. 
+That said, the good news from this analysis is that in terms of defect prediction,
+ (a)~hundreds of projects can be reasoned about using just four groups; (b)~within each group, there exist some general conclusions (see Table~\ref{tbl:coefs_4}).
 
@@
 (a) \textit{Evaluation Bias}: 
-In  {\bf  RQ3, RQ4} and {\bf RQ5} we have shown the performance of local model, hierarchical bellwether models, default bellwether model and compared them using statistical tests on their performance to make conclusion about presence of generality in SE datasets.
+In  {\bf  RQ3, RQ4} and, {\bf RQ5} we have shown the performance of local model, hierarchical bellwether models, default bellwether model and compared them using statistical tests on their performance to make conclusion about presence of generality in SE datasets.
 While those results are true, that conclusion is scoped by the evaluation metrics we used to write this paper.
-It is possible that, using other measurements, there may well be a difference in these different kinds of projects.
+It is possible that using other measurements, there may well be a difference in these different kinds of projects.
 This is a matter that needs to be explored in future research.
@@
 
-(c) \textit{External Validity}: For this study we have relied on data collected by Zhang et al.~\cite{zhang15} for their studies.
-The metrics collected for each project were done using an commercialized tool called ``Understand''.
-There is a possibility that calculation of metrics or labeling of defective vs non-defective using other tools or methods may result in different outcome.
+(c) \textit{External Validity}: For this study, we have relied on data collected by Zhang et al.~\cite{zhang15} for their studies.
+The metrics collected for each project were done using a commercialized tool called ``Understand''.
+There is a possibility that calculation of metrics or labeling of defective vs non-defective using other tools or methods may result in different outcomes.
 That said, the ``Understand'' is a commercialized tool which has detailed documentation about the metrics calculations and Zhang et al.
-has shared their scripts and process to convert the metrics to usable format and has described the approach to label defects.
+has shared their scripts and process to convert the metrics to a usable format and has described the approach to label defects.
 
@@
 That said, this sample is very large so we have some confidence that this sample represents an interesting range of projects.
-As evidence of that, we note that our sampling bias is less pronounced than other ``Bellwether'' studies since we explored.
 
@@
 in this analysis.
-Using GENERAL, we have shown that issues
-of class interface design were the most critical
-issue within a sample of 628 projects.
 
@@
 
-\section{Acknowledgements}
+\section{Acknowledgments}
 \label{sec:ack}
@@
 \bibliography{main} 
-\newpage
-\begin{minipage}{\linewidth}
+%  \newpage
+
+\begin{minipage}{.9\linewidth}
 \begin{IEEEbiography}[{\includegraphics[width=1in,clip,keepaspectratio]{figs/suvodeep.JPG}}]{Suvodeep Majumder}
